### 2022-04-08 code/analysis.Rmd
Add meta-analysis script

---
title: "A meta-analysis of mental rotation ability in the first years of life"
author: "Alexander Enge, Shreya Kapoor, Anne-Sophie Kieslinger & Michael A. Skeide"
date: "`r paste('Commit', substr(git2r::commits()[[1]]$sha, 1, 7))`"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r, setup, include=FALSE}
# Load packages
library(here)
library(ggridges)
library(tidyverse)
library(magrittr)
library(metafor)

# Global chunk options
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, get_data}
# Directory paths
data_dir <- here("data")

# Download literature search spreadsheet from Google Drive
excel_url <- "https://docs.google.com/spreadsheets/d/1xnC0NlQYTXavXaeqQidhi7UKb1pCGAl9Ry3h3Uz3mi0"
excel_file <- here(data_dir, "literature_search.xlsx")
# googledrive::drive_auth(use_oob = TRUE)
# googledrive::drive_download(excel_url, excel_file, overwrite = TRUE)

# Read sheets
screening <- readxl::read_excel(excel_file, sheet = "screening")
included <- readxl::read_excel(excel_file, sheet = "included", na = "NA")
```

# Results

Effect sizes of individual experiments:

```{r, compute_effects, echo=TRUE}
# Add columns to the table of included experiments
included %>%
  mutate(
    # Add difference between condition means
    mean_diff = case_when(
      !is.na(mean_diff) ~ mean_diff,
      TRUE ~ mean_novel - mean_familiar
    ),
    # Add d_z from paired t test of condition means (Rosenthal, 1991)
    d_z_t = t / sqrt(sample_size),
    # Add d_z from mean and standard deviation of the difference
    d_z_diff = mean_diff / sd_diff,
    # Add d_av from mean difference and standard devations (assumes r = 0)
    # (Cumming, 2012)
    sd_av = (sd_novel + sd_familiar) / 2,
    d_av = mean_diff / sd_av,
    # Add d from one-sample t test of novelty preference scores
    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,
    # Choose one type of outcome variable for each experiment
    yi = case_when(
      # 1. If d was reported directed
      !is.na(d) ~ d,
      # 2. If a paired sample t test was reported
      !is.na(d_z_t) ~ d_z_t,
      # 3. If the difference between means and its SD were reported
      !is.na(d_z_diff) ~ d_z_diff,
      # 4. If the individual condition means and their SDs were reported
      !is.na(d_av) ~ d_av,
      # 5. If a novelty preference score and its SD were reported
      !is.na(d_nov_pref) ~ d_nov_pref
    ),
    # Keep track which type of outcome measure was chosen for each article
    yi_type = case_when(
      !is.na(d) ~ "d",
      !is.na(d_z_t) ~ "d_z_t",
      !is.na(d_z_diff) ~ "d_z_diff",
      !is.na(d_av) ~ "d_av",
      !is.na(d_nov_pref) ~ "d_nov_pref",
      TRUE ~ "none"
    ) %>%
      factor(levels = c(
        "d", "d_z_t", "d_z_diff", "d_av", "d_nov_pref", "none"
      )),
    # Find studies with any value of d_z (from t test or mean / SD of the diff.)
    d_z = case_when(
      !is.na(d_z_t) ~ d_z_t,
      !is.na(d_z_diff) ~ d_z_diff
    ),
    # Compute SD of the difference based on d_z
    sd_z = mean_diff / d_z,
    # Compute correlation based on sd_z and condition SDs
    ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
  ) %>%
  # Exclude experiments with redundant samples, missing stats, or age > 2 years
  filter(!redundant & !is.na(yi) & age_mean < 730) -> dat

# Overview of the different effect sizes
dat %>%
  select(id, group, yi_type, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
  print(n = Inf)

# Correlations between dependent samples
summary(included$r)
```

Actual meta-analysis:

```{r, compute_meta, echo=TRUE}
# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni)))
  ) %>%
  select(id, group, ni, yi, sei) -> dat_r

# Create vector of experiment IDs for plotting
experiment_ids <- with(dat_r, paste(id, group, sep = ", "))

# Add sampling variance based standard error
escalc(vi = vi, sei = sei, ni = ni, data = dat_r)

# # Two-level model
# res <- rma(
#   yi = yi,
#   sei = sei,
#   data = dat_r,
#   slab = experiment_ids
# )
# print(res)
# forest(res)

# Three-level model
res_mv <- rma.mv(
  yi = yi,
  sei = sei,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

# # Saving the forest plot
# pdf("forest.pdf", width = 12, height = 12)
# forest(res_mv)
# dev.off()

# Profile likelihodd plots
profile(res_mv, sigma2 = 1)
profile(res_mv, sigma2 = 2)

# # Meta-regression with age
# res_age <- rma.mv(
#   yi, vi,
#   mods = ~age_mean, random = ~ group | id, data = dat, slab = slab
# )
# print(res_age)
# forest(res_age)

# # Meta-regression with gender
# res_gender <- rma.mv(
#   yi, vi,
#   mods = ~female_percent, random = ~ group | id, data = dat, slab = slab
# )
# print(res_gender)
# forest(res_gender)

# # Meta-regression with age, gender, and their interaction
# res_full <- rma.mv(
#   yi, vi,
#   mods = ~age_mean * female_percent, random = ~ group | id, data = dat, slab = slab
# )
# print(res_full)
# forest(res_full)
```

# Methods

## Information sources and search strategy

Article sources:

```{r}
table(screening$source)
```

## Selection process

### Interrater agreement

Percent agreement for binary decision (include/exclude):

```{r}
with(screening, mean(bin_1 == bin_2))
```

Cohen's kappa for binary decision (include/exclude):

```{r}
with(screening, psych::cohen.kappa(cbind(bin_1, bin_2)))
```

Correlation (phi) for binary decision (include/exclude):

```{r}
with(screening, cor.test(bin_1, bin_2))
```

Percent agreement for exclusion codes:

```{r}
with(screening, mean(code_1 == code_2))
```

Cohen's kappa for exclusion codes:

```{r}
with(screening, psych::cohen.kappa(cbind(code_1, code_2)))
```

### Final decisions

Exlucsion codes:

```{r}
cat("1 = not in english
2 = not a group study
3 = not infants
4 = not typically developing
5 = no mental rotation
6 = no within-group statistics
7 = include paper
8 = no access or insufficient statistics")
table(screening$code_final)
```

### Included experiments

Total number of articles (according to `screening` table):

```{r}
sum(screening$code_final == 7)
```

Total number of articles (according to `included` table):

```{r}
length(unique(included$id))
```

Total number of experiments:

```{r}
nrow(included)
```

Number of non-redundant experiments:

```{r}
nrow(filter(included, !redundant))
```

Number of experiments per type of effect size:

```{r}
table(included$yi_type)
```

Total number of infants across experiments:

```{r}
sum(included$sample_size)
```

Descriptive information about the infant samples:

```{r}
included %>%
  select(sample_size, age_mean, age_sd, age_min, age_max, female_percent) %>%
  summary()
```

Age and gender distributions of all experiments:

```{r}
included %>%
  uncount(1e4) %>%
  mutate(
    group_text = if_else(is.na(group), "NA", group),
    id_group = str_c(id, ", ", group_text),
    id_group_ordered = fct_reorder(id_group, age_mean, .desc = TRUE),
    age_sd = if_else(!is.na(age_sd), age_sd, 10.),
    days = rnorm(n(), age_mean, age_sd),
    months = days / 30.417,
  ) %>%
  ggplot(aes(x = months, y = id_group_ordered, fill = female_percent)) +
  geom_density_ridges() +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = c(1, 20), expand = FALSE) +
  labs(x = "Age (m)", fill = "Percent\nfemale") +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica", size = 10)
  )
```

Sample sizes and ages of all experiments:

```{r}
included %>%
  mutate(months = age_mean / 30.417) %>%
  ggplot(aes(
    x = months,
    y = sample_size,
    size = sample_size,
    color = female_percent
  )) +
  geom_point() +
  scale_color_viridis_c() +
  scale_size(guide = "none") +
  coord_cartesian(xlim = c(0, 16)) +
  labs(x = "Age (m)", y = "Sample size", color = "Percent\nfemale") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica", size = 10)
  )
```

### 2022-04-08 code/analysis.Rmd
Fix meta-analytic models

@@
 dat %>%
-  select(id, group, yi_type, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
+  select(id, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
   print(n = Inf)
@@
 # Correlations between dependent samples
-summary(included$r)
+summary(dat$ri)
 ```
@@
     ni = sample_size,
-    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni)))
+    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni))),
+    age_months = age_mean / 30.417
   ) %>%
-  select(id, group, ni, yi, sei) -> dat_r
+  select(id, group, age_months, female_percent, ni, yi, sei) %>%
+  # Compute sampling variance from standard errors
+  escalc(yi = yi, sei = sei, ni = ni, data = .) %>%
+  tibble() -> dat_r
 
@@
 
-# Add sampling variance based standard error
-escalc(vi = vi, sei = sei, ni = ni, data = dat_r)
-
 # # Two-level model
 # res <- rma(
-#   yi = yi,
-#   sei = sei,
+#   yi, vi,
 #   data = dat_r,
@@
 res_mv <- rma.mv(
-  yi = yi,
-  sei = sei,
+  yi, vi,
   random = ~ group | id,
@@
 
-# Profile likelihodd plots
-profile(res_mv, sigma2 = 1)
-profile(res_mv, sigma2 = 2)
+# # Profile likelihodd plots
+# profile(res_mv, sigma2 = 1)
+# profile(res_mv, sigma2 = 2)
 
-# # Meta-regression with age
-# res_age <- rma.mv(
-#   yi, vi,
-#   mods = ~age_mean, random = ~ group | id, data = dat, slab = slab
-# )
-# print(res_age)
-# forest(res_age)
+# Meta-regression with age
+res_age <- rma.mv(
+  yi, vi,
+  mods = ~age_months,
+  random = ~ group | id,
+  data = dat_r,
+  slab = experiment_ids
+)
+print(res_age)
+forest(res_age)
 
-# # Meta-regression with gender
-# res_gender <- rma.mv(
-#   yi, vi,
-#   mods = ~female_percent, random = ~ group | id, data = dat, slab = slab
-# )
-# print(res_gender)
-# forest(res_gender)
+# Meta-regression with gender
+res_gender <- rma.mv(
+  yi, vi,
+  mods = ~female_percent,
+  random = ~ group | id,
+  data = dat_r,
+  slab = experiment_ids
+)
+print(res_gender)
+forest(res_gender)
 
-# # Meta-regression with age, gender, and their interaction
-# res_full <- rma.mv(
-#   yi, vi,
-#   mods = ~age_mean * female_percent, random = ~ group | id, data = dat, slab = slab
-# )
-# print(res_full)
-# forest(res_full)
+# Meta-regression with age, gender, and their interaction
+res_full <- rma.mv(
+  yi, vi,
+  mods = ~ age_months * female_percent,
+  random = ~ group | id,
+  data = dat_r,
+  slab = experiment_ids
+)
+print(res_full)
+forest(res_full)
 ```

### 2022-04-08 code/analysis.Rmd
Update figure size
Funnel plots

@@
 # Global chunk options
-knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+knitr::opts_chunk$set(
+  echo = FALSE,
+  message = FALSE,
+  fig.height = 10,
+  fig.width = 7.5,
+  out.width = "100%"
+)
 ```
@@
 forest(res_mv)
+funnel(res_mv, main = "Standard Error")
 
@@
 forest(res_gender)
+funnel(res_age, main = "Standard Error")
 
@@
 forest(res_full)
+funnel(res_full, main = "Standard Error")
 ```

### 2022-04-08 code/analysis.Rmd
Include Egger test and correct funnel inputs

@@
 funnel(res_mv, main = "Standard Error")
+egger=regtest(x=res_mv$yi, vi=res_mv$vi, sei=res_mv$sei,model='lm',predictor='sei')
+print(egger)
 
@@
 forest(res_age)
+funnel(res_age, main = "Standard Error")
 
@@
 forest(res_gender)
-funnel(res_age, main = "Standard Error")
+funnel(res_gender, main = "Standard Error")
 

### 2022-04-11 code/analysis.Rmd
Add Bayesian multilevel model

--- 2022-04-08 code/analysis.Rmd
@@
 library(metafor)
+library(brms)
 
 # Global chunk options
-knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+knitr::opts_chunk$set(
+  echo = FALSE,
+  message = FALSE,
+  fig.height = 10,
+  fig.width = 7.5,
+  out.width = "100%"
+)
 ```
@@
 
+```{r, brms, echo=TRUE}
+# Specify priors
+priors <- c(
+  prior(normal(0, 1), class = "Intercept"),
+  prior(exponential(1), class = "sd")
+)
+
+# Run Bayesian multilevel model
+res_brm <- brm(
+  yi | se(sei) ~ 1 + (1 | group / id),
+  data = dat_r,
+  prior = priors,
+  cores = 4,
+  chains = 4,
+  iter = 2000,
+  sample_prior = TRUE,
+  save_pars = save_pars(all = TRUE)
+)
+summary(res_brm)
+
+# Sensitivity analysis
+list(
+  "ic_uninformative" = c(
+    prior(uniform(-3, 3), class = "Intercept"),
+    prior(exponential(1), class = "sd")
+  ),
+  "ic_informative" = c(
+    prior(normal(0, 0.2), class = "Intercept"),
+    prior(exponential(1), class = "sd")
+  ),
+  "sigma_uninformative" = c(
+    prior(normal(0, 1), class = "Intercept"),
+    prior(uniform(0, 5), class = "sd")
+  ),
+  "sigma_informative" = c(
+    prior(normal(0, 1), class = "Intercept"),
+    prior(exponential(0.1), class = "sd")
+  )
+) %>%
+  map(function(priors) update(res_brm, prior = priors)) -> res_sens
+```
+
 # Methods

### 2022-04-12 code/analysis.Rmd
Add simulation for checking the MLM model

@@
 ```
+
+```{r, simulation}
+generate_exp <- function(id,
+                         n_boys = 1e3,
+                         n_girls = 1e3,
+                         mean_diff_boys = 0,
+                         mean_diff_girls = 2,
+                         sd_diff_boys = 4,
+                         sd_diff_girls = 4) {
+
+  # Create randomly sampled data for boys and girls
+  # Each element is the mean looking time difference for one infant
+  boys <- rnorm(n_boys, mean_diff_boys, sd_diff_boys)
+  girls <- rnorm(n_girls, mean_diff_girls, sd_diff_girls)
+
+  # Compute separate effect sizes for the two split gender groups
+  d_boys <- mean(boys) / sd(boys)
+  d_girls <- mean(girls) / sd(girls)
+
+  # Compute common effect size for the mixed gender group
+  infants <- c(boys, girls)
+  n_infants <- length(infants)
+  d_infants <- mean(infants) / sd(infants)
+
+  # Return all results for this experiment as a list
+  return(list(
+    id = id,
+    n_boys = n_boys,
+    n_girls = n_girls,
+    n_infants = n_infants,
+    d_boys = d_boys,
+    d_girls = d_girls,
+    d_infants = d_infants
+  ))
+}
+
+# Generate random experiments
+n_boys <- 1e3
+n_girls <- 1e3
+n_exps <- 100
+ids <- paste0("exp_", 1:n_exps)
+dat <- lapply(ids, generate_exp, n_boys, n_girls)
+dat <- do.call(rbind.data.frame, dat)
+
+### MIXED EXPERIMENTS ONLY ###
+
+# Compute sampling variance of the effect size for each study; see
+# https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#w-group-smd
+r_assumed <- .5
+dat$v_d_infants <- with( # Sampling variances of the effect sizes
+  dat, ((2 * (1 - r_assumed)) / n_infants) + (d_infants^2 / (2 * n_infants))
+)
+
+# Fit 3 level meta-analysis
+res_full <- metafor::rma.mv(
+  d_infants, v_d_infants,
+  random = ~ id | id,
+  data = dat,
+  slab = id
+)
+
+# Check results
+summary(res_full)
+```

### 2022-04-13 code/analysis.Rmd
Add notes for performing split/mixed analyses

@@
 ```{r, simulation}
-generate_exp <- function(id,
-                         n_boys = 1e3,
+generate_exp <- function(n_boys = 1e3,
                          n_girls = 1e3,
@@
   return(list(
-    id = id,
     n_boys = n_boys,
@@
 n_exps <- 100
-ids <- paste0("exp_", 1:n_exps)
-dat <- lapply(ids, generate_exp, n_boys, n_girls)
+dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
 dat <- do.call(rbind.data.frame, dat)
+dat$id <- paste0("exp_", 1:n_exps)
 
@@
   d_infants, v_d_infants,
-  random = ~ id | id,
+  # random = ~ id | id,
   data = dat,
@@
 summary(res_full)
+
+### SPLIT EXPERIMENTS ONLY ###
+
+# Put effect sizes for boys and girls into separate rows
+dat_split <- tidyr::pivot_longer(
+  dat,
+  cols = c(d_boys, d_girls),
+  names_to = "gender",
+  values_to = "d_gender"
+)
+
+# Compute sampling variance of the gender-specific effect size
+dat_split$v_d_gender <- with(
+  dat_split, ((2 * (1 - r_assumed)) / n_girls) + (d_gender^2 / (2 * n_girls))
+)
+
+# Use rma.mv to compute MA on d_gender and v_d_gender values
+
+# Repeat 100 times with generate_meta
+
+# Compare mixed gender and split gender MAs
+# Same distribution of meta-analytic effect size?
+# Same variance / standard error?
+# Is the difference significant?
+
+### MIXED/SPLIT GENDER ANALYSIS ###
+
+# Make a percentage of study use mixed vs. split and choose randomly
+# Use different percentages
+# Make split vs. mixed dependent on the observed gender difference
+# Note for this we need to draw study specific effect sizes from a distribution
+
+### MAKE IT MORE REALISTIC ###
+
+# Make sample sizes per study different
+
+# Automate
+generate_meta <- function(n_exps, n_boys, n_girls) {
+
+  # Generate random experiments
+  dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
+  dat <- do.call(rbind.data.frame, dat)
+  dat$id <- paste0("exp_", 1:n_exps)
+
+  # Compute sampling variance of the effect size for each study; see
+  # https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#w-group-smd
+  r_assumed <- .5
+  dat$v_d_infants <- with( # Sampling variances of the effect sizes
+    dat, ((2 * (1 - r_assumed)) / n_infants) + (d_infants^2 / (2 * n_infants))
+  )
+
+  # Fit meta-analysis
+  res_full <- metafor::rma.mv(
+    d_infants, v_d_infants,
+    # random = ~ id | id,
+    data = dat,
+    slab = id
+  )
+
+  # Return coefficients table
+  summ <- summary(res_full)
+  return(coef(summ))
+}
+
+n_metas <- 100
+metas <- replicate(n_metas, generate_meta(100, 100, 100), simplify = FALSE)
+metas <- do.call(rbind.data.frame, metas)
+metas$id <- paste0("meta_", 1:n_metas)
+
+mean(metas$estimate)
 ```

### 2022-04-14 code/analysis.Rmd
Fix profile plots
Rename `id` to `article`

@@
 dat %>%
-  select(id, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
+  select(
+    article, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri
+  ) %>%
   print(n = Inf)
@@
   ) %>%
-  select(id, group, age_months, female_percent, ni, yi, sei) %>%
+  select(article, group, age_months, female_percent, ni, yi, sei) %>%
   # Compute sampling variance from standard errors
@@
 # Create vector of experiment IDs for plotting
-experiment_ids <- with(dat_r, paste(id, group, sep = ", "))
+experiment_ids <- with(dat_r, paste(article, group, sep = ", "))
 
@@
   yi, vi,
-  random = ~ group | id,
+  random = ~ group | article,
   data = dat_r,
@@
 # # Profile likelihodd plots
-# profile(res_mv, sigma2 = 1)
-# profile(res_mv, sigma2 = 2)
+# profile(res_mv, tau2 = 1)
+# profile(res_mv, rho = 1)
 
@@
   mods = ~age_months,
-  random = ~ group | id,
+  random = ~ group | article,
   data = dat_r,
@@
   mods = ~female_percent,
-  random = ~ group | id,
+  random = ~ group | article,
   data = dat_r,
@@
   mods = ~ age_months * female_percent,
-  random = ~ group | id,
+  random = ~ group | article,
   data = dat_r,
@@
 res_brm <- brm(
-  yi | se(sei) ~ 1 + (1 | group / id),
+  yi | se(sei) ~ 1 + (1 | group / article),
   data = dat_r,
@@
 ```{r}
-length(unique(included$id))
+length(unique(included$article))
 ```
@@
     group_text = if_else(is.na(group), "NA", group),
-    id_group = str_c(id, ", ", group_text),
+    id_group = str_c(article, ", ", group_text),
     id_group_ordered = fct_reorder(id_group, age_mean, .desc = TRUE),
@@
 dat <- do.call(rbind.data.frame, dat)
-dat$id <- paste0("exp_", 1:n_exps)
+dat$article <- paste0("exp_", 1:n_exps)
 
@@
   d_infants, v_d_infants,
-  # random = ~ id | id,
+  # random = ~ article | article,
   data = dat,
-  slab = id
+  slab = article
 )
@@
   dat <- do.call(rbind.data.frame, dat)
-  dat$id <- paste0("exp_", 1:n_exps)
+  dat$article <- paste0("exp_", 1:n_exps)
 
@@
     d_infants, v_d_infants,
-    # random = ~ id | id,
+    # random = ~ article | article,
     data = dat,
-    slab = id
+    slab = article
   )
@@
 metas <- do.call(rbind.data.frame, metas)
-metas$id <- paste0("meta_", 1:n_metas)
+metas$article <- paste0("meta_", 1:n_metas)
 

### 2022-04-18 code/analysis.Rmd
Update multilevel model formulas

@@
   yi, vi,
-  random = ~ group | article,
+  random = ~ 1 | article / group,
   data = dat_r,
@@
 # Specify priors
-priors <- c(
-  prior(normal(0, 1), class = "Intercept"),
-  prior(exponential(1), class = "sd")
+prior_c <- c(
+  set_prior("normal(0, 1)", class = "Intercept"),
+  set_prior("cauchy(0, 0.3)", class = "sd")
 )
@@
 res_brm <- brm(
-  yi | se(sei) ~ 1 + (1 | group / article),
+  yi | se(sei) ~ 1 + (1 | article / group),
   data = dat_r,
-  prior = priors,
+  prior = prior_c,
   cores = 4,

### 2022-04-18 code/analysis.Rmd
Reflect coding of gender mixed vs. split groups

@@
     ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
-  ) %>%
-  # Exclude experiments with redundant samples, missing stats, or age > 2 years
-  filter(!redundant & !is.na(yi) & age_mean < 730) -> dat
+  ) -> dat
 
@@
   select(
-    article, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri
+    article,
+    group,
+    gender_split,
+    yi_type,
+    yi,
+    d,
+    d_z_t,
+    d_z_diff,
+    d_av,
+    d_nov_pref,
+    ri
   ) %>%
   print(n = Inf)
+
+# Show number of experiments per gender grouping strategy
+table(dat$gender_split)
+
+# Extract mixed/split experiments only
+dat_mixed <- filter(dat, gender_split %in% c("mixed", "mixed_only"))
+dat_split <- filter(dat, gender_split %in% c("split", "split_only"))
+
+# Extract both strategies combined (but excluding any redundant experiments)
+dat_both <- filter(
+  dat, gender_split %in% c("mixed", "mixed_only", "split_only")
+)
 
@@
 r_assumed <- 0.5
-dat %>%
+dat_both %>%
   mutate(

### 2022-04-19 code/analysis.Rmd
Add conversion from F value to d

@@
     d_z_t = t / sqrt(sample_size),
+    # Add d_z from ANOVA F value via conversion to a t value
+    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
     # Add d_z from mean and standard deviation of the difference
@@
       !is.na(d_z_t) ~ d_z_t,
-      # 3. If the difference between means and its SD were reported
+      # 3. If ANOVA was reported
+      !is.na(d_z_f) ~ d_z_f,
+      # 4. If the difference between means and its SD were reported
       !is.na(d_z_diff) ~ d_z_diff,
-      # 4. If the individual condition means and their SDs were reported
+      # 5. If the individual condition means and their SDs were reported
       !is.na(d_av) ~ d_av,
-      # 5. If a novelty preference score and its SD were reported
+      # 6. If a novelty preference score and its SD were reported
       !is.na(d_nov_pref) ~ d_nov_pref
@@
       !is.na(d_z_t) ~ "d_z_t",
+      !is.na(d_z_f) ~ "d_z_f",
       !is.na(d_z_diff) ~ "d_z_diff",
@@
       factor(levels = c(
-        "d", "d_z_t", "d_z_diff", "d_av", "d_nov_pref", "none"
+        "d", "d_z_t", "d_z_f", "d_z_diff", "d_av", "d_nov_pref", "none"
       )),
-    # Find studies with any value of d_z (from t test or mean / SD of the diff.)
+    # Find studies with any value of d_z (from t test, ANOVA, or mean_diff)
     d_z = case_when(
       !is.na(d_z_t) ~ d_z_t,
+      !is.na(d_z_f) ~ d_z_f,
       !is.na(d_z_diff) ~ d_z_diff
@@
     d_nov_pref,
+    d_z_f,
     ri

### 2022-04-19 code/analysis.Rmd
Prepare comparison of gender grouping strategies

@@
 
+# Get empirical estimate of the correlation between dependent samples
+summary(dat$ri)
+
+# Compute standard error of Cohen's d based on assumed correlation
+# This will need a sensitivity analysis
+r_assumed <- 0.5
+dat %>%
+  mutate(
+    ni = sample_size,
+    vi = ((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni)),
+    sei = sqrt(vi),
+    age_months = age_mean / 30.417,
+    age_months_c = age_months - mean(age_months, na.rm = TRUE)
+  ) %>%
+  filter(!is.na(yi)) %>%
+  select(
+    article, group, gender_split, age_months_c, female_percent, yi, ri, vi, sei
+  ) -> dat_r
+
 # Show number of experiments per gender grouping strategy
-table(dat$gender_split)
+table(dat_r$gender_split)
 
 # Extract mixed/split experiments only
-dat_mixed <- filter(dat, gender_split %in% c("mixed", "mixed_only"))
-dat_split <- filter(dat, gender_split %in% c("split", "split_only"))
+dat_mixed <- filter(dat_r, gender_split %in% c("mixed", "mixed_only"))
+dat_split <- filter(dat_r, gender_split %in% c("split", "split_only"))
 
-# Extract both strategies combined (but excluding any redundant experiments)
-dat_both <- filter(
-  dat, gender_split %in% c("mixed", "mixed_only", "split_only")
+# Combine both strategies, preferring mixed experiments
+dat_both_mixed <- filter(
+  dat_r, gender_split %in% c("mixed", "mixed_only", "split_only")
 )
 
-# Correlations between dependent samples
-summary(dat$ri)
+# Combine both strategies, preferring mixed experiments
+dat_both_split <- filter(
+  dat_r, gender_split %in% c("split", "mixed_only", "split_only")
+)
 ```
@@
 ```{r, compute_meta, echo=TRUE}
-# Compute standard error of Cohen's d based on assumed correlation
-# This will need a sensitivity analysis
-r_assumed <- 0.5
-dat_both %>%
-  mutate(
-    ni = sample_size,
-    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni))),
-    age_months = age_mean / 30.417
-  ) %>%
-  select(article, group, age_months, female_percent, ni, yi, sei) %>%
-  # Compute sampling variance from standard errors
-  escalc(yi = yi, sei = sei, ni = ni, data = .) %>%
-  tibble() -> dat_r
-
-# Create vector of experiment IDs for plotting
-experiment_ids <- with(dat_r, paste(article, group, sep = ", "))
-
 # # Two-level model
@@
   random = ~ 1 | article / group,
-  data = dat_r,
-  slab = experiment_ids
+  data = dat_both_mixed,
+  slab = paste(article, group, sep = ", ")
 )
 print(res_mv)
-forest(res_mv)
+# forest(res_mv)
 
@@
 
-# # Profile likelihodd plots
-# profile(res_mv, tau2 = 1)
-# profile(res_mv, rho = 1)
+# # Profile likelihodd plots for checking that REML has converged
+# profile(res_mv)
 
@@
   yi, vi,
-  mods = ~age_months,
-  random = ~ group | article,
-  data = dat_r,
-  slab = experiment_ids
+  mods = ~age_months_c,
+  random = ~ 1 | article / group,
+  data = dat_both_mixed,
+  slab = paste(article, group, sep = ", ")
 )
 print(res_age)
-forest(res_age)
+# forest(res_age)
 
@@
   mods = ~female_percent,
-  random = ~ group | article,
-  data = dat_r,
-  slab = experiment_ids
+  random = ~ 1 | article / group,
+  data = dat_both_mixed,
+  slab = paste(article, group, sep = ", ")
 )
 print(res_gender)
-forest(res_gender)
+# forest(res_gender)
 
@@
   yi, vi,
-  mods = ~ age_months * female_percent,
-  random = ~ group | article,
-  data = dat_r,
-  slab = experiment_ids
+  mods = ~ age_months_c * female_percent,
+  random = ~ 1 | article / group,
+  data = dat_both_mixed,
+  slab = paste(article, group, sep = ", ")
 )
 print(res_full)
-forest(res_full)
+# forest(res_full)
 ```
@@
 
-# Run Bayesian multilevel model
-res_brm <- brm(
+# Run prior predictive simulation
+res_prior <- brm(
   yi | se(sei) ~ 1 + (1 | article / group),
-  data = dat_r,
+  data = dat_both_mixed,
   prior = prior_c,

### 2022-04-19 code/analysis.Rmd
Improve Bayesian model
- Add explicit prior predivtie checks
- Align sensitivity analysis with Williams et al. (2018)

@@
   prior = prior_c,
-  cores = 4,
+  sample_prior = "only",
+  save_pars = save_pars(all = TRUE),
   chains = 4,
   iter = 2000,
-  sample_prior = TRUE,
-  save_pars = save_pars(all = TRUE)
+  cores = 4,
+  control = list(adapt_delta = 0.99)
 )
+summary(res_prior)
+# plot(res_prior)
+
+# Run Bayesian multilevel model
+res_brm <- update(res_prior, sample_prior = FALSE)
 summary(res_brm)
+# plot(res_brm)
 
@@
 list(
-  "ic_uninformative" = c(
-    prior(uniform(-3, 3), class = "Intercept"),
-    prior(exponential(1), class = "sd")
+  "interept_uninformative" = c(
+    set_prior("uniform(-3, 3)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
   ),
-  "ic_informative" = c(
-    prior(normal(0, 0.2), class = "Intercept"),
-    prior(exponential(1), class = "sd")
+  "interept_informative" = c(
+    set_prior("normal(0, 0.2)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
   ),
-  "sigma_uninformative" = c(
-    prior(normal(0, 1), class = "Intercept"),
-    prior(uniform(0, 5), class = "sd")
+  "sd_uninformative" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("uniform(0, 10)", class = "sd", ub = 10)
   ),
-  "sigma_informative" = c(
-    prior(normal(0, 1), class = "Intercept"),
-    prior(exponential(0.1), class = "sd")
+  "sd_informative" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("student_t(10, 0, 0.2)", class = "sd")
   )
 ) %>%
-  map(function(priors) update(res_brm, prior = priors)) -> res_sens
+  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
+map(res_sens, summary)
 ```

### 2022-04-19 code/analysis.Rmd
Apply Hedges' small sample correction

@@
   mutate(
+    # Convert mean sample age from days to months and center
+    age_months = age_mean / 30.417,
+    age_months_c = age_months - mean(age_months, na.rm = TRUE),
     # Add difference between condition means
@@
     d_z_diff = mean_diff / sd_diff,
-    # Add d_av from mean difference and standard devations (assumes r = 0)
+    # Add d_av from mean difference and standard devations (assumes r = 0.5)
     # (Cumming, 2012)
@@
     # Choose one type of outcome variable for each experiment
-    yi = case_when(
+    di = case_when(
       # 1. If d was reported directed
@@
     # Keep track which type of outcome measure was chosen for each article
-    yi_type = case_when(
+    di_type = case_when(
       !is.na(d) ~ "d",
@@
     ),
-    # Compute SD of the difference based on d_z
+    # Apply small sample correction using Hedges' exact method
+    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
+    df = 2 * (sample_size - 1),
+    j = exp(lgamma(df / 2) - log(sqrt(df / 2)) - lgamma((df - 1) / 2)),
+    gi = di * j,
+    # Compute empirical correlation based on sd_z and condition SDs
     sd_z = mean_diff / d_z,
-    # Compute correlation based on sd_z and condition SDs
     ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
@@
     gender_split,
-    yi_type,
-    yi,
+    gi,
+    di,
+    di_type,
     d,
     d_z_t,
+    d_z_f,
     d_z_diff,
@@
     d_nov_pref,
-    d_z_f,
     ri
@@
     ni = sample_size,
-    vi = ((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni)),
-    sei = sqrt(vi),
-    age_months = age_mean / 30.417,
-    age_months_c = age_months - mean(age_months, na.rm = TRUE)
+    vi = ((2 * (1 - r_assumed)) / ni) + (gi^2 / (2 * ni)),
+    sei = sqrt(vi)
   ) %>%
-  filter(!is.na(yi)) %>%
+  filter(!is.na(gi)) %>%
   select(
-    article, group, gender_split, age_months_c, female_percent, yi, ri, vi, sei
+    article, group, gender_split, gi, ni, vi, sei, age_months_c, female_percent
   ) -> dat_r
@@
 # # Two-level model
-# res <- rma(
-#   yi, vi,
+# res_rma <- rma(
+#   gi, vi,
 #   data = dat_r,
@@
 # )
-# print(res)
-# forest(res)
+# print(res_rma)
+# forest(res_rma)
 
 # Three-level model
-res_mv <- rma.mv(
-  yi, vi,
+res_ml <- rma.mv(
+  gi, vi,
   random = ~ 1 | article / group,
@@
 )
-print(res_mv)
-# forest(res_mv)
+print(res_ml)
+# forest(res_ml)
 
@@
 # pdf("forest.pdf", width = 12, height = 12)
-# forest(res_mv)
+# forest(res_ml)
 # dev.off()
@@
 # # Profile likelihodd plots for checking that REML has converged
-# profile(res_mv)
+# profile(res_ml)
 
@@
 res_age <- rma.mv(
-  yi, vi,
+  gi, vi,
   mods = ~age_months_c,
@@
 res_gender <- rma.mv(
-  yi, vi,
+  gi, vi,
   mods = ~female_percent,
@@
 res_full <- rma.mv(
-  yi, vi,
+  gi, vi,
   mods = ~ age_months_c * female_percent,
@@
 res_prior <- brm(
-  yi | se(sei) ~ 1 + (1 | article / group),
+  gi | se(sei) ~ 1 + (1 | article / group),
   data = dat_both_mixed,
@@
 ```{r}
-table(included$yi_type)
+table(included$di_type)
 ```

### 2022-04-19 code/analysis.Rmd
Tweak readability

@@
 )
-```
 
-```{r, get_data}
 # Directory paths
@@
   mutate(
+
     # Convert mean sample age from days to months and center
@@
     age_months_c = age_months - mean(age_months, na.rm = TRUE),
+
     # Add difference between condition means
@@
     d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,
+
     # Choose one type of outcome variable for each experiment
@@
       )),
-    # Find studies with any value of d_z (from t test, ANOVA, or mean_diff)
-    d_z = case_when(
-      !is.na(d_z_t) ~ d_z_t,
-      !is.na(d_z_f) ~ d_z_f,
-      !is.na(d_z_diff) ~ d_z_diff
-    ),
+
     # Apply small sample correction using Hedges' exact method
@@
     # Compute empirical correlation based on sd_z and condition SDs
+    d_z = case_when(
+      !is.na(d_z_t) ~ d_z_t,
+      !is.na(d_z_f) ~ d_z_f,
+      !is.na(d_z_diff) ~ d_z_diff
+    ),
     sd_z = mean_diff / d_z,

### 2022-04-21 code/analysis.Rmd
Update main, gender, and interaction models
- Making `gender` a categorical variable
- Contrast coding for gender
- Use `experiment` as a unique group-article identifier

@@
 
+    # Add unique experiment identifier
+    experiment = str_c(article, group, seq = ", "),
+
+    # Convert gender to a categorical variable
+    gender = case_when(
+      female_percent == 1.0 ~ "female",
+      female_percent == 0.0 ~ "male",
+      !is.na(female_percent) ~ "mixed"
+    ) %>% factor(levels = c("mixed", "female", "male")),
+
     # Convert mean sample age from days to months and center
     age_months = age_mean / 30.417,
-    age_months_c = age_months - mean(age_months, na.rm = TRUE),
+    age = age_months - mean(age_months, na.rm = TRUE),
 
@@
   select(
-    article, group, gender_split, gi, ni, vi, sei, age_months_c, female_percent
+    article,
+    group,
+    experiment,
+    gender_split,
+    gi,
+    ni,
+    vi,
+    sei,
+    gender,
+    age
   ) -> dat_r
@@
 ```{r, compute_meta, echo=TRUE}
-# # Two-level model
-# res_rma <- rma(
-#   gi, vi,
-#   data = dat_r,
-#   slab = experiment_ids
-# )
-# print(res_rma)
-# forest(res_rma)
-
 # Three-level model
@@
   gi, vi,
-  random = ~ 1 | article / group,
+  random = ~ 1 | article / experiment,
   data = dat_both_mixed,
-  slab = paste(article, group, sep = ", ")
+  slab = experiment
 )
@@
 
-# # Saving the forest plot
-# pdf("forest.pdf", width = 12, height = 12)
-# forest(res_ml)
-# dev.off()
-
 # # Profile likelihodd plots for checking that REML has converged
 # profile(res_ml)
+
+# Apply sliding difference contrast coding for the gender categories
+# This means that the Intercept will be the grand mean (i.e., the average across
+# studies) whereas the betas will test female vs. mixed and male vs. female
+(contrasts(dat_both_mixed$gender) <- MASS::contr.sdif(3))
+
+# Meta-regression with gender
+res_gender <- rma.mv(
+  gi, vi,
+  mods = ~ gender - 1,
+  random = ~ 1 | article / experiment,
+  data = dat_both_mixed,
+  slab = experiment
+)
+print(res_gender)
+# forest(res_gender)
+
+# Pairwise comparison between the gender groups
+anova(res_gender, X = rbind(c(-1, 1, 0), c(-1, 0, 1), c(0, -1, 1)))
 
@@
   gi, vi,
-  mods = ~age_months_c,
-  random = ~ 1 | article / group,
+  mods = ~age,
+  random = ~ 1 | article / experiment,
   data = dat_both_mixed,
-  slab = paste(article, group, sep = ", ")
+  slab = experiment
 )
@@
 
-# Meta-regression with gender
-res_gender <- rma.mv(
-  gi, vi,
-  mods = ~female_percent,
-  random = ~ 1 | article / group,
-  data = dat_both_mixed,
-  slab = paste(article, group, sep = ", ")
-)
-print(res_gender)
-# forest(res_gender)
-
-# Meta-regression with age, gender, and their interaction
+# Meta-regression with gender, age, and their interaction
 res_full <- rma.mv(
   gi, vi,
-  mods = ~ age_months_c * female_percent,
-  random = ~ 1 | article / group,
+  mods = ~ gender * age,
+  random = ~ 1 | article / experiment,
   data = dat_both_mixed,
-  slab = paste(article, group, sep = ", ")
+  slab = experiment
 )
@@
 res_prior <- brm(
-  gi | se(sei) ~ 1 + (1 | article / group),
+  gi | se(sei) ~ 1 + (1 | article / experiment),
   data = dat_both_mixed,
@@
 # plot(res_brm)
+```
 
-# Sensitivity analysis
+```{r, prior_sens, eval=FALSE}
+# Prior sensitivity analysis
 list(

### 2022-04-21 code/analysis.Rmd
Add forest plot

@@
 library(brms)
+library(tidybayes)
 
@@
 data_dir <- here("data")
+figures_dir <- here("results/figures")
 
@@
 # plot(res_brm)
+```
+
+```{r, fig2}
+# Forest plot inputs
+level <- 0.05
+ndraws <- 1000
+dat_plot <- dat_both_mixed
+res_plot <- res_ml
+res_plot_brm <- res_brm
+
+# Helper function for printing confidence intervals
+print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
+print_ci <- function(est, lb, ub) {
+  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
+}
+
+# Get draws from the Bayesian posterior distribution
+draws <- epred_draws(res_brm, dat_plot, ndraws = ndraws)
+meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = ndraws) %>%
+  mutate(article = "Three-level model", experiment = "zzz") # For the last line
+
+# Create forest plot
+dat_plot %>%
+  # Compute frequentist confidence intervals
+  mutate(
+    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
+    fontface = "plain" # For study labels and confidence interval
+  ) %>%
+  # Add meta-analytic effect size + CI
+  bind_rows(list(
+    article = "Three-level model",
+    group = "",
+    experiment = "zzz", # Just so it's displayed as the last line
+    gi = res_plot$b,
+    ci_lb = res_plot$ci.lb,
+    ci_ub = res_plot$ci.ub,
+    fontface = "bold"
+  )) %>%
+  # Format effect size + CI for printing them on the plot
+  mutate(ci_print = print_ci(gi, ci_lb, ci_ub)) %>%
+  # Reverse order of experiments so they are plotted alphabetically
+  mutate(experiment = forcats::fct_rev(factor(experiment))) %>%
+  arrange(experiment) %>%
+  # Show article labels only for the first experiment per article
+  mutate(
+    article = if_else(article == lead(article, default = ""), "", article)
+  ) %>%
+  # Prepare plot
+  ggplot(aes(x = gi, y = experiment)) +
+  geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
+  geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
+  # Add article and group labels as text to the left
+  geom_text(aes(x = -5.6, label = article, fontface = fontface), hjust = 0) +
+  geom_text(aes(x = -3.1, label = group, fontface = fontface), hjust = 0) +
+  # Add experiment specific effect size + CI as text to the right
+  geom_text(aes(x = 4.4, label = ci_print, fontface = fontface), hjust = 1) +
+  # Add Bayesian highest posterior density interval in the background
+  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
+  stat_interval(aes(x = b_Intercept), meta_draws, point_interval = "mean_hdi") +
+  # Add study specific effect size + CIs on top
+  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
+  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
+  # Add meta-analytic effect size as a line
+  annotate("segment", x = res_plot$b, xend = res_plot$b, y = 0.7, yend = 1.3) +
+  # Styling
+  coord_cartesian(expand = FALSE) +
+  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
+  scale_color_grey(
+    start = 0.9, end = 0.6,
+    labels = as_mapper(~ scales::percent(as.numeric(.x)))
+  ) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    size = "Sample size",
+    color = "Bayesian HPDI"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.position = "bottom",
+    axis.title.x = element_text(hjust = 0.584),
+    axis.title.y = element_blank(),
+    axis.text.y = element_blank(),
+    panel.grid = element_blank(),
+    text = element_text(family = "Helvetica")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "forest.pdf"), width = 9, height = 13)
 ```

### 2022-04-21 code/analysis.Rmd
Correct formula for `sd_av`

@@
     d_z_diff = mean_diff / sd_diff,
-    # Add d_av from mean difference and standard devations (assumes r = 0.5)
-    # (Cumming, 2012)
-    sd_av = (sd_novel + sd_familiar) / 2,
+    # Add d_av from mean difference and standard devations
+    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
+    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
     d_av = mean_diff / sd_av,

### 2022-04-21 code/analysis.Rmd
Use exact formula for `vi`

@@
     # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    df = 2 * (sample_size - 1),
-    j = exp(lgamma(df / 2) - log(sqrt(df / 2)) - lgamma((df - 1) / 2)),
-    gi = di * j,
+    dfi = 2 * (sample_size - 1),
+    ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
+    gi = di * ji,
+
     # Compute empirical correlation based on sd_z and condition SDs
@@
 # Compute standard error of Cohen's d based on assumed correlation
-# This will need a sensitivity analysis
+# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
+# This will need a sensitivity analysis regarding the values of `r_assumed`
 r_assumed <- 0.5
@@
     ni = sample_size,
-    vi = ((2 * (1 - r_assumed)) / ni) + (gi^2 / (2 * ni)),
+    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
+      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
     sei = sqrt(vi)

### 2022-04-21 code/analysis.Rmd
Code experiments with missing gender as "mixed"?

@@
       female_percent == 0.0 ~ "male",
-      !is.na(female_percent) ~ "mixed"
+      TRUE ~ "mixed"
     ) %>% factor(levels = c("mixed", "female", "male")),

### 2022-04-21 code/analysis.Rmd
Add gender as color to the forest plot

@@
   stat_interval(aes(x = b_Intercept), meta_draws, point_interval = "mean_hdi") +
-  # Add study specific effect size + CIs on top
-  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
-  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
-  # Add meta-analytic effect size as a line
-  annotate("segment", x = res_plot$b, xend = res_plot$b, y = 0.7, yend = 1.3) +
-  # Styling
-  coord_cartesian(expand = FALSE) +
-  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
   scale_color_grey(
@@
   ) +
+  labs(color = "Bayesian\nHPDI") +
+  # Add study specific effect size + CIs on top
+  ggnewscale::new_scale_color() +
+  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub, color = gender)) +
+  geom_point(aes(size = ni, color = gender), shape = 15) + # Or (1 / vi)?
+  scale_color_brewer(palette = "Dark2", na.translate = FALSE) +
+  # Add meta-analytic effect size as a line
+  annotate("segment", x = res_plot$b, xend = res_plot$b, y = 0.7, yend = 1.3) +
+  annotate("errorbar", xmin = res_plot$ci.lb, xmax = res_plot$ci.ub, y = 1.0) +
+  # Styling
+  coord_cartesian(expand = FALSE) +
+  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
   labs(
     x = expression("Hedges'" ~ italic("g")),
-    size = "Sample size",
-    color = "Bayesian HPDI"
+    size = "Sample\nsize",
+    color = "Gender"
   ) +
@@
     axis.text.y = element_blank(),
+    legend.title = element_text(hjust = 0.5),
     panel.grid = element_blank(),

### 2022-04-22 code/analysis.Rmd
Jackknife that does not work

--- 2022-04-21 code/analysis.Rmd
@@
 library(metafor)
-library(brms)
-library(tidybayes)
 
@@
 )
+```
 
+```{r, get_data}
 # Directory paths
 data_dir <- here("data")
-figures_dir <- here("results/figures")
 
@@
   mutate(
-
-    # Add unique experiment identifier
-    experiment = str_c(article, group, seq = ", "),
-
-    # Convert gender to a categorical variable
-    gender = case_when(
-      female_percent == 1.0 ~ "female",
-      female_percent == 0.0 ~ "male",
-      TRUE ~ "mixed"
-    ) %>% factor(levels = c("mixed", "female", "male")),
-
-    # Convert mean sample age from days to months and center
-    age_months = age_mean / 30.417,
-    age = age_months - mean(age_months, na.rm = TRUE),
-
     # Add difference between condition means
@@
     d_z_t = t / sqrt(sample_size),
-    # Add d_z from ANOVA F value via conversion to a t value
-    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
     # Add d_z from mean and standard deviation of the difference
     d_z_diff = mean_diff / sd_diff,
-    # Add d_av from mean difference and standard devations
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
+    # Add d_av from mean difference and standard devations (assumes r = 0)
+    # (Cumming, 2012)
+    sd_av = (sd_novel + sd_familiar) / 2,
     d_av = mean_diff / sd_av,
@@
     d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,
-
     # Choose one type of outcome variable for each experiment
-    di = case_when(
+    yi = case_when(
       # 1. If d was reported directed
@@
       !is.na(d_z_t) ~ d_z_t,
-      # 3. If ANOVA was reported
-      !is.na(d_z_f) ~ d_z_f,
-      # 4. If the difference between means and its SD were reported
+      # 3. If the difference between means and its SD were reported
       !is.na(d_z_diff) ~ d_z_diff,
-      # 5. If the individual condition means and their SDs were reported
+      # 4. If the individual condition means and their SDs were reported
       !is.na(d_av) ~ d_av,
-      # 6. If a novelty preference score and its SD were reported
+      # 5. If a novelty preference score and its SD were reported
       !is.na(d_nov_pref) ~ d_nov_pref
@@
     # Keep track which type of outcome measure was chosen for each article
-    di_type = case_when(
+    yi_type = case_when(
       !is.na(d) ~ "d",
       !is.na(d_z_t) ~ "d_z_t",
-      !is.na(d_z_f) ~ "d_z_f",
       !is.na(d_z_diff) ~ "d_z_diff",
@@
       factor(levels = c(
-        "d", "d_z_t", "d_z_f", "d_z_diff", "d_av", "d_nov_pref", "none"
+        "d", "d_z_t", "d_z_diff", "d_av", "d_nov_pref", "none"
       )),
-
-    # Apply small sample correction using Hedges' exact method
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    dfi = 2 * (sample_size - 1),
-    ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
-    gi = di * ji,
-
-    # Compute empirical correlation based on sd_z and condition SDs
+    # Find studies with any value of d_z (from t test or mean / SD of the diff.)
     d_z = case_when(
       !is.na(d_z_t) ~ d_z_t,
-      !is.na(d_z_f) ~ d_z_f,
       !is.na(d_z_diff) ~ d_z_diff
     ),
+    # Compute SD of the difference based on d_z
     sd_z = mean_diff / d_z,
+    # Compute correlation based on sd_z and condition SDs
     ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
-  ) -> dat
+  ) %>%
+  # Exclude experiments with redundant samples, missing stats, or age > 2 years
+  filter(!redundant & !is.na(yi) & age_mean < 730) -> dat
 
@@
 dat %>%
-  select(
-    article,
-    group,
-    gender_split,
-    gi,
-    di,
-    di_type,
-    d,
-    d_z_t,
-    d_z_f,
-    d_z_diff,
-    d_av,
-    d_nov_pref,
-    ri
-  ) %>%
+  select(id, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
   print(n = Inf)
 
-# Get empirical estimate of the correlation between dependent samples
+# Correlations between dependent samples
 summary(dat$ri)
-
-# Compute standard error of Cohen's d based on assumed correlation
-# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
-# This will need a sensitivity analysis regarding the values of `r_assumed`
-r_assumed <- 0.5
-dat %>%
-  mutate(
-    ni = sample_size,
-    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
-      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
-    sei = sqrt(vi)
-  ) %>%
-  filter(!is.na(gi)) %>%
-  select(
-    article,
-    group,
-    experiment,
-    gender_split,
-    gi,
-    ni,
-    vi,
-    sei,
-    gender,
-    age
-  ) -> dat_r
-
-# Show number of experiments per gender grouping strategy
-table(dat_r$gender_split)
-
-# Extract mixed/split experiments only
-dat_mixed <- filter(dat_r, gender_split %in% c("mixed", "mixed_only"))
-dat_split <- filter(dat_r, gender_split %in% c("split", "split_only"))
-
-# Combine both strategies, preferring mixed experiments
-dat_both_mixed <- filter(
-  dat_r, gender_split %in% c("mixed", "mixed_only", "split_only")
-)
-
-# Combine both strategies, preferring mixed experiments
-dat_both_split <- filter(
-  dat_r, gender_split %in% c("split", "mixed_only", "split_only")
-)
 ```
@@
 ```{r, compute_meta, echo=TRUE}
+# Compute standard error of Cohen's d based on assumed correlation
+# This will need a sensitivity analysis
+r_assumed <- 0.5
+dat %>%
+  mutate(
+    ni = sample_size,
+    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni))),
+    age_months = age_mean / 30.417
+  ) %>%
+  select(id, group, age_months, female_percent, ni, yi, sei) %>%
+  # Compute sampling variance from standard errors
+  escalc(yi = yi, sei = sei, ni = ni, data = .) %>%
+  tibble() -> dat_r
+
+# Create vector of experiment IDs for plotting
+experiment_ids <- with(dat_r, paste(id, group, sep = ", "))
+
+# # Two-level model
+# res <- rma(
+#   yi, vi,
+#   data = dat_r,
+#   slab = experiment_ids
+# )
+# print(res)
+# forest(res)
+
 # Three-level model
-res_ml <- rma.mv(
-  gi, vi,
-  random = ~ 1 | article / experiment,
-  data = dat_both_mixed,
-  slab = experiment
+res_mv <- rma.mv(
+  yi, vi,
+  random = ~ group | id,
+  data = dat_r,
+  slab = experiment_ids
 )
-print(res_ml)
-# forest(res_ml)
+print(res_mv)
+forest(res_mv)
+funnel(res_mv, main = "Standard Error")
+egger <- regtest(x = res_mv$yi, vi = res_mv$vi, sei = res_mv$sei, model = "lm", predictor = "sei")
+print(egger)
 
-# # Profile likelihodd plots for checking that REML has converged
-# profile(res_ml)
+# # Saving the forest plot
+# pdf("forest.pdf", width = 12, height = 12)
+# forest(res_mv)
+# dev.off()
 
-# Apply sliding difference contrast coding for the gender categories
-# This means that the Intercept will be the grand mean (i.e., the average across
-# studies) whereas the betas will test female vs. mixed and male vs. female
-(contrasts(dat_both_mixed$gender) <- MASS::contr.sdif(3))
+# # Profile likelihodd plots
+# profile(res_mv, sigma2 = 1)
+# profile(res_mv, sigma2 = 2)
+
+# Meta-regression with age
+res_age <- rma.mv(
+  yi, vi,
+  mods = ~age_months,
+  random = ~ group | id,
+  data = dat_r,
+  slab = experiment_ids
+)
+print(res_age)
+forest(res_age)
+funnel(res_age, main = "Standard Error")
 
@@
 res_gender <- rma.mv(
-  gi, vi,
-  mods = ~ gender - 1,
-  random = ~ 1 | article / experiment,
-  data = dat_both_mixed,
-  slab = experiment
+  yi, vi,
+  mods = ~female_percent,
+  random = ~ group | id,
+  data = dat_r,
+  slab = experiment_ids
 )
 print(res_gender)
-# forest(res_gender)
+forest(res_gender)
+funnel(res_gender, main = "Standard Error")
 
-# Pairwise comparison between the gender groups
-anova(res_gender, X = rbind(c(-1, 1, 0), c(-1, 0, 1), c(0, -1, 1)))
-
-# Meta-regression with age
-res_age <- rma.mv(
-  gi, vi,
-  mods = ~age,
-  random = ~ 1 | article / experiment,
-  data = dat_both_mixed,
-  slab = experiment
-)
-print(res_age)
-# forest(res_age)
-
-# Meta-regression with gender, age, and their interaction
+# Meta-regression with age, gender, and their interaction
 res_full <- rma.mv(
-  gi, vi,
-  mods = ~ gender * age,
-  random = ~ 1 | article / experiment,
-  data = dat_both_mixed,
-  slab = experiment
+  yi, vi,
+  mods = ~ age_months * female_percent,
+  random = ~ group | id,
+  data = dat_r,
+  slab = experiment_ids
 )
 print(res_full)
-# forest(res_full)
+forest(res_full)
+funnel(res_full, main = "Standard Error")
 ```
 
-```{r, brms, echo=TRUE}
-# Specify priors
-prior_c <- c(
-  set_prior("normal(0, 1)", class = "Intercept"),
-  set_prior("cauchy(0, 0.3)", class = "sd")
+```{r,  echo=TRUE}
+library(bootstrap)
+
+theta <- function(x, dat_r) {
+  rma.mv(
+    yi, vi,
+    mods = ~age_months,
+    random = ~ group | id,
+    data = dat_r[x, ],
+    slab = experiment_ids[x]
   )
-
-# Run prior predictive simulation
-res_prior <- brm(
-  gi | se(sei) ~ 1 + (1 | article / experiment),
-  data = dat_both_mixed,
-  prior = prior_c,
-  sample_prior = "only",
-  save_pars = save_pars(all = TRUE),
-  chains = 4,
-  iter = 2000,
-  cores = 4,
-  control = list(adapt_delta = 0.99)
-)
-summary(res_prior)
-# plot(res_prior)
-
-# Run Bayesian multilevel model
-res_brm <- update(res_prior, sample_prior = FALSE)
-summary(res_brm)
-# plot(res_brm)
-```
-
-```{r, fig2}
-# Forest plot inputs
-level <- 0.05
-ndraws <- 1000
-dat_plot <- dat_both_mixed
-res_plot <- res_ml
-res_plot_brm <- res_brm
-
-# Helper function for printing confidence intervals
-print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
-print_ci <- function(est, lb, ub) {
-  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
 }
 
-# Get draws from the Bayesian posterior distribution
-draws <- epred_draws(res_brm, dat_plot, ndraws = ndraws)
-meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = ndraws) %>%
-  mutate(article = "Three-level model", experiment = "zzz") # For the last line
-
-# Create forest plot
-dat_plot %>%
-  # Compute frequentist confidence intervals
-  mutate(
-    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
-    fontface = "plain" # For study labels and confidence interval
-  ) %>%
-  # Add meta-analytic effect size + CI
-  bind_rows(list(
-    article = "Three-level model",
-    group = "",
-    experiment = "zzz", # Just so it's displayed as the last line
-    gi = res_plot$b,
-    ci_lb = res_plot$ci.lb,
-    ci_ub = res_plot$ci.ub,
-    fontface = "bold"
-  )) %>%
-  # Format effect size + CI for printing them on the plot
-  mutate(ci_print = print_ci(gi, ci_lb, ci_ub)) %>%
-  # Reverse order of experiments so they are plotted alphabetically
-  mutate(experiment = forcats::fct_rev(factor(experiment))) %>%
-  arrange(experiment) %>%
-  # Show article labels only for the first experiment per article
-  mutate(
-    article = if_else(article == lead(article, default = ""), "", article)
-  ) %>%
-  # Prepare plot
-  ggplot(aes(x = gi, y = experiment)) +
-  geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
-  geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
-  # Add article and group labels as text to the left
-  geom_text(aes(x = -5.6, label = article, fontface = fontface), hjust = 0) +
-  geom_text(aes(x = -3.1, label = group, fontface = fontface), hjust = 0) +
-  # Add experiment specific effect size + CI as text to the right
-  geom_text(aes(x = 4.4, label = ci_print, fontface = fontface), hjust = 1) +
-  # Add Bayesian highest posterior density interval in the background
-  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
-  stat_interval(aes(x = b_Intercept), meta_draws, point_interval = "mean_hdi") +
-  # Add study specific effect size + CIs on top
-  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
-  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
-  # Add meta-analytic effect size as a line
-  annotate("segment", x = res_plot$b, xend = res_plot$b, y = 0.7, yend = 1.3) +
-  # Styling
-  coord_cartesian(expand = FALSE) +
-  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
-  scale_color_grey(
-    start = 0.9, end = 0.6,
-    labels = as_mapper(~ scales::percent(as.numeric(.x)))
-  ) +
-  labs(
-    x = expression("Hedges'" ~ italic("g")),
-    size = "Sample size",
-    color = "Bayesian HPDI"
-  ) +
-  theme_minimal() +
-  theme(
-    legend.position = "bottom",
-    axis.title.x = element_text(hjust = 0.584),
-    axis.title.y = element_blank(),
-    axis.text.y = element_blank(),
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "forest.pdf"), width = 9, height = 13)
+res_jk <- jackknife(1:nrow(dat_r), theta, dat_r)
 ```
-
-```{r, prior_sens, eval=FALSE}
-# Prior sensitivity analysis
-list(
-  "interept_uninformative" = c(
-    set_prior("uniform(-3, 3)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "interept_informative" = c(
-    set_prior("normal(0, 0.2)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "sd_uninformative" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("uniform(0, 10)", class = "sd", ub = 10)
-  ),
-  "sd_informative" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("student_t(10, 0, 0.2)", class = "sd")
-  )
-) %>%
-  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
-map(res_sens, summary)
-```
-
 # Methods
@@
 ```{r}
-length(unique(included$article))
+length(unique(included$id))
 ```
@@
 ```{r}
-table(included$di_type)
+table(included$yi_type)
 ```
@@
     group_text = if_else(is.na(group), "NA", group),
-    id_group = str_c(article, ", ", group_text),
+    id_group = str_c(id, ", ", group_text),
     id_group_ordered = fct_reorder(id_group, age_mean, .desc = TRUE),
@@
 ```
-
-```{r, simulation}
-generate_exp <- function(n_boys = 1e3,
-                         n_girls = 1e3,
-                         mean_diff_boys = 0,
-                         mean_diff_girls = 2,
-                         sd_diff_boys = 4,
-                         sd_diff_girls = 4) {
-
-  # Create randomly sampled data for boys and girls
-  # Each element is the mean looking time difference for one infant
-  boys <- rnorm(n_boys, mean_diff_boys, sd_diff_boys)
-  girls <- rnorm(n_girls, mean_diff_girls, sd_diff_girls)
-
-  # Compute separate effect sizes for the two split gender groups
-  d_boys <- mean(boys) / sd(boys)
-  d_girls <- mean(girls) / sd(girls)
-
-  # Compute common effect size for the mixed gender group
-  infants <- c(boys, girls)
-  n_infants <- length(infants)
-  d_infants <- mean(infants) / sd(infants)
-
-  # Return all results for this experiment as a list
-  return(list(
-    n_boys = n_boys,
-    n_girls = n_girls,
-    n_infants = n_infants,
-    d_boys = d_boys,
-    d_girls = d_girls,
-    d_infants = d_infants
-  ))
-}
-
-# Generate random experiments
-n_boys <- 1e3
-n_girls <- 1e3
-n_exps <- 100
-dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
-dat <- do.call(rbind.data.frame, dat)
-dat$article <- paste0("exp_", 1:n_exps)
-
-### MIXED EXPERIMENTS ONLY ###
-
-# Compute sampling variance of the effect size for each study; see
-# https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#w-group-smd
-r_assumed <- .5
-dat$v_d_infants <- with( # Sampling variances of the effect sizes
-  dat, ((2 * (1 - r_assumed)) / n_infants) + (d_infants^2 / (2 * n_infants))
-)
-
-# Fit 3 level meta-analysis
-res_full <- metafor::rma.mv(
-  d_infants, v_d_infants,
-  # random = ~ article | article,
-  data = dat,
-  slab = article
-)
-
-# Check results
-summary(res_full)
-
-### SPLIT EXPERIMENTS ONLY ###
-
-# Put effect sizes for boys and girls into separate rows
-dat_split <- tidyr::pivot_longer(
-  dat,
-  cols = c(d_boys, d_girls),
-  names_to = "gender",
-  values_to = "d_gender"
-)
-
-# Compute sampling variance of the gender-specific effect size
-dat_split$v_d_gender <- with(
-  dat_split, ((2 * (1 - r_assumed)) / n_girls) + (d_gender^2 / (2 * n_girls))
-)
-
-# Use rma.mv to compute MA on d_gender and v_d_gender values
-
-# Repeat 100 times with generate_meta
-
-# Compare mixed gender and split gender MAs
-# Same distribution of meta-analytic effect size?
-# Same variance / standard error?
-# Is the difference significant?
-
-### MIXED/SPLIT GENDER ANALYSIS ###
-
-# Make a percentage of study use mixed vs. split and choose randomly
-# Use different percentages
-# Make split vs. mixed dependent on the observed gender difference
-# Note for this we need to draw study specific effect sizes from a distribution
-
-### MAKE IT MORE REALISTIC ###
-
-# Make sample sizes per study different
-
-# Automate
-generate_meta <- function(n_exps, n_boys, n_girls) {
-
-  # Generate random experiments
-  dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
-  dat <- do.call(rbind.data.frame, dat)
-  dat$article <- paste0("exp_", 1:n_exps)
-
-  # Compute sampling variance of the effect size for each study; see
-  # https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#w-group-smd
-  r_assumed <- .5
-  dat$v_d_infants <- with( # Sampling variances of the effect sizes
-    dat, ((2 * (1 - r_assumed)) / n_infants) + (d_infants^2 / (2 * n_infants))
-  )
-
-  # Fit meta-analysis
-  res_full <- metafor::rma.mv(
-    d_infants, v_d_infants,
-    # random = ~ article | article,
-    data = dat,
-    slab = article
-  )
-
-  # Return coefficients table
-  summ <- summary(res_full)
-  return(coef(summ))
-}
-
-n_metas <- 100
-metas <- replicate(n_metas, generate_meta(100, 100, 100), simplify = FALSE)
-metas <- do.call(rbind.data.frame, metas)
-metas$article <- paste0("meta_", 1:n_metas)
-
-mean(metas$estimate)
-```

### 2022-04-22 code/analysis.Rmd
Normalize all the line endings

--- 2022-04-21 code/analysis.Rmd
@@
 )
+
 print(res_ml)
@@
 print(res_gender)
+
 # forest(res_gender)
@@
 map(res_sens, summary)
+
 ```
 
+```{r,  echo=TRUE}
+library(bootstrap)
+
+theta <- function(x, dat_r) {
+  rma.mv(
+    yi, vi,
+    mods = ~age_months,
+    random = ~ group | id,
+    data = dat_r[x, ],
+    slab = experiment_ids[x]
+  )
+}
+
+res_jk <- jackknife(1:nrow(dat_r), theta, dat_r)
+```
 # Methods

### 2022-04-22 code/analysis.Rmd
Rename `dat` objects

--- 2022-04-21 code/analysis.Rmd
@@
     ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
-  ) -> dat
+  ) -> dat_all
 
 # Overview of the different effect sizes
-dat %>%
+dat_all %>%
   select(
@@
 # Get empirical estimate of the correlation between dependent samples
-summary(dat$ri)
+summary(dat_all$ri)
 
@@
 r_assumed <- 0.5
-dat %>%
+dat_all %>%
   mutate(
@@
     age
-  ) -> dat_r
+  ) -> dat_all_r
 
 # Show number of experiments per gender grouping strategy
-table(dat_r$gender_split)
+table(dat_all_r$gender_split)
 
-# Extract mixed/split experiments only
-dat_mixed <- filter(dat_r, gender_split %in% c("mixed", "mixed_only"))
-dat_split <- filter(dat_r, gender_split %in% c("split", "split_only"))
+# Extract split or mixed experiments only
+dat_split <- filter(dat_all_r, gender_split %in% c("split", "split_only"))
+dat_mixed <- filter(dat_all_r, gender_split %in% c("mixed", "mixed_only"))
+
+# Combine both strategies, preferring split experiments
+dat_both_split <- filter(
+  dat_all_r, gender_split %in% c("split", "mixed_only", "split_only")
+)
 
@@
 dat_both_mixed <- filter(
-  dat_r, gender_split %in% c("mixed", "mixed_only", "split_only")
+  dat_all_r, gender_split %in% c("mixed", "mixed_only", "split_only")
 )
 
-# Combine both strategies, preferring mixed experiments
-dat_both_split <- filter(
-  dat_r, gender_split %in% c("split", "mixed_only", "split_only")
-)
+# We go ahead with the last solution as to use the maximum amount of information
+# while not biasing the gender results
+dat <- dat_both_mixed
 ```
@@
   random = ~ 1 | article / experiment,
-  data = dat_both_mixed,
+  data = dat,
   slab = experiment
@@
 # studies) whereas the betas will test female vs. mixed and male vs. female
-(contrasts(dat_both_mixed$gender) <- MASS::contr.sdif(3))
+(contrasts(dat$gender) <- MASS::contr.sdif(3))
 
@@
   gi | se(sei) ~ 1 + (1 | article / experiment),
-  data = dat_both_mixed,
+  data = dat,
   prior = prior_c,
@@
   chains = 4,
-  iter = 2000,
+  iter = 10000,
   cores = 4,
@@
 
-```{r, fig2}
+```{r, fig_forest}
 # Forest plot inputs
@@
 ndraws <- 1000
-dat_plot <- dat_both_mixed
-res_plot <- res_ml
-res_plot_brm <- res_brm
 
@@
 # Get draws from the Bayesian posterior distribution
-draws <- epred_draws(res_brm, dat_plot, ndraws = ndraws)
+draws <- epred_draws(res_brm, dat, ndraws = ndraws)
 meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = ndraws) %>%
@@
 # Create forest plot
-dat_plot %>%
+dat %>%
   # Compute frequentist confidence intervals
@@
     experiment = "zzz", # Just so it's displayed as the last line
-    gi = res_plot$b,
-    ci_lb = res_plot$ci.lb,
-    ci_ub = res_plot$ci.ub,
+    gi = res_ml$b,
+    ci_lb = res_ml$ci.lb,
+    ci_ub = res_ml$ci.ub,
     fontface = "bold"
@@
   # Add meta-analytic effect size as a line
-  annotate("segment", x = res_plot$b, xend = res_plot$b, y = 0.7, yend = 1.3) +
-  annotate("errorbar", xmin = res_plot$ci.lb, xmax = res_plot$ci.ub, y = 1.0) +
+  annotate("segment", x = res_ml$b, xend = res_ml$b, y = 0.7, yend = 1.3) +
+  annotate("errorbar", xmin = res_ml$ci.lb, xmax = res_ml$ci.ub, y = 1.0) +
   # Styling

### 2022-04-22 code/analysis.Rmd
Align structure of code blocks with the manuscript

@@
 knitr::opts_chunk$set(
-  echo = FALSE,
+  echo = TRUE,
   message = FALSE,
@@
 
-Effect sizes of individual experiments:
+## Mental rotation ability
 
-```{r, compute_effects, echo=TRUE}
+```{r, prepare_effect_sizes}
 # Add columns to the table of included experiments
@@
     experiment = str_c(article, group, seq = ", "),
-
-    # Convert gender to a categorical variable
-    gender = case_when(
-      female_percent == 1.0 ~ "female",
-      female_percent == 0.0 ~ "male",
-      TRUE ~ "mixed"
-    ) %>% factor(levels = c("mixed", "female", "male")),
-
-    # Convert mean sample age from days to months and center
-    age_months = age_mean / 30.417,
-    age = age_months - mean(age_months, na.rm = TRUE),
 
@@
     sei,
-    gender,
-    age
+    female_percent,
+    age_mean
   ) -> dat_all_r
@@
 # while not biasing the gender results
-dat <- dat_both_mixed
+dat_select <- dat_both_mixed
+
+# Recode predictor variables for meta-regression and plotting
+dat_select %>%
+  mutate(
+
+  # Gender as a categorical variable
+  gender = case_when(
+    female_percent == 1.0 ~ "female",
+    female_percent == 0.0 ~ "male",
+    TRUE ~ "mixed"
+  ) %>% factor(levels = c("mixed", "female", "male")),
+
+  # Mean sample age in months, centered around the mean
+  age = age_mean / 30.417,
+  age = age - mean(age, na.rm = TRUE),
+  .keep = "unused"
+
+) -> dat
 ```
 
-Actual meta-analysis:
-
-```{r, compute_meta, echo=TRUE}
+```{r, meta_analysis}
 # Three-level model
@@
 # profile(res_ml)
-
-# Apply sliding difference contrast coding for the gender categories
-# This means that the Intercept will be the grand mean (i.e., the average across
-# studies) whereas the betas will test female vs. mixed and male vs. female
-(contrasts(dat$gender) <- MASS::contr.sdif(3))
-
-# Meta-regression with gender
-res_gender <- rma.mv(
-  gi, vi,
-  mods = ~ gender - 1,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_gender)
-# forest(res_gender)
-
-# Pairwise comparison between the gender groups
-anova(res_gender, X = rbind(c(-1, 1, 0), c(-1, 0, 1), c(0, -1, 1)))
-
-# Meta-regression with age
-res_age <- rma.mv(
-  gi, vi,
-  mods = ~age,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_age)
-# forest(res_age)
-
-# Meta-regression with gender, age, and their interaction
-res_full <- rma.mv(
-  gi, vi,
-  mods = ~ gender * age,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_full)
-# forest(res_full)
 ```
 
-```{r, brms, echo=TRUE}
+```{r, meta_analysis_bayes}
 # Specify priors
@@
 
-```{r, prior_sens, eval=FALSE}
-# Prior sensitivity analysis
-list(
-  "interept_uninformative" = c(
-    set_prior("uniform(-3, 3)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "interept_informative" = c(
-    set_prior("normal(0, 0.2)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "sd_uninformative" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("uniform(0, 10)", class = "sd", ub = 10)
-  ),
-  "sd_informative" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("student_t(10, 0, 0.2)", class = "sd")
+## Moderator variables
+
+```{r, meta_regression}
+# Apply sliding difference contrast coding for the gender categories
+# This means that the Intercept will be the grand mean (i.e., the average across
+# studies) whereas the betas will test female vs. mixed and male vs. female
+(contrasts(dat$gender) <- MASS::contr.sdif(3))
+
+# Meta-regression with gender
+res_gender <- rma.mv(
+  gi, vi,
+  mods = ~ gender - 1,
+  random = ~ 1 | article / experiment,
+  data = dat,
+  slab = experiment
 )
-) %>%
-  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
-map(res_sens, summary)
+print(res_gender)
+# forest(res_gender)
+
+# Pairwise comparison between the gender groups
+anova(res_gender, X = rbind(c(-1, 1, 0), c(-1, 0, 1), c(0, -1, 1)))
+
+# Meta-regression with age
+res_age <- rma.mv(
+  gi, vi,
+  mods = ~age,
+  random = ~ 1 | article / experiment,
+  data = dat,
+  slab = experiment
+)
+print(res_age)
+# forest(res_age)
+
+# Meta-regression with gender, age, and their interaction
+res_full <- rma.mv(
+  gi, vi,
+  mods = ~ gender * age,
+  random = ~ 1 | article / experiment,
+  data = dat,
+  slab = experiment
+)
+print(res_full)
+# forest(res_full)
 ```
@@
 ```
+
+# Supplementary information
+
+```{r, prior_sens}
+# Prior sensitivity analysis
+list(
+  "interept_uninformative" = c(
+    set_prior("uniform(-3, 3)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
+  ),
+  "interept_informative" = c(
+    set_prior("normal(0, 0.2)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
+  ),
+  "sd_uninformative" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("uniform(0, 10)", class = "sd", ub = 10)
+  ),
+  "sd_informative" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("student_t(10, 0, 0.2)", class = "sd")
+  )
+) %>%
+  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
+map(res_sens, summary)
+```

### 2022-04-22 code/analysis.Rmd
Add meta-regression plot

@@
     female_percent,
-    age_mean
+    age_mean,
+    age_sd,
+    age_min,
+    age_max
   ) -> dat_all_r
@@
     gender = case_when(
-    female_percent == 1.0 ~ "female",
-    female_percent == 0.0 ~ "male",
-    TRUE ~ "mixed"
-  ) %>% factor(levels = c("mixed", "female", "male")),
+      female_percent == 1.0 ~ "Female",
+      female_percent == 0.0 ~ "Male",
+      TRUE ~ "Mixed"
+    ) %>% factor(levels = c("Mixed", "Female", "Male")),
 
@@
     age = age_mean / 30.417,
-  age = age - mean(age, na.rm = TRUE),
+    age_c = age - mean(age, na.rm = TRUE),
+    age_sd = age_sd / 30.417,
     .keep = "unused"
-
   ) -> dat
@@
   gi, vi,
-  mods = ~age,
+  mods = ~age_c,
   random = ~ 1 | article / experiment,
@@
   gi, vi,
-  mods = ~ gender * age,
+  mods = ~ gender * age_c,
   random = ~ 1 | article / experiment,
@@
 # forest(res_full)
+```
+
+```{r, fig_regression}
+# Plot regression with gender and age
+alph <- 0.7
+dat %>%
+  ggplot(aes(x = age, y = gi, color = gender)) +
+  # Data points
+  # geom_errorbar(aes(xmin = age - age_sd, xmax = age + age_sd), alpha = alph) +
+  # geom_errorbar(aes(ymin = gi - sei, ymax = gi + sei), alpha = alph) +
+  geom_point(aes(size = ni), shape = 16, alpha = alph) +
+  # Regression lines - currently not reflecting the meta-analytic model
+  geom_smooth(method = lm, formula = y ~ x, alpha = .1) +
+  # Styling
+  scale_x_continuous(limits = c(3, 16), breaks = seq(4, 16, 2)) +
+  scale_y_continuous(limits = c(-1.3, 2.5), breaks = seq(-1, 2.5, 0.5)) +
+  scale_color_brewer(palette = "Dark2") +
+  labs(
+    x = "Age (months)",
+    y = expression("Hedges'" ~ italic("g")),
+    color = "Gender",
+    size = "Sample size"
+  ) +
+  theme_bw() +
+  theme(
+    panel.border = element_rect(size = 1),
+    panel.grid = element_line(color = "grey90"),
+    text = element_text(family = "Helvetica"),
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "regression.pdf"), width = 7, height = 4)
 ```

### 2022-04-23 code/analysis.Rmd
Add output of heterogeneity
Update meta-regression

--- 2022-04-22 code/analysis.Rmd
@@
     female_percent,
-    age_mean
+    age_mean,
+    age_sd,
+    age_min,
+    age_max,
+    task
   ) -> dat_all_r
@@
 # while not biasing the gender results
-dat_select <- dat_both_mixed
-
-# Recode predictor variables for meta-regression and plotting
-dat_select %>%
-  mutate(
-
-  # Gender as a categorical variable
-  gender = case_when(
-    female_percent == 1.0 ~ "female",
-    female_percent == 0.0 ~ "male",
-    TRUE ~ "mixed"
-  ) %>% factor(levels = c("mixed", "female", "male")),
-
-  # Mean sample age in months, centered around the mean
-  age = age_mean / 30.417,
-  age = age - mean(age, na.rm = TRUE),
-  .keep = "unused"
-
-) -> dat
+dat <- dat_both_mixed
 ```
@@
 # forest(res_ml)
+
+# Check heterogeneity
+(i2 <- dmetar::var.comp(res_ml))
+# plot(i2)
+
+# Check share of variance at each level of the model
+round(res_ml$sigma2[1] / sum(res_ml$sigma2), 3) # Between-article (ICC)
+round(res_ml$sigma2[2] / sum(res_ml$sigma2), 3) # Within-article (between-exp.)
 
@@
 ```{r, meta_regression}
-# Apply sliding difference contrast coding for the gender categories
-# This means that the Intercept will be the grand mean (i.e., the average across
-# studies) whereas the betas will test female vs. mixed and male vs. female
-(contrasts(dat$gender) <- MASS::contr.sdif(3))
+# Recode predictor variables for meta-regression and plotting
+dat %>%
+  mutate(
 
-# Meta-regression with gender
-res_gender <- rma.mv(
+    # Gender as a categorical (factor) variable
+    gender_f = case_when(
+      female_percent == 1.0 ~ "Female",
+      female_percent == 0.0 ~ "Male",
+      TRUE ~ "Mixed"
+    ) %>% factor(levels = c("Mixed", "Female", "Male")),
+    # Re-code as contrast for the meta-regression model
+    gender = recode(gender_f, "Mixed" = 0, "Female" = -0.5, "Male" = 0.5),
+
+    # Mean sample age in years, centered around the mean
+    age = age_mean / 365.25,
+    age_c = age - mean(age, na.rm = TRUE),
+    age_sd = age_sd / 365.25,
+
+    # Task type as a categorical (factor) variale
+    task_f = factor(task, levels = c("Habituation", "VoE")),
+    # Re-code as contrast for the meta-regression model
+    task = recode(task_f, "Habituation" = -0.5, "VoE" = 0.5),
+    .keep = "unused"
+  ) -> dat_reg
+
+# Meta-regression with gender, age, and task
+res_reg <- rma.mv(
   gi, vi,
-  mods = ~ gender - 1,
+  mods = ~ gender * age_c + task,
   random = ~ 1 | article / experiment,
-  data = dat,
+  data = dat_reg,
   slab = experiment
 )
-print(res_gender)
-# forest(res_gender)
+print(res_reg)
+# forest(res_full)
+```
 
-# Pairwise comparison between the gender groups
-anova(res_gender, X = rbind(c(-1, 1, 0), c(-1, 0, 1), c(0, -1, 1)))
+```{r, meta_regression_bayes}
+# Specify priors
+prior_c <- c(
+  set_prior("normal(0, 1)", class = "Intercept"),
+  set_prior("normal(0, 0.5)", class = "b"),
+  set_prior("cauchy(0, 0.3)", class = "sd")
+)
 
-# Meta-regression with age
-res_age <- rma.mv(
-  gi, vi,
-  mods = ~age,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
+# Run prior predictive simulation
+res_prior_reg <- brm(
+  gi | se(sei) ~ gender * age_c + task + (1 | article / experiment),
+  data = dat_reg,
+  prior = prior_c,
+  sample_prior = "only",
+  save_pars = save_pars(all = TRUE),
+  chains = 4,
+  iter = 10000,
+  cores = 4,
+  control = list(adapt_delta = 0.99)
 )
-print(res_age)
-# forest(res_age)
+summary(res_prior_reg)
+# plot(res_prior_reg)
 
-# Meta-regression with gender, age, and their interaction
-res_full <- rma.mv(
-  gi, vi,
-  mods = ~ gender * age,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
+# Run Bayesian multilevel model
+res_brm_reg <- update(res_prior_reg, sample_prior = FALSE)
+summary(res_brm_reg)
+# plot(res_brm_reg)
+```
+
+```{r, fig_regression}
+# Plot regression with gender and age
+alph <- 0.7
+dat_reg %>%
+  ggplot(aes(x = age * 12, y = gi, color = gender_f)) +
+  # Data points
+  # geom_errorbar(aes(xmin = age - age_sd, xmax = age + age_sd), alpha = alph) +
+  # geom_errorbar(aes(ymin = gi - sei, ymax = gi + sei), alpha = alph) +
+  geom_point(aes(size = ni), shape = 16, alpha = alph) +
+  # Regression lines - currently not reflecting the meta-analytic model
+  geom_smooth(method = lm, formula = y ~ x, alpha = .1) +
+  # Styling
+  scale_x_continuous(limits = c(3, 16), breaks = seq(4, 16, 2)) +
+  scale_y_continuous(limits = c(-1.3, 2.5), breaks = seq(-1, 2.5, 0.5)) +
+  scale_color_brewer(palette = "Dark2") +
+  labs(
+    x = "Age (months)",
+    y = expression("Hedges'" ~ italic("g")),
+    color = "Gender",
+    size = "Sample size"
+  ) +
+  theme_bw() +
+  theme(
+    panel.border = element_rect(size = 1),
+    panel.grid = element_line(color = "grey90"),
+    text = element_text(family = "Helvetica"),
   )
-print(res_full)
-# forest(res_full)
+
+# Save the plot
+ggsave(here(figures_dir, "regression.pdf"), width = 7, height = 4)
 ```

### 2022-04-24 code/analysis.Rmd
Remove gender (color) from forest plot

@@
   stat_interval(aes(x = b_Intercept), meta_draws, point_interval = "mean_hdi") +
+  # Add study specific effect size + CIs on top
+  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
+  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
+  # Add meta-analytic effect size as a line
+  annotate("segment", x = res_ml$b, xend = res_ml$b, y = 0.7, yend = 1.3) +
+  # Styling
+  coord_cartesian(expand = FALSE) +
+  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
   scale_color_grey(
@@
   ) +
-  labs(color = "Bayesian\nHPDI") +
-  # Add study specific effect size + CIs on top
-  ggnewscale::new_scale_color() +
-  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub, color = gender)) +
-  geom_point(aes(size = ni, color = gender), shape = 15) + # Or (1 / vi)?
-  scale_color_brewer(palette = "Dark2", na.translate = FALSE) +
-  # Add meta-analytic effect size as a line
-  annotate("segment", x = res_ml$b, xend = res_ml$b, y = 0.7, yend = 1.3) +
-  annotate("errorbar", xmin = res_ml$ci.lb, xmax = res_ml$ci.ub, y = 1.0) +
-  # Styling
-  coord_cartesian(expand = FALSE) +
-  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
   labs(
     x = expression("Hedges'" ~ italic("g")),
-    size = "Sample\nsize",
-    color = "Gender"
+    size = "Sample size",
+    color = "Bayesian HPDI"
   ) +
@@
     axis.text.y = element_blank(),
-    legend.title = element_text(hjust = 0.5),
     panel.grid = element_blank(),

### 2022-04-25 code/analysis.Rmd
Add column headers and halfeye to forest plot

@@
 level <- 0.05
-ndraws <- 1000
+n_draws <- 10000
+n_experiments <- length(unique(dat$experiment))
 
-# Helper function for printing confidence intervals
+# Helper functions for printing confidence intervals
 print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
@@
 
-# Get draws from the Bayesian posterior distribution
-draws <- epred_draws(res_brm, dat, ndraws = ndraws)
-meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = ndraws) %>%
-  mutate(article = "Three-level model", experiment = "zzz") # For the last line
+# Get posterior draws for each experiment
+draws <- epred_draws(res_brm, dat, ndraws = n_draws) %>%
+  mutate(experiment_f = factor(experiment))
+
+# Get posterior draws for the meta-analytic effect
+meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = n_draws)
+meta_effect_size <- summary(res_brm)$fixed
 
@@
 dat %>%
+  # Make sure the plot will be ordered alphabetically by experiment IDs
+  arrange(experiment) %>%
+  mutate(
+    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
+    # Show article labels only for the first experiment per article
+    article = if_else(article == lag(article, default = ""), "", article),
     # Compute frequentist confidence intervals
-  mutate(
     ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
     ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
-    fontface = "plain" # For study labels and confidence interval
+    ci_print = print_ci(gi, ci_lb, ci_ub)
   ) %>%
-  # Add meta-analytic effect size + CI
-  bind_rows(list(
-    article = "Three-level model",
-    group = "",
-    experiment = "zzz", # Just so it's displayed as the last line
-    gi = res_ml$b,
-    ci_lb = res_ml$ci.lb,
-    ci_ub = res_ml$ci.ub,
-    fontface = "bold"
-  )) %>%
-  # Format effect size + CI for printing them on the plot
-  mutate(ci_print = print_ci(gi, ci_lb, ci_ub)) %>%
-  # Reverse order of experiments so they are plotted alphabetically
-  mutate(experiment = forcats::fct_rev(factor(experiment))) %>%
-  arrange(experiment) %>%
-  # Show article labels only for the first experiment per article
-  mutate(
-    article = if_else(article == lead(article, default = ""), "", article)
-  ) %>%
-  # Prepare plot
-  ggplot(aes(x = gi, y = experiment)) +
+  # Prepare plotting canvas
+  ggplot(aes(x = gi, y = experiment_f)) +
   geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
   geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
-  # Add article and group labels as text to the left
-  geom_text(aes(x = -5.6, label = article, fontface = fontface), hjust = 0) +
-  geom_text(aes(x = -3.1, label = group, fontface = fontface), hjust = 0) +
-  # Add experiment specific effect size + CI as text to the right
-  geom_text(aes(x = 4.4, label = ci_print, fontface = fontface), hjust = 1) +
-  # Add Bayesian highest posterior density interval in the background
+  # Add article and group labels as text on the left
+  geom_text(aes(x = -5.6, label = article), hjust = 0) +
+  geom_text(aes(x = -3.1, label = group), hjust = 0) +
+  # Add experiment-specific effect sizes and CIs as text on the right
+  geom_text(aes(x = 4.4, label = ci_print), hjust = 1) +
+  # Add Bayesian highest posterior density intervals for each experiment
   stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
-  stat_interval(aes(x = b_Intercept), meta_draws, point_interval = "mean_hdi") +
-  # Add study specific effect size + CIs on top
-  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
-  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
-  # Add meta-analytic effect size as a line
-  annotate("segment", x = res_ml$b, xend = res_ml$b, y = 0.7, yend = 1.3) +
-  # Styling
-  coord_cartesian(expand = FALSE) +
-  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
   scale_color_grey(
@@
   ) +
+  # Add experiment-specific effect sizes and CIs as dots with error bars
+  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
+  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
+  # Add posterior distribution for the meta-analytic effect
+  stat_halfeye(
+    aes(x = b_Intercept, y = -1),
+    meta_draws,
+    point_interval = "mean_hdi"
+  ) +
+  annotate(
+    "text",
+    x = -5.6,
+    y = -0.5,
+    label = "Three-level model",
+    hjust = 0,
+    fontface = "bold"
+  ) +
+  annotate(
+    "text",
+    x = 4.4,
+    y = -0.5,
+    label = print_ci(
+      meta_effect_size$Estimate,
+      meta_effect_size$`l-95% CI`,
+      meta_effect_size$`u-95% CI`
+    ),
+    hjust = 1,
+    fontface = "bold"
+  ) +
+  # Add headers for each of the for columns
+  annotate( # Just to make the grid lines disappear
+    "rect",
+    xmin = -Inf,
+    xmax = Inf,
+    ymin = n_experiments + 0.5,
+    ymax = Inf,
+    fill = "white"
+  ) +
+  annotate(
+    "text",
+    x = c(-5.6, -3.1, 0, 4.4),
+    y = n_experiments + 1.5,
+    label = c(
+      "Article", "Experiment", "Effect size plot", "Effect size statistic"
+    ),
+    hjust = c(0, 0, 0.5, 1),
+    fontface = "bold"
+  ) +
+  # Styling
+  coord_cartesian(ylim = c(-1.5, n_experiments + 2), expand = FALSE) +
+  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
   labs(
@@
     legend.position = "bottom",
-    axis.title.x = element_text(hjust = 0.584),
+    axis.title.x = element_text(hjust = 0.565),
     axis.title.y = element_blank(),

### 2022-04-25 code/analysis.Rmd
Tune forest plot
- Make x axis symmetric
- Use long group IDs
- Split effect size + CI into 3 separate columns

@@
     group,
+    group_long,
     experiment,
@@
   ggplot(aes(x = gi, y = experiment_f)) +
-  geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
-  geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
+  geom_vline(xintercept = seq(-3, 3, 1), size = 0.8, color = "grey90") +
+  geom_vline(xintercept = seq(-2.5, 2.5, 1), size = 0.4, color = "grey90") +
   # Add article and group labels as text on the left
-  geom_text(aes(x = -5.6, label = article), hjust = 0) +
-  geom_text(aes(x = -3.1, label = group), hjust = 0) +
+  geom_text(aes(x = -9.9, label = article), hjust = 0) +
+  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
   # Add experiment-specific effect sizes and CIs as text on the right
-  geom_text(aes(x = 4.4, label = ci_print), hjust = 1) +
+  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
+  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
+  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
   # Add Bayesian highest posterior density intervals for each experiment
@@
     "text",
-    x = -5.6,
+    x = c(-9.9, 3.7, 4.4, 5.1),
     y = -0.5,
-    label = "Three-level model",
-    hjust = 0,
-    fontface = "bold"
-  ) +
-  annotate(
-    "text",
-    x = 4.4,
-    y = -0.5,
-    label = print_ci(
-      meta_effect_size$Estimate,
-      meta_effect_size$`l-95% CI`,
-      meta_effect_size$`u-95% CI`
+    label = c(
+      "Three-level model",
+      print_num(meta_effect_size$Estimate),
+      print_num(meta_effect_size$`l-95% CI`),
+      print_num(meta_effect_size$`u-95% CI`)
     ),
-    hjust = 1,
+    hjust = c(0, 1, 1, 1),
     fontface = "bold"
@@
     "text",
-    x = c(-5.6, -3.1, 0, 4.4),
+    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
     y = n_experiments + 1.5,
     label = c(
-      "Article", "Experiment", "Effect size plot", "Effect size statistic"
+      "Article",
+      "Experiment",
+      "Effect size plot",
+      "Effect size",
+      "Lower",
+      "Upper"
     ),
-    hjust = c(0, 0, 0.5, 1),
+    hjust = c(0, 0, 0.5, 1, 1, 1),
     fontface = "bold"
@@
   coord_cartesian(ylim = c(-1.5, n_experiments + 2), expand = FALSE) +
-  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
+  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
   labs(
@@
       legend.position = "bottom",
-    axis.title.x = element_text(hjust = 0.565),
+      axis.title.x = element_text(hjust = 0.67),
       axis.title.y = element_blank(),
@@
 # Save the plot
-ggsave(here(figures_dir, "forest.pdf"), width = 9, height = 13)
+ggsave(here(figures_dir, "forest.pdf"), width = 12, height = 14)
 ```

### 2022-04-26 code/analysis.Rmd
Order experiments by year
Add study table

@@
 figures_dir <- here("results/figures")
+tables_dir <- here("results/tables")
 
@@
     # Add unique experiment identifier
-    experiment = str_c(article, group, seq = ", "),
+    experiment = str_c(year, article, group, seq = ", "),
 
@@
     ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
-  ) -> dat_all
+  ) %>%
+  # Order rows by experiment ID
+  arrange(experiment) -> dat_all
 
@@
   ) %>%
-  filter(!is.na(gi)) %>%
-  select(
-    article,
-    group,
-    group_long,
-    experiment,
-    gender_split,
-    gi,
-    ni,
-    vi,
-    sei,
-    female_percent,
-    age_mean,
-    age_sd,
-    age_min,
-    age_max,
-    task
-  ) -> dat_all_r
+  filter(!is.na(gi)) -> dat_all_r
 
@@
 # Helper functions for printing confidence intervals
-print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
+print_num <- function(x, digits = 2) {
+  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
+  x[x == "NA"] <- NA
+  return(x)
+}
 print_ci <- function(est, lb, ub) {
@@
 ggsave(here(figures_dir, "forest.pdf"), width = 12, height = 14)
+```
+
+```{r, tab_within}
+# Helper functions to re-format age in years and/or months
+format_days_years <- function(days) {
+  days_per_year <- 365.25
+  days_per_month <- 30.417
+  years <- days %/% days_per_year
+  months <- round((days - years * days_per_year) / days_per_month)
+  str <- paste0(as.character(years), "y ", as.character(months), "m")
+  str[is.na(days)] <- NA
+  return(str)
+}
+format_days_months <- function(days, digits = 1) {
+  days_per_month <- 30.417
+  months <- days / days_per_month
+  str <- format(round(months, digits), trim = TRUE, nsmall = digits)
+  str <- paste0(str, "m")
+  str[is.na(days)] <- NA
+  return(str)
+}
+
+# Save within-analysis table of experiments
+dat %>%
+  transmute(
+    Article = if_else(article == lag(article, default = ""), "", article),
+    Experiment = group_long,
+    `Sample size` = sample_size,
+    `Females` = round(female_percent * sample_size),
+    `Mean age^a` = format_days_years(age_mean),
+    SD = format_days_months(age_sd),
+    Task = task,
+    `Stimulus type` = str_to_sentence(stimuli_presentation),
+    `Stimulus dimensions` = stimuli_dimensions
+  ) %>%
+  print(n = Inf)
+write_csv(
+  file = here(tables_dir, "within_experiments.csv"),
+  na = "n/a"
+)
 ```

### 2022-04-26 code/analysis.Rmd
Re-format study table

@@
 # Helper functions to re-format age in years and/or months
-format_days_years <- function(days) {
-  days_per_year <- 365.25
+format_days_months <- function(days) {
   days_per_month <- 30.417
-  years <- days %/% days_per_year
-  months <- round((days - years * days_per_year) / days_per_month)
-  str <- paste0(as.character(years), "y ", as.character(months), "m")
-  str[is.na(days)] <- NA
-  return(str)
-}
-format_days_months <- function(days, digits = 1) {
-  days_per_month <- 30.417
-  months <- days / days_per_month
-  str <- format(round(months, digits), trim = TRUE, nsmall = digits)
-  str <- paste0(str, "m")
+  months <- days %/% days_per_month
+  days_left <- round(days - months * days_per_month)
+  str <- paste0(as.character(months), "m ", as.character(days_left), "d")
   str[is.na(days)] <- NA
@@
 dat %>%
+  mutate(
+    age_mean = format_days_months(age_mean),
+    age_sd = str_c(as.character(round(age_sd)), "d"),
+  ) %>%
   transmute(
@@
     `Females` = round(female_percent * sample_size),
-    `Mean age^a` = format_days_years(age_mean),
-    SD = format_days_months(age_sd),
+    Age = str_c(age_mean, "±", age_sd, sep = " "),
     Task = task,
@@
   ) %>%
-  print(n = Inf)
 write_csv(

### 2022-04-26 code/analysis.Rmd
Tweak regression models and plot

@@
     # Gender as a categorical (factor) variable
-    gender_f = case_when(
+    gender = case_when(
       female_percent == 1.0 ~ "Female",
@@
     ) %>% factor(levels = c("Mixed", "Female", "Male")),
-    # Re-code as contrast for the meta-regression model
-    gender = recode(gender_f, "Mixed" = 0, "Female" = -0.5, "Male" = 0.5),
 
@@
     # Task type as a categorical (factor) variale
-    task_f = factor(task, levels = c("Habituation", "VoE")),
-    # Re-code as contrast for the meta-regression model
-    task = recode(task_f, "Habituation" = -0.5, "VoE" = 0.5),
-    .keep = "unused"
+    task = factor(task, levels = c("Habituation", "VoE")),
+
+    # Combine gender and task into one column for plotting
+    gender_task = factor(
+      str_c(gender, task, sep = ", "),
+      levels = c(
+        "Female, Habituation",
+        "Male, Habituation",
+        "Mixed, Habituation",
+        "Mixed, VoE"
+      )
+    )
   ) -> dat_reg
+
+# Set numerical contrasts for factor variables
+contrasts(dat_reg$gender) <- MASS::contr.sdif(3)
+contrasts(dat_reg$task) <- MASS::contr.sdif(2)
 
@@
 ```{r, fig_regression}
-# Plot regression with gender and age
-alph <- 0.7
+# Get draws from the posterior distribution
+draws_reg <- epred_draws(
+  res_brm_reg,
+  dat_reg,
+  ndraws = n_draws,
+  re_formula = NA
+)
+
+# Use colors as proposed in https://arxiv.org/abs/2107.02270
+habi_colors <- c(
+  "Female, Habituation" = "#5790fc",
+  "Male, Habituation" = "#f89c20",
+  "Mixed, Habituation" = "#e42536"
+)
+voe_colors <- c("Mixed, VoE" = "#964a8b")
+
+# Regression plot
 dat_reg %>%
-  ggplot(aes(x = age * 12, y = gi, color = gender_f)) +
-  # Data points
-  # geom_errorbar(aes(xmin = age - age_sd, xmax = age + age_sd), alpha = alph) +
-  # geom_errorbar(aes(ymin = gi - sei, ymax = gi + sei), alpha = alph) +
-  geom_point(aes(size = ni), shape = 16, alpha = alph) +
-  # Regression lines - currently not reflecting the meta-analytic model
-  geom_smooth(method = lm, formula = y ~ x, alpha = .1) +
+  ggplot(aes(x = age * 12, y = gi)) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+
+  # Regression lines and HPDIs - Habituation tasks
+  stat_lineribbon(
+    aes(y = .epred, color = gender_task),
+    data = draws_reg,
+    alpha = .4,
+    point_interval = "mean_hdi"
+  ) +
+  # Individual study effect sizes - Habituation tasks
+  geom_point(aes(color = gender_task, size = ni), shape = 0) +
+  scale_color_manual(
+    values = habituation_colors,
+    breaks = names(habi_colors),
+    labels = c("Females", "Males", "Mixed gender"),
+    na.value = NA
+  ) +
+  guides(color = guide_legend(
+    title = "Habituation tasks",
+    override.aes = list(fill = NA),
+    order = 1
+  )) +
+
+  # Regression lines and HPDIs - VoE tasks
+  ggnewscale::new_scale_color() +
+  stat_lineribbon(
+    aes(y = .epred, color = gender_task),
+    data = draws_reg,
+    alpha = .4,
+    fill = NA,
+    point_interval = "mean_hdi"
+  ) +
+  # Individual study effect sizes - VoE tasks
+  geom_point(aes(color = gender_task, size = ni), shape = 0) +
+  scale_color_manual(
+    values = voe_colors,
+    breaks = names(voe_colors),
+    labels = c("Mixed gender"),
+    na.value = NA
+  ) +
+  guides(
+    color = guide_legend(
+      title = "Violation of\nexpectation tasks"
+    ),
+    order = 2
+  ) +
+
   # Styling
-  scale_x_continuous(limits = c(3, 16), breaks = seq(4, 16, 2)) +
-  scale_y_continuous(limits = c(-1.3, 2.5), breaks = seq(-1, 2.5, 0.5)) +
-  scale_color_brewer(palette = "Dark2") +
+  coord_cartesian(expand = FALSE) +
+  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
+  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
+  scale_fill_grey(
+    start = 0.9, end = 0.7,
+    labels = as_mapper(~ scales::percent(as.numeric(.x)))
+  ) +
   labs(
@@
     y = expression("Hedges'" ~ italic("g")),
-    color = "Gender",
+    fill = "Bayesian HPDI",
     size = "Sample size"
@@
   theme(
+    legend.key = element_blank(),
     panel.border = element_rect(size = 1),
-    panel.grid = element_line(color = "grey90"),
+    panel.grid = element_blank(), # element_line(color = "grey90"),
     text = element_text(family = "Helvetica"),
@@
 # Save the plot
-ggsave(here(figures_dir, "regression.pdf"), width = 7, height = 4)
+ggsave(here(figures_dir, "regression.pdf"), width = 8, height = 5)
 ```

### 2022-04-27 code/analysis.Rmd
Fix regression plot

@@
   dat_reg,
-  ndraws = n_draws,
+  ndraws = NULL,
   re_formula = NA
@@
   scale_color_manual(
-    values = habituation_colors,
+    values = habi_colors,
     breaks = names(habi_colors),

### 2022-04-27 code/analysis.Rmd
Draw HPDI as outlines in regression plot

@@
 
+# Summarise to obtain HPDIs
+draws_reg_hdi <- mean_hdi(draws_reg)
+
 # Use colors as proposed in https://arxiv.org/abs/2107.02270
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-
-  # Regression lines and HPDIs - Habituation tasks
-  stat_lineribbon(
-    aes(y = .epred, color = gender_task),
-    data = draws_reg,
-    alpha = .4,
-    point_interval = "mean_hdi"
+  # Regression lines - Habituation tasks
+  geom_lineribbon(
+    aes(y = .epred, ymin = .lower, ymax = .upper, color = gender_task),
+    data = draws_reg_hdi,
+    fill = NA
+  ) +
+  # Bayesian HPDIs - Habituation tasks
+  geom_ribbon(
+    aes(ymin = .lower, ymax = .upper, color = gender_task),
+    data = draws_reg_hdi,
+    fill = NA
   ) +
@@
   )) +
-
-  # Regression lines and HPDIs - VoE tasks
   ggnewscale::new_scale_color() +
-  stat_lineribbon(
-    aes(y = .epred, color = gender_task),
-    data = draws_reg,
-    alpha = .4,
-    fill = NA,
-    point_interval = "mean_hdi"
+  # Regression lines - VoE tasks
+  geom_lineribbon(
+    aes(y = .epred, ymin = .lower, ymax = .upper, color = gender_task),
+    data = draws_reg_hdi,
+    fill = NA
+  ) +
+  # Bayesian HPDIs - VoE tasks
+  geom_ribbon(
+    aes(ymin = .lower, ymax = .upper, color = gender_task),
+    data = draws_reg_hdi,
+    fill = NA
   ) +
@@
   ) +
-
   # Styling
@@
   scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
-  scale_fill_grey(
-    start = 0.9, end = 0.7,
-    labels = as_mapper(~ scales::percent(as.numeric(.x)))
-  ) +
   labs(

### 2022-04-27 code/analysis.Rmd
Add regression coefficient plot

--- 2022-04-27 code/analysis.Rmd
@@
 library(tidybayes)
+library(cowplot)
 
@@
   theme(
+    legend.direction = "vertical",
     legend.key = element_blank(),
+    legend.position = "none",
     panel.border = element_rect(size = 1),
@@
     text = element_text(family = "Helvetica"),
-  )
+  ) -> plot_reg
 
-# Save the plot
-ggsave(here(figures_dir, "regression.pdf"), width = 8, height = 5)
+# Extract the legend so that we can put it inside the plotting area
+plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))
+
+# Plot posterior distributions of the regression coefficients
+draws_reg_coef <- tidy_draws(res_brm_reg)
+draws_reg_coef %>%
+  select(coef_colnames) %>%
+  gather() %>%
+  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
+  ggplot(aes(x = value, y = fct_rev(coef))) +
+  geom_vline(xintercept = 0) +
+  stat_halfeye(point_interval = mean_hdi) +
+  coord_cartesian(xlim = c(-1.25, 1.25)) +
+  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
+  labs(
+    x = expression("Regression weight (" * Delta * italic("g") * ")"),
+    y = NULL
+  ) +
+  theme_bw() +
+  theme(
+    axis.text.y  = element_text(hjust = 1),
+    panel.border = element_rect(size = 1)
+  ) -> plot_coef
+
+# Combine plots
+plot_grid(
+  plot_reg, plot_coef,
+  nrow = 1, rel_widths = c(3, 2), labels = "AUTO"
+) +
+  draw_plot(plot_reg_legend, x = 0.42, y = 0.84, hjust = 0.5, vjust = 0.5)
+
+# Save plot
+ggsave(here(figures_dir, "regression_coef.pdf"), width = 12, height = 5)
 ```

### 2022-04-27 code/analysis.Rmd
Revert HPDIs in regression plot to fill

--- 2022-04-27 code/analysis.Rmd
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-
   # Regression lines and HPDIs - Habituation tasks
@@
   )) +
-
   # Regression lines and HPDIs - VoE tasks
@@
     text = element_text(family = "Helvetica"),
-  )
+  ) -> plot_reg
 
-# Save the plot
-ggsave(here(figures_dir, "regression.pdf"), width = 8, height = 5)
+# Extract the legend so that we can put it inside the plotting area
+plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))
+
+# Plot posterior distributions of the regression coefficients
+draws_reg_coef <- tidy_draws(res_brm_reg)
+draws_reg_coef %>%
+  select(coef_colnames) %>%
+  gather() %>%
+  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
+  ggplot(aes(x = value, y = fct_rev(coef))) +
+  geom_vline(xintercept = 0) +
+  stat_halfeye(point_interval = mean_hdi) +
+  coord_cartesian(xlim = c(-1.25, 1.25)) +
+  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
+  labs(
+    x = expression("Regression weight (" * Delta * italic("g") * ")"),
+    y = NULL
+  ) +
+  theme_bw() +
+  theme(
+    panel.grid = element_blank(),
+    axis.text.y = element_text(hjust = 1),
+    panel.border = element_rect(size = 1)
+  ) -> plot_coef
+
+# Combine plots
+plot_grid(
+  plot_reg, plot_coef,
+  nrow = 1, rel_widths = c(3, 2), labels = "AUTO"
+) +
+  draw_plot(plot_reg_legend, x = 0.37, y = 0.84, hjust = 0.5, vjust = 0.5)
+
+# Save plot
+ggsave(here(figures_dir, "regression_coef.pdf"), width = 12, height = 5)
 ```

### 2022-04-28 code/analysis.Rmd
Fix regression plot

@@
     # Add unique experiment identifier
-    experiment = str_c(year, article, group, seq = ", "),
+    experiment = str_c(year, article, group, sep = ", "),
 
@@
   ) +
-  guides(
-    color = guide_legend(
-      title = "Violation of\nexpectation tasks"
-    ),
-    order = 2
-  ) +
+  guides(color = guide_legend(title = "VoE tasks", order = 2)) +
   # Styling
@@
 
+# Define new labels for the regression coefficients
+coef_colnames <- c(
+  "Intercept" = "b_Intercept",
+  "Females - mixed" = "b_gender2M1",
+  "Males - females" = "b_gender3M2",
+  "Age (per year)" = "b_age_c",
+  "Habituation - VoE" = "b_task2M1",
+  "(Females - Mixed) × age" = "b_gender2M1:age_c",
+  "(Males - Females) × age" = "b_gender3M2:age_c"
+)
+
 # Plot posterior distributions of the regression coefficients
@@
 draws_reg_coef %>%
-  select(coef_colnames) %>%
+  select(all_of(coef_colnames)) %>%
   gather() %>%
@@
     x = expression("Regression weight (" * Delta * italic("g") * ")"),
-    y = NULL
+    y = "Fixed effect"
   ) +

### 2022-04-28 code/analysis.Rmd
Fine-tune plots

@@
 ```{r, fig_forest}
-# Forest plot inputs
-level <- 0.05
-n_draws <- 10000
+# Define some plotting parameters
 n_experiments <- length(unique(dat$experiment))
+linewidth <- 0.5
 
@@
 # Get posterior draws for each experiment
-draws <- epred_draws(res_brm, dat, ndraws = n_draws) %>%
+draws <- epred_draws(res_brm, dat, ndraws = NULL) %>%
   mutate(experiment_f = factor(experiment))
@@
 # Get posterior draws for the meta-analytic effect
-meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = n_draws)
+meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = NULL)
 meta_effect_size <- summary(res_brm)$fixed
@@
     # Compute frequentist confidence intervals
-    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
     ci_print = print_ci(gi, ci_lb, ci_ub)
@@
   ggplot(aes(x = gi, y = experiment_f)) +
-  geom_vline(xintercept = seq(-3, 3, 1), size = 0.8, color = "grey90") +
-  geom_vline(xintercept = seq(-2.5, 2.5, 1), size = 0.4, color = "grey90") +
+  geom_vline(
+    xintercept = seq(-3, 3, 0.5), size = linewidth / 2, color = "grey70"
+  ) +
   # Add article and group labels as text on the left
@@
     legend.position = "bottom",
-    axis.title.x = element_text(hjust = 0.67),
+    axis.text.x = element_text(family = "Helvetica", color = "black"),
+    axis.text.y = element_blank(),
+    axis.title.x = element_text(hjust = 0.67, margin = margin(t = 7, b = -10)),
     axis.title.y = element_blank(),
-    axis.text.y = element_blank(),
     panel.grid = element_blank(),
@@
   ggplot(aes(x = age * 12, y = gi)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_hline(yintercept = 0, size = linewidth / 2) +
   # Regression lines and HPDIs - Habituation tasks
@@
   theme(
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black", size = linewidth / 2),
     legend.direction = "vertical",
@@
     legend.position = "none",
-    panel.border = element_rect(size = 1),
-    panel.grid = element_blank(), # element_line(color = "grey90"),
-    text = element_text(family = "Helvetica"),
+    panel.border = element_rect(color = "black", size = linewidth),
+    panel.grid = element_blank(),
+    text = element_text(family = "Helvetica", color = "black")
   ) -> plot_reg
@@
   ggplot(aes(x = value, y = fct_rev(coef))) +
-  geom_vline(xintercept = 0) +
+  geom_vline(xintercept = 0, size = linewidth / 2) +
   stat_halfeye(point_interval = mean_hdi) +
@@
   theme(
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.title.y = element_text(margin = margin(l = 17, r = -17)),
+    axis.ticks = element_line(color = "black", size = linewidth / 2),
     panel.grid = element_blank(),
     axis.text.y = element_text(hjust = 1),
-    panel.border = element_rect(size = 1)
+    panel.border = element_rect(color = "black", size = linewidth),
+    text = element_text(family = "Helvetica", color = "black")
   ) -> plot_coef
@@
   plot_reg, plot_coef,
-  nrow = 1, rel_widths = c(3, 2), labels = "AUTO"
+  nrow = 1, rel_widths = c(3, 2), labels = "AUTO",
+  label_size = 12, label_fontfamily = "Helvetica",
+  label_x = 0.008, label_y = 0.99
 ) +

### 2022-04-28 code/analysis.Rmd
Add ICC and hypothesis tests

@@
 # plot(res_brm)
+
+# Compute intra-class correlation
+sd_article <- VarCorr(res_brm)$article$sd
+sd_experiment <- VarCorr(res_brm)$`article:experiment`$sd
+(icc <- sd_article / (sd_article + sd_experiment))
+
+# Compute probabilities of the meta-analytic being greater than 0
+hypothesis(res_brm, "Intercept > 0")$hypothesis
 ```
@@
 # forest(res_full)
+
+# Compute intra-class correlation
+sd_article_reg <- VarCorr(res_brm_reg)$article$sd
+sd_experiment_reg <- VarCorr(res_brm_reg)$`article:experiment`$sd
+(icc_reg <- sd_article_reg / (sd_article_reg + sd_experiment_reg))
+
+# Compute reduction in heterogeneity compared to the original meta-analysis
+1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)
+
+# Compute probabilities of the different effects being greater than 0
+hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
+hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
+hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis
 ```

### 2022-04-28 code/analysis.Rmd
Plot ETI/QI instead of HPDI

@@
   # Add Bayesian highest posterior density intervals for each experiment
-  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
+  stat_interval(
+    aes(x = .epred),
+    data = draws,
+    alpha = .8,
+    point_interval = "mean_qi",
+    .width = c(0.5, 0.95),
+  ) +
   scale_color_grey(
-    start = 0.9, end = 0.6,
+    start = 0.85, end = 0.65,
     labels = as_mapper(~ scales::percent(as.numeric(.x)))
@@
   # Add experiment-specific effect sizes and CIs as dots with error bars
-  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
-  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
+  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
+  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
   # Add posterior distribution for the meta-analytic effect
@@
     meta_draws,
-    point_interval = "mean_hdi"
+    point_interval = "mean_qi",
+    .width = c(0.95)
   ) +
@@
     size = "Sample size",
-    color = "Bayesian HPDI"
+    color = "CrI level"
   ) +
@@
 # Summarise to obtain HPDIs
-draws_reg_hdi <- mean_hdi(draws_reg)
+draws_reg_hdi <- mean_qi(draws_reg)
 
@@
     alpha = .4,
-    point_interval = "mean_hdi"
+    point_interval = "mean_qi",
+    .width = c(0.5, 0.95)
   ) +
@@
     data = draws_reg,
+    fill = NA,
     alpha = .4,
-    fill = NA,
-    point_interval = "mean_hdi"
+    point_interval = "mean_qi",
+    .width = c(0.5, 0.95)
   ) +
@@
   scale_fill_grey(
-    start = 0.9, end = 0.7,
+    start = 0.85, end = 0.65,
     labels = as_mapper(~ scales::percent(as.numeric(.x)))
@@
     y = expression("Hedges'" ~ italic("g")),
-    fill = "Bayesian HPDI",
+    fill = "CrI level",
     size = "Sample size"
@@
   geom_vline(xintercept = 0, size = linewidth / 2) +
-  stat_halfeye(point_interval = mean_hdi) +
+  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
   coord_cartesian(xlim = c(-1.25, 1.25)) +
@@
   plot_reg, plot_coef,
-  nrow = 1, rel_widths = c(3, 2), labels = "AUTO",
+  nrow = 1, rel_widths = c(3, 2), labels = "auto",
   label_size = 12, label_fontfamily = "Helvetica",
-  label_x = 0.008, label_y = 0.99
+  label_x = 0.008, label_y = 0.995
 ) +

### 2022-04-29 code/analysis.Rmd
Add descriptive stats for the Introduction

@@
 included <- readxl::read_excel(excel_file, sheet = "included", na = "NA")
-```
 
-# Results
-
-## Mental rotation ability
-
-```{r, prepare_effect_sizes}
 # Add columns to the table of included experiments
@@
 ```
+
+# Introduction
+
+```{r, results_literature_search}
+# Number of experiments
+nrow(dat)
+
+# Number of infants
+sum(dat$sample_size)
+
+# Age range in months
+min(dat$age_min, na.rm = TRUE) / 30.417
+max(dat$age_max, na.rm = TRUE) / 30.417
+
+# Mean age in months
+sum((dat$age_mean * dat$sample_size)) / sum(dat$sample_size) / 30.417
+
+# Number of experiments per task type
+table(dat$task)
+```
+
+# Results
+
+## Mental rotation ability
 

### 2022-04-29 code/analysis.Rmd
Fix ICC and hypotheses for `brm_reg`

@@
 # forest(res_full)
-
-# Compute intra-class correlation
-sd_article_reg <- VarCorr(res_brm_reg)$article$sd
-sd_experiment_reg <- VarCorr(res_brm_reg)$`article:experiment`$sd
-(icc_reg <- sd_article_reg / (sd_article_reg + sd_experiment_reg))
-
-# Compute reduction in heterogeneity compared to the original meta-analysis
-1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)
-
-# Compute probabilities of the different effects being greater than 0
-hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
-hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
-hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis
 ```
@@
 # plot(res_brm_reg)
+
+# Compute probabilities of the different effects being greater than 0
+hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
+hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
+hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis
+
+# Compute intra-class correlation
+sd_article_reg <- VarCorr(res_brm_reg)$article$sd
+sd_experiment_reg <- VarCorr(res_brm_reg)$`article:experiment`$sd
+(icc_reg <- sd_article_reg / (sd_article_reg + sd_experiment_reg))
+
+# Compute reduction in heterogeneity compared to the original meta-analysis
+1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)
 ```

### 2022-04-29 code/analysis.Rmd
Update axes in figures

@@
 ```{r, fig_forest}
-# Define some plotting parameters
-n_experiments <- length(unique(dat$experiment))
-linewidth <- 0.5
-
 # Helper functions for printing confidence intervals
@@
 # Create forest plot
+n_experiments <- length(unique(dat$experiment))
 dat %>%
@@
   ggplot(aes(x = gi, y = experiment_f)) +
-  geom_vline(
-    xintercept = seq(-3, 3, 0.5), size = linewidth / 2, color = "grey70"
-  ) +
+  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
   # Add article and group labels as text on the left
@@
   # Styling
-  coord_cartesian(ylim = c(-1.5, n_experiments + 2), expand = FALSE) +
+  coord_cartesian(
+    ylim = c(-1.5, n_experiments + 2), expand = FALSE, clip = "off"
+  ) +
   scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
+  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
   labs(
@@
     axis.text.y = element_blank(),
-    axis.title.x = element_text(hjust = 0.67, margin = margin(t = 7, b = -10)),
+    axis.ticks.x = element_line(colour = "black"),
+    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
     axis.title.y = element_blank(),
@@
   ggplot(aes(x = age * 12, y = gi)) +
-  geom_hline(yintercept = 0, size = linewidth / 2) +
+  geom_hline(yintercept = seq(-1, 2, 0.5), color = "grey90") +
+  annotate(
+    "rect",
+    xmin = 5.5, xmax = Inf, ymin = 1.25, ymax = Inf,
+    color = NA, fill = "white"
+  ) +
   # Regression lines and HPDIs - Habituation tasks
@@
   ) +
-  theme_bw() +
+  theme_classic() +
   theme(
     axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black", size = linewidth / 2),
+    axis.ticks = element_line(color = "black"),
     legend.direction = "vertical",
@@
     legend.position = "none",
-    panel.border = element_rect(color = "black", size = linewidth),
     panel.grid = element_blank(),
@@
   ggplot(aes(x = value, y = fct_rev(coef))) +
-  geom_vline(xintercept = 0, size = linewidth / 2) +
+  geom_vline(xintercept = seq(-1, 1, 0.5), color = "grey90") +
   stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
-  coord_cartesian(xlim = c(-1.25, 1.25)) +
+  coord_cartesian(xlim = c(-1.25, 1.25), clip = "off") +
   scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
-  labs(
-    x = expression("Regression weight (" * Delta * italic("g") * ")"),
-    y = "Fixed effect"
+  labs(x = expression("Regression weight (" * Delta * italic("g") * ")")) +
+  annotate(
+    "text",
+    label = "Fixed effects", x = -3.175, y = 7.86, hjust = 0,
+    family = "Helvetica", fontface = "bold", color = "black"
   ) +
-  theme_bw() +
+  theme_minimal() +
   theme(
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.title.y = element_text(margin = margin(l = 17, r = -17)),
-    axis.ticks = element_line(color = "black", size = linewidth / 2),
+    axis.line.x = element_line(colour = "black"),
+    axis.text.x = element_text(family = "Helvetica", color = "black"),
+    axis.text.y = element_text(
+      family = "Helvetica", color = "black", size = 3.88 * .pt,
+      hjust = 0, vjust = -0.1, margin = margin(l = 20)
+    ),
+    axis.ticks.x = element_line(color = "black"),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank(),
     panel.grid = element_blank(),
-    axis.text.y = element_text(hjust = 1),
-    panel.border = element_rect(color = "black", size = linewidth),
     text = element_text(family = "Helvetica", color = "black")
@@
   nrow = 1, rel_widths = c(3, 2), labels = "auto",
-  label_size = 12, label_fontfamily = "Helvetica",
-  label_x = 0.008, label_y = 0.995
+  label_size = 11, label_fontfamily = "Helvetica",
+  label_x = 0.008, label_y = 0.99
 ) +
-  draw_plot(plot_reg_legend, x = 0.37, y = 0.84, hjust = 0.5, vjust = 0.5)
+  draw_plot(plot_reg_legend, x = 0.385, y = 0.865, hjust = 0.5, vjust = 0.5)
 

### 2022-04-29 code/analysis.Rmd
Correct heterogeneity and ICC estimates

@@
 
+# Compute by-experiment variance
+sd_experiment_draws <- as.matrix(
+  res_brm,
+  variable = "sd_article:experiment__Intercept"
+)
+mean_qi(sd_experiment_draws^2)
+
+# Compute by-article variance
+sd_article_draws <- as.matrix(
+  res_brm,
+  variable = "sd_article__Intercept"
+)
+mean_qi(sd_article_draws^2)
+
 # Compute intra-class correlation
-sd_article <- VarCorr(res_brm)$article$sd
-sd_experiment <- VarCorr(res_brm)$`article:experiment`$sd
-(icc <- sd_article / (sd_article + sd_experiment))
+icc_draws <- sd_article_draws^2 / (sd_article_draws^2 + sd_experiment_draws^2)
+mean_qi(icc_draws)
 

### 2022-04-29 code/analysis.Rmd
Correct heterogeneity and ICC estimates

--- 2022-04-29 code/analysis.Rmd
@@
 
-# Compute intra-class correlation
-sd_article <- VarCorr(res_brm)$article$sd
-sd_experiment <- VarCorr(res_brm)$`article:experiment`$sd
-(icc <- sd_article / (sd_article + sd_experiment))
-
 # Compute probabilities of the meta-analytic being greater than 0
 hypothesis(res_brm, "Intercept > 0")$hypothesis
+
+# Compute by-experiment variance
+var_experiment <- as.matrix(
+  res_brm,
+  variable = "sd_article:experiment__Intercept"
+)^2
+mean_qi(var_experiment)
+
+# Compute by-article variance
+var_article <- as.matrix(
+  res_brm,
+  variable = "sd_article__Intercept"
+)^2
+mean_qi(var_article_draws)
+
+# Compute intra-class correlation
+var_total <- (var_experiment + var_article)
+icc_draws <- var_article / var_total
+mean_qi(icc_draws)
 ```
@@
 
+# Compute by-experiment variance
+var_experiment_reg <- as.matrix(
+  res_brm_reg,
+  variable = "sd_article:experiment__Intercept"
+)^2
+mean_qi(var_experiment_reg)
+
+# Compute by-article variance
+var_article_reg <- as.matrix(
+  res_brm_reg,
+  variable = "sd_article__Intercept"
+)^2
+mean_qi(var_article_reg)
+
 # Compute intra-class correlation
-sd_article_reg <- VarCorr(res_brm_reg)$article$sd
-sd_experiment_reg <- VarCorr(res_brm_reg)$`article:experiment`$sd
-(icc_reg <- sd_article_reg / (sd_article_reg + sd_experiment_reg))
+var_total_reg <- var_experiment_reg + var_article_reg
+icc_reg <- var_article_reg / var_total_reg
+mean_qi(icc_reg)
 
 # Compute reduction in heterogeneity compared to the original meta-analysis
-1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)
+1 - mean(var_total_reg / var_total)
 ```

### 2022-04-30 code/analysis.Rmd
Improve Bayesian models
- Use non-centered intercept, which doesn't change the results but
samples better

- Use `bayestestR` to summarize the posterior distribution (incl. Bayes
factors)

@@
 library(brms)
+library(bayestestR)
 library(tidybayes)
@@
 prior_c <- c(
-  set_prior("normal(0, 1)", class = "Intercept"),
+  set_prior("normal(0, 1)", class = "b"),
   set_prior("cauchy(0, 0.3)", class = "sd")
@@
 # Run prior predictive simulation
+n_iter <- 20000
 res_prior <- brm(
-  gi | se(sei) ~ 1 + (1 | article / experiment),
+  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
   data = dat,
@@
   chains = 4,
-  iter = 10000,
+  iter = n_iter,
+  warmup = 1000,
   cores = 4,
@@
 
-# Compute probabilities of the meta-analytic being greater than 0
-hypothesis(res_brm, "Intercept > 0")$hypothesis
+# Summarise fixed effects (incl. Bayes factors)
+describe_posterior(
+  res_brm,
+  centrality = "mean", ci = 0.95, ci_method = "ETI",
+  test = c("p_direction", "rope", "bayesfactor"),
+  rope_range = c(-0.1, 0.1)
+)
 
@@
 )^2
-mean_qi(var_article_draws)
+mean_qi(var_article)
 
@@
 prior_c <- c(
-  set_prior("normal(0, 1)", class = "Intercept"),
+  set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
   set_prior("normal(0, 0.5)", class = "b"),
@@
 res_prior_reg <- brm(
-  gi | se(sei) ~ gender * age_c + task + (1 | article / experiment),
+  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
+    (1 | article / experiment),
   data = dat_reg,
@@
 
-# Compute probabilities of the different effects being greater than 0
-hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
-hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
-hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis
+# Summarise fixed effects (incl. Bayes factors)
+describe_posterior(
+  res_brm_reg,
+  centrality = "mean", ci = 0.95, ci_method = "ETI",
+  test = c("p_direction", "rope", "bayesfactor"),
+  rope_range = c(-0.1, 0.1)
+)
 

### 2022-04-30 code/analysis.Rmd
Add sensitivity analysis for `r_assumed`

@@
     ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
-    gi = di * ji,
-
-    # Compute empirical correlation based on sd_z and condition SDs
-    d_z = case_when(
-      !is.na(d_z_t) ~ d_z_t,
-      !is.na(d_z_f) ~ d_z_f,
-      !is.na(d_z_diff) ~ d_z_diff
-    ),
-    sd_z = mean_diff / d_z,
-    ri = (sd_z^2 - sd_novel^2 - sd_familiar^2) / (-2 * sd_novel * sd_familiar)
+    gi = di * ji
   ) %>%
@@
     d_av,
-    d_nov_pref,
-    ri
+    d_nov_pref
   ) %>%
   print(n = Inf)
-
-# Get empirical estimate of the correlation between dependent samples
-summary(dat_all$ri)
 
@@
 
+```{r, ri_assumed_sens}
+# Compute empirical estimate of the correlation between dependent samples
+dat %>%
+  mutate(
+    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
+    d_diff = case_when(
+      !is.na(d) ~ d,
+      !is.na(d_z_t) ~ d_z_t,
+      !is.na(d_z_f) ~ d_z_f,
+      !is.na(d_z_diff) ~ d_z_diff
+    ),
+    # Compute empirical correlation
+    # Basesd on the SD of the difference and the SDs within the two conditions
+    sd_diff = mean_diff / d_diff,
+    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
+      (-2 * sd_novel * sd_familiar)
+  ) %>%
+  pull(ri) -> ri_empirical
+
+# Summarise the estimated correlations
+summary(ri_empirical)
+
+# Re-run the meta-analysis for different values of r_assumed
+seq(-0.9, 0.9, by = 0.3) %>%
+  map_dfr(function(ri_sens) {
+
+    # Re-compute standard errors of the effect sizes
+    mutate(
+      dat,
+      vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
+        (1 + gi^2 * (ni / (2 * (1 - ri_sens)))) - (gi^2 / ji^2),
+      sei = sqrt(vi)
+    ) -> dat_ri_sens
+
+    # Re-run meta-analysis
+    res_ri_sens <- update(res_brm, newdata = dat_ri_sens, refresh = 0)
+
+    # Extract posterior draws
+    tidy_draws(res_ri_sens) %>%
+      mutate(ri_sens = ri_sens)
+  }) -> draws_ri_sens
+
+# Plot meta-analytic results for each assumed correlation
+draws_ri_sens %>%
+  mutate(ri_sens_f = fct_rev(factor(print_num(ri_sens)))) %>%
+  ggplot(aes(y = ri_sens_f, x = b_Intercept)) +
+  geom_vline(xintercept = seq(-0.75, 0.75, 0.25), color = "grey90") +
+  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
+  coord_cartesian(xlim = c(-0.75, 0.75), clip = "off") +
+  scale_x_continuous(breaks = seq(-0.75, 0.75, 0.25)) +
+  labs(x = expression("Hedges" ~ italic("g"))) +
+  annotate(
+    "text",
+    label = "Correlation", x = -1.1, y = 7.86, hjust = 0,
+    family = "Helvetica", fontface = "bold", color = "black"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.line.x = element_line(colour = "black"),
+    axis.text.x = element_text(family = "Helvetica", color = "black"),
+    axis.text.y = element_text(
+      family = "Helvetica", color = "black", size = 3.88 * .pt,
+      hjust = 0, vjust = -0.1, margin = margin(l = 20)
+    ),
+    axis.ticks.x = element_line(color = "black"),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank(),
+    panel.grid = element_blank(),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "ri_sens.pdf"), width = 4, height = 5)
+```
+
 ```{r, prior_sens}

### 2022-05-01 code/analysis.Rmd
Make sensitivity analysis of `r_assumed` a table

@@
 
-    # Extract posterior draws
-    tidy_draws(res_ri_sens) %>%
-      mutate(ri_sens = ri_sens)
-  }) -> draws_ri_sens
-
-# Plot meta-analytic results for each assumed correlation
-draws_ri_sens %>%
-  mutate(ri_sens_f = fct_rev(factor(print_num(ri_sens)))) %>%
-  ggplot(aes(y = ri_sens_f, x = b_Intercept)) +
-  geom_vline(xintercept = seq(-0.75, 0.75, 0.25), color = "grey90") +
-  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
-  coord_cartesian(xlim = c(-0.75, 0.75), clip = "off") +
-  scale_x_continuous(breaks = seq(-0.75, 0.75, 0.25)) +
-  labs(x = expression("Hedges" ~ italic("g"))) +
-  annotate(
-    "text",
-    label = "Correlation", x = -1.1, y = 7.86, hjust = 0,
-    family = "Helvetica", fontface = "bold", color = "black"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.line.x = element_line(colour = "black"),
-    axis.text.x = element_text(family = "Helvetica", color = "black"),
-    axis.text.y = element_text(
-      family = "Helvetica", color = "black", size = 3.88 * .pt,
-      hjust = 0, vjust = -0.1, margin = margin(l = 20)
-    ),
-    axis.ticks.x = element_line(color = "black"),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank(),
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica", color = "black")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "ri_sens.pdf"), width = 4, height = 5)
+    # Compute ICC
+    var_experiment_ri_sens <- as.matrix(
+      res_ri_sens,
+      variable = "sd_article:experiment__Intercept"
+    )^2
+    var_article_ri_sens <- as.matrix(
+      res_ri_sens,
+      variable = "sd_article__Intercept"
+    )^2
+    var_total_ri_sens <- var_experiment_ri_sens + var_article_ri_sens
+    icc_ri_sens <- var_article_ri_sens / var_total_ri_sens
+    icc_row <- mean_qi(icc_ri_sens) %>%
+      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)
+
+    # Extract summary statistics as a data frame row
+    with(summary(res_ri_sens), bind_rows(fixed, bind_rows(random))) %>%
+      bind_rows(icc_row) %>%
+      transmute(
+        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
+        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
+      ) %>%
+      pivot_wider(names_from = parameter, values_from = Estimate) %>%
+      bind_cols(`Assumed r_i` = print_num(ri_sens), .)
+  }) -> tab_ri_sens
+
+# Save the table
+write_csv(tab_ri_sens, file = here(tables_dir, "ri_sens.csv"))
 ```

### 2022-05-01 code/analysis.Rmd
Delete old methods, simulations

@@
 
-# Methods
-
-## Information sources and search strategy
-
-Article sources:
-
-```{r}
-table(screening$source)
-```
-
-## Selection process
-
-### Interrater agreement
-
-Percent agreement for binary decision (include/exclude):
-
-```{r}
-with(screening, mean(bin_1 == bin_2))
-```
-
-Cohen's kappa for binary decision (include/exclude):
-
-```{r}
-with(screening, psych::cohen.kappa(cbind(bin_1, bin_2)))
-```
-
-Correlation (phi) for binary decision (include/exclude):
-
-```{r}
-with(screening, cor.test(bin_1, bin_2))
-```
-
-Percent agreement for exclusion codes:
-
-```{r}
-with(screening, mean(code_1 == code_2))
-```
-
-Cohen's kappa for exclusion codes:
-
-```{r}
-with(screening, psych::cohen.kappa(cbind(code_1, code_2)))
-```
-
-### Final decisions
-
-Exlucsion codes:
-
-```{r}
-cat("1 = not in english
-2 = not a group study
-3 = not infants
-4 = not typically developing
-5 = no mental rotation
-6 = no within-group statistics
-7 = include paper
-8 = no access or insufficient statistics")
-table(screening$code_final)
-```
-
-### Included experiments
-
-Total number of articles (according to `screening` table):
-
-```{r}
-sum(screening$code_final == 7)
-```
-
-Total number of articles (according to `included` table):
-
-```{r}
-length(unique(included$article))
-```
-
-Total number of experiments:
-
-```{r}
-nrow(included)
-```
-
-Number of non-redundant experiments:
-
-```{r}
-nrow(filter(included, !redundant))
-```
-
-Number of experiments per type of effect size:
-
-```{r}
-table(included$di_type)
-```
-
-Total number of infants across experiments:
-
-```{r}
-sum(included$sample_size)
-```
-
-Descriptive information about the infant samples:
-
-```{r}
-included %>%
-  select(sample_size, age_mean, age_sd, age_min, age_max, female_percent) %>%
-  summary()
-```
-
-Age and gender distributions of all experiments:
-
-```{r}
-included %>%
-  uncount(1e4) %>%
-  mutate(
-    group_text = if_else(is.na(group), "NA", group),
-    id_group = str_c(article, ", ", group_text),
-    id_group_ordered = fct_reorder(id_group, age_mean, .desc = TRUE),
-    age_sd = if_else(!is.na(age_sd), age_sd, 10.),
-    days = rnorm(n(), age_mean, age_sd),
-    months = days / 30.417,
-  ) %>%
-  ggplot(aes(x = months, y = id_group_ordered, fill = female_percent)) +
-  geom_density_ridges() +
-  scale_fill_distiller(palette = "RdYlBu") +
-  coord_cartesian(xlim = c(1, 20), expand = FALSE) +
-  labs(x = "Age (m)", fill = "Percent\nfemale") +
-  theme_minimal() +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    text = element_text(family = "Helvetica", size = 10)
-  )
-```
-
-Sample sizes and ages of all experiments:
-
-```{r}
-included %>%
-  mutate(months = age_mean / 30.417) %>%
-  ggplot(aes(
-    x = months,
-    y = sample_size,
-    size = sample_size,
-    color = female_percent
-  )) +
-  geom_point() +
-  scale_color_viridis_c() +
-  scale_size(guide = "none") +
-  coord_cartesian(xlim = c(0, 16)) +
-  labs(x = "Age (m)", y = "Sample size", color = "Percent\nfemale") +
-  theme_minimal() +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    text = element_text(family = "Helvetica", size = 10)
-  )
-```
-
-```{r, simulation}
-generate_exp <- function(n_boys = 1e3,
-                         n_girls = 1e3,
-                         mean_diff_boys = 0,
-                         mean_diff_girls = 2,
-                         sd_diff_boys = 4,
-                         sd_diff_girls = 4) {
-
-  # Create randomly sampled data for boys and girls
-  # Each element is the mean looking time difference for one infant
-  boys <- rnorm(n_boys, mean_diff_boys, sd_diff_boys)
-  girls <- rnorm(n_girls, mean_diff_girls, sd_diff_girls)
-
-  # Compute separate effect sizes for the two split gender groups
-  d_boys <- mean(boys) / sd(boys)
-  d_girls <- mean(girls) / sd(girls)
-
-  # Compute common effect size for the mixed gender group
-  infants <- c(boys, girls)
-  n_infants <- length(infants)
-  d_infants <- mean(infants) / sd(infants)
-
-  # Return all results for this experiment as a list
-  return(list(
-    n_boys = n_boys,
-    n_girls = n_girls,
-    n_infants = n_infants,
-    d_boys = d_boys,
-    d_girls = d_girls,
-    d_infants = d_infants
-  ))
-}
-
-# Generate random experiments
-n_boys <- 1e3
-n_girls <- 1e3
-n_exps <- 100
-dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
-dat <- do.call(rbind.data.frame, dat)
-dat$article <- paste0("exp_", 1:n_exps)
-
-### MIXED EXPERIMENTS ONLY ###
-
-# Compute sampling variance of the effect size for each study; see
-# https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#w-group-smd
-r_assumed <- .5
-dat$v_d_infants <- with( # Sampling variances of the effect sizes
-  dat, ((2 * (1 - r_assumed)) / n_infants) + (d_infants^2 / (2 * n_infants))
-)
-
-# Fit 3 level meta-analysis
-res_full <- metafor::rma.mv(
-  d_infants, v_d_infants,
-  # random = ~ article | article,
-  data = dat,
-  slab = article
-)
-
-# Check results
-summary(res_full)
-
-### SPLIT EXPERIMENTS ONLY ###
-
-# Put effect sizes for boys and girls into separate rows
-dat_split <- tidyr::pivot_longer(
-  dat,
-  cols = c(d_boys, d_girls),
-  names_to = "gender",
-  values_to = "d_gender"
-)
-
-# Compute sampling variance of the gender-specific effect size
-dat_split$v_d_gender <- with(
-  dat_split, ((2 * (1 - r_assumed)) / n_girls) + (d_gender^2 / (2 * n_girls))
-)
-
-# Use rma.mv to compute MA on d_gender and v_d_gender values
-
-# Repeat 100 times with generate_meta
-
-# Compare mixed gender and split gender MAs
-# Same distribution of meta-analytic effect size?
-# Same variance / standard error?
-# Is the difference significant?
-
-### MIXED/SPLIT GENDER ANALYSIS ###
-
-# Make a percentage of study use mixed vs. split and choose randomly
-# Use different percentages
-# Make split vs. mixed dependent on the observed gender difference
-# Note for this we need to draw study specific effect sizes from a distribution
-
-### MAKE IT MORE REALISTIC ###
-
-# Make sample sizes per study different
-
-# Automate
-generate_meta <- function(n_exps, n_boys, n_girls) {
-
-  # Generate random experiments
-  dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
-  dat <- do.call(rbind.data.frame, dat)
-  dat$article <- paste0("exp_", 1:n_exps)
-
-  # Compute sampling variance of the effect size for each study; see
-  # https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#w-group-smd
-  r_assumed <- .5
-  dat$v_d_infants <- with( # Sampling variances of the effect sizes
-    dat, ((2 * (1 - r_assumed)) / n_infants) + (d_infants^2 / (2 * n_infants))
-  )
-
-  # Fit meta-analysis
-  res_full <- metafor::rma.mv(
-    d_infants, v_d_infants,
-    # random = ~ article | article,
-    data = dat,
-    slab = article
-  )
-
-  # Return coefficients table
-  summ <- summary(res_full)
-  return(coef(summ))
-}
-
-n_metas <- 100
-metas <- replicate(n_metas, generate_meta(100, 100, 100), simplify = FALSE)
-metas <- do.call(rbind.data.frame, metas)
-metas$article <- paste0("meta_", 1:n_metas)
-
-mean(metas$estimate)
-```
-
 # Supplementary information

### 2022-05-01 code/analysis.Rmd
Create shared table for sensitivity analyses

@@
 seq(-0.9, 0.9, by = 0.3) %>%
-  map_dfr(function(ri_sens) {
+  set_names(., str_c("r = ", print_num(.))) %>%
+  map(function(ri_sens) {
 
@@
     # Re-run meta-analysis
-    res_ri_sens <- update(res_brm, newdata = dat_ri_sens, refresh = 0)
+    update(res_brm, newdata = dat_ri_sens, refresh = 0)
+  }) -> res_ri_sens
+
+# Prior sensitivity analysis
+list(
+  "Intercept U(-10,10)" = c(
+    set_prior("uniform(-10, 10)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
+  ),
+  "Intercept N(0,0.2)" = c(
+    set_prior("normal(0, 0.2)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
+  ),
+  "SD U(0,10)" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("uniform(0, 10)", class = "sd")
+  ),
+  "SD Student-t(10,0,0.2)" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("student_t(10, 0, 0.2)", class = "sd")
+  )
+) %>%
+  # Re-run the meta-analysis with different priors
+  map(
+    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
+  ) -> res_prior_sens
+
+# Create a table summarizing all sensitivity analyses
+map2_dfr(
+  c(res_ri_sens, res_prior_sens),
+  c(names(res_ri_sens), names(res_prior_sens)),
+  function(res, name) {
 
     # Compute ICC
-    var_experiment_ri_sens <- as.matrix(
-      res_ri_sens,
+    var_experiment <- as.matrix(
+      res,
       variable = "sd_article:experiment__Intercept"
     )^2
-    var_article_ri_sens <- as.matrix(
-      res_ri_sens,
+    var_article <- as.matrix(
+      res,
       variable = "sd_article__Intercept"
     )^2
-    var_total_ri_sens <- var_experiment_ri_sens + var_article_ri_sens
-    icc_ri_sens <- var_article_ri_sens / var_total_ri_sens
-    icc_row <- mean_qi(icc_ri_sens) %>%
+    var_total <- var_experiment + var_article
+    icc <- var_article / var_total
+    icc_row <- mean_qi(icc) %>%
       rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)
 
-    # Extract summary statistics as a data frame row
-    with(summary(res_ri_sens), bind_rows(fixed, bind_rows(random))) %>%
+    # Create a data frame row of summary statistics
+    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
       bind_rows(icc_row) %>%
@@
       pivot_wider(names_from = parameter, values_from = Estimate) %>%
-      bind_cols(`Assumed r_i` = print_num(ri_sens), .)
-  }) -> tab_ri_sens
+      bind_cols(Simulation = name, .)
+  }
+) -> tab_sens
 
 # Save the table
-write_csv(tab_ri_sens, file = here(tables_dir, "ri_sens.csv"))
+write_csv(tab_sens, file = here(tables_dir, "sensitivity_analysis.csv"))
 ```
-
-```{r, prior_sens}
-# Prior sensitivity analysis
-list(
-  "interept_uninformative" = c(
-    set_prior("uniform(-3, 3)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "interept_informative" = c(
-    set_prior("normal(0, 0.2)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "sd_uninformative" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("uniform(0, 10)", class = "sd", ub = 10)
-  ),
-  "sd_informative" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("student_t(10, 0, 0.2)", class = "sd")
-  )
-) %>%
-  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
-map(res_sens, summary)
-```

### 2022-05-03 code/analysis.Rmd
Convert to papaja + add supplement

@@
 ---
-title: "A meta-analysis of mental rotation ability in the first years of life"
-author: "Alexander Enge, Shreya Kapoor, Anne-Sophie Kieslinger & Michael A. Skeide"
-date: "`r paste('Commit', substr(git2r::commits()[[1]]$sha, 1, 7))`"
-output:
-  pdf_document:
-    latex_engine: xelatex
+title             : "A small male advantage in infant mental rotation"
+shorttitle        : "Infant mental rotation"
+
+author: 
+  - name          : "Alexander Enge"
+    affiliation   : "1,2"
+    corresponding : "yes"
+    address       : "Stephanstraße 1a, 04103 Leipzig"
+    email         : "enge@cbs.mpg.de"
+  - name          : "Shreya Kapoor"
+    affiliation   : "1"
+  - name          : "Anne-Sophie Kieslinger"
+    affiliation   : "1"
+  - name          : "Michael A. Skeide"
+    affiliation   : "1"
+affiliation:
+  - id            : "1"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences"
+  - id            : "2"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
+
+authornote: |
+  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
+
+  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
+
+  The data and code for this study are openly available at ???.
+  We have no conflict of interest to disclose.
+  There were no ethical concerns since we did not collect any new data.
+
+abstract: |
+  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement (Shepard & Metzler, 1971; Hegarty & Kozhevnikov, 1999; Johnshon & Bouchard, 2005).
+  On average, males outperform females in mental rotation tasks (Linn & Petersen 1985, Voyer et al. 1995, Voyer 2011, Maeda & Yoon 2013).
+  When such performance differences emerge during development, however, remains poorly understood (Lauer et al. 2019).
+  Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
+  We robustly found that male infants looked longer at rotated objects than female infants.
+  These findings indicate that the average male cognitive advantage in mental rotation already emerges in the first months of life.
+
+keywords          : "mental rotation, spatial cognition, spatial ability, infants, children, gender, meta-analysis"
+wordcount         : "X"
+
+bibliography      : ["r-references.bib"]
+csl               : "nature.csl"
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : no
+mask              : no
+draft             : no
+
+documentclass     : "apa7"
+classoption       : "man,donotrepeattitle"
+fontsize          : "10pt"
+output            : papaja::apa6_pdf
+header-includes:
+  - \geometry{a4paper}
+  - \raggedbottom
+  - \usepackage[all]{nowidow}
+  - \usepackage{setspace}
+  - \AtBeginEnvironment{tabular}{\doublespacing}
+  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
+  - \captionsetup{font={stretch=1}, belowskip=15pt}
 ---
@@
 # Load packages
+library(papaja)
 library(here)
@@
 knitr::opts_chunk$set(
-  echo = TRUE,
+  include = FALSE,
   message = FALSE,
@@
   fig.width = 7.5,
-  out.width = "100%"
+  out.width = "100%",
+  warning = FALSE
 )
@@
     ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
-    gi = di * ji
+    gi = di * ji,
+
+    # Recode gender as a categorical (factor) variable for meta-regression
+    gender = case_when(
+      female_percent == 1.0 ~ "Female",
+      female_percent == 0.0 ~ "Male",
+      TRUE ~ "Mixed"
+    ) %>% factor(levels = c("Mixed", "Female", "Male")),
+
+    # Recode mean sample age in years (centered) for meta-regression
+    age = age_mean / 365.25,
+    age_c = age - mean(age, na.rm = TRUE),
+    age_sd = age_sd / 365.25,
+
+    # Recode task type as a categorical (factor) variale for meta-regression
+    task = factor(task, levels = c("Habituation", "VoE")),
+
+    # Combine gender and task into one column for plotting
+    gender_task = factor(
+      str_c(gender, task, sep = ", "),
+      levels = c(
+        "Female, Habituation",
+        "Male, Habituation",
+        "Mixed, Habituation",
+        "Mixed, VoE"
+      )
+    )
   ) %>%
@@
 
-```{r, results_literature_search}
-# Number of experiments
-nrow(dat)
+The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life (Johnson & Moore 2020, Moore & Johnson 2020).
+Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement (Shepard & Metzler, 1971; Hegarty & Kozhevnikov, 1999; Johnshon & Bouchard, 2005).
 
-# Number of infants
-sum(dat$sample_size)
+Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average (Linn & Petersen 1985, Voyer et al. 1995, Voyer 2011, Maeda & Yoon 2013).
+Effect sizes of this difference, however, are heterogeneous and often only medium (mean weighted g = 0.37–0.73).
+Interestingly, a recent meta-analysis in 3-17-year-old children and adolescents suggests even only a small-to-medium male advantage (mean weighted g = 0.39) (Lauer et al. 2019).
+Whether gender differences in mental rotation performance already emerge during infancy remains unknown.
 
-# Age range in months
-min(dat$age_min, na.rm = TRUE) / 30.417
-max(dat$age_max, na.rm = TRUE) / 30.417
+In the present study we meta-analyzed 59 effect sizes derived from looking times in mental rotation tasks conducted by 1,798 infants (47.5% female) aged 3 to 16 months (mean = 7 months 14 days).
+All tasks were embedded either into habituation experiments (40) or violation of expectation experiments (19) (Fantz 1964; Baillargeon et al. 1985).
+These experiments comprised real world stimuli (e.g., toy objects, Antrilli & Wang, 2016), three-dimensional digital stimuli (e.g., cube figures; Moore & Johnson, 2008), or two-dimensional digital stimuli (e.g., digits; Quinn & Liben, 2008).
+In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object.
+Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation.
+In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle.
+Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle.
+Subsequently, the object disappeared behind an occluder. Finally, the occluder was removed and either the object or its mirror object were shown.
+Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle.
+In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
 
-# Mean age in months
-sum((dat$age_mean * dat$sample_size)) / sum(dat$sample_size) / 30.417
-
-# Number of experiments per task type
-table(dat$task)
-```
+Following previous work in older populations we hypothesized that looking times in mental rotation experiments are on average significantly longer in male compared to female infants.
+Effect sizes were assumed to be small.
 
@@
 
-## Mental rotation ability
+## Mental rotation performance
 
 ```{r, meta_analysis}
-# Three-level model
-res_ml <- rma.mv(
-  gi, vi,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_ml)
-# forest(res_ml)
-
-# Check heterogeneity
-(i2 <- dmetar::var.comp(res_ml))
-# plot(i2)
-
-# Check share of variance at each level of the model
-round(res_ml$sigma2[1] / sum(res_ml$sigma2), 3) # Between-article (ICC)
-round(res_ml$sigma2[2] / sum(res_ml$sigma2), 3) # Within-article (between-exp.)
-
-# # Profile likelihodd plots for checking that REML has converged
-# profile(res_ml)
-```
-
-```{r, meta_analysis_bayes}
 # Specify priors
@@
 n_iter <- 20000
+n_warmup <- 1000
+n_chains <- 4
 res_prior <- brm(
@@
   save_pars = save_pars(all = TRUE),
-  chains = 4,
+  chains = n_chains,
   iter = n_iter,
-  warmup = 1000,
-  cores = 4,
-  control = list(adapt_delta = 0.99)
+  warmup = n_warmup,
+  cores = n_chains,
+  control = list(adapt_delta = 0.99),
+  file = here("results", "models", "res_prior")
 )
@@
 # Run Bayesian multilevel model
-res_brm <- update(res_prior, sample_prior = FALSE)
+res_brm <- update(
+  res_prior,
+  sample_prior = FALSE,
+  file = here("results", "models", "res_brm")
+)
 summary(res_brm)
@@
 
-# Summarise fixed effects (incl. Bayes factors)
-describe_posterior(
-  res_brm,
-  centrality = "mean", ci = 0.95, ci_method = "ETI",
-  test = c("p_direction", "rope", "bayesfactor"),
-  rope_range = c(-0.1, 0.1)
-)
+# # Summarise fixed effects (incl. Bayes factors)
+# describe_posterior(
+#   res_brm,
+#   centrality = "mean", ci = 0.95, ci_method = "ETI",
+#   test = c("p_direction", "rope", "bayesfactor"),
+#   rope_range = c(-0.1, 0.1)
+# )
 
@@
 
-```{r, fig_forest}
+For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times between novel and familiar rotated objects.
+Based on this effect size index we tested if there was evidence that infants can perform mental rotation.
+Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of g = 0.26, 95% credible interval (CrI) [0.12, 0.41] (Fig.
+1).
+The probability for this effect being greater than zero was 99.9%.
+The heterogeneity of effect sizes was $sigma$2Experiment = 0.03, 95% CrI [0.00, 0.12], at the experiment level and $sigma$2Article = 0.17, 95% CrI [0.09, 0.29] at the article level.
+Therefore, approximately 86.7% of the heterogeneity between effect sizes was attributable to differences between experiments and 13.3% was attributable to differences between articles.
+
+```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
 # Helper functions for printing confidence intervals
@@
 
-```{r, tab_within}
-# Helper functions to re-format age in years and/or months
-format_days_months <- function(days) {
-  days_per_month <- 30.417
-  months <- days %/% days_per_month
-  days_left <- round(days - months * days_per_month)
-  str <- paste0(as.character(months), "m ", as.character(days_left), "d")
-  str[is.na(days)] <- NA
-  return(str)
-}
+(ref:fig1-caption) Mental rotation performance.
+A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
+White squares indicate the effect sizes (Hedges’ g) for infants’ mental rotation ability in all individual experiments and black lines their 95% confidence intervals.
+Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
+Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
+The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI and its posterior distribution (gray curve).
 
-# Save within-analysis table of experiments
-dat %>%
-  mutate(
-    age_mean = format_days_months(age_mean),
-    age_sd = str_c(as.character(round(age_sd)), "d"),
-  ) %>%
-  transmute(
-    Article = if_else(article == lag(article, default = ""), "", article),
-    Experiment = group_long,
-    `Sample size` = sample_size,
-    `Females` = round(female_percent * sample_size),
-    Age = str_c(age_mean, "±", age_sd, sep = " "),
-    Task = task,
-    `Stimulus type` = str_to_sentence(stimuli_presentation),
-    `Stimulus dimensions` = stimuli_dimensions
-  ) %>%
-  write_csv(
-    file = here(tables_dir, "within_experiments.csv"),
-    na = "n/a"
-  )
-```
-
-## Moderator variables
+## Effects of gender, age, and task type
 
 ```{r, meta_regression}
-# Recode predictor variables for meta-regression and plotting
-dat %>%
-  mutate(
+# Set numerical contrasts for factor variables
+contrasts(dat$gender) <- MASS::contr.sdif(3)
+contrasts(dat$task) <- MASS::contr.sdif(2)
 
-    # Gender as a categorical (factor) variable
-    gender = case_when(
-      female_percent == 1.0 ~ "Female",
-      female_percent == 0.0 ~ "Male",
-      TRUE ~ "Mixed"
-    ) %>% factor(levels = c("Mixed", "Female", "Male")),
-
-    # Mean sample age in years, centered around the mean
-    age = age_mean / 365.25,
-    age_c = age - mean(age, na.rm = TRUE),
-    age_sd = age_sd / 365.25,
-
-    # Task type as a categorical (factor) variale
-    task = factor(task, levels = c("Habituation", "VoE")),
-
-    # Combine gender and task into one column for plotting
-    gender_task = factor(
-      str_c(gender, task, sep = ", "),
-      levels = c(
-        "Female, Habituation",
-        "Male, Habituation",
-        "Mixed, Habituation",
-        "Mixed, VoE"
-      )
-    )
-  ) -> dat_reg
-
-# Set numerical contrasts for factor variables
-contrasts(dat_reg$gender) <- MASS::contr.sdif(3)
-contrasts(dat_reg$task) <- MASS::contr.sdif(2)
-
-# Meta-regression with gender, age, and task
-res_reg <- rma.mv(
-  gi, vi,
-  mods = ~ gender * age_c + task,
-  random = ~ 1 | article / experiment,
-  data = dat_reg,
-  slab = experiment
-)
-print(res_reg)
-# forest(res_full)
-```
-
-```{r, meta_regression_bayes}
 # Specify priors
@@
     (1 | article / experiment),
-  data = dat_reg,
+  data = dat,
   prior = prior_c,
@@
   save_pars = save_pars(all = TRUE),
-  chains = 4,
+  chains = n_chains,
   iter = n_iter,
-  warmup = 1000,
-  cores = 4,
-  control = list(adapt_delta = 0.99)
+  warmup = n_warmup,
+  cores = n_chains,
+  control = list(adapt_delta = 0.99),
+  file = here("results", "models", "res_prior_reg")
 )
@@
 # Run Bayesian multilevel model
-res_brm_reg <- update(res_prior_reg, sample_prior = FALSE)
+res_brm_reg <- update(
+  res_prior_reg,
+  sample_prior = FALSE,
+  file = here("results", "models", "res_brm_reg")
+)
 summary(res_brm_reg)
@@
 
-```{r, fig_regression}
+We next performed a meta-regression analysis to explain the heterogeneity of effect sizes and to test if the age of the gender of the infants, their age, and/or the type of mental rotation task influenced mental rotation performance (Fig.
+2).
+Indeed, there was evidence that experiments with all-male samples obtained better mental rotation performance than experiments with all-female samples, b = 0.48, 95% CrI [0.06, 0.91].
+The probability for this effect being greater than zero was 98.5%.
+Experiments with mixed-gender samples performed only slightly better than experiments than all-female samples, b = 0.13, 95% CrI [-0.20, 0.52].
+The probability for this effect being greater than zero was 75.4%.
+There was no evidence that the mean age of the infants influenced mental rotation performance, with a change per year of b = 0.05, 95% [-0.58, 0.68].
+Similarly, there was no evidence for an interaction between gender and age.
+Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, b = 0.26, 95% [-0.08, 0.58].
+The probability for this effect being greater than zero was 93.5%.
+
+```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
 # Get draws from the posterior distribution
@@
   res_brm_reg,
-  dat_reg,
-  ndraws = NULL,
+  dat,
+  ndraws = NA,
   re_formula = NA
 )
-
-# Summarise to obtain HPDIs
-draws_reg_hdi <- mean_qi(draws_reg)
 
@@
 # Regression plot
-dat_reg %>%
+dat %>%
   ggplot(aes(x = age * 12, y = gi)) +
@@
 
+(ref:fig2-caption) Effects of gender, age, and task task.
+a Open squares show the effect size (Hedges’ g) for infants’ mental rotation ability in each of 59 individual experiments, color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
+Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 95% and 50% credible interval (CrI).
+b Fixed effect estimates from the Bayesian three-level meta-regression model are shown as black dots together with their 95% (thin black lines) and 50% (thick black lines) CrI.
+Gray curves show the posterior distribution for each effect.
+
 # Supplementary information
 
-```{r, ri_assumed_sens}
+```{r, tabs1, include=TRUE}
+# Helper functions to re-format age in years and/or months
+format_days_months <- function(days) {
+  days_per_month <- 30.417
+  months <- days %/% days_per_month
+  days_left <- round(days - months * days_per_month)
+  str <- paste0(as.character(months), "m ", as.character(days_left), "d")
+  str[is.na(days)] <- NA
+  return(str)
+}
+
+# Save within-analysis table of experiments
+dat %>%
+  mutate(
+    age_mean = format_days_months(age_mean),
+    age_sd = str_c(as.character(round(age_sd)), "d"),
+  ) %>%
+  transmute(
+    Article = if_else(article == lag(article, default = ""), "", article),
+    Experiment = group_long,
+    `Sample size` = sample_size,
+    `Females` = round(female_percent * sample_size),
+    Age = str_c(age_mean, "±", age_sd, sep = " "),
+    Task = task,
+    `Stimulus type` = str_to_sentence(stimuli_presentation),
+    `Stimulus dimensions` = stimuli_dimensions
+  ) -> tabS1
+
+# Save the table
+write_csv(tabS1, file = here(tables_dir, "within_experiments.csv"), na = "n/a")
+
+# Display the table
+apa_table(
+  tabS1,
+  caption = "Experiments included in the main analysis", label = "S1",
+  landscape = TRUE
+)
+```
+
+```{r, figs2, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs2-caption)"}
+# Extract convergence statistics from results
+conv_stats <- with(summary(res_brm), tibble(
+  parameter = c(
+    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
+  ),
+  name_expr = c(
+    "Hedges ~ italic(g)", "italic(sigma)[article]", "italic(sigma)[experiment]"
+  ),
+  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
+  bulk_ess = round(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
+  tail_ess = round(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
+  r_hat_expr = str_c("italic(R)[hat] == ", r_hat),
+  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == ", bulk_ess),
+  tail_ess_expr = str_c("italic(N)[eff(tail)] == ", tail_ess),
+  y_pos = c(0.7, 0.75, 0.8)
+))
+
+# Create trace plot
+n_draws <- n_iter - n_warmup
+bayesplot::mcmc_trace(
+  res_brm,
+  pars = conv_stats$parameter, facet_args = list(ncol = 1)
+) +
+  geom_text(
+    aes(y = 0.45, label = name_expr, color = NA),
+    conv_stats,
+    y = 0.45, x = -800, color = "black", parse = TRUE, angle = 90
+  ) +
+  geom_text(
+    aes(y = y_pos, label = r_hat_expr, color = NA),
+    conv_stats,
+    x = 13000, hjust = 1, color = "black", parse = TRUE,
+  ) +
+  geom_text(
+    aes(y = y_pos, label = bulk_ess_expr, color = NA),
+    conv_stats,
+    x = 16000, hjust = 1, color = "black", parse = TRUE,
+  ) +
+  geom_text(
+    aes(y = y_pos, label = tail_ess_expr, color = NA),
+    conv_stats,
+    x = 19000, hjust = 1, color = "black", parse = TRUE,
+  ) +
+  labs(x = "Sample number", y = NULL, color = "MCMC\nchain") +
+  coord_cartesian(expand = FALSE, clip = "off") +
+  scale_x_continuous(limits = c(0, n_draws), breaks = seq(0, n_draws, 2000)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  scale_color_grey(start = 0.0, end = 0.9) +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    plot.margin = margin(t = 10, l = 25),
+    strip.background = element_blank(),
+    strip.text = element_blank(),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "trace.pdf"), width = 12, height = 6)
+```
+
+(ref:figs2-caption) Convergence checks.
+
+```{r, frequentist_results}
+# Three-level model
+res_ml <- rma.mv(
+  gi, vi,
+  random = ~ 1 | article / experiment,
+  data = dat,
+  slab = experiment
+)
+print(res_ml)
+# forest(res_ml)
+
+# Check share of variance at each level of the model
+round(res_ml$sigma2[1] / sum(res_ml$sigma2), 3) # Between-article (ICC)
+round(res_ml$sigma2[2] / sum(res_ml$sigma2), 3) # Within-article (between-exp.)
+
+# # Profile likelihodd plots for checking that REML has converged
+# profile(res_ml)
+
+# Meta-regression with gender, age, and task
+res_reg <- rma.mv(
+  gi, vi,
+  mods = ~ gender * age_c + task,
+  random = ~ 1 | article / experiment,
+  data = dat,
+  slab = experiment
+)
+print(res_reg)
+# forest(res_full)
+```
+
+```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
 # Compute empirical estimate of the correlation between dependent samples

### 2022-05-03 code/analysis.Rmd
Add table for frequentist results

@@
 # forest(res_full)
+
+# Extract standard deviations and ICCs
+vars_ml <- list(matrix())
+
+# Export results as a table
+map2_dfr(
+  c("Meta-analysis", "Meta-regression"),
+  list(res_ml, res_reg),
+  function(name, res) {
+    # Intercept / regression weights
+    tibble(
+      Model = c(name, rep(NA, length(res$b) - 1)),
+      Parameter = rownames(res$b),
+      Estimate = print_num(as.numeric(res$b)),
+      SE = print_num(res$se),
+      z = print_num(res$zval),
+      p = print_num(res$pval, digits = 3),
+      ci_lower = print_num(res$ci.lb),
+      ci_upper = print_num(res$ci.ub)
+    ) %>%
+      # Re-format confidence interval
+      mutate(
+        `95% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
+        .keep = "unused"
+      ) %>%
+      # Add variances
+      bind_rows(tibble(
+        Parameter = res$s.name,
+        Estimate = print_num(res$sigma2)
+      ))
+  }
+) %>%
+  mutate(
+    Parameter = c(
+      "Hedges' g",
+      "s2article",
+      "s2experiment",
+      "Intercept",
+      "Female - mixed",
+      "Male - female",
+      "Age (per year)",
+      "Habituation - VoE",
+      "(Female - mixed) × age",
+      "(Male - female) × age",
+      "s2article",
+      "s2experiment"
+    )
+  ) -> tab_freq
+
+# Save the table
+write_csv(tab_freq, file = here(tables_dir, "frequentist_results.csv"), na = "")
 ```

### 2022-05-03 code/analysis.Rmd
Update manuscript text

@@
   Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement (Shepard & Metzler, 1971; Hegarty & Kozhevnikov, 1999; Johnshon & Bouchard, 2005).
-  On average, males outperform females in mental rotation tasks (Linn & Petersen 1985, Voyer et al. 1995, Voyer 2011, Maeda & Yoon 2013).
-  When such performance differences emerge during development, however, remains poorly understood (Lauer et al. 2019).
+On average, males solve mental rotation tasks slightly faster than females (Linn & Petersen 1985, Voyer et al.
+1995, Voyer 2011, Maeda & Yoon 2013).
+When such behavioral differences emerge during development, however, remains poorly understood (Lauer et al.
+2019).
 Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
-  We robustly found that male infants looked longer at rotated objects than female infants.
-  These findings indicate that the average male cognitive advantage in mental rotation already emerges in the first months of life.
+We robustly found that male infants looked longer at novel rotated objects than female infants.
+The effect size of this average difference was small and did not change with age.
+These findings indicate that gender differences in mental rotation are already present in the first months of life.
 
@@
   - \usepackage[all]{nowidow}
+  - \usepackage{makecell}
   - \usepackage{setspace}
-  - \AtBeginEnvironment{tabular}{\doublespacing}
-  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
+  - \renewcommand{\arraystretch}{1.0}
   - \captionsetup{font={stretch=1}, belowskip=15pt}
@@
 
-Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average (Linn & Petersen 1985, Voyer et al. 1995, Voyer 2011, Maeda & Yoon 2013).
+Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average (Linn & Petersen 1985, Voyer et al.
+1995, Voyer 2011, Maeda & Yoon 2013).
 Effect sizes of this difference, however, are heterogeneous and often only medium (mean weighted g = 0.37–0.73).
-Interestingly, a recent meta-analysis in 3-17-year-old children and adolescents suggests even only a small-to-medium male advantage (mean weighted g = 0.39) (Lauer et al. 2019).
-Whether gender differences in mental rotation performance already emerge during infancy remains unknown.
-
-In the present study we meta-analyzed 59 effect sizes derived from looking times in mental rotation tasks conducted by 1,798 infants (47.5% female) aged 3 to 16 months (mean = 7 months 14 days).
-All tasks were embedded either into habituation experiments (40) or violation of expectation experiments (19) (Fantz 1964; Baillargeon et al. 1985).
+Interestingly, a recent meta-analysis in 3-17-year-old children and adolescents suggests even only a small-to-medium difference (mean weighted g = 0.39) (Lauer et al.
+2019).
+Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
+
+In the present study we meta-analyzed 59 effect sizes derived from looking times in mental rotation tasks conducted by 1,798 infants (47.5% female) aged 3 to 16 months (mean age of 7 months 14 days).
+All tasks were embedded either into habituation experiments (40) or violation of expectation experiments (19) (Fantz 1964; Baillargeon et al.
+1985).
 These experiments comprised real world stimuli (e.g., toy objects, Antrilli & Wang, 2016), three-dimensional digital stimuli (e.g., cube figures; Moore & Johnson, 2008), or two-dimensional digital stimuli (e.g., digits; Quinn & Liben, 2008).
@@
 Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle.
-Subsequently, the object disappeared behind an occluder. Finally, the occluder was removed and either the object or its mirror object were shown.
+Subsequently, the object disappeared behind an occluder.
+Finally, the occluder was removed and either the object or its mirror object were shown.
 Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle.
 In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
-
 Following previous work in older populations we hypothesized that looking times in mental rotation experiments are on average significantly longer in male compared to female infants.
@@
 
-For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times between novel and familiar rotated objects.
-Based on this effect size index we tested if there was evidence that infants can perform mental rotation.
+For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects.
+Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
 Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of g = 0.26, 95% credible interval (CrI) [0.12, 0.41] (Fig.
@@
 A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
-White squares indicate the effect sizes (Hedges’ g) for infants’ mental rotation ability in all individual experiments and black lines their 95% confidence intervals.
-Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
-Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
-The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI and its posterior distribution (gray curve).
+White squares depict the effect sizes (Hedges’ g) for infants’ mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
+Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI).
+These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the model.
+The last line shows the meta-analytic effect size (black dot) together with its 95% CrI and its posterior distribution (gray curve).
 
@@
 
-# Summarise fixed effects (incl. Bayes factors)
-describe_posterior(
-  res_brm_reg,
-  centrality = "mean", ci = 0.95, ci_method = "ETI",
-  test = c("p_direction", "rope", "bayesfactor"),
-  rope_range = c(-0.1, 0.1)
-)
+# # Summarise fixed effects (incl. Bayes factors)
+# describe_posterior(
+#   res_brm_reg,
+#   centrality = "mean", ci = 0.95, ci_method = "ETI",
+#   test = c("p_direction", "rope", "bayesfactor"),
+#   rope_range = c(-0.1, 0.1)
+# )
 
@@
 
-We next performed a meta-regression analysis to explain the heterogeneity of effect sizes and to test if the age of the gender of the infants, their age, and/or the type of mental rotation task influenced mental rotation performance (Fig.
+As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig.
 2).
-Indeed, there was evidence that experiments with all-male samples obtained better mental rotation performance than experiments with all-female samples, b = 0.48, 95% CrI [0.06, 0.91].
-The probability for this effect being greater than zero was 98.5%.
-Experiments with mixed-gender samples performed only slightly better than experiments than all-female samples, b = 0.13, 95% CrI [-0.20, 0.52].
-The probability for this effect being greater than zero was 75.4%.
-There was no evidence that the mean age of the infants influenced mental rotation performance, with a change per year of b = 0.05, 95% [-0.58, 0.68].
-Similarly, there was no evidence for an interaction between gender and age.
+Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, b = 0.48, 95% CrI [0.06, 0.91].
+The probability for this effect being larger than zero was 98.5%.
+We found no difference between mixed-gender and all-female samples, b = 0.13, 95% CrI [-0.20, 0.52] (75.4% probability of an effect larger than zero).
+Additionally, mean age was not related to mental rotation performance, with a change per year of b = 0.05, 95% [-0.58, 0.68].
+We also did not detect an interaction between gender and age ([females - mixed] × age: b = 0.02, 95% CrI [-0.81, 0.84]; [males - females] × age: b = 0.06, 95% CrI [-0.84, 0.96]).
 Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, b = 0.26, 95% [-0.08, 0.58].
@@
   dat,
-  ndraws = NA,
+  ndraws = NULL,
   re_formula = NA
@@
 
-(ref:fig2-caption) Effects of gender, age, and task task.
-a Open squares show the effect size (Hedges’ g) for infants’ mental rotation ability in each of 59 individual experiments, color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
+(ref:fig2-caption) Effects of gender, age, and task.
+a Squares show the effect size (Hedges’ g) for infants’ mental rotation performance in each of the 59 individual experiments.
+Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
 Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 95% and 50% credible interval (CrI).
-b Fixed effect estimates from the Bayesian three-level meta-regression model are shown as black dots together with their 95% (thin black lines) and 50% (thick black lines) CrI.
-Gray curves show the posterior distribution for each effect.
+b Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 95% Crl (thin black lines) and 50% Crl (thick black lines).
+Gray curves indicate the posterior distribution for each effect.
+
+To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported within each article by the original authors.
+Our additional analysis revealed a meta-analytic effect size of g = 0.20, 95% Crl [0.03, 0.38] (Supplementary Fig.
+1) and a probability of this effect being greater than zero of 98.9%.
+The heterogeneity of effect sizes was $sigma$2Experiment = 0.01, 95% CrI [0.00, 0.07], at the experiment level, and $sigma$2Article = 0.02, 95% CrI [0.00, 0.10] at the article level.
+This means that 56.1% of the total variance can be attributed to differences between articles and 43.1% to differences within articles.
+
+## Evaluation of publication bias
+
+By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig.
+3).
+Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero (t(57) = 3.37, p = 0.001).
+Nevertheless, a jackknife leave-one-out analysis confirmed that the current results are robust to the effects of individual studies (see Supplementary Table 5).
+
+# Discussion
+
+We analyzed looking times during mental rotation in 1,798 infants ranging from 3 to 16 months of age.
+To this end, we scrutinized the robustness of 59 experimental effect sizes.
+We found that male infants looked on average slightly longer at novel rotated objects compared to female infants.
+This effect was small and unrelated to age in the current range.
+
+## Effect size estimates
+
+We interpret the meta-regression-based estimate of the gender difference (b = 0.48, b = $Delta$g ) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
+The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference more likely report separate effect sizes for males and females.
+In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment (g = .20) can be viewed as a lower bound of the true effect size.
+This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences some of these experiments will have found a non-zero gender difference but the size of this effect was not reported because of a lack of power to render it statistically significant.
+
+## Gender differences
+
+The gender differences observed here remain to be explained by interacting genetic and environmental factors that are largely unknown.
+To the best of our knowledge, there are currently no genetic association or gene-environment interaction studies with a focus on mental rotation.
+Nevertheless, it is documented that genetic contributions to behavioral variance in mental rotation are substantially smaller than unique non-shared environmental contributions both in male and female adults (Shakeshaft et al.
+2016).
+Whether this observation also applies to infants remains to be explored.
+
+One recent study on 5-6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work (Constantinescu et al.
+2018).
+As far as we know, potentially mediating and moderating factors that could already be operational in infancy, however, are not yet empirically established.
+In a similar vein, while mental rotation training has small-to-medium post-test effects in children, it is unclear whether it can remove gender differences and be adapted to infants Uttal et al.
+(2013).
+
+Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance (Toivainen et al.
+2018, Constantinescu et al.
+2018, Erdmann et al.
+2019).
+Possible biological developmental pathways, however, bridging the gap from hormonal to behavioral differences are currently far from understood.
+
+## Additional factors
+
+A number of additional factors have been associated with individual differences in infant mental rotation performance.
+For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task (Möhring and Frick 2013; Schwarzer et al.
+2013b; Slone et al.
+2018).
+This relation also applies to previous experience with manually rotating toys (Schwarzer et al.
+2013b).
+While these preliminary results require replication they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g.
+Ausubel 1968; Bradley & Bryant 1983; Halberda et al.
+2008).
+Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control and crawling skills (Schwarzer et al.
+2013a; Schwarzer et al.
+2013b).
+
+# Conclusion
+
+The present study robustly revealed that male infants look slightly but significantly longer at novel rotated objects than female infants.
+Thus, on average, males outperform females in mental rotation already in the first months of life.
+
+# Methods
+
+## Protocol
+
+We used established PRISMA 2020 (Preferred Reporting Items for Systematic reviews and Meta-Analyses; Page et al., 2021) guidelines to conduct this meta-analysis.
+Fig.
+4 presents the PRISMA flowchart and Supplementary Table 2 contains the PRISMA checklist.
+
+```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", out.width="50%"}
+# Include the flowchart (created with MS PowerPoint)
+knitr::include_graphics("results/figures/flowchart.pdf")
+```
+
+(ref:fig4-caption) Literature search and selection process.
+We searched four online databases as well as review articles and reference sections to identify articles that reported mental rotation experiments in infants.
+Experiments from these articles were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
+Redundant articles that reported the same experiment(s) as another article were excluded.
+aAdditional reasons for excluding articles were an experimental paradigm that differed substantially compared to all other articles (1 article) and a sample of infants that was substantially older compared to all other articles (1 article).
+
+## Eligibility criteria
+
+Articles needed to fulfill six criteria for being included in the meta-analysis: (1) The article was written English or German; (2) The article includes results from a group study with human participants (excluding review articles, meta-analyses, case studies, and animal studies); (3) These participants include at least one group of infants (mean age between 0.0 and 3.0 years); (4) Infants had no preterm status or clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see below).
+We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
+
+## Information sources and search strategy
+
+We entered the search terms (“mental rotation” OR “mental transformation” OR “spatial rotation” OR “spatial transformation” OR “spatial ability” OR “spatial skills”) AND (“infant” OR “infants” OR “infanthood” OR “toddler” OR “toddlers” OR “toddlerhood” OR “child” OR “children” OR “childhood” OR “month” OR “months”) into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, ProQuest Dissertations & Theses Global).
+All database queries were completed on December 6, 2021.
+We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
+This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Figure 1).
+We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills (Frick et al., 2014; Johnson & Moore, 2020; Kubicek & Schwarzer, 2018; Lauer et al., 2019; Linn & Petersen, 1985; Moore & Johnson, 2020; Uttal et al., 2013; Voyer et al., 1995; Yang et al., 2020).
+Of these, 34 had not been covered by the database search.
+We also identified 94 articles by screening the reference sections of all articles that had been included after the first pass of the selection process.
+Of these, 49 had not been covered by the database search.
+We thus screened 2,037 unique articles in total.
+
+## Selection process
+
+Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
+Interrater agreement for the binary decision to include versus exclude an article was 98.5% ($Kappa$w [Cohen’s weighted kappa] = 0.67, 95% CI [0.55, 0.78]).
+Interrater agreement for the specific eligibility criteria were 88.2% ($Kappa$w = 0.72, 95% CI [0.40, 1.00]).
+Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
+One article (Mash et al., 2007) was excluded because the authors used a unique mental rotation paradigm that was not comparable to that used in the other articles.
+One article (Pedrett et al., 2020) was excluded because the average age of the infants (30.7 months) was almost twice as high as that of the next article (15.8 months), z = ???
+compared to all articles.
+We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
+This procedure led to a total of 23 articles being included in the meta-analysis (Fig.
+4).
+
+Many of these articles consisted of multiple experiments, e.g., using different variations of the mental rotation task or different subpopulations of infants.
+We included all of these experiments in the meta-analysis and accounted for the dependencies between them by means of multilevel modeling with by-article random effects (see below).
+However, we excluded experiments if there was insufficient information to compute a standardized effect size (see below).
+Whenever an article reported separate effect sizes for boys and girls—or other subgroups like crawling and non-crawling infants)—but also an effect size combining these groups, we only included the combined effect size.
+We dropped effect sizes that were clearly based on the same data but reported in different articles.
+This procedure led to a total of 59 experiments being included in the meta-analysis (Supplementary Table 1).
+
+## Data collection process and items
+
+Outcome measures and other relevant variables were extracted from each article by one of three raters and verified by a second rater.
+Outcome measures were any summary statistic (Table 1) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
+Other extracted variables included, if available, the sample size, the number of girls and boys, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habitation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table 1).
+
+```{r, tab1, include=TRUE}
+print("Nice table goes here")
+```
+
+No study investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
+
+## Effect size measures
+
+One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ g) using the formulas provided in Table 1.
+The sampling variance Var_g of the outcome measure g for each experiment was computed using the formula provided by Goulet-Pelletier & Cousineau (2018):
+
+v = (df(df - 2)) * ((2 * (1 - r)) / n) * (1 + g^2 * (n / (2 * (1 - r)))) - (g^2 / j^2)
+
+where n is the sample size of the experiment, df are the degrees of freedom (with df=2*(n-1)), r is the correlation between the two dependent measures in the experiment, and j is the correction factor for small samples as described in Table 1.
+The correlation r was not reported in any of the original articles.
+We therefore always assumed a correlation of r = .50 to make our analysis comparable to standard (between-group) meta-analyses (Lakens, 2013) and because we were able to infer an average correlation of r ≈ .50 from a subsample of articles which provided sufficient information (Supplementary Methods 1).
+A sensitivity analysis indicated that changing the assumed correlation to values from r = -.90 via r = .00 to r = .90 had no meaningful impact on the meta-analytic effect size (Supplementary Table 3).
+
+For the meta-analysis of gender differences within each article, effect sizes were computed according to the following formulas in Table yy, and redundant groups were excluded from the analysis.
+
+```{r, tab2, include=TRUE}
+print("Nice table goes here")
+```
+
+Furthermore, the sampling variance was computed according to the following equation:
+
+$sigma$between group = dfdf -2   2ñ1 + g2ñ2- g2J2
+
+Where ñ is the harmonic mean of the group sizes  and   ñ = nmale  nmalenfemale + nmale.
+A sensitivity analysis reported in supplementary xxx highlights the stability of the effect size computed using the Bayesian meta analysis.
+
+## Bayesian meta-analysis
+
+We synthesized the effect sizes and their sampling variances using a Bayesian multilevel model.
+This model had three levels, with infant participants nested in experiments and experiments nested in articles (Van den Noortgate et al., 2013).
+We used a weakly-informative normal (N(0,1)) prior for the meta-analytic effect size and a weakly-informative half-Cauchy (HC(0, 0.3)) prior for all standard deviations (Williams et al., 2018).
+A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 3).
+All Bayesian models were fitted using the brms package (Version 2.16.3; Bürkner, 2017, 2018) in R (Version 4.1.2; R Core Team, 2021) and the Stan language (Version 2.29.2; Stan Development Team, 2022).
+Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling 10,000 draws (including 5,000 warm-up draws) from the posterior distribution.
+To verify the convergence of the Markov chains, we examined rank plots as well as the R_{hat} and N_{eff} statistics (Vehtari et al., 2021; Supplementary Fig.
+1).
+For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results (Kruschke, 2015).
+
+## Bayesian meta-regression
+
+We examined the influence of three moderator variables on the mental rotation outcomes across studies, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
+Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts so that we could compare all-female versus mixed samples and all-male samples versus all-female samples (Schad et al., 2020).
+Age was coded as a continuous predictor in years and centered by subtracting the average across all studies.
+Task was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast (Schad et al., 2020).
+We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender task type (i.e., [female - mixed] × age and [male - female] × age) into a Bayesian meta-regression model.
+This model used the same random effects structure and sampling and sampling parameters as described above.
+
+## Frequentist meta-analysis
+
+We verified the results from our Bayesian analyses using classical (frequentist) meta-analysis and meta-regression.
+We used the metafor package (Version 3.0.2; Viechtbauer, 2010) in R to specify the same three-level models as described above but dropping the Bayesian priors (Supplementary Table 3).
+The models were fitted using restricted maximum likelihood estimation (REML).
+To verify that REML converged on the correct estimates, we examined profile likelihood plots for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; see Supplementary Fig.
+2).
+
+## Reporting bias and certainty assessment
+
+We assessed publication bias by means of a funnel plot and Egger regression test (Egger et al.
+1997).
+We adapted code from the R package metaviz (Version 0.3.1; Kossmeier et al., 2020) to produce the funnel plot and used the R package metafor for the Egger regression test.
+We examined heterogeneity in our study samples by means of a jackknife leave-one-out-analysis (Gee 2005).
+We adapted code from the bootstrap R package (Version 2019.6; Scott Kostyshak et al., 2019) to fit the Bayesian model repeatedly to our study samples, leaving out one experiment sample for every iteration.
+To take into account the variance inherent in Bayesian model estimation, we averaged over x iterations of the jackknife.
+
+## Data & code availability
 
@@
     `Stimulus dimensions` = stimuli_dimensions
-  ) -> tabS1
+  ) -> tabs1
 
 # Save the table
-write_csv(tabS1, file = here(tables_dir, "within_experiments.csv"), na = "n/a")
+write_csv(tabs1, file = here(tables_dir, "within_experiments.csv"), na = "n/a")
 
@@
 apa_table(
-  tabS1,
+  tabs1,
   caption = "Experiments included in the main analysis", label = "S1",
-  landscape = TRUE
+  landscape = TRUE, font_size = "scriptsize"
 )

### 2022-05-05 code/analysis.Rmd
Update intro, main analysis

@@
 ---
-title             : "A small male advantage in infant mental rotation"
+title             : "Gender differences in infant mental rotation"
 shorttitle        : "Infant mental rotation"
@@
   - name          : "Alexander Enge"
-    affiliation   : "1,2"
+    affiliation   : "1,2,*"
     corresponding : "yes"
@@
   - name          : "Shreya Kapoor"
-    affiliation   : "1"
+    affiliation   : "1,*"
   - name          : "Anne-Sophie Kieslinger"
-    affiliation   : "1"
+    affiliation   : "1,*"
   - name          : "Michael A. Skeide"
@@
     institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
+  - id            : "*"
+    institution   : "These authors contributed equally"
 
@@
 abstract: |
-  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement (Shepard & Metzler, 1971; Hegarty & Kozhevnikov, 1999; Johnshon & Bouchard, 2005).
-On average, males solve mental rotation tasks slightly faster than females (Linn & Petersen 1985, Voyer et al.
-1995, Voyer 2011, Maeda & Yoon 2013).
-When such behavioral differences emerge during development, however, remains poorly understood (Lauer et al.
-2019).
+  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
+On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
+When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
 Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : "references.bib"
 csl               : "nature.csl"
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 library(here)
-library(ggridges)
+library(scales)
 library(tidyverse)
@@
 dat <- dat_both_mixed
+
+# Helper functions to re-format age from days to months + days
+format_days_months <- function(days, long = FALSE) {
+  m_str <- ifelse(long, " months ", "m ")
+  d_str <- ifelse(long, " days", "d")
+  days_per_month <- 30.417
+  months <- days %/% days_per_month
+  days_left <- as.integer(days - months * days_per_month)
+  str <- paste0(as.character(months), m_str, as.character(days_left), d_str)
+  str[is.na(days)] <- NA
+  return(str)
+}
+
+# Helper function for printing percentages
+print_perc <- function(x) scales::percent(x, accuracy = 0.1)
+
+# Extract some descriptive statistics for usage in the main text
+descs <- list(
+  n_experiments = nrow(dat),
+  n_infants = sum(dat$sample_size),
+  percent_female = mean(dat$female_percent, na.rm = TRUE),
+  min_age_months = as.integer(min(dat$age_min, na.rm = TRUE) / 30.417),
+  mean_age_weighted = format_days_months(
+    sum(dat$age_mean * dat$ni) / (sum(dat$ni)),
+    long = TRUE
+  ),
+  n_experiments_habituation = nrow(filter(dat, task == "Habituation")),
+  n_experiments_voe = nrow(filter(dat, task == "VoE"))
+)
 ```
@@
 
-The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life (Johnson & Moore 2020, Moore & Johnson 2020).
-Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement (Shepard & Metzler, 1971; Hegarty & Kozhevnikov, 1999; Johnshon & Bouchard, 2005).
-
-Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average (Linn & Petersen 1985, Voyer et al.
-1995, Voyer 2011, Maeda & Yoon 2013).
-Effect sizes of this difference, however, are heterogeneous and often only medium (mean weighted g = 0.37–0.73).
-Interestingly, a recent meta-analysis in 3-17-year-old children and adolescents suggests even only a small-to-medium difference (mean weighted g = 0.39) (Lauer et al.
-2019).
+The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life [@moore2020; @johnson2020].
+Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
+
+Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013].
+Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
+Interestingly, a recent meta-analysis [@lauer2019a] in 3-17-year-old children and adolescents suggests even only a small-to-medium difference (mean weighted $g = 0.39$).
 Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
 
-In the present study we meta-analyzed 59 effect sizes derived from looking times in mental rotation tasks conducted by 1,798 infants (47.5% female) aged 3 to 16 months (mean age of 7 months 14 days).
-All tasks were embedded either into habituation experiments (40) or violation of expectation experiments (19) (Fantz 1964; Baillargeon et al.
-1985).
-These experiments comprised real world stimuli (e.g., toy objects, Antrilli & Wang, 2016), three-dimensional digital stimuli (e.g., cube figures; Moore & Johnson, 2008), or two-dimensional digital stimuli (e.g., digits; Quinn & Liben, 2008).
+In the present study, we meta-analyzed `r descs$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r descs$n_infants` infants (`r print_perc(descs$percent_female)` female) aged `r descs$min_age_months` to `r descs$max_age_months` months (mean age of `r descs$mean_age_weighted`; Supplementary Table 1).
+All tasks were embedded either into habituation experiments (`r descs$n_experiments_habituation`) or violation of expectation experiments (`r descs$n_experiments_voe`) [@fantz1964; @baillargeon1985].
+These experiments comprised real world stimuli (e.g., toy objects [@antrilli2016]), three-dimensional digital stimuli (e.g., cube figures [@moore2008]), or two-dimensional digital stimuli (e.g., digits [@quinn2008]).
 In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object.
@@
 In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
-Following previous work in older populations we hypothesized that looking times in mental rotation experiments are on average significantly longer in male compared to female infants.
+
+Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average significantly longer in male compared to female infants.
 Effect sizes were assumed to be small.
@@
 # Run prior predictive simulation
-n_iter <- 20000
+n_iter <- 4000
 n_warmup <- 1000
@@
 
+# Get posterior probability mass > 0 for the meta-analytic effect
+(hyp_brm <- hypothesis(res_brm, "Intercept > 0")$hypothesis)
+
 # # Summarise fixed effects (incl. Bayes factors)
@@
 
-# Compute by-experiment variance
-var_experiment <- as.matrix(
+# Extract posterior draws for the meta-analytic effects
+spread_draws(
   res_brm,
-  variable = "sd_article:experiment__Intercept"
-)^2
-mean_qi(var_experiment)
-
-# Compute by-article variance
-var_article <- as.matrix(
-  res_brm,
-  variable = "sd_article__Intercept"
-)^2
-mean_qi(var_article)
-
-# Compute intra-class correlation
-var_total <- (var_experiment + var_article)
-icc_draws <- var_article / var_total
-mean_qi(icc_draws)
+  b_Intercept, sd_article__Intercept, `sd_article:experiment__Intercept`,
+  ndraws = NULL
+) %>%
+  # Compute variances and ICC
+  mutate(
+    intercept = b_Intercept,
+    sigma_article = sd_article__Intercept,
+    sigma_experiment = `sd_article:experiment__Intercept`,
+    sigma2_article = sigma_article^2,
+    sigma2_experiment = sigma_experiment^2,
+    sigma2_total = sigma2_article + sigma2_experiment,
+    icc = sigma2_article / sigma2_total,
+    .keep = "unused"
+  ) -> draws_brm
+
+# Summarize as mean and 95% credible intervals
+(summ_brm <- as.list(mean_qi(draws_brm)))
 ```
 
-For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects.
-Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
-Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of g = 0.26, 95% credible interval (CrI) [0.12, 0.41] (Fig.
-1).
-The probability for this effect being greater than zero was 99.9%.
-The heterogeneity of effect sizes was $sigma$2Experiment = 0.03, 95% CrI [0.00, 0.12], at the experiment level and $sigma$2Article = 0.17, 95% CrI [0.09, 0.29] at the article level.
-Therefore, approximately 86.7% of the heterogeneity between effect sizes was attributable to differences between experiments and 13.3% was attributable to differences between articles.
-
 ```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
-# Helper functions for printing confidence intervals
+# Helper functions for printing numbers with exactly 2 decimal points
 print_num <- function(x, digits = 2) {
@@
 }
-print_ci <- function(est, lb, ub) {
-  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
+
+# Helper function for confidence intervals (optionally adding the mean)
+print_ci <- function(lb, ub, mean = NULL) {
+  mean_str <- ifelse(mean, paste0(print_num(mean), " "))
+  paste0(mean_str, "[", print_num(lb), ", ", print_num(ub), "]")
 }
 
-# Get posterior draws for each experiment
-draws <- epred_draws(res_brm, dat, ndraws = NULL) %>%
+# Get posterior draws for the effect in each experiment
+epred_draws_brm <- epred_draws(res_brm, dat, ndraws = NULL) %>%
   mutate(experiment_f = factor(experiment))
 
-# Get posterior draws for the meta-analytic effect
-meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = NULL)
-meta_effect_size <- summary(res_brm)$fixed
-
 # Create forest plot
-n_experiments <- length(unique(dat$experiment))
 dat %>%
@@
     ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_print = print_ci(gi, ci_lb, ci_ub)
+    ci_print = print_ci(ci_lb, ci_ub, mean = gi)
   ) %>%
@@
     aes(x = .epred),
-    data = draws,
+    data = epred_draws_brm,
     alpha = .8,
@@
   stat_halfeye(
-    aes(x = b_Intercept, y = -1),
-    meta_draws,
+    aes(x = intercept, y = -1),
+    draws_brm,
     point_interval = "mean_qi",
@@
       "Three-level model",
-      print_num(meta_effect_size$Estimate),
-      print_num(meta_effect_size$`l-95% CI`),
-      print_num(meta_effect_size$`u-95% CI`)
+      print_num(summ_brm$intercept),
+      print_num(summ_brm$intercept.lower),
+      print_num(summ_brm$intercept.upper)
     ),
@@
   # Add headers for each of the for columns
-  annotate( # Just to make the grid lines disappear
+  annotate(
     "rect",
@@
     xmax = Inf,
-    ymin = n_experiments + 0.5,
+    ymin = descs$n_experiments + 0.5,
     ymax = Inf,
@@
     x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
-    y = n_experiments + 1.5,
+    y = descs$n_experiments + 1.5,
     label = c(
@@
   coord_cartesian(
-    ylim = c(-1.5, n_experiments + 2), expand = FALSE, clip = "off"
+    ylim = c(-1.5, descs$n_experiments + 2), expand = FALSE, clip = "off"
   ) +
@@
 These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the model.
-The last line shows the meta-analytic effect size (black dot) together with its 95% CrI and its posterior distribution (gray curve).
+The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
+
+For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects.
+Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
+Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_brm$intercept`$, 95% credible interval (CrI) [`r summ_brm$intercept.lower`, `r summ_brm$intercept.upper`] (Fig.
+1).
+The probability for this effect being greater than zero was `r print_perc(hyp_brm$Post.Prob)`.
+The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm$sigma2_experiment`$, 95% CrI [`r summ_brm$sigma2_experiment.lower`, `r summ_brm$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm$sigma2_article`$, 95% CrI [`r summ_brm$sigma2_article.lower`, `r summ_brm$sigma2_article.upper`] at the article level.
+Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments and `r print_perc(summ_brm$icc)` was attributable to differences between articles.
 
@@
 
-# Compute intra-class correlation
-var_total_reg <- var_experiment_reg + var_article_reg
-icc_reg <- var_article_reg / var_total_reg
-mean_qi(icc_reg)
-
-# Compute reduction in heterogeneity compared to the original meta-analysis
-1 - mean(var_total_reg / var_total)
+# # Compute intra-class correlation
+# var_total_reg <- var_experiment_reg + var_article_reg
+# icc_reg <- var_article_reg / var_total_reg
+# mean_qi(icc_reg)
+
+# # Compute reduction in heterogeneity compared to the original meta-analysis
+# 1 - mean(var_total_reg / var_total)
 ```
 
-As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig.
-2).
+As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig. 2).
 Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, b = 0.48, 95% CrI [0.06, 0.91].
@@
 (ref:fig2-caption) Effects of gender, age, and task.
-a Squares show the effect size (Hedges’ g) for infants’ mental rotation performance in each of the 59 individual experiments.
+a Squares show the effect size (Hedges' g) for infants' mental rotation performance in each of the 59 individual experiments.
 Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
@@
 To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported within each article by the original authors.
-Our additional analysis revealed a meta-analytic effect size of g = 0.20, 95% Crl [0.03, 0.38] (Supplementary Fig.
-1) and a probability of this effect being greater than zero of 98.9%.
-The heterogeneity of effect sizes was $sigma$2Experiment = 0.01, 95% CrI [0.00, 0.07], at the experiment level, and $sigma$2Article = 0.02, 95% CrI [0.00, 0.10] at the article level.
+Our additional analysis revealed a meta-analytic effect size of g = 0.20, 95% Crl [0.03, 0.38] (Supplementary Fig. 1) and a probability of this effect being greater than zero of 98.9%.
+The heterogeneity of effect sizes was \$sigma\$2Experiment = 0.01, 95% CrI [0.00, 0.07], at the experiment level, and \$sigma\$2Article = 0.02, 95% CrI [0.00, 0.10] at the article level.
 This means that 56.1% of the total variance can be attributed to differences between articles and 43.1% to differences within articles.
@@
 
-By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig.
-3).
+By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig. 3).
 Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero (t(57) = 3.37, p = 0.001).
@@
 A number of additional factors have been associated with individual differences in infant mental rotation performance.
-For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task (Möhring and Frick 2013; Schwarzer et al.
-2013b; Slone et al.
-2018).
-This relation also applies to previous experience with manually rotating toys (Schwarzer et al.
-2013b).
+For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task (Möhring and Frick 2013; Schwarzer et al. 2013b; Slone et al. 2018).
+This relation also applies to previous experience with manually rotating toys (Schwarzer et al. 2013b).
 While these preliminary results require replication they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g.
@@
 # Include the flowchart (created with MS PowerPoint)
-knitr::include_graphics("results/figures/flowchart.pdf")
+knitr::include_graphics(here("results/figures/flowchart.pdf"))
 ```
@@
 
-We entered the search terms (“mental rotation” OR “mental transformation” OR “spatial rotation” OR “spatial transformation” OR “spatial ability” OR “spatial skills”) AND (“infant” OR “infants” OR “infanthood” OR “toddler” OR “toddlers” OR “toddlerhood” OR “child” OR “children” OR “childhood” OR “month” OR “months”) into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, ProQuest Dissertations & Theses Global).
+We entered the search terms ("mental rotation" OR "mental transformation" OR "spatial rotation" OR "spatial transformation" OR "spatial ability" OR "spatial skills") AND ("infant" OR "infants" OR "infanthood" OR "toddler" OR "toddlers" OR "toddlerhood" OR "child" OR "children" OR "childhood" OR "month" OR "months") into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, ProQuest Dissertations & Theses Global).
 All database queries were completed on December 6, 2021.
@@
 Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
-Interrater agreement for the binary decision to include versus exclude an article was 98.5% ($Kappa$w [Cohen’s weighted kappa] = 0.67, 95% CI [0.55, 0.78]).
+Interrater agreement for the binary decision to include versus exclude an article was 98.5% ($Kappa$w [Cohen's weighted kappa] = 0.67, 95% CI [0.55, 0.78]).
 Interrater agreement for the specific eligibility criteria were 88.2% ($Kappa$w = 0.72, 95% CI [0.40, 1.00]).
@@
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of 23 articles being included in the meta-analysis (Fig.
-4).
+This procedure led to a total of 23 articles being included in the meta-analysis (Fig. 4).
 
@@
 However, we excluded experiments if there was insufficient information to compute a standardized effect size (see below).
-Whenever an article reported separate effect sizes for boys and girls—or other subgroups like crawling and non-crawling infants)—but also an effect size combining these groups, we only included the combined effect size.
+Whenever an article reported separate effect sizes for boys and girls---or other subgroups like crawling and non-crawling infants)---but also an effect size combining these groups, we only included the combined effect size.
 We dropped effect sizes that were clearly based on the same data but reported in different articles.
@@
 
-One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ g) using the formulas provided in Table 1.
+One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' g) using the formulas provided in Table 1.
 The sampling variance Var_g of the outcome measure g for each experiment was computed using the formula provided by Goulet-Pelletier & Cousineau (2018):
 
-v = (df(df - 2)) * ((2 * (1 - r)) / n) * (1 + g^2 * (n / (2 * (1 - r)))) - (g^2 / j^2)
-
-where n is the sample size of the experiment, df are the degrees of freedom (with df=2*(n-1)), r is the correlation between the two dependent measures in the experiment, and j is the correction factor for small samples as described in Table 1.
+v = (df(df - 2)) \* ((2 \* (1 - r)) / n) \* (1 + g\^2 \* (n / (2 \* (1 - r)))) - (g\^2 / j\^2)
+
+where n is the sample size of the experiment, df are the degrees of freedom (with df=2\*(n-1)), r is the correlation between the two dependent measures in the experiment, and j is the correction factor for small samples as described in Table 1.
 The correlation r was not reported in any of the original articles.
-We therefore always assumed a correlation of r = .50 to make our analysis comparable to standard (between-group) meta-analyses (Lakens, 2013) and because we were able to infer an average correlation of r ≈ .50 from a subsample of articles which provided sufficient information (Supplementary Methods 1).
+We therefore always assumed a correlation of r = .50 to make our analysis comparable to standard (between-group) meta-analyses (Lakens, 2013) and because we were able to infer an average correlation of r $\approx$ .50 from a subsample of articles which provided sufficient information (Supplementary Methods 1).
 A sensitivity analysis indicated that changing the assumed correlation to values from r = -.90 via r = .00 to r = .90 had no meaningful impact on the meta-analytic effect size (Supplementary Table 3).
@@
 Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling 10,000 draws (including 5,000 warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the R_{hat} and N_{eff} statistics (Vehtari et al., 2021; Supplementary Fig.
-1).
+To verify the convergence of the Markov chains, we examined rank plots as well as the R\_{hat} and N\_{eff} statistics (Vehtari et al., 2021; Supplementary Fig. 1).
 For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results (Kruschke, 2015).
@@
 
-We assessed publication bias by means of a funnel plot and Egger regression test (Egger et al.
-1997).
+We assessed publication bias by means of a funnel plot and Egger regression test (Egger et al. 1997).
 We adapted code from the R package metaviz (Version 0.3.1; Kossmeier et al., 2020) to produce the funnel plot and used the R package metafor for the Egger regression test.
@@
 ```{r, tabs1, include=TRUE}
-# Helper functions to re-format age in years and/or months
-format_days_months <- function(days) {
-  days_per_month <- 30.417
-  months <- days %/% days_per_month
-  days_left <- round(days - months * days_per_month)
-  str <- paste0(as.character(months), "m ", as.character(days_left), "d")
-  str[is.na(days)] <- NA
-  return(str)
-}
-
 # Save within-analysis table of experiments

### 2022-05-05 code/analysis.Rmd
Update regression results

@@
 
-In the present study, we meta-analyzed `r descs$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r descs$n_infants` infants (`r print_perc(descs$percent_female)` female) aged `r descs$min_age_months` to `r descs$max_age_months` months (mean age of `r descs$mean_age_weighted`; Supplementary Table 1).
+In the present study, we meta-analyzed `r descs$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descs$n_infants, big.mark = ",")` infants (`r print_perc(descs$percent_female)` female) aged `r descs$min_age_months` to `r descs$max_age_months` months (mean age of `r descs$mean_age_weighted`; Supplementary Table 1).
 All tasks were embedded either into habituation experiments (`r descs$n_experiments_habituation`) or violation of expectation experiments (`r descs$n_experiments_voe`) [@fantz1964; @baillargeon1985].
@@
 # Extract posterior draws for the meta-analytic effects
-spread_draws(
-  res_brm,
-  b_Intercept, sd_article__Intercept, `sd_article:experiment__Intercept`,
-  ndraws = NULL
-) %>%
+spread_draws(res_brm, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
   # Compute variances and ICC
@@
 
-(ref:fig1-caption) Mental rotation performance.
-A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
-White squares depict the effect sizes (Hedges’ g) for infants’ mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
+(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
+White squares depict the effect sizes (Hedges’ $g$) for infants’ mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
 Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI).
@@
 
+# Get posterior probability mass > 0 for all regression weights
+(hyps_brm_reg <- list(
+  intercept = hypothesis(res_brm_reg, "Intercept > 0")$hypothesis,
+  female_mixed = hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis,
+  male_female = hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis,
+  age = hypothesis(res_brm_reg, "age_c > 0")$hypothesis,
+  voe_habituation = hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis,
+  female_mixed_age = hypothesis(res_brm_reg, "gender2M1:age_c > 0")$hypothesis,
+  male_female_age = hypothesis(res_brm_reg, "gender3M2:age_c > 0")$hypothesis
+))
+
 # # Summarise fixed effects (incl. Bayes factors)
@@
 
-# Compute by-experiment variance
-var_experiment_reg <- as.matrix(
-  res_brm_reg,
-  variable = "sd_article:experiment__Intercept"
-)^2
-mean_qi(var_experiment_reg)
-
-# Compute by-article variance
-var_article_reg <- as.matrix(
-  res_brm_reg,
-  variable = "sd_article__Intercept"
-)^2
-mean_qi(var_article_reg)
-
-# # Compute intra-class correlation
-# var_total_reg <- var_experiment_reg + var_article_reg
-# icc_reg <- var_article_reg / var_total_reg
-# mean_qi(icc_reg)
-
-# # Compute reduction in heterogeneity compared to the original meta-analysis
-# 1 - mean(var_total_reg / var_total)
+# Extract posterior draws for the meta-analytic effects
+spread_draws(res_brm_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+  # Compute variances and ICC
+  mutate(
+    intercept = b_Intercept,
+    female_mixed = b_gender2M1,
+    male_female = b_gender3M2,
+    age = b_age_c,
+    voe_habituation = b_task2M1,
+    female_mixed_age = `b_gender2M1:age_c`,
+    male_female_age = `b_gender3M2:age_c`,
+    sigma_article = sd_article__Intercept,
+    sigma_experiment = `sd_article:experiment__Intercept`,
+    sigma2_article = sd_article__Intercept^2,
+    sigma2_experiment = `sd_article:experiment__Intercept`^2,
+    sigma2_total = sigma2_article + sigma2_experiment,
+    icc = sigma2_article / sigma2_total,
+  ) -> draws_brm_reg
+
+# Summarize as mean and 95% credible intervals
+(summ_brm_reg <- as.list(mean_qi(draws_brm_reg)))
 ```
@@
 As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig. 2).
-Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, b = 0.48, 95% CrI [0.06, 0.91].
-The probability for this effect being larger than zero was 98.5%.
-We found no difference between mixed-gender and all-female samples, b = 0.13, 95% CrI [-0.20, 0.52] (75.4% probability of an effect larger than zero).
-Additionally, mean age was not related to mental rotation performance, with a change per year of b = 0.05, 95% [-0.58, 0.68].
-We also did not detect an interaction between gender and age ([females - mixed] × age: b = 0.02, 95% CrI [-0.81, 0.84]; [males - females] × age: b = 0.06, 95% CrI [-0.84, 0.96]).
-Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, b = 0.26, 95% [-0.08, 0.58].
-The probability for this effect being greater than zero was 93.5%.
+Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_brm_reg$male_female`$, 95% CrI [`r summ_brm_reg$male_female.lower`, `r summ_brm_reg$male_female.upper`].
+The probability for this effect being larger than zero was `r print_perc(hyps_brm_reg$male_female$Post.Prob)`.
+We found no difference between mixed-gender and all-female samples, $b = `r -summ_brm_reg$female_mixed`$, 95% CrI [`r -summ_brm_reg$female_mixed.lower`, `r -summ_brm_reg$female_mixed.upper`] (`r print_perc(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
+Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_brm_reg$age`$, 95% [`r summ_brm_reg$age.lower`, `r summ_brm_reg$age.upper`].
+We also did not detect an interaction between gender and age ([females - mixed] × age: $b = `r summ_brm_reg$female_mixed_age`$, 95% CrI [`r summ_brm_reg$female_mixed_age.lower`, `r summ_brm_reg$female_mixed_age.upper`]; [males - females] × age: $b = `r summ_brm_reg$male_female_age`$, 95% CrI [`r summ_brm_reg$male_female_age.lower`, `r summ_brm_reg$male_female_age.upper`]).
+Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_brm_reg$voe_habituation`$, 95% [`r summ_brm_reg$voe_habituation.lower`, `r summ_brm_reg$voe_habituation.upper`].
+The probability for this effect being greater than zero was `r print_perc(hyps_brm_reg$voe_habituation$Post.Prob)`.
 
@@
 
-(ref:fig2-caption) Effects of gender, age, and task.
-a Squares show the effect size (Hedges' g) for infants' mental rotation performance in each of the 59 individual experiments.
+(ref:fig2-caption) **Effects of gender, age, and task.** **a,** Squares show the effect size (Hedges’ g) for infants’ mental rotation performance in each of the 59 individual experiments.
 Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
 Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 95% and 50% credible interval (CrI).
-b Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 95% Crl (thin black lines) and 50% Crl (thick black lines).
+**b,** Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 95% Crl (thin black lines) and 50% Crl (thick black lines).
 Gray curves indicate the posterior distribution for each effect.

### 2022-05-05 code/analysis.Rmd
Update references
Incorporate gender difference analysis

@@
 Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
-We robustly found that male infants looked longer at novel rotated objects than female infants.
+We robustly found that male infants recognized novel rotated objects more reliably than female infants.
 The effect size of this average difference was small and did not change with age.
@@
 library(here)
+library(readxl)
 library(scales)
@@
 # Read sheets
-screening <- readxl::read_excel(excel_file, sheet = "screening")
-included <- readxl::read_excel(excel_file, sheet = "included", na = "NA")
+screening <- read_excel(excel_file, sheet = "screening")
+included <- read_excel(excel_file, sheet = "included", na = "NA")
+gender <- read_excel(excel_file, sheet = "gender_differences", na = "NA")
 
@@
     # Add unique experiment identifier
-    experiment = str_c(year, article, group, sep = ", "),
+    experiment = str_c(year, article, group_long, sep = ", "),
 
@@
 
+```{r, gender_differences}
+# Extract relevant effect sizes
+gender %>%
+  # Remove redundant samples
+  filter(!redundant) %>%
+  # Add columns
+  mutate(
+
+    # Add unique experiment identifier
+    experiment = str_c(year, article, group_long, sep = ", "),
+
+    # Re-code non-significant f values as an effect of 0
+    f = as.numeric(f),
+    f_assumed = ifelse(is.nan(f), 0, f),
+
+    # Add d from two-samples t test (Lakens, 2013)
+    d_t = t * sqrt(1 / female_n + 1 / male_n),
+
+    # Add d from ANOVA F value via conversion to a t value
+    d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),
+
+    # Add d from mean difference and pooled standard deviation
+    mean_diff = mean_diff_males_mean - mean_diff_females_mean,
+    sd_diff_pooled_numerator = (male_n - 1) * (mean_diff_males_sd^2) +
+      (female_n - 1) * (mean_diff_females_sd^2),
+    df = male_n + female_n - 2,
+    sd_diff_pooled = sqrt(sd_diff_pooled_numerator / df),
+    d_diff = mean_diff / sd_diff_pooled,
+
+    # Add d from one-sample t test of novelty preference scores
+    mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
+    sd_nov_pref_pooled_numerator = (male_n - 1) * (novelty_pref_males_sd^2) +
+      (female_n) * (novelty_pref_females_sd^2),
+    sd_nov_pref_pooled = sqrt(sd_nov_pref_pooled_numerator / df),
+    d_nov_pref = mean_nov_pref / sd_nov_pref_pooled,
+
+    # Choose one type of outcome variable for each experiment
+    di = case_when(
+      # 1. If d was reported directed
+      !is.na(d) ~ d,
+      # 2. If a t test was reported
+      !is.na(d_t) ~ d_t,
+      # 3. If ANOVA was reported
+      !is.na(d_f) ~ d_f,
+      # 4. If the difference between means and their SDs were reported
+      !is.na(d_diff) ~ d_diff,
+      # 5. If novelty preference scores and their SDs were reported
+      !is.na(d_nov_pref) ~ d_nov_pref
+    ),
+    # Keep track which type of outcome measure was chosen for each article
+    di_type = case_when(
+      !is.na(d) ~ "d",
+      !is.na(d_t) ~ "d_t",
+      !is.na(d_f) ~ "d_f",
+      !is.na(d_diff) ~ "d_diff",
+      !is.na(d_nov_pref) ~ "d_nov_pref"
+    ) %>%
+      factor(levels = c("d", "d_t", "d_f", "d_diff", "d_nov_pref")),
+
+    # Apply small sample correction using Hedges' exact method
+    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
+    j = exp(lgamma(df / 2) - log(sqrt(df / 2)) - lgamma((df - 1) / 2)),
+    gi = di * j,
+
+    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
+    ni = female_n + male_n,
+    nhi = (female_n * male_n) / ni,
+    vi = (df * 2 * (1 + (gi^2 * nhi * 0.5))) / ((df - 2) * nhi) - (gi^2 / j^2),
+    sei = sqrt(vi)
+  ) %>%
+  # Remove experiments that didn't provide an effect size
+  filter(!is.na(gi)) -> dat_gender
+
+# Overview of the different effect sizes
+dat_gender %>%
+  select(
+    article,
+    group_long,
+    gi,
+    di,
+    di_type,
+    d,
+    d_t,
+    d_f,
+    d_diff,
+    sei
+  ) %>%
+  print(n = Inf)
+
+# Specify priors
+prior_c <- c(
+  set_prior("normal(0, 1)", class = "b"),
+  set_prior("cauchy(0, 0.3)", class = "sd")
+)
+
+# Run prior predictive simulation
+res_prior_gender <- brm(
+  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
+  data = dat_gender,
+  prior = prior_c,
+  sample_prior = "only",
+  save_pars = save_pars(all = TRUE),
+  chains = n_chains,
+  iter = n_iter,
+  warmup = n_warmup,
+  cores = n_chains,
+  control = list(adapt_delta = 0.99),
+  file = here("results", "models", "res_prior_gender")
+)
+summary(res_prior_gender)
+# plot(res_prior_gender)
+
+# Run Bayesian multilevel model
+res_brm_gender <- update(
+  res_prior_gender,
+  sample_prior = FALSE,
+  file = here("results", "models", "res_brm_gender")
+)
+summary(res_brm_gender)
+# plot(res_brm_gender)
+
+# Get posterior probability mass > 0 for the meta-analytic effect
+(hyp_brm_gender <- hypothesis(res_brm_gender, "Intercept > 0")$hypothesis)
+
+# # Summarise fixed effects (incl. Bayes factors)
+# describe_posterior(
+#   res_brm_gender,
+#   centrality = "mean", ci = 0.95, ci_method = "ETI",
+#   test = c("p_direction", "rope", "bayesfactor"),
+#   rope_range = c(-0.1, 0.1)
+# )
+
+# Extract posterior draws for the meta-analytic effects
+spread_draws(res_brm_gender, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+  # Compute variances and ICC
+  mutate(
+    intercept = b_Intercept,
+    sigma_article = sd_article__Intercept,
+    sigma_experiment = `sd_article:experiment__Intercept`,
+    sigma2_article = sigma_article^2,
+    sigma2_experiment = sigma_experiment^2,
+    sigma2_total = sigma2_article + sigma2_experiment,
+    icc = sigma2_article / sigma2_total,
+    .keep = "unused"
+  ) -> draws_brm_gender
+
+# Summarize as mean and 95% credible intervals
+(summ_brm_gender <- as.list(mean_qi(draws_brm_gender)))
+```
+
 To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported within each article by the original authors.
-Our additional analysis revealed a meta-analytic effect size of g = 0.20, 95% Crl [0.03, 0.38] (Supplementary Fig. 1) and a probability of this effect being greater than zero of 98.9%.
-The heterogeneity of effect sizes was \$sigma\$2Experiment = 0.01, 95% CrI [0.00, 0.07], at the experiment level, and \$sigma\$2Article = 0.02, 95% CrI [0.00, 0.10] at the article level.
-This means that 56.1% of the total variance can be attributed to differences between articles and 43.1% to differences within articles.
+Our additional analysis revealed a meta-analytic effect size of $g = `r summ_brm_gender$intercept`$, 95% Crl [`r summ_brm_gender$intercept.lower`, `r summ_brm_gender$intercept.upper`] (Supplementary Fig.
+1) and a probability of this effect being greater than zero of `r print_perc(hyp_brm_gender$Post.Prob)`.
+The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm_gender$sigma2_experiment`$, 95% CrI [`r summ_brm_gender$sigma2_experiment.lower`, `r summ_brm_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm_gender$sigma2_article`$, 95% CrI [`r summ_brm_gender$sigma2_article.lower`, `r summ_brm_gender$sigma2_article.upper`] at the article level.
+Therefore, approximately `r print_perc(1 - summ_brm_gender$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments and `r print_perc(summ_brm_gender$icc)` was attributable to differences between articles.
 
@@
 ## Data & code availability
+
+Blah blah blah
+
+# References
+
+<div id="refs"></div>
+
+\newpage
 
@@
 ```
+
+```{r, figs1, include=TRUE, fig.height=10, fig.width=12, fig.cap="(ref:figs1-caption)"}
+# Get posterior draws for the effect in each experiment
+epred_draws_brm_gender <- epred_draws(res_brm_gender, dat_gender, ndraws = NULL) %>%
+  mutate(experiment_f = factor(experiment))
+
+# Create forest plot
+dat_gender %>%
+  # Make sure the plot will be ordered alphabetically by experiment IDs
+  arrange(experiment) %>%
+  mutate(
+    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
+    # Show article labels only for the first experiment per article
+    article = if_else(article == lag(article, default = ""), "", article),
+    # Compute frequentist confidence intervals
+    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_print = print_ci(gi, ci_lb, ci_ub)
+  ) %>%
+  # Prepare plotting canvas
+  ggplot(aes(x = gi, y = experiment_f)) +
+  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
+  # Add article and group labels as text on the left
+  geom_text(aes(x = -9.9, label = article), hjust = 0) +
+  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
+  # Add experiment-specific effect sizes and CIs as text on the right
+  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
+  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
+  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
+  # Add Bayesian highest posterior density intervals for each experiment
+  stat_interval(
+    aes(x = .epred),
+    data = epred_draws_brm_gender,
+    alpha = .8,
+    point_interval = "mean_qi",
+    .width = c(0.5, 0.95),
+  ) +
+  scale_color_grey(
+    start = 0.85, end = 0.65,
+    labels = as_mapper(~ scales::percent(as.numeric(.x)))
+  ) +
+  # Add experiment-specific effect sizes and CIs as dots with error bars
+  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
+  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
+  # Add posterior distribution for the meta-analytic effect
+  stat_halfeye(
+    aes(x = intercept, y = -1),
+    draws_brm_gender,
+    point_interval = "mean_qi",
+    .width = c(0.95)
+  ) +
+  annotate(
+    "text",
+    x = c(-9.9, 3.7, 4.4, 5.1),
+    y = -0.5,
+    label = c(
+      "Three-level model",
+      print_num(summ_brm_gender$intercept),
+      print_num(summ_brm_gender$intercept.lower),
+      print_num(summ_brm_gender$intercept.upper)
+    ),
+    hjust = c(0, 1, 1, 1),
+    fontface = "bold"
+  ) +
+  # Add headers for each of the for columns
+  annotate( # Just to make the grid lines disappear
+    "rect",
+    xmin = -Inf,
+    xmax = Inf,
+    ymin = nrow(dat_gender) + 0.5,
+    ymax = Inf,
+    fill = "white"
+  ) +
+  annotate(
+    "text",
+    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
+    y = nrow(dat_gender) + 1.5,
+    label = c(
+      "Article",
+      "Experiment",
+      "Effect size plot",
+      "Effect size",
+      "Lower",
+      "Upper"
+    ),
+    hjust = c(0, 0, 0.5, 1, 1, 1),
+    fontface = "bold"
+  ) +
+  # Styling
+  coord_cartesian(
+    ylim = c(-1.5, nrow(dat_gender) + 2), expand = FALSE, clip = "off"
+  ) +
+  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
+  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    size = "Sample size",
+    color = "CrI level"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.position = "bottom",
+    axis.text.x = element_text(family = "Helvetica", color = "black"),
+    axis.text.y = element_blank(),
+    axis.ticks.x = element_line(colour = "black"),
+    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
+    axis.title.y = element_blank(),
+    panel.grid = element_blank(),
+    text = element_text(family = "Helvetica")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "forest_gender.pdf"), width = 12, height = 8)
+```
+
+(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants.
+White squares indicate the effect sizes (Hedges’ $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals.
+Note that for experiments that observed a non-significant gender difference and did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
+Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
+Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
+The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
 

### 2022-05-05 code/analysis.Rmd
Fix italics vs. bold

@@
 The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm$sigma2_experiment`$, 95% CrI [`r summ_brm$sigma2_experiment.lower`, `r summ_brm$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm$sigma2_article`$, 95% CrI [`r summ_brm$sigma2_article.lower`, `r summ_brm$sigma2_article.upper`] at the article level.
-Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments and `r print_perc(summ_brm$icc)` was attributable to differences between articles.
+Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_brm$icc)` was attributable to differences *between* articles.
 
@@
 
-To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported within each article by the original authors.
+To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
 Our additional analysis revealed a meta-analytic effect size of $g = `r summ_brm_gender$intercept`$, 95% Crl [`r summ_brm_gender$intercept.lower`, `r summ_brm_gender$intercept.upper`] (Supplementary Fig.
@@
 The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm_gender$sigma2_experiment`$, 95% CrI [`r summ_brm_gender$sigma2_experiment.lower`, `r summ_brm_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm_gender$sigma2_article`$, 95% CrI [`r summ_brm_gender$sigma2_article.lower`, `r summ_brm_gender$sigma2_article.upper`] at the article level.
-Therefore, approximately `r print_perc(1 - summ_brm_gender$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments and `r print_perc(summ_brm_gender$icc)` was attributable to differences between articles.
+This means that `r print_perc(summ_brm_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_brm_gender$icc)` to differences between experiments *within* articles.
 

### 2022-05-05 code/analysis.Rmd
Add Egger test + funnel plot

@@
 
-## Evaluation of publication bias
-
-By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig. 3).
-Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero (t(57) = 3.37, p = 0.001).
-Nevertheless, a jackknife leave-one-out analysis confirmed that the current results are robust to the effects of individual studies (see Supplementary Table 5).
+## Publication bias and certainty assessment
+
+```{r, publication_bias, echo=TRUE}
+# Classical Egger regression test
+(egger <- regtest(x = dat$gi, sei = dat$sei, model = "lm", predictor = "sei"))
+(egger_ci <- confint(egger$fit)["Xsei", ])
+```
+
+By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig.
+3).
+Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero in a two-sided $t$-test, $b = `r coef(egger$fit)["Xsei"]`$, $t(`r egger$dfs`) = `r egger$zval`$, $p = `r print_p(egger$pval)`$, 95% confidence interval (CI) [`r egger_ci["2.5 %"]`, `r egger_ci["97.5 %"]`].
+Nevertheless, a jackknife leave-one-out analysis confirmed that the current results are robust to the effects of individual studies (Supplementary Table 3).
+
+```{r, fig3, include=TRUE, fig.height=3.5, fig.width=5.56, fig.cap="(ref:fig3-caption)", out.width="50%"}
+# Compute funnel
+funnel_z_crit <- stats::qnorm(0.975)
+funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
+funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
+funnel <- data.frame(
+  x = c(
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
+  ),
+  y = c(funnel_max_se, 0, 0, funnel_max_se)
+)
+
+# Create funnel plot
+dat %>%
+  ggplot(aes(x = gi, y = sei)) +
+  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
+  # Meta-analytic effect size
+  geom_vline(xintercept = summ_brm$intercept, color = "black") +
+  # Experiment-specific effect sizes
+  geom_point(shape = 0) +
+  # Funnel
+  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
+  # Styling
+  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
+  scale_y_reverse() +
+  coord_cartesian(
+    xlim = c(-2.5, 2.5),
+    ylim = c(funnel_max_se, 0),
+    expand = FALSE
+  ) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    y = "Standard error",
+  ) +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "funnel.pdf"), width = 5.56, height = 3.5)
+```
+
+(ref:fig3-caption) **Evaluation of publication bias.** The funnel plot shows the standard errors and the effect sizes for each of the individual studies.
+The funnel contours (dashed lines) show a 95%-pseudo-confidence interval of the standard error around the meta-analytic effect size (vertical solid line).
+A slight asymmetry induced by the underrepresentation of studies with high standard error and small effect size suggest a small publication bias.
 

### 2022-05-05 code/analysis.Rmd
Improva caption formatting

@@
   - \usepackage{setspace}
-  - \renewcommand{\arraystretch}{1.0}
-  - \captionsetup{font={stretch=1}, belowskip=15pt}
+  - \DeclareCaptionLabelSeparator{bar}{ | }
+  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
+  - \captionsetup[table]{font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
+  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
 ---
@@
 Blah blah blah
+
+\newpage
 

### 2022-05-05 manuscript.Rmd
Move manuscript and supplement to root dir

--- 2022-05-05 code/analysis.Rmd
@@
 
-bibliography      : "references.bib"
-csl               : "nature.csl"
+bibliography      : "manuscript_files/references.bib"
+csl               : "manuscript_files/nature.csl"
+
+appendix          : "supplement.Rmd"
 
@@
 
-# Supplementary information
-
-```{r, tabs1, include=TRUE}
-# Save within-analysis table of experiments
-dat %>%
-  mutate(
-    age_mean = format_days_months(age_mean),
-    age_sd = str_c(as.character(round(age_sd)), "d"),
-  ) %>%
-  transmute(
-    Article = if_else(article == lag(article, default = ""), "", article),
-    Experiment = group_long,
-    `Sample size` = sample_size,
-    `Females` = round(female_percent * sample_size),
-    Age = str_c(age_mean, "±", age_sd, sep = " "),
-    Task = task,
-    `Stimulus type` = str_to_sentence(stimuli_presentation),
-    `Stimulus dimensions` = stimuli_dimensions
-  ) -> tabs1
-
-# Save the table
-write_csv(tabs1, file = here(tables_dir, "within_experiments.csv"), na = "n/a")
-
-# Display the table
-apa_table(
-  tabs1,
-  caption = "Experiments included in the main analysis", label = "S1",
-  landscape = TRUE, font_size = "scriptsize"
-)
+```{r child = "supplement.Rmd"}
 ```
-
-```{r, figs1, include=TRUE, fig.height=10, fig.width=12, fig.cap="(ref:figs1-caption)"}
-# Get posterior draws for the effect in each experiment
-epred_draws_brm_gender <- epred_draws(res_brm_gender, dat_gender, ndraws = NULL) %>%
-  mutate(experiment_f = factor(experiment))
-
-# Create forest plot
-dat_gender %>%
-  # Make sure the plot will be ordered alphabetically by experiment IDs
-  arrange(experiment) %>%
-  mutate(
-    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
-    # Show article labels only for the first experiment per article
-    article = if_else(article == lag(article, default = ""), "", article),
-    # Compute frequentist confidence intervals
-    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_print = print_ci(gi, ci_lb, ci_ub)
-  ) %>%
-  # Prepare plotting canvas
-  ggplot(aes(x = gi, y = experiment_f)) +
-  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
-  # Add article and group labels as text on the left
-  geom_text(aes(x = -9.9, label = article), hjust = 0) +
-  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
-  # Add experiment-specific effect sizes and CIs as text on the right
-  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
-  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
-  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
-  # Add Bayesian highest posterior density intervals for each experiment
-  stat_interval(
-    aes(x = .epred),
-    data = epred_draws_brm_gender,
-    alpha = .8,
-    point_interval = "mean_qi",
-    .width = c(0.5, 0.95),
-  ) +
-  scale_color_grey(
-    start = 0.85, end = 0.65,
-    labels = as_mapper(~ scales::percent(as.numeric(.x)))
-  ) +
-  # Add experiment-specific effect sizes and CIs as dots with error bars
-  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
-  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
-  # Add posterior distribution for the meta-analytic effect
-  stat_halfeye(
-    aes(x = intercept, y = -1),
-    draws_brm_gender,
-    point_interval = "mean_qi",
-    .width = c(0.95)
-  ) +
-  annotate(
-    "text",
-    x = c(-9.9, 3.7, 4.4, 5.1),
-    y = -0.5,
-    label = c(
-      "Three-level model",
-      print_num(summ_brm_gender$intercept),
-      print_num(summ_brm_gender$intercept.lower),
-      print_num(summ_brm_gender$intercept.upper)
-    ),
-    hjust = c(0, 1, 1, 1),
-    fontface = "bold"
-  ) +
-  # Add headers for each of the for columns
-  annotate( # Just to make the grid lines disappear
-    "rect",
-    xmin = -Inf,
-    xmax = Inf,
-    ymin = nrow(dat_gender) + 0.5,
-    ymax = Inf,
-    fill = "white"
-  ) +
-  annotate(
-    "text",
-    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
-    y = nrow(dat_gender) + 1.5,
-    label = c(
-      "Article",
-      "Experiment",
-      "Effect size plot",
-      "Effect size",
-      "Lower",
-      "Upper"
-    ),
-    hjust = c(0, 0, 0.5, 1, 1, 1),
-    fontface = "bold"
-  ) +
-  # Styling
-  coord_cartesian(
-    ylim = c(-1.5, nrow(dat_gender) + 2), expand = FALSE, clip = "off"
-  ) +
-  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
-  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
-  labs(
-    x = expression("Hedges'" ~ italic("g")),
-    size = "Sample size",
-    color = "CrI level"
-  ) +
-  theme_minimal() +
-  theme(
-    legend.position = "bottom",
-    axis.text.x = element_text(family = "Helvetica", color = "black"),
-    axis.text.y = element_blank(),
-    axis.ticks.x = element_line(colour = "black"),
-    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
-    axis.title.y = element_blank(),
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "forest_gender.pdf"), width = 12, height = 8)
-```
-
-(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants.
-White squares indicate the effect sizes (Hedges’ $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals.
-Note that for experiments that observed a non-significant gender difference and did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
-Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
-Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
-The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
-
-```{r, figs2, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs2-caption)"}
-# Extract convergence statistics from results
-conv_stats <- with(summary(res_brm), tibble(
-  parameter = c(
-    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
-  ),
-  name_expr = c(
-    "Hedges ~ italic(g)", "italic(sigma)[article]", "italic(sigma)[experiment]"
-  ),
-  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
-  bulk_ess = round(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
-  tail_ess = round(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
-  r_hat_expr = str_c("italic(R)[hat] == ", r_hat),
-  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == ", bulk_ess),
-  tail_ess_expr = str_c("italic(N)[eff(tail)] == ", tail_ess),
-  y_pos = c(0.7, 0.75, 0.8)
-))
-
-# Create trace plot
-n_draws <- n_iter - n_warmup
-bayesplot::mcmc_trace(
-  res_brm,
-  pars = conv_stats$parameter, facet_args = list(ncol = 1)
-) +
-  geom_text(
-    aes(y = 0.45, label = name_expr, color = NA),
-    conv_stats,
-    y = 0.45, x = -800, color = "black", parse = TRUE, angle = 90
-  ) +
-  geom_text(
-    aes(y = y_pos, label = r_hat_expr, color = NA),
-    conv_stats,
-    x = 13000, hjust = 1, color = "black", parse = TRUE,
-  ) +
-  geom_text(
-    aes(y = y_pos, label = bulk_ess_expr, color = NA),
-    conv_stats,
-    x = 16000, hjust = 1, color = "black", parse = TRUE,
-  ) +
-  geom_text(
-    aes(y = y_pos, label = tail_ess_expr, color = NA),
-    conv_stats,
-    x = 19000, hjust = 1, color = "black", parse = TRUE,
-  ) +
-  labs(x = "Sample number", y = NULL, color = "MCMC\nchain") +
-  coord_cartesian(expand = FALSE, clip = "off") +
-  scale_x_continuous(limits = c(0, n_draws), breaks = seq(0, n_draws, 2000)) +
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
-  scale_color_grey(start = 0.0, end = 0.9) +
-  theme_classic() +
-  theme(
-    axis.line = element_line(colour = "black"),
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    plot.margin = margin(t = 10, l = 25),
-    strip.background = element_blank(),
-    strip.text = element_blank(),
-    text = element_text(family = "Helvetica", color = "black")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "trace.pdf"), width = 12, height = 6)
-```
-
-(ref:figs2-caption) Convergence checks.
-
-```{r, frequentist_results}
-# Three-level model
-res_ml <- rma.mv(
-  gi, vi,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_ml)
-# forest(res_ml)
-
-# Check share of variance at each level of the model
-round(res_ml$sigma2[1] / sum(res_ml$sigma2), 3) # Between-article (ICC)
-round(res_ml$sigma2[2] / sum(res_ml$sigma2), 3) # Within-article (between-exp.)
-
-# # Profile likelihodd plots for checking that REML has converged
-# profile(res_ml)
-
-# Meta-regression with gender, age, and task
-res_reg <- rma.mv(
-  gi, vi,
-  mods = ~ gender * age_c + task,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_reg)
-# forest(res_full)
-
-# Extract standard deviations and ICCs
-vars_ml <- list(matrix())
-
-# Export results as a table
-map2_dfr(
-  c("Meta-analysis", "Meta-regression"),
-  list(res_ml, res_reg),
-  function(name, res) {
-    # Intercept / regression weights
-    tibble(
-      Model = c(name, rep(NA, length(res$b) - 1)),
-      Parameter = rownames(res$b),
-      Estimate = print_num(as.numeric(res$b)),
-      SE = print_num(res$se),
-      z = print_num(res$zval),
-      p = print_num(res$pval, digits = 3),
-      ci_lower = print_num(res$ci.lb),
-      ci_upper = print_num(res$ci.ub)
-    ) %>%
-      # Re-format confidence interval
-      mutate(
-        `95% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
-        .keep = "unused"
-      ) %>%
-      # Add variances
-      bind_rows(tibble(
-        Parameter = res$s.name,
-        Estimate = print_num(res$sigma2)
-      ))
-  }
-) %>%
-  mutate(
-    Parameter = c(
-      "Hedges' g",
-      "s2article",
-      "s2experiment",
-      "Intercept",
-      "Female - mixed",
-      "Male - female",
-      "Age (per year)",
-      "Habituation - VoE",
-      "(Female - mixed) × age",
-      "(Male - female) × age",
-      "s2article",
-      "s2experiment"
-    )
-  ) -> tab_freq
-
-# Save the table
-write_csv(tab_freq, file = here(tables_dir, "frequentist_results.csv"), na = "")
-```
-
-```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
-# Compute empirical estimate of the correlation between dependent samples
-dat %>%
-  mutate(
-    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
-    d_diff = case_when(
-      !is.na(d) ~ d,
-      !is.na(d_z_t) ~ d_z_t,
-      !is.na(d_z_f) ~ d_z_f,
-      !is.na(d_z_diff) ~ d_z_diff
-    ),
-    # Compute empirical correlation
-    # Basesd on the SD of the difference and the SDs within the two conditions
-    sd_diff = mean_diff / d_diff,
-    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
-      (-2 * sd_novel * sd_familiar)
-  ) %>%
-  pull(ri) -> ri_empirical
-
-# Summarise the estimated correlations
-summary(ri_empirical)
-
-# Re-run the meta-analysis for different values of r_assumed
-seq(-0.9, 0.9, by = 0.3) %>%
-  set_names(., str_c("r = ", print_num(.))) %>%
-  map(function(ri_sens) {
-
-    # Re-compute standard errors of the effect sizes
-    mutate(
-      dat,
-      vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
-        (1 + gi^2 * (ni / (2 * (1 - ri_sens)))) - (gi^2 / ji^2),
-      sei = sqrt(vi)
-    ) -> dat_ri_sens
-
-    # Re-run meta-analysis
-    update(res_brm, newdata = dat_ri_sens, refresh = 0)
-  }) -> res_ri_sens
-
-# Prior sensitivity analysis
-list(
-  "Intercept U(-10,10)" = c(
-    set_prior("uniform(-10, 10)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "Intercept N(0,0.2)" = c(
-    set_prior("normal(0, 0.2)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "SD U(0,10)" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("uniform(0, 10)", class = "sd")
-  ),
-  "SD Student-t(10,0,0.2)" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("student_t(10, 0, 0.2)", class = "sd")
-  )
-) %>%
-  # Re-run the meta-analysis with different priors
-  map(
-    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
-  ) -> res_prior_sens
-
-# Create a table summarizing all sensitivity analyses
-map2_dfr(
-  c(res_ri_sens, res_prior_sens),
-  c(names(res_ri_sens), names(res_prior_sens)),
-  function(res, name) {
-
-    # Compute ICC
-    var_experiment <- as.matrix(
-      res,
-      variable = "sd_article:experiment__Intercept"
-    )^2
-    var_article <- as.matrix(
-      res,
-      variable = "sd_article__Intercept"
-    )^2
-    var_total <- var_experiment + var_article
-    icc <- var_article / var_total
-    icc_row <- mean_qi(icc) %>%
-      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)
-
-    # Create a data frame row of summary statistics
-    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
-      bind_rows(icc_row) %>%
-      transmute(
-        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
-        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
-      ) %>%
-      pivot_wider(names_from = parameter, values_from = Estimate) %>%
-      bind_cols(Simulation = name, .)
-  }
-) -> tab_sens
-
-# Save the table
-write_csv(tab_sens, file = here(tables_dir, "sensitivity_analysis.csv"))
-```

### 2022-05-05 supplement.Rmd
Move manuscript and supplement to root dir

--- 2022-05-05 code/analysis.Rmd
@@
----
-title             : "Gender differences in infant mental rotation"
-shorttitle        : "Infant mental rotation"
+<!-- Re-define labels for tables and figures -->
+\captionsetup[table]{name=Supplementary Table}
+\captionsetup[figure]{name=Supplementary Fig.}
 
-author: 
-  - name          : "Alexander Enge"
-    affiliation   : "1,2,*"
-    corresponding : "yes"
-    address       : "Stephanstraße 1a, 04103 Leipzig"
-    email         : "enge@cbs.mpg.de"
-  - name          : "Shreya Kapoor"
-    affiliation   : "1,*"
-  - name          : "Anne-Sophie Kieslinger"
-    affiliation   : "1,*"
-  - name          : "Michael A. Skeide"
-    affiliation   : "1"
-affiliation:
-  - id            : "1"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences"
-  - id            : "2"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
-  - id            : "*"
-    institution   : "These authors contributed equally"
-
-authornote: |
-  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
-
-  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
-
-  The data and code for this study are openly available at ???.
-  We have no conflict of interest to disclose.
-  There were no ethical concerns since we did not collect any new data.
-
-abstract: |
-  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
-We robustly found that male infants recognized novel rotated objects more reliably than female infants.
-The effect size of this average difference was small and did not change with age.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
-
-keywords          : "mental rotation, spatial cognition, spatial ability, infants, children, gender, meta-analysis"
-wordcount         : "X"
-
-bibliography      : "references.bib"
-csl               : "nature.csl"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-
-documentclass     : "apa7"
-classoption       : "man,donotrepeattitle"
-fontsize          : "10pt"
-output            : papaja::apa6_pdf
-header-includes:
-  - \geometry{a4paper}
-  - \raggedbottom
-  - \usepackage[all]{nowidow}
-  - \usepackage{makecell}
-  - \usepackage{setspace}
-  - \renewcommand{\arraystretch}{1.0}
-  - \captionsetup{font={stretch=1}, belowskip=15pt}
----
-
-```{r, setup, include=FALSE}
-# Load packages
-library(papaja)
-library(here)
-library(readxl)
-library(scales)
-library(tidyverse)
-library(magrittr)
-library(metafor)
-library(brms)
-library(bayestestR)
-library(tidybayes)
-library(cowplot)
-
-# Global chunk options
-knitr::opts_chunk$set(
-  include = FALSE,
-  message = FALSE,
-  fig.height = 10,
-  fig.width = 7.5,
-  out.width = "100%",
-  warning = FALSE
-)
-
-# Directory paths
-data_dir <- here("data")
-figures_dir <- here("results/figures")
-tables_dir <- here("results/tables")
-
-# Download literature search spreadsheet from Google Drive
-excel_url <- "https://docs.google.com/spreadsheets/d/1xnC0NlQYTXavXaeqQidhi7UKb1pCGAl9Ry3h3Uz3mi0"
-excel_file <- here(data_dir, "literature_search.xlsx")
-# googledrive::drive_auth(use_oob = TRUE)
-# googledrive::drive_download(excel_url, excel_file, overwrite = TRUE)
-
-# Read sheets
-screening <- read_excel(excel_file, sheet = "screening")
-included <- read_excel(excel_file, sheet = "included", na = "NA")
-gender <- read_excel(excel_file, sheet = "gender_differences", na = "NA")
-
-# Add columns to the table of included experiments
-included %>%
-  mutate(
-
-    # Add unique experiment identifier
-    experiment = str_c(year, article, group_long, sep = ", "),
-
-    # Add difference between condition means
-    mean_diff = case_when(
-      !is.na(mean_diff) ~ mean_diff,
-      TRUE ~ mean_novel - mean_familiar
-    ),
-    # Add d_z from paired t test of condition means (Rosenthal, 1991)
-    d_z_t = t / sqrt(sample_size),
-    # Add d_z from ANOVA F value via conversion to a t value
-    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
-    # Add d_z from mean and standard deviation of the difference
-    d_z_diff = mean_diff / sd_diff,
-    # Add d_av from mean difference and standard devations
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
-    d_av = mean_diff / sd_av,
-    # Add d from one-sample t test of novelty preference scores
-    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,
-
-    # Choose one type of outcome variable for each experiment
-    di = case_when(
-      # 1. If d was reported directed
-      !is.na(d) ~ d,
-      # 2. If a paired sample t test was reported
-      !is.na(d_z_t) ~ d_z_t,
-      # 3. If ANOVA was reported
-      !is.na(d_z_f) ~ d_z_f,
-      # 4. If the difference between means and its SD were reported
-      !is.na(d_z_diff) ~ d_z_diff,
-      # 5. If the individual condition means and their SDs were reported
-      !is.na(d_av) ~ d_av,
-      # 6. If a novelty preference score and its SD were reported
-      !is.na(d_nov_pref) ~ d_nov_pref
-    ),
-    # Keep track which type of outcome measure was chosen for each article
-    di_type = case_when(
-      !is.na(d) ~ "d",
-      !is.na(d_z_t) ~ "d_z_t",
-      !is.na(d_z_f) ~ "d_z_f",
-      !is.na(d_z_diff) ~ "d_z_diff",
-      !is.na(d_av) ~ "d_av",
-      !is.na(d_nov_pref) ~ "d_nov_pref",
-      TRUE ~ "none"
-    ) %>%
-      factor(levels = c(
-        "d", "d_z_t", "d_z_f", "d_z_diff", "d_av", "d_nov_pref", "none"
-      )),
-
-    # Apply small sample correction using Hedges' exact method
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    dfi = 2 * (sample_size - 1),
-    ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
-    gi = di * ji,
-
-    # Recode gender as a categorical (factor) variable for meta-regression
-    gender = case_when(
-      female_percent == 1.0 ~ "Female",
-      female_percent == 0.0 ~ "Male",
-      TRUE ~ "Mixed"
-    ) %>% factor(levels = c("Mixed", "Female", "Male")),
-
-    # Recode mean sample age in years (centered) for meta-regression
-    age = age_mean / 365.25,
-    age_c = age - mean(age, na.rm = TRUE),
-    age_sd = age_sd / 365.25,
-
-    # Recode task type as a categorical (factor) variale for meta-regression
-    task = factor(task, levels = c("Habituation", "VoE")),
-
-    # Combine gender and task into one column for plotting
-    gender_task = factor(
-      str_c(gender, task, sep = ", "),
-      levels = c(
-        "Female, Habituation",
-        "Male, Habituation",
-        "Mixed, Habituation",
-        "Mixed, VoE"
-      )
-    )
-  ) %>%
-  # Order rows by experiment ID
-  arrange(experiment) -> dat_all
-
-# Overview of the different effect sizes
-dat_all %>%
-  select(
-    article,
-    group,
-    gender_split,
-    gi,
-    di,
-    di_type,
-    d,
-    d_z_t,
-    d_z_f,
-    d_z_diff,
-    d_av,
-    d_nov_pref
-  ) %>%
-  print(n = Inf)
-
-# Compute standard error of Cohen's d based on assumed correlation
-# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
-# This will need a sensitivity analysis regarding the values of `r_assumed`
-r_assumed <- 0.5
-dat_all %>%
-  mutate(
-    ni = sample_size,
-    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
-      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
-    sei = sqrt(vi)
-  ) %>%
-  filter(!is.na(gi)) -> dat_all_r
-
-# Show number of experiments per gender grouping strategy
-table(dat_all_r$gender_split)
-
-# Extract split or mixed experiments only
-dat_split <- filter(dat_all_r, gender_split %in% c("split", "split_only"))
-dat_mixed <- filter(dat_all_r, gender_split %in% c("mixed", "mixed_only"))
-
-# Combine both strategies, preferring split experiments
-dat_both_split <- filter(
-  dat_all_r, gender_split %in% c("split", "mixed_only", "split_only")
-)
-
-# Combine both strategies, preferring mixed experiments
-dat_both_mixed <- filter(
-  dat_all_r, gender_split %in% c("mixed", "mixed_only", "split_only")
-)
-
-# We go ahead with the last solution as to use the maximum amount of information
-# while not biasing the gender results
-dat <- dat_both_mixed
-
-# Helper functions to re-format age from days to months + days
-format_days_months <- function(days, long = FALSE) {
-  m_str <- ifelse(long, " months ", "m ")
-  d_str <- ifelse(long, " days", "d")
-  days_per_month <- 30.417
-  months <- days %/% days_per_month
-  days_left <- as.integer(days - months * days_per_month)
-  str <- paste0(as.character(months), m_str, as.character(days_left), d_str)
-  str[is.na(days)] <- NA
-  return(str)
-}
-
-# Helper function for printing percentages
-print_perc <- function(x) scales::percent(x, accuracy = 0.1)
-
-# Extract some descriptive statistics for usage in the main text
-descs <- list(
-  n_experiments = nrow(dat),
-  n_infants = sum(dat$sample_size),
-  percent_female = mean(dat$female_percent, na.rm = TRUE),
-  min_age_months = as.integer(min(dat$age_min, na.rm = TRUE) / 30.417),
-  mean_age_weighted = format_days_months(
-    sum(dat$age_mean * dat$ni) / (sum(dat$ni)),
-    long = TRUE
-  ),
-  n_experiments_habituation = nrow(filter(dat, task == "Habituation")),
-  n_experiments_voe = nrow(filter(dat, task == "VoE"))
-)
-```
-
-# Introduction
-
-The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life [@moore2020; @johnson2020].
-Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-
-Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
-Interestingly, a recent meta-analysis [@lauer2019a] in 3-17-year-old children and adolescents suggests even only a small-to-medium difference (mean weighted $g = 0.39$).
-Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
-
-In the present study, we meta-analyzed `r descs$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descs$n_infants, big.mark = ",")` infants (`r print_perc(descs$percent_female)` female) aged `r descs$min_age_months` to `r descs$max_age_months` months (mean age of `r descs$mean_age_weighted`; Supplementary Table 1).
-All tasks were embedded either into habituation experiments (`r descs$n_experiments_habituation`) or violation of expectation experiments (`r descs$n_experiments_voe`) [@fantz1964; @baillargeon1985].
-These experiments comprised real world stimuli (e.g., toy objects [@antrilli2016]), three-dimensional digital stimuli (e.g., cube figures [@moore2008]), or two-dimensional digital stimuli (e.g., digits [@quinn2008]).
-In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object.
-Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation.
-In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle.
-Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle.
-Subsequently, the object disappeared behind an occluder.
-Finally, the occluder was removed and either the object or its mirror object were shown.
-Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle.
-In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
-
-Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average significantly longer in male compared to female infants.
-Effect sizes were assumed to be small.
-
-# Results
-
-## Mental rotation performance
-
-```{r, meta_analysis}
-# Specify priors
-prior_c <- c(
-  set_prior("normal(0, 1)", class = "b"),
-  set_prior("cauchy(0, 0.3)", class = "sd")
-)
-
-# Run prior predictive simulation
-n_iter <- 4000
-n_warmup <- 1000
-n_chains <- 4
-res_prior <- brm(
-  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
-  data = dat,
-  prior = prior_c,
-  sample_prior = "only",
-  save_pars = save_pars(all = TRUE),
-  chains = n_chains,
-  iter = n_iter,
-  warmup = n_warmup,
-  cores = n_chains,
-  control = list(adapt_delta = 0.99),
-  file = here("results", "models", "res_prior")
-)
-summary(res_prior)
-# plot(res_prior)
-
-# Run Bayesian multilevel model
-res_brm <- update(
-  res_prior,
-  sample_prior = FALSE,
-  file = here("results", "models", "res_brm")
-)
-summary(res_brm)
-# plot(res_brm)
-
-# Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_brm <- hypothesis(res_brm, "Intercept > 0")$hypothesis)
-
-# # Summarise fixed effects (incl. Bayes factors)
-# describe_posterior(
-#   res_brm,
-#   centrality = "mean", ci = 0.95, ci_method = "ETI",
-#   test = c("p_direction", "rope", "bayesfactor"),
-#   rope_range = c(-0.1, 0.1)
-# )
-
-# Extract posterior draws for the meta-analytic effects
-spread_draws(res_brm, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC
-  mutate(
-    intercept = b_Intercept,
-    sigma_article = sd_article__Intercept,
-    sigma_experiment = `sd_article:experiment__Intercept`,
-    sigma2_article = sigma_article^2,
-    sigma2_experiment = sigma_experiment^2,
-    sigma2_total = sigma2_article + sigma2_experiment,
-    icc = sigma2_article / sigma2_total,
-    .keep = "unused"
-  ) -> draws_brm
-
-# Summarize as mean and 95% credible intervals
-(summ_brm <- as.list(mean_qi(draws_brm)))
-```
-
-```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
-# Helper functions for printing numbers with exactly 2 decimal points
-print_num <- function(x, digits = 2) {
-  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
-  x[x == "NA"] <- NA
-  return(x)
-}
-
-# Helper function for confidence intervals (optionally adding the mean)
-print_ci <- function(lb, ub, mean = NULL) {
-  mean_str <- ifelse(mean, paste0(print_num(mean), " "))
-  paste0(mean_str, "[", print_num(lb), ", ", print_num(ub), "]")
-}
-
-# Get posterior draws for the effect in each experiment
-epred_draws_brm <- epred_draws(res_brm, dat, ndraws = NULL) %>%
-  mutate(experiment_f = factor(experiment))
-
-# Create forest plot
-dat %>%
-  # Make sure the plot will be ordered alphabetically by experiment IDs
-  arrange(experiment) %>%
-  mutate(
-    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
-    # Show article labels only for the first experiment per article
-    article = if_else(article == lag(article, default = ""), "", article),
-    # Compute frequentist confidence intervals
-    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_print = print_ci(ci_lb, ci_ub, mean = gi)
-  ) %>%
-  # Prepare plotting canvas
-  ggplot(aes(x = gi, y = experiment_f)) +
-  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
-  # Add article and group labels as text on the left
-  geom_text(aes(x = -9.9, label = article), hjust = 0) +
-  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
-  # Add experiment-specific effect sizes and CIs as text on the right
-  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
-  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
-  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
-  # Add Bayesian highest posterior density intervals for each experiment
-  stat_interval(
-    aes(x = .epred),
-    data = epred_draws_brm,
-    alpha = .8,
-    point_interval = "mean_qi",
-    .width = c(0.5, 0.95),
-  ) +
-  scale_color_grey(
-    start = 0.85, end = 0.65,
-    labels = as_mapper(~ scales::percent(as.numeric(.x)))
-  ) +
-  # Add experiment-specific effect sizes and CIs as dots with error bars
-  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
-  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
-  # Add posterior distribution for the meta-analytic effect
-  stat_halfeye(
-    aes(x = intercept, y = -1),
-    draws_brm,
-    point_interval = "mean_qi",
-    .width = c(0.95)
-  ) +
-  annotate(
-    "text",
-    x = c(-9.9, 3.7, 4.4, 5.1),
-    y = -0.5,
-    label = c(
-      "Three-level model",
-      print_num(summ_brm$intercept),
-      print_num(summ_brm$intercept.lower),
-      print_num(summ_brm$intercept.upper)
-    ),
-    hjust = c(0, 1, 1, 1),
-    fontface = "bold"
-  ) +
-  # Add headers for each of the for columns
-  annotate(
-    "rect",
-    xmin = -Inf,
-    xmax = Inf,
-    ymin = descs$n_experiments + 0.5,
-    ymax = Inf,
-    fill = "white"
-  ) +
-  annotate(
-    "text",
-    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
-    y = descs$n_experiments + 1.5,
-    label = c(
-      "Article",
-      "Experiment",
-      "Effect size plot",
-      "Effect size",
-      "Lower",
-      "Upper"
-    ),
-    hjust = c(0, 0, 0.5, 1, 1, 1),
-    fontface = "bold"
-  ) +
-  # Styling
-  coord_cartesian(
-    ylim = c(-1.5, descs$n_experiments + 2), expand = FALSE, clip = "off"
-  ) +
-  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
-  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
-  labs(
-    x = expression("Hedges'" ~ italic("g")),
-    size = "Sample size",
-    color = "CrI level"
-  ) +
-  theme_minimal() +
-  theme(
-    legend.position = "bottom",
-    axis.text.x = element_text(family = "Helvetica", color = "black"),
-    axis.text.y = element_blank(),
-    axis.ticks.x = element_line(colour = "black"),
-    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
-    axis.title.y = element_blank(),
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "forest.pdf"), width = 12, height = 14)
-```
-
-(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
-White squares depict the effect sizes (Hedges’ $g$) for infants’ mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
-Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI).
-These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the model.
-The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
-
-For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects.
-Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
-Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_brm$intercept`$, 95% credible interval (CrI) [`r summ_brm$intercept.lower`, `r summ_brm$intercept.upper`] (Fig.
-1).
-The probability for this effect being greater than zero was `r print_perc(hyp_brm$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm$sigma2_experiment`$, 95% CrI [`r summ_brm$sigma2_experiment.lower`, `r summ_brm$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm$sigma2_article`$, 95% CrI [`r summ_brm$sigma2_article.lower`, `r summ_brm$sigma2_article.upper`] at the article level.
-Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_brm$icc)` was attributable to differences *between* articles.
-
-## Effects of gender, age, and task type
-
-```{r, meta_regression}
-# Set numerical contrasts for factor variables
-contrasts(dat$gender) <- MASS::contr.sdif(3)
-contrasts(dat$task) <- MASS::contr.sdif(2)
-
-# Specify priors
-prior_c <- c(
-  set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
-  set_prior("normal(0, 0.5)", class = "b"),
-  set_prior("cauchy(0, 0.3)", class = "sd")
-)
-
-# Run prior predictive simulation
-res_prior_reg <- brm(
-  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
-    (1 | article / experiment),
-  data = dat,
-  prior = prior_c,
-  sample_prior = "only",
-  save_pars = save_pars(all = TRUE),
-  chains = n_chains,
-  iter = n_iter,
-  warmup = n_warmup,
-  cores = n_chains,
-  control = list(adapt_delta = 0.99),
-  file = here("results", "models", "res_prior_reg")
-)
-summary(res_prior_reg)
-# plot(res_prior_reg)
-
-# Run Bayesian multilevel model
-res_brm_reg <- update(
-  res_prior_reg,
-  sample_prior = FALSE,
-  file = here("results", "models", "res_brm_reg")
-)
-summary(res_brm_reg)
-# plot(res_brm_reg)
-
-# Get posterior probability mass > 0 for all regression weights
-(hyps_brm_reg <- list(
-  intercept = hypothesis(res_brm_reg, "Intercept > 0")$hypothesis,
-  female_mixed = hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis,
-  male_female = hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis,
-  age = hypothesis(res_brm_reg, "age_c > 0")$hypothesis,
-  voe_habituation = hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis,
-  female_mixed_age = hypothesis(res_brm_reg, "gender2M1:age_c > 0")$hypothesis,
-  male_female_age = hypothesis(res_brm_reg, "gender3M2:age_c > 0")$hypothesis
-))
-
-# # Summarise fixed effects (incl. Bayes factors)
-# describe_posterior(
-#   res_brm_reg,
-#   centrality = "mean", ci = 0.95, ci_method = "ETI",
-#   test = c("p_direction", "rope", "bayesfactor"),
-#   rope_range = c(-0.1, 0.1)
-# )
-
-# Extract posterior draws for the meta-analytic effects
-spread_draws(res_brm_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC
-  mutate(
-    intercept = b_Intercept,
-    female_mixed = b_gender2M1,
-    male_female = b_gender3M2,
-    age = b_age_c,
-    voe_habituation = b_task2M1,
-    female_mixed_age = `b_gender2M1:age_c`,
-    male_female_age = `b_gender3M2:age_c`,
-    sigma_article = sd_article__Intercept,
-    sigma_experiment = `sd_article:experiment__Intercept`,
-    sigma2_article = sd_article__Intercept^2,
-    sigma2_experiment = `sd_article:experiment__Intercept`^2,
-    sigma2_total = sigma2_article + sigma2_experiment,
-    icc = sigma2_article / sigma2_total,
-  ) -> draws_brm_reg
-
-# Summarize as mean and 95% credible intervals
-(summ_brm_reg <- as.list(mean_qi(draws_brm_reg)))
-```
-
-As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig. 2).
-Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_brm_reg$male_female`$, 95% CrI [`r summ_brm_reg$male_female.lower`, `r summ_brm_reg$male_female.upper`].
-The probability for this effect being larger than zero was `r print_perc(hyps_brm_reg$male_female$Post.Prob)`.
-We found no difference between mixed-gender and all-female samples, $b = `r -summ_brm_reg$female_mixed`$, 95% CrI [`r -summ_brm_reg$female_mixed.lower`, `r -summ_brm_reg$female_mixed.upper`] (`r print_perc(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
-Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_brm_reg$age`$, 95% [`r summ_brm_reg$age.lower`, `r summ_brm_reg$age.upper`].
-We also did not detect an interaction between gender and age ([females - mixed] × age: $b = `r summ_brm_reg$female_mixed_age`$, 95% CrI [`r summ_brm_reg$female_mixed_age.lower`, `r summ_brm_reg$female_mixed_age.upper`]; [males - females] × age: $b = `r summ_brm_reg$male_female_age`$, 95% CrI [`r summ_brm_reg$male_female_age.lower`, `r summ_brm_reg$male_female_age.upper`]).
-Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_brm_reg$voe_habituation`$, 95% [`r summ_brm_reg$voe_habituation.lower`, `r summ_brm_reg$voe_habituation.upper`].
-The probability for this effect being greater than zero was `r print_perc(hyps_brm_reg$voe_habituation$Post.Prob)`.
-
-```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
-# Get draws from the posterior distribution
-draws_reg <- epred_draws(
-  res_brm_reg,
-  dat,
-  ndraws = NULL,
-  re_formula = NA
-)
-
-# Use colors as proposed in https://arxiv.org/abs/2107.02270
-habi_colors <- c(
-  "Female, Habituation" = "#5790fc",
-  "Male, Habituation" = "#f89c20",
-  "Mixed, Habituation" = "#e42536"
-)
-voe_colors <- c("Mixed, VoE" = "#964a8b")
-
-# Regression plot
-dat %>%
-  ggplot(aes(x = age * 12, y = gi)) +
-  geom_hline(yintercept = seq(-1, 2, 0.5), color = "grey90") +
-  annotate(
-    "rect",
-    xmin = 5.5, xmax = Inf, ymin = 1.25, ymax = Inf,
-    color = NA, fill = "white"
-  ) +
-  # Regression lines and HPDIs - Habituation tasks
-  stat_lineribbon(
-    aes(y = .epred, color = gender_task),
-    data = draws_reg,
-    alpha = .4,
-    point_interval = "mean_qi",
-    .width = c(0.5, 0.95)
-  ) +
-  # Individual study effect sizes - Habituation tasks
-  geom_point(aes(color = gender_task, size = ni), shape = 0) +
-  scale_color_manual(
-    values = habi_colors,
-    breaks = names(habi_colors),
-    labels = c("Females", "Males", "Mixed gender"),
-    na.value = NA
-  ) +
-  guides(color = guide_legend(
-    title = "Habituation tasks",
-    override.aes = list(fill = NA),
-    order = 1
-  )) +
-  # Regression lines and HPDIs - VoE tasks
-  ggnewscale::new_scale_color() +
-  stat_lineribbon(
-    aes(y = .epred, color = gender_task),
-    data = draws_reg,
-    fill = NA,
-    alpha = .4,
-    point_interval = "mean_qi",
-    .width = c(0.5, 0.95)
-  ) +
-  # Individual study effect sizes - VoE tasks
-  geom_point(aes(color = gender_task, size = ni), shape = 0) +
-  scale_color_manual(
-    values = voe_colors,
-    breaks = names(voe_colors),
-    labels = c("Mixed gender"),
-    na.value = NA
-  ) +
-  guides(color = guide_legend(title = "VoE tasks", order = 2)) +
-  # Styling
-  coord_cartesian(expand = FALSE) +
-  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
-  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
-  scale_fill_grey(
-    start = 0.85, end = 0.65,
-    labels = as_mapper(~ scales::percent(as.numeric(.x)))
-  ) +
-  labs(
-    x = "Age (months)",
-    y = expression("Hedges'" ~ italic("g")),
-    fill = "CrI level",
-    size = "Sample size"
-  ) +
-  theme_classic() +
-  theme(
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    legend.direction = "vertical",
-    legend.key = element_blank(),
-    legend.position = "none",
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica", color = "black")
-  ) -> plot_reg
-
-# Extract the legend so that we can put it inside the plotting area
-plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))
-
-# Define new labels for the regression coefficients
-coef_colnames <- c(
-  "Intercept" = "b_Intercept",
-  "Females - mixed" = "b_gender2M1",
-  "Males - females" = "b_gender3M2",
-  "Age (per year)" = "b_age_c",
-  "Habituation - VoE" = "b_task2M1",
-  "(Females - Mixed) × age" = "b_gender2M1:age_c",
-  "(Males - Females) × age" = "b_gender3M2:age_c"
-)
-
-# Plot posterior distributions of the regression coefficients
-draws_reg_coef <- tidy_draws(res_brm_reg)
-draws_reg_coef %>%
-  select(all_of(coef_colnames)) %>%
-  gather() %>%
-  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
-  ggplot(aes(x = value, y = fct_rev(coef))) +
-  geom_vline(xintercept = seq(-1, 1, 0.5), color = "grey90") +
-  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
-  coord_cartesian(xlim = c(-1.25, 1.25), clip = "off") +
-  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
-  labs(x = expression("Regression weight (" * Delta * italic("g") * ")")) +
-  annotate(
-    "text",
-    label = "Fixed effects", x = -3.175, y = 7.86, hjust = 0,
-    family = "Helvetica", fontface = "bold", color = "black"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.line.x = element_line(colour = "black"),
-    axis.text.x = element_text(family = "Helvetica", color = "black"),
-    axis.text.y = element_text(
-      family = "Helvetica", color = "black", size = 3.88 * .pt,
-      hjust = 0, vjust = -0.1, margin = margin(l = 20)
-    ),
-    axis.ticks.x = element_line(color = "black"),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank(),
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica", color = "black")
-  ) -> plot_coef
-
-# Combine plots
-plot_grid(
-  plot_reg, plot_coef,
-  nrow = 1, rel_widths = c(3, 2), labels = "auto",
-  label_size = 11, label_fontfamily = "Helvetica",
-  label_x = 0.008, label_y = 0.99
-) +
-  draw_plot(plot_reg_legend, x = 0.385, y = 0.865, hjust = 0.5, vjust = 0.5)
-
-# Save plot
-ggsave(here(figures_dir, "regression_coef.pdf"), width = 12, height = 5)
-```
-
-(ref:fig2-caption) **Effects of gender, age, and task.** **a,** Squares show the effect size (Hedges’ g) for infants’ mental rotation performance in each of the 59 individual experiments.
-Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
-Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 95% and 50% credible interval (CrI).
-**b,** Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 95% Crl (thin black lines) and 50% Crl (thick black lines).
-Gray curves indicate the posterior distribution for each effect.
-
-```{r, gender_differences}
-# Extract relevant effect sizes
-gender %>%
-  # Remove redundant samples
-  filter(!redundant) %>%
-  # Add columns
-  mutate(
-
-    # Add unique experiment identifier
-    experiment = str_c(year, article, group_long, sep = ", "),
-
-    # Re-code non-significant f values as an effect of 0
-    f = as.numeric(f),
-    f_assumed = ifelse(is.nan(f), 0, f),
-
-    # Add d from two-samples t test (Lakens, 2013)
-    d_t = t * sqrt(1 / female_n + 1 / male_n),
-
-    # Add d from ANOVA F value via conversion to a t value
-    d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),
-
-    # Add d from mean difference and pooled standard deviation
-    mean_diff = mean_diff_males_mean - mean_diff_females_mean,
-    sd_diff_pooled_numerator = (male_n - 1) * (mean_diff_males_sd^2) +
-      (female_n - 1) * (mean_diff_females_sd^2),
-    df = male_n + female_n - 2,
-    sd_diff_pooled = sqrt(sd_diff_pooled_numerator / df),
-    d_diff = mean_diff / sd_diff_pooled,
-
-    # Add d from one-sample t test of novelty preference scores
-    mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
-    sd_nov_pref_pooled_numerator = (male_n - 1) * (novelty_pref_males_sd^2) +
-      (female_n) * (novelty_pref_females_sd^2),
-    sd_nov_pref_pooled = sqrt(sd_nov_pref_pooled_numerator / df),
-    d_nov_pref = mean_nov_pref / sd_nov_pref_pooled,
-
-    # Choose one type of outcome variable for each experiment
-    di = case_when(
-      # 1. If d was reported directed
-      !is.na(d) ~ d,
-      # 2. If a t test was reported
-      !is.na(d_t) ~ d_t,
-      # 3. If ANOVA was reported
-      !is.na(d_f) ~ d_f,
-      # 4. If the difference between means and their SDs were reported
-      !is.na(d_diff) ~ d_diff,
-      # 5. If novelty preference scores and their SDs were reported
-      !is.na(d_nov_pref) ~ d_nov_pref
-    ),
-    # Keep track which type of outcome measure was chosen for each article
-    di_type = case_when(
-      !is.na(d) ~ "d",
-      !is.na(d_t) ~ "d_t",
-      !is.na(d_f) ~ "d_f",
-      !is.na(d_diff) ~ "d_diff",
-      !is.na(d_nov_pref) ~ "d_nov_pref"
-    ) %>%
-      factor(levels = c("d", "d_t", "d_f", "d_diff", "d_nov_pref")),
-
-    # Apply small sample correction using Hedges' exact method
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    j = exp(lgamma(df / 2) - log(sqrt(df / 2)) - lgamma((df - 1) / 2)),
-    gi = di * j,
-
-    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
-    ni = female_n + male_n,
-    nhi = (female_n * male_n) / ni,
-    vi = (df * 2 * (1 + (gi^2 * nhi * 0.5))) / ((df - 2) * nhi) - (gi^2 / j^2),
-    sei = sqrt(vi)
-  ) %>%
-  # Remove experiments that didn't provide an effect size
-  filter(!is.na(gi)) -> dat_gender
-
-# Overview of the different effect sizes
-dat_gender %>%
-  select(
-    article,
-    group_long,
-    gi,
-    di,
-    di_type,
-    d,
-    d_t,
-    d_f,
-    d_diff,
-    sei
-  ) %>%
-  print(n = Inf)
-
-# Specify priors
-prior_c <- c(
-  set_prior("normal(0, 1)", class = "b"),
-  set_prior("cauchy(0, 0.3)", class = "sd")
-)
-
-# Run prior predictive simulation
-res_prior_gender <- brm(
-  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
-  data = dat_gender,
-  prior = prior_c,
-  sample_prior = "only",
-  save_pars = save_pars(all = TRUE),
-  chains = n_chains,
-  iter = n_iter,
-  warmup = n_warmup,
-  cores = n_chains,
-  control = list(adapt_delta = 0.99),
-  file = here("results", "models", "res_prior_gender")
-)
-summary(res_prior_gender)
-# plot(res_prior_gender)
-
-# Run Bayesian multilevel model
-res_brm_gender <- update(
-  res_prior_gender,
-  sample_prior = FALSE,
-  file = here("results", "models", "res_brm_gender")
-)
-summary(res_brm_gender)
-# plot(res_brm_gender)
-
-# Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_brm_gender <- hypothesis(res_brm_gender, "Intercept > 0")$hypothesis)
-
-# # Summarise fixed effects (incl. Bayes factors)
-# describe_posterior(
-#   res_brm_gender,
-#   centrality = "mean", ci = 0.95, ci_method = "ETI",
-#   test = c("p_direction", "rope", "bayesfactor"),
-#   rope_range = c(-0.1, 0.1)
-# )
-
-# Extract posterior draws for the meta-analytic effects
-spread_draws(res_brm_gender, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC
-  mutate(
-    intercept = b_Intercept,
-    sigma_article = sd_article__Intercept,
-    sigma_experiment = `sd_article:experiment__Intercept`,
-    sigma2_article = sigma_article^2,
-    sigma2_experiment = sigma_experiment^2,
-    sigma2_total = sigma2_article + sigma2_experiment,
-    icc = sigma2_article / sigma2_total,
-    .keep = "unused"
-  ) -> draws_brm_gender
-
-# Summarize as mean and 95% credible intervals
-(summ_brm_gender <- as.list(mean_qi(draws_brm_gender)))
-```
-
-To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_brm_gender$intercept`$, 95% Crl [`r summ_brm_gender$intercept.lower`, `r summ_brm_gender$intercept.upper`] (Supplementary Fig.
-1) and a probability of this effect being greater than zero of `r print_perc(hyp_brm_gender$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm_gender$sigma2_experiment`$, 95% CrI [`r summ_brm_gender$sigma2_experiment.lower`, `r summ_brm_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm_gender$sigma2_article`$, 95% CrI [`r summ_brm_gender$sigma2_article.lower`, `r summ_brm_gender$sigma2_article.upper`] at the article level.
-This means that `r print_perc(summ_brm_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_brm_gender$icc)` to differences between experiments *within* articles.
-
-## Evaluation of publication bias
-
-By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig. 3).
-Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero (t(57) = 3.37, p = 0.001).
-Nevertheless, a jackknife leave-one-out analysis confirmed that the current results are robust to the effects of individual studies (see Supplementary Table 5).
-
-# Discussion
-
-We analyzed looking times during mental rotation in 1,798 infants ranging from 3 to 16 months of age.
-To this end, we scrutinized the robustness of 59 experimental effect sizes.
-We found that male infants looked on average slightly longer at novel rotated objects compared to female infants.
-This effect was small and unrelated to age in the current range.
-
-## Effect size estimates
-
-We interpret the meta-regression-based estimate of the gender difference (b = 0.48, b = $Delta$g ) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
-The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference more likely report separate effect sizes for males and females.
-In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment (g = .20) can be viewed as a lower bound of the true effect size.
-This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences some of these experiments will have found a non-zero gender difference but the size of this effect was not reported because of a lack of power to render it statistically significant.
-
-## Gender differences
-
-The gender differences observed here remain to be explained by interacting genetic and environmental factors that are largely unknown.
-To the best of our knowledge, there are currently no genetic association or gene-environment interaction studies with a focus on mental rotation.
-Nevertheless, it is documented that genetic contributions to behavioral variance in mental rotation are substantially smaller than unique non-shared environmental contributions both in male and female adults (Shakeshaft et al.
-2016).
-Whether this observation also applies to infants remains to be explored.
-
-One recent study on 5-6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work (Constantinescu et al.
-2018).
-As far as we know, potentially mediating and moderating factors that could already be operational in infancy, however, are not yet empirically established.
-In a similar vein, while mental rotation training has small-to-medium post-test effects in children, it is unclear whether it can remove gender differences and be adapted to infants Uttal et al.
-(2013).
-
-Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance (Toivainen et al.
-2018, Constantinescu et al.
-2018, Erdmann et al.
-2019).
-Possible biological developmental pathways, however, bridging the gap from hormonal to behavioral differences are currently far from understood.
-
-## Additional factors
-
-A number of additional factors have been associated with individual differences in infant mental rotation performance.
-For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task (Möhring and Frick 2013; Schwarzer et al. 2013b; Slone et al. 2018).
-This relation also applies to previous experience with manually rotating toys (Schwarzer et al. 2013b).
-While these preliminary results require replication they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g.
-Ausubel 1968; Bradley & Bryant 1983; Halberda et al.
-2008).
-Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control and crawling skills (Schwarzer et al.
-2013a; Schwarzer et al.
-2013b).
-
-# Conclusion
-
-The present study robustly revealed that male infants look slightly but significantly longer at novel rotated objects than female infants.
-Thus, on average, males outperform females in mental rotation already in the first months of life.
-
-# Methods
-
-## Protocol
-
-We used established PRISMA 2020 (Preferred Reporting Items for Systematic reviews and Meta-Analyses; Page et al., 2021) guidelines to conduct this meta-analysis.
-Fig.
-4 presents the PRISMA flowchart and Supplementary Table 2 contains the PRISMA checklist.
-
-```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", out.width="50%"}
-# Include the flowchart (created with MS PowerPoint)
-knitr::include_graphics(here("results/figures/flowchart.pdf"))
-```
-
-(ref:fig4-caption) Literature search and selection process.
-We searched four online databases as well as review articles and reference sections to identify articles that reported mental rotation experiments in infants.
-Experiments from these articles were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
-Redundant articles that reported the same experiment(s) as another article were excluded.
-aAdditional reasons for excluding articles were an experimental paradigm that differed substantially compared to all other articles (1 article) and a sample of infants that was substantially older compared to all other articles (1 article).
-
-## Eligibility criteria
-
-Articles needed to fulfill six criteria for being included in the meta-analysis: (1) The article was written English or German; (2) The article includes results from a group study with human participants (excluding review articles, meta-analyses, case studies, and animal studies); (3) These participants include at least one group of infants (mean age between 0.0 and 3.0 years); (4) Infants had no preterm status or clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see below).
-We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
-
-## Information sources and search strategy
-
-We entered the search terms ("mental rotation" OR "mental transformation" OR "spatial rotation" OR "spatial transformation" OR "spatial ability" OR "spatial skills") AND ("infant" OR "infants" OR "infanthood" OR "toddler" OR "toddlers" OR "toddlerhood" OR "child" OR "children" OR "childhood" OR "month" OR "months") into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, ProQuest Dissertations & Theses Global).
-All database queries were completed on December 6, 2021.
-We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Figure 1).
-We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills (Frick et al., 2014; Johnson & Moore, 2020; Kubicek & Schwarzer, 2018; Lauer et al., 2019; Linn & Petersen, 1985; Moore & Johnson, 2020; Uttal et al., 2013; Voyer et al., 1995; Yang et al., 2020).
-Of these, 34 had not been covered by the database search.
-We also identified 94 articles by screening the reference sections of all articles that had been included after the first pass of the selection process.
-Of these, 49 had not been covered by the database search.
-We thus screened 2,037 unique articles in total.
-
-## Selection process
-
-Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
-Interrater agreement for the binary decision to include versus exclude an article was 98.5% ($Kappa$w [Cohen's weighted kappa] = 0.67, 95% CI [0.55, 0.78]).
-Interrater agreement for the specific eligibility criteria were 88.2% ($Kappa$w = 0.72, 95% CI [0.40, 1.00]).
-Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
-One article (Mash et al., 2007) was excluded because the authors used a unique mental rotation paradigm that was not comparable to that used in the other articles.
-One article (Pedrett et al., 2020) was excluded because the average age of the infants (30.7 months) was almost twice as high as that of the next article (15.8 months), z = ???
-compared to all articles.
-We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of 23 articles being included in the meta-analysis (Fig. 4).
-
-Many of these articles consisted of multiple experiments, e.g., using different variations of the mental rotation task or different subpopulations of infants.
-We included all of these experiments in the meta-analysis and accounted for the dependencies between them by means of multilevel modeling with by-article random effects (see below).
-However, we excluded experiments if there was insufficient information to compute a standardized effect size (see below).
-Whenever an article reported separate effect sizes for boys and girls---or other subgroups like crawling and non-crawling infants)---but also an effect size combining these groups, we only included the combined effect size.
-We dropped effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of 59 experiments being included in the meta-analysis (Supplementary Table 1).
-
-## Data collection process and items
-
-Outcome measures and other relevant variables were extracted from each article by one of three raters and verified by a second rater.
-Outcome measures were any summary statistic (Table 1) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
-Other extracted variables included, if available, the sample size, the number of girls and boys, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habitation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table 1).
-
-```{r, tab1, include=TRUE}
-print("Nice table goes here")
-```
-
-No study investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
-
-## Effect size measures
-
-One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' g) using the formulas provided in Table 1.
-The sampling variance Var_g of the outcome measure g for each experiment was computed using the formula provided by Goulet-Pelletier & Cousineau (2018):
-
-v = (df(df - 2)) \* ((2 \* (1 - r)) / n) \* (1 + g\^2 \* (n / (2 \* (1 - r)))) - (g\^2 / j\^2)
-
-where n is the sample size of the experiment, df are the degrees of freedom (with df=2\*(n-1)), r is the correlation between the two dependent measures in the experiment, and j is the correction factor for small samples as described in Table 1.
-The correlation r was not reported in any of the original articles.
-We therefore always assumed a correlation of r = .50 to make our analysis comparable to standard (between-group) meta-analyses (Lakens, 2013) and because we were able to infer an average correlation of r $\approx$ .50 from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from r = -.90 via r = .00 to r = .90 had no meaningful impact on the meta-analytic effect size (Supplementary Table 3).
-
-For the meta-analysis of gender differences within each article, effect sizes were computed according to the following formulas in Table yy, and redundant groups were excluded from the analysis.
-
-```{r, tab2, include=TRUE}
-print("Nice table goes here")
-```
-
-Furthermore, the sampling variance was computed according to the following equation:
-
-$sigma$between group = dfdf -2 2ñ1 + g2ñ2- g2J2
-
-Where ñ is the harmonic mean of the group sizes and ñ = nmale nmalenfemale + nmale.
-A sensitivity analysis reported in supplementary xxx highlights the stability of the effect size computed using the Bayesian meta analysis.
-
-## Bayesian meta-analysis
-
-We synthesized the effect sizes and their sampling variances using a Bayesian multilevel model.
-This model had three levels, with infant participants nested in experiments and experiments nested in articles (Van den Noortgate et al., 2013).
-We used a weakly-informative normal (N(0,1)) prior for the meta-analytic effect size and a weakly-informative half-Cauchy (HC(0, 0.3)) prior for all standard deviations (Williams et al., 2018).
-A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 3).
-All Bayesian models were fitted using the brms package (Version 2.16.3; Bürkner, 2017, 2018) in R (Version 4.1.2; R Core Team, 2021) and the Stan language (Version 2.29.2; Stan Development Team, 2022).
-Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling 10,000 draws (including 5,000 warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the R\_{hat} and N\_{eff} statistics (Vehtari et al., 2021; Supplementary Fig. 1).
-For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results (Kruschke, 2015).
-
-## Bayesian meta-regression
-
-We examined the influence of three moderator variables on the mental rotation outcomes across studies, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
-Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts so that we could compare all-female versus mixed samples and all-male samples versus all-female samples (Schad et al., 2020).
-Age was coded as a continuous predictor in years and centered by subtracting the average across all studies.
-Task was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast (Schad et al., 2020).
-We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender task type (i.e., [female - mixed] × age and [male - female] × age) into a Bayesian meta-regression model.
-This model used the same random effects structure and sampling and sampling parameters as described above.
-
-## Frequentist meta-analysis
-
-We verified the results from our Bayesian analyses using classical (frequentist) meta-analysis and meta-regression.
-We used the metafor package (Version 3.0.2; Viechtbauer, 2010) in R to specify the same three-level models as described above but dropping the Bayesian priors (Supplementary Table 3).
-The models were fitted using restricted maximum likelihood estimation (REML).
-To verify that REML converged on the correct estimates, we examined profile likelihood plots for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; see Supplementary Fig.
-2).
-
-## Reporting bias and certainty assessment
-
-We assessed publication bias by means of a funnel plot and Egger regression test (Egger et al. 1997).
-We adapted code from the R package metaviz (Version 0.3.1; Kossmeier et al., 2020) to produce the funnel plot and used the R package metafor for the Egger regression test.
-We examined heterogeneity in our study samples by means of a jackknife leave-one-out-analysis (Gee 2005).
-We adapted code from the bootstrap R package (Version 2019.6; Scott Kostyshak et al., 2019) to fit the Bayesian model repeatedly to our study samples, leaving out one experiment sample for every iteration.
-To take into account the variance inherent in Bayesian model estimation, we averaged over x iterations of the jackknife.
-
-## Data & code availability
-
-Blah blah blah
-
-# References
-
-<div id="refs"></div>
-
-\newpage
+<!-- Restart numbering of figures, tables, equations, and pages -->
+\renewcommand{\thefigure}{\arabic{figure}}
+\renewcommand{\thetable}{\arabic{table}}
+\renewcommand{\theequation}{\arabic{table}}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\setcounter{equation}{0}
+\setcounter{page}{1}
 

### 2022-05-05 supplement.Rmd
Add gender differences to frequentist

@@
 
+# Display the table
+apa_table(
+  tabs1,
+  caption = "Experiments included in the main analysis",
+  landscape = TRUE, font_size = "scriptsize"
+)
+
 # Save the table
-write_csv(tabs1, file = here(tables_dir, "within_experiments.csv"), na = "n/a")
+write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")
+```
+
+\renewcommand{\arraystretch}{1.5}
+
+```{r, frequentist}
+# Three-level model
+res_freq <- rma.mv(
+  gi, vi,
+  random = ~ 1 | article / experiment,
+  data = dat,
+  slab = experiment
+)
+print(res_freq)
+
+# Check share of variance at each level of the model
+round(res_freq$sigma2[1] / sum(res_freq$sigma2), 3) # Between-art. (ICC)
+round(res_freq$sigma2[2] / sum(res_freq$sigma2), 3) # Within-art. (between-exp.)
+
+# Meta-regression with gender, age, and task
+res_reg_freq <- rma.mv(
+  gi, vi,
+  mods = ~ gender * age_c + task,
+  random = ~ 1 | article / experiment,
+  data = dat,
+  slab = experiment
+)
+print(res_reg_freq)
+
+# Meta-analysis of gender differences
+res_gender_freq <- rma.mv(
+  gi, vi,
+  random = ~ 1 | article / experiment,
+  data = dat_gender,
+  slab = experiment
+)
+print(res_gender_freq)
+```
+
+```{r, tabs2, include=TRUE}
+# Format all frequentist results together as a table
+map2_dfr(
+  c("Meta-analysis", "Meta-regression", "Gender differences"),
+  list(res_freq, res_reg_freq, res_gender_freq),
+  function(name, res) {
+    # Intercept / regression weights
+    tibble(
+      Model = c(name, rep(NA, length(res$b) - 1)),
+      Parameter = rownames(res$b),
+      Estimate = print_num(as.numeric(res$b)),
+      `$SE$` = print_num(res$se),
+      `$z$` = print_num(res$zval),
+      `$p$` = print_num(res$pval, digits = 3),
+      ci_lower = print_num(res$ci.lb),
+      ci_upper = print_num(res$ci.ub)
+    ) %>%
+      # Re-format confidence interval
+      mutate(
+        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
+        .keep = "unused"
+      ) %>%
+      # Add variances
+      bind_rows(tibble(
+        Parameter = res$s.name,
+        Estimate = print_num(res$sigma2)
+      ))
+  }
+) %>%
+  # Rename parameters for readibility
+  mutate(
+    Parameter = c(
+      "Hedges' $g$",
+      "$\\sigma_{\\text{Article}}^2$",
+      "$\\sigma_{\\text{Experiment}}^2$",
+      "Intercept",
+      "Female - mixed",
+      "Male - female",
+      "Age (per year)",
+      "Habituation - VoE",
+      "(Female - mixed) × age",
+      "(Male - female) × age",
+      "$\\sigma_{\\text{Article}}^2$",
+      "$\\sigma_{\\text{Experiment}}^2$",
+      "Hedges' $g$",
+      "$\\sigma_{\\text{Article}}^2$",
+      "$\\sigma_{\\text{Experiment}}^2$"
+    )
+  ) %>%
+  # Replace NAs with blank cells
+  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
 
@@
 apa_table(
-  tabs1,
-  caption = "Experiments included in the main analysis", label = "S1",
-  landscape = TRUE, font_size = "scriptsize"
+  tab_freq,
+  align = "llccccc",
+  caption = "Frequentist meta-analyses and meta-regression",
+  font_size = "scriptsize",
+  escape = FALSE
 )
+
+# Save the table
+write_csv(tab_freq, file = here(tables_dir, "tabs2_frequentist.csv"))
 ```
+
+```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
+# Compute empirical estimate of the correlation between dependent samples
+dat %>%
+  mutate(
+    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
+    d_diff = case_when(
+      !is.na(d) ~ d,
+      !is.na(d_z_t) ~ d_z_t,
+      !is.na(d_z_f) ~ d_z_f,
+      !is.na(d_z_diff) ~ d_z_diff
+    ),
+    # Compute empirical correlation
+    # Basesd on the SD of the difference and the SDs within the two conditions
+    sd_diff = mean_diff / d_diff,
+    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
+      (-2 * sd_novel * sd_familiar)
+  ) %>%
+  pull(ri) -> ri_empirical
+
+# Summarise the estimated correlations
+summary(ri_empirical)
+
+# Re-run the meta-analysis for different values of r_assumed
+seq(-0.9, 0.9, by = 0.3) %>%
+  set_names(., str_c("r = ", print_num(.))) %>%
+  map(function(ri_sens) {
+
+    # Re-compute standard errors of the effect sizes
+    mutate(
+      dat,
+      vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
+        (1 + gi^2 * (ni / (2 * (1 - ri_sens)))) - (gi^2 / ji^2),
+      sei = sqrt(vi)
+    ) -> dat_ri_sens
+
+    # Re-run meta-analysis
+    update(res_brm, newdata = dat_ri_sens, refresh = 0)
+  }) -> res_ri_sens
+
+# Prior sensitivity analysis
+list(
+  "Intercept U(-10,10)" = c(
+    set_prior("uniform(-10, 10)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
+  ),
+  "Intercept N(0,0.2)" = c(
+    set_prior("normal(0, 0.2)", class = "Intercept"),
+    set_prior("cauchy(0, 0.3)", class = "sd")
+  ),
+  "SD U(0,10)" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("uniform(0, 10)", class = "sd")
+  ),
+  "SD Student-t(10,0,0.2)" = c(
+    set_prior("normal(0, 1)", class = "Intercept"),
+    set_prior("student_t(10, 0, 0.2)", class = "sd")
+  )
+) %>%
+  # Re-run the meta-analysis with different priors
+  map(
+    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
+  ) -> res_prior_sens
+
+# Create a table summarizing all sensitivity analyses
+map2_dfr(
+  c(res_ri_sens, res_prior_sens),
+  c(names(res_ri_sens), names(res_prior_sens)),
+  function(res, name) {
+
+    # Compute ICC
+    var_experiment <- as.matrix(
+      res,
+      variable = "sd_article:experiment__Intercept"
+    )^2
+    var_article <- as.matrix(
+      res,
+      variable = "sd_article__Intercept"
+    )^2
+    var_total <- var_experiment + var_article
+    icc <- var_article / var_total
+    icc_row <- mean_qi(icc) %>%
+      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)
+
+    # Create a data frame row of summary statistics
+    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
+      bind_rows(icc_row) %>%
+      transmute(
+        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
+        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
+      ) %>%
+      pivot_wider(names_from = parameter, values_from = Estimate) %>%
+      bind_cols(Simulation = name, .)
+  }
+) -> tab_sens
+
+# Display the table
+apa_table(
+  tab_freq,
+  caption = "Sensitivity analyses",
+  font_size = "scriptsize"
+)
+
+# Save the table
+write_csv(tab_sens, file = here(tables_dir, "sensitivity.csv"))
+```
+
+<!-- Supplementary figures -->
 
@@
 
-(ref:figs2-caption) Convergence checks.
-
-```{r, frequentist_results}
-# Three-level model
-res_ml <- rma.mv(
-  gi, vi,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_ml)
-# forest(res_ml)
-
-# Check share of variance at each level of the model
-round(res_ml$sigma2[1] / sum(res_ml$sigma2), 3) # Between-article (ICC)
-round(res_ml$sigma2[2] / sum(res_ml$sigma2), 3) # Within-article (between-exp.)
-
-# # Profile likelihodd plots for checking that REML has converged
-# profile(res_ml)
-
-# Meta-regression with gender, age, and task
-res_reg <- rma.mv(
-  gi, vi,
-  mods = ~ gender * age_c + task,
-  random = ~ 1 | article / experiment,
-  data = dat,
-  slab = experiment
-)
-print(res_reg)
-# forest(res_full)
-
-# Extract standard deviations and ICCs
-vars_ml <- list(matrix())
-
-# Export results as a table
-map2_dfr(
-  c("Meta-analysis", "Meta-regression"),
-  list(res_ml, res_reg),
-  function(name, res) {
-    # Intercept / regression weights
-    tibble(
-      Model = c(name, rep(NA, length(res$b) - 1)),
-      Parameter = rownames(res$b),
-      Estimate = print_num(as.numeric(res$b)),
-      SE = print_num(res$se),
-      z = print_num(res$zval),
-      p = print_num(res$pval, digits = 3),
-      ci_lower = print_num(res$ci.lb),
-      ci_upper = print_num(res$ci.ub)
-    ) %>%
-      # Re-format confidence interval
-      mutate(
-        `95% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
-        .keep = "unused"
-      ) %>%
-      # Add variances
-      bind_rows(tibble(
-        Parameter = res$s.name,
-        Estimate = print_num(res$sigma2)
-      ))
-  }
-) %>%
-  mutate(
-    Parameter = c(
-      "Hedges' g",
-      "s2article",
-      "s2experiment",
-      "Intercept",
-      "Female - mixed",
-      "Male - female",
-      "Age (per year)",
-      "Habituation - VoE",
-      "(Female - mixed) × age",
-      "(Male - female) × age",
-      "s2article",
-      "s2experiment"
-    )
-  ) -> tab_freq
-
-# Save the table
-write_csv(tab_freq, file = here(tables_dir, "frequentist_results.csv"), na = "")
-```
-
-```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
-# Compute empirical estimate of the correlation between dependent samples
-dat %>%
-  mutate(
-    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
-    d_diff = case_when(
-      !is.na(d) ~ d,
-      !is.na(d_z_t) ~ d_z_t,
-      !is.na(d_z_f) ~ d_z_f,
-      !is.na(d_z_diff) ~ d_z_diff
-    ),
-    # Compute empirical correlation
-    # Basesd on the SD of the difference and the SDs within the two conditions
-    sd_diff = mean_diff / d_diff,
-    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
-      (-2 * sd_novel * sd_familiar)
-  ) %>%
-  pull(ri) -> ri_empirical
-
-# Summarise the estimated correlations
-summary(ri_empirical)
-
-# Re-run the meta-analysis for different values of r_assumed
-seq(-0.9, 0.9, by = 0.3) %>%
-  set_names(., str_c("r = ", print_num(.))) %>%
-  map(function(ri_sens) {
-
-    # Re-compute standard errors of the effect sizes
-    mutate(
-      dat,
-      vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
-        (1 + gi^2 * (ni / (2 * (1 - ri_sens)))) - (gi^2 / ji^2),
-      sei = sqrt(vi)
-    ) -> dat_ri_sens
-
-    # Re-run meta-analysis
-    update(res_brm, newdata = dat_ri_sens, refresh = 0)
-  }) -> res_ri_sens
-
-# Prior sensitivity analysis
-list(
-  "Intercept U(-10,10)" = c(
-    set_prior("uniform(-10, 10)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "Intercept N(0,0.2)" = c(
-    set_prior("normal(0, 0.2)", class = "Intercept"),
-    set_prior("cauchy(0, 0.3)", class = "sd")
-  ),
-  "SD U(0,10)" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("uniform(0, 10)", class = "sd")
-  ),
-  "SD Student-t(10,0,0.2)" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
-    set_prior("student_t(10, 0, 0.2)", class = "sd")
-  )
-) %>%
-  # Re-run the meta-analysis with different priors
-  map(
-    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
-  ) -> res_prior_sens
-
-# Create a table summarizing all sensitivity analyses
-map2_dfr(
-  c(res_ri_sens, res_prior_sens),
-  c(names(res_ri_sens), names(res_prior_sens)),
-  function(res, name) {
-
-    # Compute ICC
-    var_experiment <- as.matrix(
-      res,
-      variable = "sd_article:experiment__Intercept"
-    )^2
-    var_article <- as.matrix(
-      res,
-      variable = "sd_article__Intercept"
-    )^2
-    var_total <- var_experiment + var_article
-    icc <- var_article / var_total
-    icc_row <- mean_qi(icc) %>%
-      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)
-
-    # Create a data frame row of summary statistics
-    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
-      bind_rows(icc_row) %>%
-      transmute(
-        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
-        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
-      ) %>%
-      pivot_wider(names_from = parameter, values_from = Estimate) %>%
-      bind_cols(Simulation = name, .)
-  }
-) -> tab_sens
-
-# Save the table
-write_csv(tab_sens, file = here(tables_dir, "sensitivity_analysis.csv"))
-```
+(ref:figs2-caption) **Convergence checks for the Bayesian meta-analysis.** For each of the three parameters in the three-level meta-analytic model, gray traces show the exploration of the posterior distribution by four independent Markov Chain Monte Carlo (MCMC) chains.
+Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution.
+Rhat = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, Neff(bulk) = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), Neff(tail) = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
+For details about these and other convergence criteria, we refer the reader to @vehtari2021.

### 2022-05-05 supplement.Rmd
Add profile likelihood plots

@@
 round(res_freq$sigma2[2] / sum(res_freq$sigma2), 3) # Within-art. (between-exp.)
+
+# Get profile likelihoods for sigmas to check that REML has converged
+prof_liks <- profile(res_freq, plot = FALSE)
 
@@
 # Save the plot
-ggsave(here(figures_dir, "forest_gender.pdf"), width = 12, height = 8)
+ggsave(here(figures_dir, "figs1_gender.pdf"), width = 12, height = 8)
 ```
@@
 # Save the plot
-ggsave(here(figures_dir, "trace.pdf"), width = 12, height = 6)
+ggsave(here(figures_dir, "figs2_convergence.pdf"), width = 12, height = 6)
 ```
@@
 For details about these and other convergence criteria, we refer the reader to @vehtari2021.
+
+```{r, figs3, include=TRUE, fig.height=4, fig.width=12, fig.cap="(ref:figs3-caption)"}
+# Combine profile likelihood results into one data frame
+prof_liks %>%
+  head(-1) %>% # Remove the `comp` element
+  map(~ tibble(sigma2 = .$sigma2, ll = .$ll)) %>%
+  bind_rows(.id = "parameter") %>%
+  # Create new labels for plotting
+  mutate(parameter = factor(
+    parameter,
+    levels = c(1, 2),
+    labels = c("italic(sigma)[article]^2", "italic(sigma)[experiment]^2")
+  )) -> prof_liks_df
+
+# Find the best-fitting parameter estimates
+prof_liks_df %>%
+  group_by(parameter) %>%
+  filter(ll == max(ll)) -> prof_liks_max
+
+# Create plot
+prof_liks_df %>%
+  ggplot(aes(x = sigma2, y = ll)) +
+  facet_wrap(~parameter, scales = "free", labeller = label_parsed) +
+  # Best fitting parameters
+  geom_hline(
+    aes(yintercept = ll),
+    data = prof_liks_max, linetype = "dashed"
+  ) +
+  geom_vline(
+    aes(xintercept = sigma2),
+    data = prof_liks_max, linetype = "dashed"
+  ) +
+  # All tested parameters
+  geom_point() +
+  geom_line() +
+  # Styling
+  labs(x = "Parameter value", y = "Restricted log-likelihood") +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    strip.background = element_blank(),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "figs3_convergence_freq.pdf"), width = 12, height = 4)
+```
+
+(ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Profile likelihood plots [@raue2009; @viechtbauer2010] indicate that restricted maximum likelihood estimation (REML) was able to identify the most likely parameter estimates for the two variance components in the three-level meta-analytic model, that is, for the between-article variance and for the between-experiment (within-article) variance.

### 2022-05-05 manuscript.Rmd
Improve figure placement

@@
   message = FALSE,
+  fig.align = "center",
   fig.height = 10,
+  fig.pos = "tp",
   fig.width = 7.5,

### 2022-05-05 manuscript.Rmd
Incorporate discussion

@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
@@
   min_age_months = as.integer(min(dat$age_min, na.rm = TRUE) / 30.417),
+  max_age_months = as.integer(max(dat$age_max, na.rm = TRUE) / 30.417),
   mean_age_weighted = format_days_months(
@@
 
-We analyzed looking times during mental rotation in 1,798 infants ranging from 3 to 16 months of age.
-To this end, we scrutinized the robustness of 59 experimental effect sizes.
+We analyzed looking times during mental rotation in `r formatC(descs$n_infants, big.mark = ",")` infants ranging from `r descs$min_age_months` to `r descs$max_age_months` months of age.
+To this end, we scrutinized the robustness of `r descs$n_experiments` experimental effect sizes.
 We found that male infants looked on average slightly longer at novel rotated objects compared to female infants.
@@
 
-We interpret the meta-regression-based estimate of the gender difference (b = 0.48, b = $Delta$g ) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
+We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_brm_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
 The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference more likely report separate effect sizes for males and females.
-In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment (g = .20) can be viewed as a lower bound of the true effect size.
-This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences some of these experiments will have found a non-zero gender difference but the size of this effect was not reported because of a lack of power to render it statistically significant.
+In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_brm_gender$intercept`$) can be viewed as a lower bound of the true effect size.
+This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences were likely also observed but just not reported because of missing power to render these effects statistically significant.
 
@@
 To the best of our knowledge, there are currently no genetic association or gene-environment interaction studies with a focus on mental rotation.
-Nevertheless, it is documented that genetic contributions to behavioral variance in mental rotation are substantially smaller than unique non-shared environmental contributions both in male and female adults (Shakeshaft et al.
-2016).
+Nevertheless, it is documented that genetic contributions to behavioral variance in mental rotation are substantially smaller than unique non-shared environmental contributions both in male and female adults [@shakeshaft2016].
 Whether this observation also applies to infants remains to be explored.
 
-One recent study on 5-6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work (Constantinescu et al.
-2018).
+One recent study on 5--6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work [@constantinescu2018].
 As far as we know, potentially mediating and moderating factors that could already be operational in infancy, however, are not yet empirically established.
-In a similar vein, while mental rotation training has small-to-medium post-test effects in children, it is unclear whether it can remove gender differences and be adapted to infants Uttal et al.
-(2013).
-
-Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance (Toivainen et al.
-2018, Constantinescu et al.
-2018, Erdmann et al.
-2019).
+In a similar vein, while mental rotation training has small-to-medium post-test effects in children, it is unclear whether it can remove gender differences and be adapted to infants [@uttal2013].
+
+Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance [@toivainen2018; @constantinescu2018; @erdmann2019].
 Possible biological developmental pathways, however, bridging the gap from hormonal to behavioral differences are currently far from understood.
@@
 A number of additional factors have been associated with individual differences in infant mental rotation performance.
-For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task (Möhring and Frick 2013; Schwarzer et al. 2013b; Slone et al. 2018).
-This relation also applies to previous experience with manually rotating toys (Schwarzer et al. 2013b).
+For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task [@mohring2013; @schwarzer2013a; @slone2018].
+This relation also applies to previous experience with manually rotating toys [@schwarzer2013a].
 While these preliminary results require replication they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g.
-Ausubel 1968; Bradley & Bryant 1983; Halberda et al.
-2008).
-Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control and crawling skills (Schwarzer et al.
-2013a; Schwarzer et al.
-2013b).
+[@ausubel1968; @bradley1983; @halberda2008]).
+Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].
 

### 2022-05-06 manuscript.Rmd
Add draft for LaTeX tables

@@
 descs <- list(
+  n_articles = length(unique(dat$article)),
   n_experiments = nrow(dat),
@@
 
-We used established PRISMA 2020 (Preferred Reporting Items for Systematic reviews and Meta-Analyses; Page et al., 2021) guidelines to conduct this meta-analysis.
-Fig.
-4 presents the PRISMA flowchart and Supplementary Table 2 contains the PRISMA checklist.
+In the present meta-analysis we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses [@page2021]).
+The PRISMA flowchart is provided in Fig.
+4 and Supplementary Table 4 contains the PRISMA checklist.
 
@@
 
-(ref:fig4-caption) Literature search and selection process.
-We searched four online databases as well as review articles and reference sections to identify articles that reported mental rotation experiments in infants.
-Experiments from these articles were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
-Redundant articles that reported the same experiment(s) as another article were excluded.
-aAdditional reasons for excluding articles were an experimental paradigm that differed substantially compared to all other articles (1 article) and a sample of infants that was substantially older compared to all other articles (1 article).
+(ref:fig4-caption) **Literature search and selection process.** **a,** We searched four online databases as well as reviews and reference sections to identify articles in which mental rotation experiments in infants were reported.
+**b,** Experiments were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
+**c,** Redundant articles comprising the same experiment(s) were excluded.
+aAdditionally, we excluded an article that was based on an uncommon experimental paradigm differing substantially from all other articles (1 article).
+Finally, we excluded an article that was based on a sample of infants  who were substantially older compared to all other articles (1 article).
 
@@
 
-Articles needed to fulfill six criteria for being included in the meta-analysis: (1) The article was written English or German; (2) The article includes results from a group study with human participants (excluding review articles, meta-analyses, case studies, and animal studies); (3) These participants include at least one group of infants (mean age between 0.0 and 3.0 years); (4) Infants had no preterm status or clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see below).
+Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection and process items below).
 We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
@@
 
-We entered the search terms ("mental rotation" OR "mental transformation" OR "spatial rotation" OR "spatial transformation" OR "spatial ability" OR "spatial skills") AND ("infant" OR "infants" OR "infanthood" OR "toddler" OR "toddlers" OR "toddlerhood" OR "child" OR "children" OR "childhood" OR "month" OR "months") into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, ProQuest Dissertations & Theses Global).
+We entered the search terms (“mental rotation” OR “mental transformation” OR “spatial rotation” OR “spatial transformation” OR “spatial ability” OR “spatial skills”) AND (“infant” OR “infants” OR “infanthood” OR “toddler” OR “toddlers” OR “toddlerhood” OR “child” OR “children” OR “childhood” OR “month” OR “months”) into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, and ProQuest Dissertations & Theses Global).
 All database queries were completed on December 6, 2021.
 We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Figure 1).
-We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills (Frick et al., 2014; Johnson & Moore, 2020; Kubicek & Schwarzer, 2018; Lauer et al., 2019; Linn & Petersen, 1985; Moore & Johnson, 2020; Uttal et al., 2013; Voyer et al., 1995; Yang et al., 2020).
-Of these, 34 had not been covered by the database search.
-We also identified 94 articles by screening the reference sections of all articles that had been included after the first pass of the selection process.
-Of these, 49 had not been covered by the database search.
-We thus screened 2,037 unique articles in total.
+This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Figure 4a).
+We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills [@frick2014; @johnson2020; @kubicek2018; @lauer2019a; @linn1985; @moore2020; @uttal2013; @voyer1995; @yang2020].
+Of these, 34 articles had not been covered by the database search.
+We also identified 94 articles by screening the reference sections of all publications that had been included after the first pass of the selection process.
+Of these, 49 articles had not been covered by the database search.
+Accordingly, we screened 2,037 unique articles in total.
 
@@
 
+```{r, selection_process}
+# Compute interrater agreement for binary decision (include vs. exclude)
+(irr_bin_perc <- with(screening, mean(bin_1 == bin_2)))
+(irr_bin_kappa <- with(screening, psych::cohen.kappa(cbind(bin_1, bin_2))))
+irr_bin_kappa_w <- as.list(irr_bin_kappa$confid["weighted kappa", ])
+
+# Compute interrater agreement for specific exclusion codes
+(irr_code_perc <- with(screening, mean(code_1 == code_2)))
+(irr_code_kappa <- with(screening, psych::cohen.kappa(cbind(code_1, code_2))))
+irr_code_kappa_w <- as.list(irr_code_kappa$confid["weighted kappa", ])
+
+# Justify exclusion of @pedrett2020 based on outlier mean age
+mean_age_pedrett2020 <- 2.56 * 365.25 # In days
+mean_age_pedrett2020_m <- mean_age_pedrett2020 / 30.417 # In months
+mean_age_pedrett2020_z <- (mean_age_pedrett2020 - mean(dat$age_mean)) /
+  sd(dat$age_mean) # As z score
+
+```
+
 Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
-Interrater agreement for the binary decision to include versus exclude an article was 98.5% ($Kappa$w [Cohen's weighted kappa] = 0.67, 95% CI [0.55, 0.78]).
-Interrater agreement for the specific eligibility criteria were 88.2% ($Kappa$w = 0.72, 95% CI [0.40, 1.00]).
+Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen’s weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]).
+Interrater agreement for the specific eligibility criteria were `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r irr_code_kappa_w$upper`]).
 Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
-One article (Mash et al., 2007) was excluded because the authors used a unique mental rotation paradigm that was not comparable to that used in the other articles.
-One article (Pedrett et al., 2020) was excluded because the average age of the infants (30.7 months) was almost twice as high as that of the next article (15.8 months), z = ???
-compared to all articles.
+One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles.
+Another article [@pedrett2020] was excluded because the average age of the infants studied (`r round(mean_age_pedrett2020_m, 1)` months) was almost twice as high as the average age of the next article (`r round(max(dat$age_mean), 1)` months; $z = `r mean_age_pedrett2020_z`$ compared to all articles).
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of 23 articles being included in the meta-analysis (Fig. 4).
-
-Many of these articles consisted of multiple experiments, e.g., using different variations of the mental rotation task or different subpopulations of infants.
-We included all of these experiments in the meta-analysis and accounted for the dependencies between them by means of multilevel modeling with by-article random effects (see below).
-However, we excluded experiments if there was insufficient information to compute a standardized effect size (see below).
-Whenever an article reported separate effect sizes for boys and girls---or other subgroups like crawling and non-crawling infants)---but also an effect size combining these groups, we only included the combined effect size.
-We dropped effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of 59 experiments being included in the meta-analysis (Supplementary Table 1).
+This procedure led to a total of `r descs$n_articles` articles being included in the meta-analysis (Fig.
+4).
+
+Many of these articles consisted of multiple experiments, e.g., using different variations of the mental rotation task or different subsamples of infants.
+We included all of these experiments in the meta-analysis and accounted for the dependencies between them by means of multilevel modeling with by-article random effects (see Bayesian meta-analysis below).
+However, we excluded experiments if there was insufficient information to compute a standardized effect size (see Data collection process and items below).
+Whenever an article reported separate effect sizes for males and females---or other subgroups like crawling and non-crawling infants---but also an effect size combining these groups, we only included the combined effect size.
+Moreover, we disregarded effect sizes that were clearly based on the same data but reported in different articles.
+This procedure led to a total of `r descs$n_experiments` experiments being included in the meta-analysis (Supplementary Table 1).
 
@@
 Outcome measures were any summary statistic (Table 1) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
-Other extracted variables included, if available, the sample size, the number of girls and boys, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habitation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table 1).
-
-```{r, tab1, include=TRUE}
-print("Nice table goes here")
+Other extracted variables included, if available, the sample size, the number of males and females, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habituation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table 1).
+
+\scriptsize
+
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| Available statistics                                                  | Conversion to standardized mean difference (Hedges' $g$)                             |
++=======================================================================+======================================================================================+
+| (1) Cohen's $d$ and sample size $n$                                   | $df=2(n-1)$;\quad                                                                    |
+| [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
+|                                                                       | $g=d*j$                                                                              |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (2) $t$-statistic and sample size $n$                                 | $d=\frac{t}{\sqrt{n}}$;\quad                                                         |
+| [@rosenthal1991]                                                      | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (3) Mean difference $m_\text{diff}$ and $SD_\text{diff}$              | $d=\frac{m_\text{diff}}{SD_\text{diff}}$;\quad                                       |
+| [@lakens2013]                                                         | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (4) Mean looking times per condition + $SD$s                          | $SD_\text{av}=\sqrt{\frac{SD_\text{novel}^2+SD_\text{familiar}^2}{2}}$;\quad         |
+| [@cumming2012]                                                        | $d=\frac{m_\text{movel}-m_\text{familiar}}{SD_\text{av}}$;\quad                      |
+|                                                                       | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $d=\frac{m_\text{pref}}{SD_\text{pref}}$;\quad                                       |
+| [@lakens2013]                                                         | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+
+Table: Extracted between-article summary statistics and conversion to effect sizes
+
+\normalsize
+
+```{r, tab1, eval=FALSE, include=TRUE}
+# Print table for conversion of effect sizes
+tibble(
+  `Available statistics` = c(
+    "(1) Cohen's $d$ and sample size $n$ [@goulet-pelletier2018]",
+    "(2) $t$-statistic and sample size $n$",
+    "(3) Mean difference $m_\\text{diff}$ and $SD_{m_\\text{diff}}$",
+    "(4) Mean looking times per condition and their $SD$s",
+    "(5) Mean novelty preference score $m_\\text{pref}$ and its $SD$"
+  ),
+  `Conversion to standardized mean difference (Hedges' $g$)` = c(
+    paste(
+      "$df=2(n-1)$",
+      "$j=\\frac{\\Gamma(\\frac{1}{2}v)}{\\sqrt{\\frac{v}{2}}\\Gamma(\\frac{1}{2}(v-1))}$",
+      "$g=d*j$",
+      sep = "\\newline"
+    ),
+    "$d=\\frac{t}{\\sqrt{n}}$; then (1)",
+    "$d=\\frac{m_\\text{diff}}{SD_{m_\\text{diff}}}$, then (1)",
+    paste(
+      "$SD_\\text{av}=$",
+      "$d=\\frac{m_\\text{novel}-m_\\text{familiar}}{}$",
+      sep = "\\newline"
+    ),
+    ""
+  )
+) %>%
+  apa_table(
+    caption = "Extracted between-article summary statistics and conversion to effect sizes",
+    font_size = "scriptsize", escape = FALSE
+  )
 ```
 
-No study investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
+No investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
 
@@
 
-```{r, tab2, include=TRUE}
-print("Nice table goes here")
-```
+\scriptsize
+
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| Available statistics                                                  | Conversion to standardized mean difference (Hedges' $g$)                             |
++=======================================================================+======================================================================================+
+| (1) Cohen's $d$ and sample size $n$                                   | $df=2(n-1)$;\quad                                                                    |
+| [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
+|                                                                       | $g=d*j$                                                                              |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (2) $t$-statistic and sample size $n$                                 | $d=\frac{t}{\sqrt{n}}$;\quad                                                         |
+| [@rosenthal1991]                                                      | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (3) Mean difference $m_\text{diff}$ and $SD_\text{diff}$              | $d=\frac{m_\text{diff}}{SD_\text{diff}}$;\quad                                       |
+| [@lakens2013]                                                         | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (4) Mean looking times per condition + $SD$s                          | $SD_\text{av}=\sqrt{\frac{SD_\text{novel}^2+SD_\text{familiar}^2}{2}}$;\quad         |
+| [@cumming2012]                                                        | $d=\frac{m_\text{movel}-m_\text{familiar}}{SD_\text{av}}$;\quad                      |
+|                                                                       | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $d=\frac{m_\text{pref}}{SD_\text{pref}}$;\quad                                       |
+| [@lakens2013]                                                         | then (1)                                                                             |
++-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+
+Table: Extracted within-article summary statistics and conversion to effect sizes
+
+\normalsize
 

### 2022-05-06 supplement.Rmd
trim-and-fill for frequentist

@@
 (ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Profile likelihood plots [@raue2009; @viechtbauer2010] indicate that restricted maximum likelihood estimation (REML) was able to identify the most likely parameter estimates for the two variance components in the three-level meta-analytic model, that is, for the between-article variance and for the between-experiment (within-article) variance.
+
+```{r, trim_and_fill}
+
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# run trim and fill
+res_tf <- trimfill(r_mod)
+print(res_tf)
+res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
+
+summ_brm <- list(intercept = res_tf$beta)
+# Compute funnel
+funnel_z_crit <- stats::qnorm(0.975)
+funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
+funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
+funnel <- data.frame(
+  x = c(
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
+  ),
+  y = c(funnel_max_se, 0, 0, funnel_max_se)
+)
+
+# # Create funnel plot
+plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
+ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
+  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
+  # Meta-analytic effect size
+  geom_vline(xintercept = summ_brm$intercept, color = "black") +
+  # Experiment-specific effect sizes
+  geom_point(shape = 0) +
+  # Funnel
+  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
+  # Styling
+  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
+  scale_y_reverse() +
+  coord_cartesian(
+    xlim = c(-2.5, 2.5),
+    ylim = c(funnel_max_se, 0),
+    expand = FALSE
+  ) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    y = "Standard error",
+  ) +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
+```

### 2022-05-06 supplement.Rmd
Selection models

@@
 ```
+
+```{r,selection_models}
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# EASY WEIGHT_FUNCTION MODEL
+# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
+# to estimate the population effect size after adjusting for selection bias."
+# specifying p value cutpoints of 0.01, 0.05, and 0.10
+sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
+print(sel_mod)
+print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')
+
+# 4 DIFFERENT STEP FUNCTION MODELS
+# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
+# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
+tab <- data.frame(
+  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
+  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
+  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
+  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
+  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))
+
+sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
+sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
+sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
+sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)
+
+print(sel_moderateonetailed)
+print(sel_severeonetailed)
+print(sel_moderatetwotailed)
+print(sel_severetwotailed)
+
+print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
+print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
+print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
+print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')
+
+interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
+
+```

### 2022-05-06 manuscript.Rmd
Add flowchart

@@
 # Run prior predictive simulation
+dir.create(here("results", "models"), showWarnings = TRUE)
 n_iter <- 4000
@@
 
-In the present meta-analysis we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses [@page2021]).
+In the present meta-analysis we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021].
 The PRISMA flowchart is provided in Fig.
@@
 # Include the flowchart (created with MS PowerPoint)
-knitr::include_graphics(here("results/figures/flowchart.pdf"))
+knitr::include_graphics(here("manuscript_files/flowchart.pdf"))
 ```
@@
 
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
++-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
 | Available statistics                                                  | Conversion to standardized mean difference (Hedges' $g$)                                 |
-+=======================================================================+======================================================================================+
++=======================================================================+==========================================================================================+
 | (1) Cohen's $d$ and sample size $n$                                   | $df=2(n-1)$;\quad                                                                        |
-| [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
-|                                                                       | $g=d*j$                                                                              |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
+| [@goulet-pelletier2018; @hedges1985]                                  | $J(df)=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
+|                                                                       | $g=d*J(df)$                                                                              |
++-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
 | (2) $t$-statistic and sample size $n$                                 | $d=\frac{t}{\sqrt{n}}$;\quad                                                             |
 | [@rosenthal1991]                                                      | then (1)                                                                                 |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
++-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
 | (3) Mean difference $m_\text{diff}$ and $SD_\text{diff}$              | $d=\frac{m_\text{diff}}{SD_\text{diff}}$;\quad                                           |
 | [@lakens2013]                                                         | then (1)                                                                                 |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
++-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
 | (4) Mean looking times per condition + $SD$s                          | $SD_\text{av}=\sqrt{\frac{SD_\text{novel}^2+SD_\text{familiar}^2}{2}}$;\quad             |
@@
 |                                                                       | then (1)                                                                                 |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
++-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
 | (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $d=\frac{m_\text{pref}}{SD_\text{pref}}$;\quad                                           |
 | [@lakens2013]                                                         | then (1)                                                                                 |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
++-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
 
@@
 
-One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' g) using the formulas provided in Table 1.
-The sampling variance Var_g of the outcome measure g for each experiment was computed using the formula provided by Goulet-Pelletier & Cousineau (2018):
-
-v = (df(df - 2)) \* ((2 \* (1 - r)) / n) \* (1 + g\^2 \* (n / (2 \* (1 - r)))) - (g\^2 / j\^2)
-
-where n is the sample size of the experiment, df are the degrees of freedom (with df=2\*(n-1)), r is the correlation between the two dependent measures in the experiment, and j is the correction factor for small samples as described in Table 1.
-The correlation r was not reported in any of the original articles.
-We therefore always assumed a correlation of r = .50 to make our analysis comparable to standard (between-group) meta-analyses (Lakens, 2013) and because we were able to infer an average correlation of r $\approx$ .50 from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from r = -.90 via r = .00 to r = .90 had no meaningful impact on the meta-analytic effect size (Supplementary Table 3).
+One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ g) using the formulas provided in Table 1.
+The standard error $SE_g$ of the outcome measure $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018:
+
+$$SE_g=\sqrt{\frac{df}{df-2}\frac{2(1-r)}{n}(1+g^2\frac{n}{2(1-r)})-\frac{g^2}{J^2}}$$
+
+where $n$ is the sample size of the experiment, $df$ are the degrees of freedom (with $df = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J(df)$ is the correction factor for small samples as described in Table 1.
+The correlation $r$ was not reported in any of the original articles [@harrer2021].
+We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
+A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Table 5).
 
@@
 We synthesized the effect sizes and their sampling variances using a Bayesian multilevel model.
-This model had three levels, with infant participants nested in experiments and experiments nested in articles (Van den Noortgate et al., 2013).
-We used a weakly-informative normal (N(0,1)) prior for the meta-analytic effect size and a weakly-informative half-Cauchy (HC(0, 0.3)) prior for all standard deviations (Williams et al., 2018).
-A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 3).
-All Bayesian models were fitted using the brms package (Version 2.16.3; Bürkner, 2017, 2018) in R (Version 4.1.2; R Core Team, 2021) and the Stan language (Version 2.29.2; Stan Development Team, 2022).
-Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling 10,000 draws (including 5,000 warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the R\_{hat} and N\_{eff} statistics (Vehtari et al., 2021; Supplementary Fig. 1).
-For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results (Kruschke, 2015).
+This model had three levels, with infant participants nested in experiments and experiments nested in articles [@vandennoortgate2013].
+We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for all standard deviations [@williams2018].
+A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 5).
+All Bayesian models were fitted using the brms package (Version `r packageVersion("brms")`) [@burkner2017; @burkner2018] in R (Version `r packageVersion("base")`) [@rcoreteam2021] and the Stan language (Version `r packageVersion("rstan")`) [@standevelopmentteam2022].
+Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r formatC(n_iter, big.mark = ",")` draws (including `r formatC(n_warmup, big.mark = ",")` warm-up draws) from the posterior distribution.
+To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig.
+2) [@vehtari2021].
+For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].
 
@@
 We examined the influence of three moderator variables on the mental rotation outcomes across studies, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
-Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts so that we could compare all-female versus mixed samples and all-male samples versus all-female samples (Schad et al., 2020).
+Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts [@schad2020] so that we could compare all-female versus mixed samples and all-male samples versus all-female samples.
 Age was coded as a continuous predictor in years and centered by subtracting the average across all studies.
-Task was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast (Schad et al., 2020).
+Task was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast [@schad2020].
 We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender task type (i.e., [female - mixed] × age and [male - female] × age) into a Bayesian meta-regression model.
-This model used the same random effects structure and sampling and sampling parameters as described above.
+This model used the same random effects structure and sampling parameters as described above.
 
@@
 
-We verified the results from our Bayesian analyses using classical (frequentist) meta-analysis and meta-regression.
-We used the metafor package (Version 3.0.2; Viechtbauer, 2010) in R to specify the same three-level models as described above but dropping the Bayesian priors (Supplementary Table 3).
-The models were fitted using restricted maximum likelihood estimation (REML).
-To verify that REML converged on the correct estimates, we examined profile likelihood plots for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; see Supplementary Fig.
-2).
+We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression.
+To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table 5).
+These models were fitted using restricted maximum likelihood estimation (REML).
+To verify that the REML converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; Supplementary Fig.
+3).
 
@@
 
-We assessed publication bias by means of a funnel plot and Egger regression test (Egger et al. 1997).
-We adapted code from the R package metaviz (Version 0.3.1; Kossmeier et al., 2020) to produce the funnel plot and used the R package metafor for the Egger regression test.
-We examined heterogeneity in our study samples by means of a jackknife leave-one-out-analysis (Gee 2005).
-We adapted code from the bootstrap R package (Version 2019.6; Scott Kostyshak et al., 2019) to fit the Bayesian model repeatedly to our study samples, leaving out one experiment sample for every iteration.
-To take into account the variance inherent in Bayesian model estimation, we averaged over x iterations of the jackknife.
-
-## Data & code availability
-
-Blah blah blah
+Publication bias was evaluated based on a funnel plot and an Egger regression test [@egger1997; @sterne2005].
+To produce the funnel plot, which visualizes the relationship between standard errors and effect sizes, we adapted code from the R package metaviz (`r packageVersion("metaviz")`) [@kossmeier2020].
+For the Egger regression test we used the R package metafor (Version `r packageVersion("metafor")`) [@viechtbauer2010] to identify a potential relationship between standard errors and effect sizes.
+Such a relationship is indicated by the observation that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero in a two-sided $t$-test.
+
+To scrutinize the robustness of the meta-analytic effect size against the effects of individual studies we conducted a jackknife leave-one-out-analysis [@gee2005; @efron1993].
+To this end, we adapted code from the bootstrap R package (Version `r packageVersion("bootstrap")`) [@kostyshak2019].
+Specifically, we fit the Bayesian models repeatedly to our study samples, leaving out one experiment sample for every iteration.
+To take into account the variance inherent in Bayesian model estimation, we averaged over ???
+iterations of the jackknife.
+
+## Data availability
+
+The data is available via (OSF link here).
+
+## Code availability
+
+The code is available via (OSF link here).
 
@@
 <div id="refs"></div>
+
+\newpage
+
+# Contributions
+
+M.A.S. conceived, designed, and obtained funding for the study.
+
+A.E., S.K., and A.K.
+designed and executed the search strategy, performed study selection and screening procedures, managed the database of search results and performed data analysis in consultation with M.A.S.
+
+A.E. and M.A.S. wrote the manuscript with feedback from S.K. and A.K.
 

### 2022-05-06 manuscript.Rmd
Add contours and gender analysis to funnel plot

@@
 
-```{r, fig3, include=TRUE, fig.height=3.5, fig.width=5.56, fig.cap="(ref:fig3-caption)", out.width="50%"}
-# Compute funnel
-funnel_z_crit <- stats::qnorm(0.975)
-funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
-funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
-funnel <- data.frame(
-  x = c(
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
-  ),
-  y = c(funnel_max_se, 0, 0, funnel_max_se)
-)
-
-# Create funnel plot
-dat %>%
-  ggplot(aes(x = gi, y = sei)) +
+```{r, fig3, include=TRUE, fig.height=3.5, fig.width=12, fig.cap="(ref:fig3-caption)"}
+# Create funnel plots
+list(dat, dat_gender) %>%
+  map(function(plot_dat) {
+
+    # Define maximul SE of interest (a bit larger than the largest observed one)
+    max_se <- max(plot_dat$sei) + 0.05
+
+    # Compute two different funnels under the null hypothesis
+    z_crit_05 <- stats::qnorm(0.975)
+    funnel_05 <- data.frame(
+      x = c(0 - z_crit_05 * sqrt(max_se^2), 0, 0 + z_crit_05 * sqrt(max_se^2)),
+      y = c(max_se, 0, max_se)
+    )
+
+    # Compute two different funnels under the null hypothesis
+    z_crit_01 <- stats::qnorm(0.995)
+    funnel_01 <- data.frame(
+      x = c(0 - z_crit_01 * sqrt(max_se^2), 0, 0 + z_crit_01 * sqrt(max_se^2)),
+      y = c(max_se, 0, max_se)
+    )
+
+    # Compute funnel around the observed meta-analytic effect size
+    funnel_observed <- mutate(funnel_05, x = x + summ_brm$intercept)
+
+    # Plot the funnel(s)
+    ggplot(plot_dat, aes(x = gi, y = sei)) +
+      # Null funnels
+      geom_polygon(
+        data = funnel_01, aes(x = x, y = y), fill = "grey60", alpha = 0.2
+      ) +
+      geom_polygon(
+        data = funnel_05, aes(x = x, y = y), fill = "grey60", alpha = 0.2
+      ) +
+      # Grid lines
       geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
+      # Observed_funnel
+      geom_path(data = funnel_observed, aes(x = x, y = y)) +
       # Meta-analytic effect size
@@
       geom_point(shape = 0) +
-  # Funnel
-  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
       # Styling
@@
         xlim = c(-2.5, 2.5),
-    ylim = c(funnel_max_se, 0),
+        ylim = c(max_se, 0),
         expand = FALSE
@@
       )
+  }) %>%
+  plot_grid(
+    plotlist = ., nrow = 1, labels = "auto",
+    label_size = 11, label_fontfamily = "Helvetica"
+  )
 
 # Save the plot
-ggsave(here(figures_dir, "funnel.pdf"), width = 5.56, height = 3.5)
+ggsave(here(figures_dir, "funnel.pdf"), width = 12, height = 3.5)
 ```

### 2022-05-06 manuscript.Rmd
equations and directories fix

--- 2022-05-06 manuscript.Rmd
@@
 +=======================================================================+======================================================================================+
-| (1) Cohen's $d$ and sample size $n$                                   | $df=2(n-1)$;\quad                                                                    |
+| (1) Cohen's $d$ and group sample size $n$                             | $df=n_{female}+ n_{male}-1$; \quad                                                   |
 | [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
@@
 +-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (2) $t$-statistic and sample size $n$                                 | $d=\frac{t}{\sqrt{n}}$;\quad                                                         |
-| [@rosenthal1991]                                                      | then (1)                                                                             |
+| (2) $t$-statistic and group sample size $n$                           | $d = t \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                         |
+| [@lankens2013]                                                        | then (1)                                                                             |
 +-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (3) Mean difference $m_\text{diff}$ and $SD_\text{diff}$              | $d=\frac{m_\text{diff}}{SD_\text{diff}}$;\quad                                       |
+| (3) $F$ statistic and group sample size                               | $d = \sqrt{f} \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                  |
 | [@lakens2013]                                                         | then (1)                                                                             |
 +-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (4) Mean looking times per condition + $SD$s                          | $SD_\text{av}=\sqrt{\frac{SD_\text{novel}^2+SD_\text{familiar}^2}{2}}$;\quad         |
-| [@cumming2012]                                                        | $d=\frac{m_\text{movel}-m_\text{familiar}}{SD_\text{av}}$;\quad                      |
+| (4) Mean difference in looking times per group + $SD$s                | $SD_\text{mean} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
+| [@lankens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{mean}}$;\quad                       |
 |                                                                       | then (1)                                                                             |
 +-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $d=\frac{m_\text{pref}}{SD_\text{pref}}$;\quad                                       |
-| [@lakens2013]                                                         | then (1)                                                                             |
+| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $SD_\text{pref} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
+|  [@lakens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{pref}}$;\quad                       |
+|                                                                       | then (1)                                                                             |
 +-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
@@
 Furthermore, the sampling variance was computed according to the following equation:
-
-$sigma$between group = dfdf -2 2ñ1 + g2ñ2- g2J2
-
-Where ñ is the harmonic mean of the group sizes and ñ = nmale nmalenfemale + nmale.
+$    \sigma_{between group} = \sqrt{\frac{df}{df-2} \frac{2}{\tilde{n}} (1 + g^2\frac{\tilde{n}}{2}) - frac{g^2}{J^2}}          $
+Where ñ is the harmonic mean of the group sizes and $ñ = \frac{n_{female} n_{male}}{n_{female} + n_{male}}$ and $df$ are given by the equation in Table xxx.
 A sensitivity analysis reported in supplementary xxx highlights the stability of the effect size computed using the Bayesian meta analysis.

### 2022-05-06 supplement.Rmd
Make table for selection model analysis

@@
 ```
+
+```{r, tabs_trimfill_selectionmodels, include=TRUE}
+# Format all frequentist results together as a table
+map2_dfr(
+  c(
+    "Two-level random effects model",
+    "Trim-and-fill",
+    "Selection model: moderate one-tailed",
+    "Selection model: severe one-tailed",
+    "Selection model: moderate two-tailed",
+  "Selection model:severe two-tailed",
+  "Selection model: weight-function [0.01,0.05,0.3]"),
+    list(
+      r_mod,
+      res_tf,
+      sel_moderateonetailed,
+      sel_severeonetailed,
+      sel_moderatetwotailed,
+      sel_severetwotailed,
+      sel_mod),
+  function(name, res) {
+    print(name)
+    # Intercept / regression weights
+    tibble(
+      Model = c(name, rep(NA, length(res$b) - 1)),
+      Parameter = rownames(res$b),
+      Estimate = print_num(as.numeric(res$b)),
+      `$SE$` = print_num(res$se),
+      `$z$` = print_num(res$zval),
+      `$p$` = print_num(res$pval, digits = 3),
+      ci_lower = print_num(res$ci.lb),
+      ci_upper = print_num(res$ci.ub)
+    ) %>%
+      # Re-format confidence interval
+      mutate(
+        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
+        .keep = "unused"
+      ) %>%
+      bind_rows()
+  }
+) %>%
+  # Rename parameters for readibility
+  mutate(
+    Parameter = c(
+      "Hedges' $g$"
+    )
+  ) %>%
+  # Replace NAs with blank cells
+  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
+
+# Display the table
+apa_table(
+  tab_freq,
+  align = "llccccc",
+  caption = "Sensitivity/robustness analyses frequentist",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+
+# Save the table
+write_csv(tab_freq, file = here(tables_dir, "robustness_freq.csv"))
+```

### 2022-05-06 manuscript.Rmd
Small fixes to the text

--- 2022-05-06 manuscript.Rmd
@@
 # Justify exclusion of @pedrett2020 based on outlier mean age
-mean_age_pedrett2020 <- 2.56 * 365.25 # In days
-mean_age_pedrett2020_m <- mean_age_pedrett2020 / 30.417 # In months
-mean_age_pedrett2020_z <- (mean_age_pedrett2020 - mean(dat$age_mean)) /
-  sd(dat$age_mean) # As z score
-
+descs_pedrett2020 <- list(age_years = 2.56)
+descs_pedrett2020 <- within(descs_pedrett2020, {
+  age_months <- age_years * 12
+  next_largest_age_months <- max(dat$age_mean) / 30.417
+  age <- age_years * 365.25
+  z <- (age - mean(dat$age_mean)) / sd(dat$age_mean)
+})
 ```
@@
 Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen’s weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]).
-Interrater agreement for the specific eligibility criteria were `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r irr_code_kappa_w$upper`]).
+Interrater agreement for the specific eligibility criteria were `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]).
 Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
 One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles.
-Another article [@pedrett2020] was excluded because the average age of the infants studied (`r round(mean_age_pedrett2020_m, 1)` months) was almost twice as high as the average age of the next article (`r round(max(dat$age_mean), 1)` months; $z = `r mean_age_pedrett2020_z`$ compared to all articles).
+Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, 1)` months; $z = `r descs_pedrett2020$z`$ compared to all articles).
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
@@
 
-```{r, tab1, eval=FALSE, include=TRUE}
-# Print table for conversion of effect sizes
-tibble(
-  `Available statistics` = c(
-    "(1) Cohen's $d$ and sample size $n$ [@goulet-pelletier2018]",
-    "(2) $t$-statistic and sample size $n$",
-    "(3) Mean difference $m_\\text{diff}$ and $SD_{m_\\text{diff}}$",
-    "(4) Mean looking times per condition and their $SD$s",
-    "(5) Mean novelty preference score $m_\\text{pref}$ and its $SD$"
-  ),
-  `Conversion to standardized mean difference (Hedges' $g$)` = c(
-    paste(
-      "$df=2(n-1)$",
-      "$j=\\frac{\\Gamma(\\frac{1}{2}v)}{\\sqrt{\\frac{v}{2}}\\Gamma(\\frac{1}{2}(v-1))}$",
-      "$g=d*j$",
-      sep = "\\newline"
-    ),
-    "$d=\\frac{t}{\\sqrt{n}}$; then (1)",
-    "$d=\\frac{m_\\text{diff}}{SD_{m_\\text{diff}}}$, then (1)",
-    paste(
-      "$SD_\\text{av}=$",
-      "$d=\\frac{m_\\text{novel}-m_\\text{familiar}}{}$",
-      sep = "\\newline"
-    ),
-    ""
-  )
-) %>%
-  apa_table(
-    caption = "Extracted between-article summary statistics and conversion to effect sizes",
-    font_size = "scriptsize", escape = FALSE
-  )
-```
-
 No investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.

### 2022-05-06 manuscript.Rmd

--- 2022-05-06 manuscript.Rmd
@@
 \normalsize
-
-```{r, tab1, eval=FALSE, include=TRUE}
-# Print table for conversion of effect sizes
-tibble(
-  `Available statistics` = c(
-    "(1) Cohen's $d$ and sample size $n$ [@goulet-pelletier2018]",
-    "(2) $t$-statistic and sample size $n$",
-    "(3) Mean difference $m_\\text{diff}$ and $SD_{m_\\text{diff}}$",
-    "(4) Mean looking times per condition and their $SD$s",
-    "(5) Mean novelty preference score $m_\\text{pref}$ and its $SD$"
-  ),
-  `Conversion to standardized mean difference (Hedges' $g$)` = c(
-    paste(
-      "$df=2(n-1)$",
-      "$j=\\frac{\\Gamma(\\frac{1}{2}v)}{\\sqrt{\\frac{v}{2}}\\Gamma(\\frac{1}{2}(v-1))}$",
-      "$g=d*j$",
-      sep = "\\newline"
-    ),
-    "$d=\\frac{t}{\\sqrt{n}}$; then (1)",
-    "$d=\\frac{m_\\text{diff}}{SD_{m_\\text{diff}}}$, then (1)",
-    paste(
-      "$SD_\\text{av}=$",
-      "$d=\\frac{m_\\text{novel}-m_\\text{familiar}}{}$",
-      sep = "\\newline"
-    ),
-    ""
-  )
-) %>%
-  apa_table(
-    caption = "Extracted between-article summary statistics and conversion to effect sizes",
-    font_size = "scriptsize", escape = FALSE
-  )
-```
 

### 2022-05-07 manuscript.Rmd
Explicitly create directories in scripts

@@
 data_dir <- here("data")
+models_dir <- here("results/models")
 figures_dir <- here("results/figures")
@@
 # Run prior predictive simulation
-dir.create(here("results", "models"), showWarnings = TRUE)
+dir.create(models_dir, showWarnings = FALSE)
 n_iter <- 4000
@@
   control = list(adapt_delta = 0.99),
-  file = here("results", "models", "res_prior")
+  file = here(models_dir, "res_prior")
 )
@@
   sample_prior = FALSE,
-  file = here("results", "models", "res_brm")
+  file = here(models_dir, "res_brm")
 )
@@
 # Save the plot
+dir.create(figures_dir, showWarnings = FALSE)
 ggsave(here(figures_dir, "forest.pdf"), width = 12, height = 14)
@@
   control = list(adapt_delta = 0.99),
-  file = here("results", "models", "res_prior_reg")
+  file = here(models_dir, "res_prior_reg")
 )
@@
   sample_prior = FALSE,
-  file = here("results", "models", "res_brm_reg")
+  file = here(models_dir, "res_brm_reg")
 )
@@
   control = list(adapt_delta = 0.99),
-  file = here("results", "models", "res_prior_gender")
+  file = here(models_dir, "res_prior_gender")
 )
@@
   sample_prior = FALSE,
-  file = here("results", "models", "res_brm_gender")
+  file = here(models_dir, "res_brm_gender")
 )

### 2022-05-07 supplement.Rmd
Explicitly create directories in scripts

--- 2022-05-06 supplement.Rmd
@@
 # Save the table
+dir.create(tables_dir, showWarnings = FALSE)
 write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")
@@
 (ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Profile likelihood plots [@raue2009; @viechtbauer2010] indicate that restricted maximum likelihood estimation (REML) was able to identify the most likely parameter estimates for the two variance components in the three-level meta-analytic model, that is, for the between-article variance and for the between-experiment (within-article) variance.
-
-```{r, trim_and_fill}
-
-# random-effects 2 level model
-r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
-
-# run trim and fill
-res_tf <- trimfill(r_mod)
-print(res_tf)
-res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
-
-summ_brm <- list(intercept = res_tf$beta)
-# Compute funnel
-funnel_z_crit <- stats::qnorm(0.975)
-funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
-funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
-funnel <- data.frame(
-  x = c(
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
-  ),
-  y = c(funnel_max_se, 0, 0, funnel_max_se)
-)
-
-# # Create funnel plot
-plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
-ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
-  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
-  # Meta-analytic effect size
-  geom_vline(xintercept = summ_brm$intercept, color = "black") +
-  # Experiment-specific effect sizes
-  geom_point(shape = 0) +
-  # Funnel
-  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
-  # Styling
-  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
-  scale_y_reverse() +
-  coord_cartesian(
-    xlim = c(-2.5, 2.5),
-    ylim = c(funnel_max_se, 0),
-    expand = FALSE
-  ) +
-  labs(
-    x = expression("Hedges'" ~ italic("g")),
-    y = "Standard error",
-  ) +
-  theme_classic() +
-  theme(
-    axis.line = element_line(colour = "black"),
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    text = element_text(family = "Helvetica", color = "black")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
-```

### 2022-05-08 manuscript.Rmd
Specify MCMC options at the beginning

@@
 )
+
+# Options for MCMC sampling when fitting Bayesian multilevel models
+n_iter <- 4000 # Posterior samples per chain, including `n_warmup`
+n_warmup <- 1000 # Warmup samples per chain
+n_chains <- 4 # Number of (parallel) chains
+seed <- 1234 # Random seed to make the results reproducible
 
@@
 dir.create(models_dir, showWarnings = FALSE)
-n_iter <- 4000
-n_warmup <- 1000
-n_chains <- 4
 res_prior <- brm(
@@
   control = list(adapt_delta = 0.99),
-  file = here(models_dir, "res_prior")
+  seed = seed,
+  file = here(models_dir, "res_prior"),
+  file_refit = "on_change"
 )
@@
   sample_prior = FALSE,
-  file = here(models_dir, "res_brm")
+  file = here(models_dir, "res_brm"),
+  file_refit = "on_change"
 )
@@
   control = list(adapt_delta = 0.99),
-  file = here(models_dir, "res_prior_reg")
+  seed = seed,
+  file = here(models_dir, "res_prior_reg"),
+  file_refit = "on_change"
 )
@@
   sample_prior = FALSE,
-  file = here(models_dir, "res_brm_reg")
+  file = here(models_dir, "res_brm_reg"),
+  file_refit = "on_change"
 )
@@
   control = list(adapt_delta = 0.99),
-  file = here(models_dir, "res_prior_gender")
+  seed = seed,
+  file = here(models_dir, "res_prior_gender"),
+  file_refit = "on_change"
 )
@@
   sample_prior = FALSE,
-  file = here(models_dir, "res_brm_gender")
+  file = here(models_dir, "res_brm_gender"),
+  file_refit = "on_change"
 )

### 2022-05-08 manuscript.Rmd
Fix LaTeX tables and equations

@@
 
-+-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
 | Available statistics                                           | Conversion to standardized mean difference (Hedges' $g$)                                    |
-+=======================================================================+==========================================================================================+
-| (1) Cohen's $d$ and sample size $n$                                   | $df=2(n-1)$;\quad                                                                        |
-| [@goulet-pelletier2018; @hedges1985]                                  | $J(df)=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
-|                                                                       | $g=d*J(df)$                                                                              |
-+-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
-| (2) $t$-statistic and sample size $n$                                 | $d=\frac{t}{\sqrt{n}}$;\quad                                                             |
-| [@rosenthal1991]                                                      | then (1)                                                                                 |
-+-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
-| (3) Mean difference $m_\text{diff}$ and $SD_\text{diff}$              | $d=\frac{m_\text{diff}}{SD_\text{diff}}$;\quad                                           |
-| [@lakens2013]                                                         | then (1)                                                                                 |
-+-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
-| (4) Mean looking times per condition + $SD$s                          | $SD_\text{av}=\sqrt{\frac{SD_\text{novel}^2+SD_\text{familiar}^2}{2}}$;\quad             |
-| [@cumming2012]                                                        | $d=\frac{m_\text{movel}-m_\text{familiar}}{SD_\text{av}}$;\quad                          |
-|                                                                       | then (1)                                                                                 |
-+-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
-| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $d=\frac{m_\text{pref}}{SD_\text{pref}}$;\quad                                           |
-| [@lakens2013]                                                         | then (1)                                                                                 |
-+-----------------------------------------------------------------------+------------------------------------------------------------------------------------------+
++================================================================+=============================================================================================+
+| (1\) Cohen's $d$ and sample size                               | ${df}=2(n-1)$;\quad                                                                         |
+| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
+|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| (2\) $t$-statistic and sample size [@rosenthal1991]            | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| (3\) $F$-statistic and sample size [@lakens2013]               | $t=\sqrt{f}$;\quad then (2\)                                                                |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| (4\) Mean difference between conditions [@lakens2013]          | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| (5\) Mean looking time and ${SD}$ per condition [@cumming2012] | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
+|                                                                | $d=\frac{m_\text{movel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| (6\) Mean novelty preference score [@lakens2013]               | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
 
@@
 
-One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ g) using the formulas provided in Table 1.
+One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ $g$) using the formulas provided in Table 1.
 The standard error $SE_g$ of the outcome measure $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018:
 
-$$SE_g=\sqrt{\frac{df}{df-2}\frac{2(1-r)}{n}(1+g^2\frac{n}{2(1-r)})-\frac{g^2}{J^2}}$$
-
-where $n$ is the sample size of the experiment, $df$ are the degrees of freedom (with $df = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J(df)$ is the correction factor for small samples as described in Table 1.
+$${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J^2}}$$
+
+where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Table 1.
 The correlation $r$ was not reported in any of the original articles [@harrer2021].
@@
 
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
++----------------------------------------+--------------------------------------------------------------------------------------------------+
 | Available statistics                   | Conversion to standardized mean difference (Hedges' $g$)                                         |
-+=======================================================================+======================================================================================+
-| (1) Cohen's $d$ and group sample size $n$                             | $df=n_{female}+ n_{male}-1$; \quad                                                   |
-| [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
-|                                                                       | $g=d*j$                                                                              |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (2) $t$-statistic and group sample size $n$                           | $d = t \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                         |
-| [@lankens2013]                                                        | then (1)                                                                             |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (3) $F$ statistic and group sample size                               | $d = \sqrt{f} \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                  |
-| [@lakens2013]                                                         | then (1)                                                                             |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (4) Mean difference in looking times per group + $SD$s                | $SD_\text{mean} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
-| [@lankens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{mean}}$;\quad                       |
-|                                                                       | then (1)                                                                             |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
-| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $SD_\text{pref} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
-|  [@lakens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{pref}}$;\quad                       |
-|                                                                       | then (1)                                                                             |
-+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
++========================================+==================================================================================================+
+| (1\) Cohen's $d$ and group sizes       | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
+| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
+|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+| (2\) $t$-statistic and group sizes     | $d=t\sqrt\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}$;\quad then (1)                       |
+| [@lakens2013]                          |                                                                                                  |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+| (3\) $F$-statistic and group sizes     | $t=\sqrt{f}$;\quad then (2\)                                                                     |
+| [@lakens2013]                          |                                                                                                  |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+| (4\) Mean differences between          | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
+| conditions or preference scores        | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
+| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
 
@@
 Furthermore, the sampling variance was computed according to the following equation:
-$    \sigma_{between group} = \sqrt{\frac{df}{df-2} \frac{2}{\tilde{n}} (1 + g^2\frac{\tilde{n}}{2}) - frac{g^2}{J^2}}          $
-Where ñ is the harmonic mean of the group sizes and $ñ = \frac{n_{female} n_{male}}{n_{female} + n_{male}}$ and $df$ are given by the equation in Table xxx.
-A sensitivity analysis reported in supplementary xxx highlights the stability of the effect size computed using the Bayesian meta analysis.
+
+$${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$
+
+Where $\tilde{n}$ is the harmonic mean of the group sizes
+(i.e., $\tilde{n}=\frac{n_\text{female}n_\text{male}}{n_\text{female}+n_\text{male}}$)
+and ${df}$ are the degrees of freedom as provided in row (1) of Table 2.
+A sensitivity analysis highlights the stability of the effect size computed using the Bayesian meta analysis (Supplementary Table 5).
 

### 2022-05-08 manuscript.Rmd
Fix harmonic mean / SE for gender differences

@@
     ni = female_n + male_n,
-    nhi = (female_n * male_n) / ni,
-    vi = (df * 2 * (1 + (gi^2 * nhi * 0.5))) / ((df - 2) * nhi) - (gi^2 / j^2),
+    nhi = 2 / (1 / female_n + 1 / male_n),
+    vi = (df / (df - 2)) * (2 / nhi) * (1 + gi^2 * (nhi / 2)) - (gi^2 / (j^2)),
     sei = sqrt(vi)
@@
 Where $\tilde{n}$ is the harmonic mean of the group sizes
-(i.e., $\tilde{n}=\frac{n_\text{female}n_\text{male}}{n_\text{female}+n_\text{male}}$)
+(i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$)
 and ${df}$ are the degrees of freedom as provided in row (1) of Table 2.

### 2022-05-09 manuscript.Rmd
Improve funnel plot

@@
 
-    # Compute two different funnels under the null hypothesis
+    # Compute a 95% funnel under the null hypothesis
     z_crit_05 <- stats::qnorm(0.975)
-    funnel_05 <- data.frame(
+    funnel_greater_05 <- data.frame(
       x = c(0 - z_crit_05 * sqrt(max_se^2), 0, 0 + z_crit_05 * sqrt(max_se^2)),
-      y = c(max_se, 0, max_se)
-    )
-
-    # Compute two different funnels under the null hypothesis
+      y = c(max_se, 0, max_se),
+      level = "greater_05"
+    )
+
+    # Compute a 99% funnel under the null hypothesis
     z_crit_01 <- stats::qnorm(0.995)
-    funnel_01 <- data.frame(
+    funnel_smaller_05 <- data.frame(
       x = c(0 - z_crit_01 * sqrt(max_se^2), 0, 0 + z_crit_01 * sqrt(max_se^2)),
-      y = c(max_se, 0, max_se)
-    )
-
-    # Compute funnel around the observed meta-analytic effect size
-    funnel_observed <- mutate(funnel_05, x = x + summ_brm$intercept)
+      y = c(max_se, 0, max_se),
+      level = "smaller_05"
+    )
+
+    # Create a third pseudo-funnel under the null hypothesis just for the legend
+    funnel_smaller_01 <- mutate(funnel_greater_05, level = "smaller_01")
+
+    # Compute a 95% funnel around the observed meta-analytic effect size
+    funnel_observed <- mutate(funnel_greater_05, x = x + summ_brm$intercept)
 
@@
     ggplot(plot_dat, aes(x = gi, y = sei)) +
-      # Null funnels
-      geom_polygon(
-        data = funnel_01, aes(x = x, y = y), fill = "grey60", alpha = 0.2
-      ) +
-      geom_polygon(
-        data = funnel_05, aes(x = x, y = y), fill = "grey60", alpha = 0.2
+      # Funnels under the null hypothesis
+      geom_polygon(data = funnel_smaller_01, aes(x = x, y = y, fill = level)) +
+      geom_polygon(data = funnel_smaller_05, aes(x = x, y = y, fill = level)) +
+      geom_polygon(data = funnel_greater_05, aes(x = x, y = y, fill = level)) +
+      scale_fill_manual(
+        values = c("gray80", "grey90", "white"),
+        breaks = c("greater_05", "smaller_05", "smaller_01"),
+        labels = c(
+          expression(italic(p) > .05),
+          expression(italic(p) < .05),
+          expression(italic(p) < .01)
+        )
       ) +
@@
       labs(
-        x = expression("Hedges'" ~ italic("g")),
-        y = "Standard error",
+        x = expression("Hedges'" ~ italic("g")), y = "Standard error",
+        fill = "Significance level"
       ) +
@@
         axis.ticks = element_line(color = "black"),
+        legend.position = "none",
         text = element_text(family = "Helvetica", color = "black")
       )
-  }) %>%
+  }) -> plots_funnel
+
+# Extract legend
+legend_funnel <- get_legend(
+  plots_funnel[[1]] + theme(legend.position = "right")
+)
+
+# Combine plots and legend
 plot_grid(
-    plotlist = ., nrow = 1, labels = "auto",
+  plotlist = plots_funnel, nrow = 1, labels = "auto",
   label_size = 11, label_fontfamily = "Helvetica"
-  )
+) +
+  draw_plot(legend_funnel, x = -0.39, y = 0.355)
 
@@
 
-(ref:fig3-caption) **Evaluation of publication bias.** The funnel plot shows the standard errors and the effect sizes for each of the individual studies.
-The funnel contours (dashed lines) show a 95%-pseudo-confidence interval of the standard error around the meta-analytic effect size (vertical solid line).
-A slight asymmetry induced by the underrepresentation of studies with high standard error and small effect size suggest a small publication bias.
+(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance **(a)** and for the meta-analysis of gender differences within each article **(b)**.
+The plots show the standard error and effect size for each of the individual experiments as a black square.
+The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect size (vertical black line).
+Gray shades indicate a 95% pseudo-confidence interval (dark gray) and 99% pseudo-confidence interval (light gray) under the null hypothesis.
+These shades thus illustrate which of the original studies observed a significant effect.
+A slight asymmetry induced by the underrepresentation of studies with high standard errors and small effect sizes suggests a small publication bias.
 

### 2022-05-09 manuscript.Rmd
Add Supplementary Methods 1

@@
 The correlation $r$ was not reported in any of the original articles [@harrer2021].
-We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
+We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
 A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Table 5).

### 2022-05-09 supplement.Rmd
Add Supplementary Methods 1

@@
 # Supplementary information
+
+<!-- Supplementary methods -->
+
+## Supplementary Methods 1 | Correlation between dependent samples
+
+```{r, r_assumed}
+# Compute empirical estimate of the correlation between dependent samples
+dat %>%
+  mutate(
+    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
+    d_diff = case_when(
+      !is.na(d) ~ d,
+      !is.na(d_z_t) ~ d_z_t,
+      !is.na(d_z_f) ~ d_z_f,
+      !is.na(d_z_diff) ~ d_z_diff
+    ),
+    # Compute empirical correlation
+    # Based on the SD of the difference and the SDs within the two conditions
+    sd_diff = mean_diff / d_diff,
+    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
+      (-2 * sd_novel * sd_familiar)
+  ) %>%
+  pull(ri) -> ri_empirical
+
+# Subset articles that have an empirical estimate for the correlation
+dat_ri_empirical <- filter(dat, !is.na(ri_empirical))
+
+# Summarise the estimated correlations
+(summ_ri_empirical <- print_num(summary(ri_empirical)))
+```
+
+Meta-analytic methods require an estimate of the sampling variance of each included experiment [@harrer2021].
+For within-participant experimental designs (i.e., repeated measures on the same individuals in different conditions), this sampling variance needs to reflect that repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants, thus not providing independent information.
+This is reflected by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018].
+This correlation between repeated measures unfortunately tends to go unreported in research articles.
+In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants’ looking times in the novel and familiar rotation object conditions.
+
+However, there were `r nrow(dat_ri_empirical)` experiments taken from seven different articles that included enough statistical information to reconstruct this correlation.
+This was done using the following procedure:
+
+1.
+Extract an effect size $d_\text{diff}$ based on a paired $t$-test, a one-sample $t$-test of difference scores, or an ANOVA (see Rows (1) to (4) in Table 1).
+All three of these tests take the correlation between the repeated measures into account.
+
+2. Extract the mean looking time difference $m_\text{diff}$ (in seconds) between the novel and familiar conditions.
+
+3. Compute the standard deviation of the mean looking time difference:
+
+$${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
+
+4. Extract the standard deviations ${SD}_\text{novel}$ and ${SD}_\text{familiar}$ of looking times within each of the two conditions.
+
+5. Compute the observed correlation between conditions based on rearranging an equation by @cohen1988:
+
+$$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
+
+Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]).
+However, we decided to assume a correlation of $r  = .50$ when computing ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments.
+This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
+We ran a sensitivity analysis to test the robustness of our Bayesian meta-analytic model against this assumption (Supplementary Table 4).
+
+<!-- Supplementary tables -->
 
@@
 ```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
-# Compute empirical estimate of the correlation between dependent samples
-dat %>%
-  mutate(
-    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
-    d_diff = case_when(
-      !is.na(d) ~ d,
-      !is.na(d_z_t) ~ d_z_t,
-      !is.na(d_z_f) ~ d_z_f,
-      !is.na(d_z_diff) ~ d_z_diff
-    ),
-    # Compute empirical correlation
-    # Basesd on the SD of the difference and the SDs within the two conditions
-    sd_diff = mean_diff / d_diff,
-    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
-      (-2 * sd_novel * sd_familiar)
-  ) %>%
-  pull(ri) -> ri_empirical
-
-# Summarise the estimated correlations
-summary(ri_empirical)
-
 # Re-run the meta-analysis for different values of r_assumed

### 2022-05-09 supplement.Rmd
Bias correction also for gender

--- 2022-05-06 supplement.Rmd
@@
 
-```{r, trim_and_fill}
+```{r, trim_and_fill_within}
 
@@
 
-```{r,selection_models}
+```{r,selection_models_within}
 # random-effects 2 level model
@@
 
-```{r, tabs_trimfill_selectionmodels, include=TRUE}
+```{r, tabs_trimfill_selectionmodels_within, include=TRUE}
 # Format all frequentist results together as a table
@@
     "Trim-and-fill",
+    "Selection model: weight-function [0.01, 0.05, 0.3]",
     "Selection model: moderate one-tailed",
@@
     "Selection model: moderate two-tailed",
-  "Selection model:severe two-tailed",
-  "Selection model: weight-function [0.01,0.05,0.3]"),
+  "Selection model: severe two-tailed"
+  ),
     list(
@@
       res_tf,
+      sel_mod,
       sel_moderateonetailed,
@@
       sel_moderatetwotailed,
-      sel_severetwotailed,
-      sel_mod),
+      sel_severetwotailed
+      ),
   function(name, res) {
@@
 ```
+
+```{r, trim_and_fill_gender}
+dat=dat_gender
+
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# run trim and fill
+res_tf <- trimfill(r_mod)
+print(res_tf)
+# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
+
+summ_brm <- list(intercept = res_tf$beta)
+# Compute funnel
+funnel_z_crit <- stats::qnorm(0.975)
+funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
+funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
+funnel <- data.frame(
+  x = c(
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
+  ),
+  y = c(funnel_max_se, 0, 0, funnel_max_se)
+)
+
+# # Create funnel plot
+plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
+ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
+  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
+  # Meta-analytic effect size
+  geom_vline(xintercept = summ_brm$intercept, color = "black") +
+  # Experiment-specific effect sizes
+  geom_point(shape = 0) +
+  # Funnel
+  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
+  # Styling
+  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
+  scale_y_reverse() +
+  coord_cartesian(
+    xlim = c(-2.5, 2.5),
+    ylim = c(funnel_max_se, 0),
+    expand = FALSE
+  ) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    y = "Standard error",
+  ) +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
+```
+
+```{r,selection_models_gender}
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# EASY WEIGHT_FUNCTION MODEL
+# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
+# to estimate the population effect size after adjusting for selection bias."
+# specifying p value cutpoints of 0.01, 0.05, and 0.10
+sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
+print(sel_mod)
+# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')
+
+# 4 DIFFERENT STEP FUNCTION MODELS
+# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
+# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
+tab <- data.frame(
+  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
+  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
+  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
+  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
+  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))
+
+sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
+sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
+sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
+sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)
+
+print(sel_moderateonetailed)
+print(sel_severeonetailed)
+print(sel_moderatetwotailed)
+print(sel_severetwotailed)
+
+# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
+# print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
+# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
+# print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')
+
+# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
+
+```
+
+```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
+# Format all frequentist results together as a table
+map2_dfr(
+  c(
+    "Two-level random effects model",
+    "Trim-and-fill",
+    "Selection model: weight-function [0.01, 0.05, 0.3]",
+    "Selection model: moderate one-tailed",
+    "Selection model: severe one-tailed",
+    "Selection model: moderate two-tailed",
+  "Selection model: severe two-tailed"
+  ),
+    list(
+      r_mod,
+      res_tf,
+      sel_mod,
+      sel_moderateonetailed,
+      sel_severeonetailed,
+      sel_moderatetwotailed,
+      sel_severetwotailed
+      ),
+  function(name, res) {
+    print(name)
+    # Intercept / regression weights
+    tibble(
+      Model = c(name, rep(NA, length(res$b) - 1)),
+      Parameter = rownames(res$b),
+      Estimate = print_num(as.numeric(res$b)),
+      `$SE$` = print_num(res$se),
+      `$z$` = print_num(res$zval),
+      `$p$` = print_num(res$pval, digits = 3),
+      ci_lower = print_num(res$ci.lb),
+      ci_upper = print_num(res$ci.ub)
+    ) %>%
+      # Re-format confidence interval
+      mutate(
+        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
+        .keep = "unused"
+      ) %>%
+      bind_rows()
+  }
+) %>%
+  # Rename parameters for readibility
+  mutate(
+    Parameter = c(
+      "Hedges' $g$"
+    )
+  ) %>%
+  # Replace NAs with blank cells
+  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
+
+# Display the table
+apa_table(
+  tab_freq,
+  align = "llccccc",
+  caption = "Sensitivity/robustness analyses frequentist",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+
+# Save the table
+write_csv(tab_freq, file = here(tables_dir, "robustness_freq_gender.csv"))
+```

### 2022-05-09 manuscript.Rmd
Add sensitivity analyses

@@
   - \usepackage{setspace}
+  - \renewcommand{\arraystretch}{0.5}
   - \DeclareCaptionLabelSeparator{bar}{ | }
@@
   warning = FALSE
+)
+
+# Re-run steps that take a long time?
+run <- list(
+  bayesian_models = FALSE,
+  sensitivity_analysis = FALSE
 )
@@
 dir.create(models_dir, showWarnings = FALSE)
+brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
 res_prior <- brm(
@@
   file = here(models_dir, "res_prior"),
-  file_refit = "on_change"
+  file_refit = brms_file_refit
 )
@@
   file = here(models_dir, "res_brm"),
-  file_refit = "on_change"
+  file_refit = brms_file_refit
 )
@@
   file = here(models_dir, "res_prior_reg"),
-  file_refit = "on_change"
+  file_refit = brms_file_refit
 )
@@
   file = here(models_dir, "res_brm_reg"),
-  file_refit = "on_change"
+  file_refit = brms_file_refit
 )
@@
   file = here(models_dir, "res_prior_gender"),
-  file_refit = "on_change"
+  file_refit = brms_file_refit
 )
@@
   file = here(models_dir, "res_brm_gender"),
-  file_refit = "on_change"
+  file_refit = brms_file_refit
 )

### 2022-05-09 supplement.Rmd
Add sensitivity analyses

--- 2022-05-09 supplement.Rmd
@@
 
-```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
+```{r, sensitivity_analysis}
+# Re-run the sensitivity analyses only if requested
+if (run$sensitivity_analysis) {
+
   # Re-run the meta-analysis for different values of r_assumed
   seq(-0.9, 0.9, by = 0.3) %>%
-  set_names(., str_c("r = ", print_num(.))) %>%
-  map(function(ri_sens) {
+    map_dfr(function(ri_sens) {
 
@@
       # Re-run meta-analysis
-    update(res_brm, newdata = dat_ri_sens, refresh = 0)
-  }) -> res_ri_sens
+      res <- update(res_brm, newdata = dat_ri_sens, refresh = 0)
+
+      # Re-run meta-regression
+      res_reg <- update(res_brm_reg, newdata = dat_ri_sens, refresh = 0)
+
+      # Return both as a tibble together with the label
+      return(
+        tibble(
+          manipulation_value = str_c("$r = ", print_num(ri_sens), "$"),
+          res = list(res),
+          res_reg = list(res_reg),
+        )
+      )
+    }) %>%
+    bind_cols(
+      manipulation_name = c("Assumed correlation", rep("", nrow(.) - 1)), .
+    ) -> res_ri_sens
 
@@
   list(
-  "Intercept U(-10,10)" = c(
-    set_prior("uniform(-10, 10)", class = "Intercept"),
+    `$b_Intercept\\sim\\mathcal{U}(-10,10)$` = c(
+      set_prior("uniform(-10, 10)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
       set_prior("cauchy(0, 0.3)", class = "sd")
     ),
-  "Intercept N(0,0.2)" = c(
-    set_prior("normal(0, 0.2)", class = "Intercept"),
+    `b\\sim$\\mathcal{N}(0,0.2)$` = c(
+      set_prior("normal(0, 0.2)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
       set_prior("cauchy(0, 0.3)", class = "sd")
     ),
-  "SD U(0,10)" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
+    `$\\sigma\\sim\\mathcal{U}(0,10)$` = c(
+      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
       set_prior("uniform(0, 10)", class = "sd")
     ),
-  "SD Student-t(10,0,0.2)" = c(
-    set_prior("normal(0, 1)", class = "Intercept"),
+    `$\\sigma\\sim\\text{Student-}t(10,0,0.2)$` = c(
+      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
       set_prior("student_t(10, 0, 0.2)", class = "sd")
@@
   ) %>%
-  # Re-run the meta-analysis with different priors
-  map(
-    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
+    map2_dfr(names(.), function(prior_sens, prior_name) {
+
+      # Re-run meta-analysis of mental rotation performance
+      res <- update(res_brm, prior = prior_sens, refresh = 0)
+
+      # Re-run meta-regression of mental rotation performance
+      res_reg <- update(res_brm_reg, prior = prior_sens, refresh = 0)
+
+      # Re-run meta-analysis of gender differences
+      res_gender <- update(res_brm_gender, prior = prior_sens, refresh = 0)
+
+      # Return both as a tibble together with the label
+      return(
+        tibble(
+          manipulation_value = prior_name,
+          res = list(res),
+          res_reg = list(res_reg),
+          res_gender = list(res_gender)
+        )
+      )
+    }) %>%
+    bind_cols(
+      manipulation_name = c("Prior specification", rep("", nrow(.) - 1)), .
     ) -> res_prior_sens
 
-# Create a table summarizing all sensitivity analyses
-map2_dfr(
-  c(res_ri_sens, res_prior_sens),
-  c(names(res_ri_sens), names(res_prior_sens)),
-  function(res, name) {
+  # Combine results from all sensitivity analyses
+  res_sens <- bind_rows(res_ri_sens, res_prior_sens)
 
-    # Compute ICC
-    var_experiment <- as.matrix(
-      res,
-      variable = "sd_article:experiment__Intercept"
-    )^2
-    var_article <- as.matrix(
-      res,
-      variable = "sd_article__Intercept"
-    )^2
-    var_total <- var_experiment + var_article
-    icc <- var_article / var_total
-    icc_row <- mean_qi(icc) %>%
-      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)
+  # Backup for reuse
+  saveRDS(res_sens, here(models_dir, "res_sens.rds"))
+} else {
+  # Otherwise we load the pre-fitted models
+  res_sens <- readRDS(here(models_dir, "res_sens.rds"))
+}
+```
 
-    # Create a data frame row of summary statistics
-    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
-      bind_rows(icc_row) %>%
+\renewcommand{\arraystretch}{1.0}
+
+```{r, tabs5, include=TRUE}
+# Helper functions for printing results as a table
+print_res_table <- function(res, label_1, label_2) {
+  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
     transmute(
-        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
-        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
+      `Hedges $g$` = b_Intercept,
+      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
+      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
+      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
+        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
     ) %>%
-      pivot_wider(names_from = parameter, values_from = Estimate) %>%
-      bind_cols(Simulation = name, .)
+    summarize(across(.fns = mean_qi)) %>%
+    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
+    bind_cols(Manipulation = label_1, ` ` = label_2, .)
 }
-) -> tab_sens
+
+# Combine results for the (main) meta-analysis of mental rotation performance
+tab_sens <- res_sens %>%
+  select(res, manipulation_name, manipulation_value) %>%
+  pmap_dfr(function(res, manipulation_name, manipulation_value) {
+    print_res_table(res, manipulation_name, manipulation_value)
+  })
 
@@
 apa_table(
-  tab_freq,
-  caption = "Sensitivity analyses",
-  font_size = "scriptsize"
+  tab_sens,
+  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
+  font_size = "scriptsize", escape = FALSE
 )
@@
 # Save the table
-write_csv(tab_sens, file = here(tables_dir, "sensitivity.csv"))
+write_csv(tab_sens, file = here(tables_dir, "tabs5_sens.csv"))
+```
+
+```{r, tabs6, include=TRUE}
+# Helper functions for printing results as a table
+print_res_reg_table <- function(res_reg, label_1, label_2) {
+  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+    transmute(
+      `Hedges $g$` = b_Intercept,
+      `Female - mixed` = b_gender2M1,
+      `Male - female` = b_gender3M2,
+      `Age (per year)` = b_age_c,
+      `Habituation - VoE` = b_task2M1,
+      `[Female - mixed] × age` = `b_gender2M1:age_c`,
+      `[Male - female] × age` = `b_gender3M2:age_c`
+    ) %>%
+    summarize(across(.fns = mean_qi)) %>%
+    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
+    bind_cols(Manipulation = label_1, ` ` = label_2, .)
+}
+
+# Combine results for the meta-regression of mental rotation performance
+tab_sens_reg <- res_sens %>%
+  select(res_reg, manipulation_name, manipulation_value) %>%
+  pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
+    print_res_reg_table(res_reg, manipulation_name, manipulation_value)
+  })
+
+# Display the table
+apa_table(
+  tab_sens_reg,
+  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
+  font_size = "scriptsize", landscape = TRUE, escape = FALSE
+)
+
+# Save the table
+write_csv(tab_sens_reg, file = here(tables_dir, "tabs6_sens_reg.csv"))
+```
+
+```{r, tabs7, include=TRUE}
+# Combine results for the meta-analysis of gender differences
+tab_sens_gender <- res_sens %>%
+  filter(!map_lgl(res_gender, is.null)) %>%
+  select(res_gender, manipulation_name, manipulation_value) %>%
+  pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
+    print_res_table(res_gender, manipulation_name, manipulation_value)
+  })
+
+# Display the table
+apa_table(
+  tab_sens_gender,
+  caption = "Sensitivity analyses for the meta-analysis of gender differences",
+  font_size = "scriptsize", escape = FALSE
+)
+
+# Save the table
+write_csv(tab_sens_gender, file = here(tables_dir, "tabs7_sens_gender.csv"))
 ```

### 2022-05-09 manuscript.Rmd
Update methods

@@
   - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
-  - \captionsetup[table]{font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
+  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
   - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
@@
 
-Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection and process items below).
+Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection process and items below).
 We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
@@
 Moreover, we disregarded effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of `r descs$n_experiments` experiments being included in the meta-analysis (Supplementary Table 1).
+This procedure led to a total of `r descs$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table 1) and 30 articles being included in the meta-analysis of gender differences in mental rotation performance.
 
@@
 Outcome measures and other relevant variables were extracted from each article by one of three raters and verified by a second rater.
-Outcome measures were any summary statistic (Table 1) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
+For the meta-analysis of mental rotation performance, outcome measures were any summary statistic (Table 1) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
 Other extracted variables included, if available, the sample size, the number of males and females, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habituation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table 1).
@@
 
-No investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
-
-## Effect size measures
-
-One outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ $g$) using the formulas provided in Table 1.
-The standard error $SE_g$ of the outcome measure $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018:
-
-$${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J^2}}$$
-
-where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Table 1.
-The correlation $r$ was not reported in any of the original articles [@harrer2021].
-We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Table 5).
-
-For the meta-analysis of gender differences within each article, effect sizes were computed according to the following formulas in Table yy, and redundant groups were excluded from the analysis.
+We also conducted a meta-analysis of the gender differences in mental rotation performance observed within the original articles.
+For this analysis, the outcome measures were any summary statistic (Table 2) that could be used to determine the standardized mean difference between male infants’ mental rotation performance and female infants’ mental rotation performance.
+Other extracted variables included the sample size, the mean age and its standard deviation, and the minimum and maximum age of each gender group.
 
@@
 
-Furthermore, the sampling variance was computed according to the following equation:
-
-$${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$
-
-Where $\tilde{n}$ is the harmonic mean of the group sizes
-(i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$)
-and ${df}$ are the degrees of freedom as provided in row (1) of Table 2.
-A sensitivity analysis highlights the stability of the effect size computed using the Bayesian meta analysis (Supplementary Table 5).
+No investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
+
+## Effect size measures
+
+For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ $g$) using the formulas provided in Table 1.
+The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Table 1.
+The correlation $r$ was not reported in any of the original articles [@harrer2021].
+We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
+A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Table 5).
+
+For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between non-redundant male and female groups of infants was converted into a standardized mean difference with small sample correction (Hedges’ $g$) using the formulas provided in Table 2.
+The standard error of Hedges’ $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$), and $J(df)$ is the correction factor for small samples as described in Row (1) of Table 2.
 
@@
 A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 5).
+For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges’ g) between the novel and familiar rotation condition, weighted by its standard error (see Effect size measures above).
+For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges’ g) between male infants’ mental rotation performance and female infants’ mental rotation performance, weighted by its standard error.
 All Bayesian models were fitted using the brms package (Version `r packageVersion("brms")`) [@burkner2017; @burkner2018] in R (Version `r packageVersion("base")`) [@rcoreteam2021] and the Stan language (Version `r packageVersion("rstan")`) [@standevelopmentteam2022].
@@
 
-Publication bias was evaluated based on a funnel plot and an Egger regression test [@egger1997; @sterne2005].
-To produce the funnel plot, which visualizes the relationship between standard errors and effect sizes, we adapted code from the R package metaviz (`r packageVersion("metaviz")`) [@kossmeier2020].
-For the Egger regression test we used the R package metafor (Version `r packageVersion("metafor")`) [@viechtbauer2010] to identify a potential relationship between standard errors and effect sizes.
-Such a relationship is indicated by the observation that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero in a two-sided $t$-test.
-
-To scrutinize the robustness of the meta-analytic effect size against the effects of individual studies we conducted a jackknife leave-one-out-analysis [@gee2005; @efron1993].
+Publication bias was evaluated based on funnel plots and Egger regression tests [@egger1997; @sterne2005].
+Funnel plots visualize the relationship between standard errors and effect sizes.
+They were created by adapting code from the R package metaviz (`r packageVersion("metaviz")`) [@kossmeier2020].
+The Egger regression test is a formal statistical test for this relationship between standard errors and effect sizes, probing if the weighted linear regression weight of the effect sizes on the standard errors is significantly different from zero.
+This test was performed using code from the metafor package and applying a two-sided false-positive error rate of $\alpha = .05$.
+
+To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false-positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993].
 To this end, we adapted code from the bootstrap R package (Version `r packageVersion("bootstrap")`) [@kostyshak2019].
-Specifically, we fit the Bayesian models repeatedly to our study samples, leaving out one experiment sample for every iteration.
-To take into account the variance inherent in Bayesian model estimation, we averaged over ???
-iterations of the jackknife.
+Specifically, we refitted the Bayesian three-level models repeatedly while leaving out a different one of the original experiments on every iteration.
+To take into account the variance inherent in Bayesian model estimation, we averaged over $x$ iterations of the jackknife.
 

### 2022-05-10 run_slurm.sh
Add Docker/HPC infrastructure

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+# Parse input arguments
+PROJECT_DIR=$1
+REMOTE_DIR=$2
+IMAGE_FILE=$3
+
+# Knit the document
+singularity exec \
+    --bind "$PROJECT_DIR":"$REMOTE_DIR" \
+    --cleanenv \
+    --home "/home/rstudio" \
+    --no-home \
+    --pwd "$REMOTE_DIR" \
+    "$IMAGE_FILE" \
+    Rscript -e "rmarkdown::render(input = 'manuscript.Rmd')"

### 2022-05-10 supplement.Rmd

@@
 (ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Profile likelihood plots [@raue2009; @viechtbauer2010] indicate that restricted maximum likelihood estimation (REML) was able to identify the most likely parameter estimates for the two variance components in the three-level meta-analytic model, that is, for the between-article variance and for the between-experiment (within-article) variance.
+
+```{r, trim_and_fill_within}
+
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# run trim and fill
+res_tf <- trimfill(r_mod)
+print(res_tf)
+res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
+
+summ_brm <- list(intercept = res_tf$beta)
+# Compute funnel
+funnel_z_crit <- stats::qnorm(0.975)
+funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
+funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
+funnel <- data.frame(
+  x = c(
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
+  ),
+  y = c(funnel_max_se, 0, 0, funnel_max_se)
+)
+
+# # Create funnel plot
+plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
+ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
+  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
+  # Meta-analytic effect size
+  geom_vline(xintercept = summ_brm$intercept, color = "black") +
+  # Experiment-specific effect sizes
+  geom_point(shape = 0) +
+  # Funnel
+  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
+  # Styling
+  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
+  scale_y_reverse() +
+  coord_cartesian(
+    xlim = c(-2.5, 2.5),
+    ylim = c(funnel_max_se, 0),
+    expand = FALSE
+  ) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    y = "Standard error",
+  ) +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
+```
+
+```{r,selection_models_within}
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# EASY WEIGHT_FUNCTION MODEL
+# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
+# to estimate the population effect size after adjusting for selection bias."
+# specifying p value cutpoints of 0.01, 0.05, and 0.10
+sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
+print(sel_mod)
+print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')
+
+# 4 DIFFERENT STEP FUNCTION MODELS
+# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
+# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
+tab <- data.frame(
+  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
+  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
+  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
+  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
+  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))
+
+sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
+sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
+sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
+sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)
+
+print(sel_moderateonetailed)
+print(sel_severeonetailed)
+print(sel_moderatetwotailed)
+print(sel_severetwotailed)
+
+print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
+print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
+print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
+print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')
+
+interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
+
+```
+
+```{r, tabs_trimfill_selectionmodels_within, include=TRUE}
+# Format all frequentist results together as a table
+map2_dfr(
+  c(
+    "Two-level random effects model",
+    "Trim-and-fill",
+    "Selection model: weight-function [0.01, 0.05, 0.3]",
+    "Selection model: moderate one-tailed",
+    "Selection model: severe one-tailed",
+    "Selection model: moderate two-tailed",
+  "Selection model: severe two-tailed"
+  ),
+    list(
+      r_mod,
+      res_tf,
+      sel_mod,
+      sel_moderateonetailed,
+      sel_severeonetailed,
+      sel_moderatetwotailed,
+      sel_severetwotailed
+      ),
+  function(name, res) {
+    print(name)
+    # Intercept / regression weights
+    tibble(
+      Model = c(name, rep(NA, length(res$b) - 1)),
+      Parameter = rownames(res$b),
+      Estimate = print_num(as.numeric(res$b)),
+      `$SE$` = print_num(res$se),
+      `$z$` = print_num(res$zval),
+      `$p$` = print_num(res$pval, digits = 3),
+      ci_lower = print_num(res$ci.lb),
+      ci_upper = print_num(res$ci.ub)
+    ) %>%
+      # Re-format confidence interval
+      mutate(
+        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
+        .keep = "unused"
+      ) %>%
+      bind_rows()
+  }
+) %>%
+  # Rename parameters for readibility
+  mutate(
+    Parameter = c(
+      "Hedges' $g$"
+    )
+  ) %>%
+  # Replace NAs with blank cells
+  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
+
+# Display the table
+apa_table(
+  tab_freq,
+  align = "llccccc",
+  caption = "Sensitivity/robustness analyses frequentist",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+
+# Save the table
+write_csv(tab_freq, file = here(tables_dir, "robustness_freq.csv"))
+```
+
+```{r, trim_and_fill_gender}
+dat=dat_gender
+
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# run trim and fill
+res_tf <- trimfill(r_mod)
+print(res_tf)
+# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
+
+summ_brm <- list(intercept = res_tf$beta)
+# Compute funnel
+funnel_z_crit <- stats::qnorm(0.975)
+funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
+funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
+funnel <- data.frame(
+  x = c(
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
+    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
+    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
+  ),
+  y = c(funnel_max_se, 0, 0, funnel_max_se)
+)
+
+# # Create funnel plot
+plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
+ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
+  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
+  # Meta-analytic effect size
+  geom_vline(xintercept = summ_brm$intercept, color = "black") +
+  # Experiment-specific effect sizes
+  geom_point(shape = 0) +
+  # Funnel
+  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
+  # Styling
+  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
+  scale_y_reverse() +
+  coord_cartesian(
+    xlim = c(-2.5, 2.5),
+    ylim = c(funnel_max_se, 0),
+    expand = FALSE
+  ) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    y = "Standard error",
+  ) +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
+```
+
+```{r,selection_models_gender}
+# random-effects 2 level model
+r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# EASY WEIGHT_FUNCTION MODEL
+# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
+# to estimate the population effect size after adjusting for selection bias."
+# specifying p value cutpoints of 0.01, 0.05, and 0.10
+sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
+print(sel_mod)
+# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')
+
+# 4 DIFFERENT STEP FUNCTION MODELS
+# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
+# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
+tab <- data.frame(
+  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
+  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
+  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
+  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
+  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))
+
+sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
+sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
+sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
+sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)
+
+print(sel_moderateonetailed)
+print(sel_severeonetailed)
+print(sel_moderatetwotailed)
+print(sel_severetwotailed)
+
+# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
+# print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
+# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
+# print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')
+
+# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
+
+```
+
+```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
+# Format all frequentist results together as a table
+map2_dfr(
+  c(
+    "Two-level random effects model",
+    "Trim-and-fill",
+    "Selection model: weight-function [0.01, 0.05, 0.3]",
+    "Selection model: moderate one-tailed",
+    "Selection model: severe one-tailed",
+    "Selection model: moderate two-tailed",
+  "Selection model: severe two-tailed"
+  ),
+    list(
+      r_mod,
+      res_tf,
+      sel_mod,
+      sel_moderateonetailed,
+      sel_severeonetailed,
+      sel_moderatetwotailed,
+      sel_severetwotailed
+      ),
+  function(name, res) {
+    print(name)
+    # Intercept / regression weights
+    tibble(
+      Model = c(name, rep(NA, length(res$b) - 1)),
+      Parameter = rownames(res$b),
+      Estimate = print_num(as.numeric(res$b)),
+      `$SE$` = print_num(res$se),
+      `$z$` = print_num(res$zval),
+      `$p$` = print_num(res$pval, digits = 3),
+      ci_lower = print_num(res$ci.lb),
+      ci_upper = print_num(res$ci.ub)
+    ) %>%
+      # Re-format confidence interval
+      mutate(
+        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
+        .keep = "unused"
+      ) %>%
+      bind_rows()
+  }
+) %>%
+  # Rename parameters for readibility
+  mutate(
+    Parameter = c(
+      "Hedges' $g$"
+    )
+  ) %>%
+  # Replace NAs with blank cells
+  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
+
+# Display the table
+apa_table(
+  tab_freq,
+  align = "llccccc",
+  caption = "Sensitivity/robustness analyses frequentist",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+
+# Save the table
+write_csv(tab_freq, file = here(tables_dir, "robustness_freq_gender.csv"))
+```

### 2022-05-10 manuscript.Rmd

@@
 run <- list(
-  bayesian_models = FALSE,
-  sensitivity_analysis = FALSE
+  bayesian_models = TRUE,
+  sensitivity_analysis = TRUE
 )
@@
 # Options for MCMC sampling when fitting Bayesian multilevel models
-n_iter <- 4000 # Posterior samples per chain, including `n_warmup`
-n_warmup <- 1000 # Warmup samples per chain
+n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
+n_warmup <- 2000 # Warmup samples per chain
 n_chains <- 4 # Number of (parallel) chains
@@
 # Run prior predictive simulation
-dir.create(models_dir, showWarnings = FALSE)
+dir.create(models_dir, showWarnings = FALSE, recursive = TRUE)
 brms_file_refit <- ifelse(run$bayesian_models, "always", "never")

### 2022-05-10 supplement.Rmd
Fix typo in formula

--- 2022-05-09 supplement.Rmd
@@
     ),
-    `b\\sim$\\mathcal{N}(0,0.2)$` = c(
+    `$b\\sim\\mathcal{N}(0,0.2)$` = c(
       set_prior("normal(0, 0.2)", class = "b", coef = "Intercept"),

### 2022-05-11 manuscript.Rmd
Small tweaks to LaTeX

@@
   - \usepackage{setspace}
-  - \renewcommand{\arraystretch}{0.5}
+  - \renewcommand{\arraystretch}{0.6}
   - \DeclareCaptionLabelSeparator{bar}{ | }
@@
 run <- list(
-  bayesian_models = TRUE,
-  sensitivity_analysis = TRUE
+  bayesian_models = FALSE,
+  sensitivity_analysis = FALSE
 )
@@
 # Options for MCMC sampling when fitting Bayesian multilevel models
-n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
-n_warmup <- 2000 # Warmup samples per chain
+n_iter <- 4000 # Posterior samples per chain, including `n_warmup`
+n_warmup <- 1000 # Warmup samples per chain
 n_chains <- 4 # Number of (parallel) chains
@@
 Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_brm_reg$age`$, 95% [`r summ_brm_reg$age.lower`, `r summ_brm_reg$age.upper`].
-We also did not detect an interaction between gender and age ([females - mixed] × age: $b = `r summ_brm_reg$female_mixed_age`$, 95% CrI [`r summ_brm_reg$female_mixed_age.lower`, `r summ_brm_reg$female_mixed_age.upper`]; [males - females] × age: $b = `r summ_brm_reg$male_female_age`$, 95% CrI [`r summ_brm_reg$male_female_age.lower`, `r summ_brm_reg$male_female_age.upper`]).
+We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_brm_reg$female_mixed_age`$, 95% CrI [`r summ_brm_reg$female_mixed_age.lower`, `r summ_brm_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_brm_reg$male_female_age`$, 95% CrI [`r summ_brm_reg$male_female_age.lower`, `r summ_brm_reg$male_female_age.upper`]).
 Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_brm_reg$voe_habituation`$, 95% [`r summ_brm_reg$voe_habituation.lower`, `r summ_brm_reg$voe_habituation.upper`].
@@
 coef_colnames <- c(
-  "Intercept" = "b_Intercept",
-  "Females - mixed" = "b_gender2M1",
-  "Males - females" = "b_gender3M2",
-  "Age (per year)" = "b_age_c",
-  "Habituation - VoE" = "b_task2M1",
-  "(Females - Mixed) × age" = "b_gender2M1:age_c",
-  "(Males - Females) × age" = "b_gender3M2:age_c"
+  b_Intercept = expression("Intercept (Hedges" ~ italic(g) * ")"),
+  b_gender2M1 = expression("Females - mixed"),
+  b_gender3M2 = expression("Males - females"),
+  b_age_c = expression("Age (per year)"),
+  b_task2M1 = expression("Habituation - VoE"),
+  `b_gender2M1:age_c` = expression("(Females - Mixed)" %*% "age"),
+  `b_gender3M2:age_c` = expression("(Males - Females)" %*% "age")
 )
@@
 draws_reg_coef %>%
-  select(all_of(coef_colnames)) %>%
+  select(all_of(names(coef_colnames))) %>%
   gather() %>%
@@
   scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
+  scale_y_discrete(labels = coef_colnames) +
   labs(x = expression("Regression weight (" * Delta * italic("g") * ")")) +
@@
 For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ $g$) using the formulas provided in Table 1.
-The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Table 1.
+The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Table 1.
 The correlation $r$ was not reported in any of the original articles [@harrer2021].
@@
 Task was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast [@schad2020].
-We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender task type (i.e., [female - mixed] × age and [male - female] × age) into a Bayesian meta-regression model.
+We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender task type (i.e., [female - mixed] $\times$ age and [male - female] $\times$ age) into a Bayesian meta-regression model.
 This model used the same random effects structure and sampling parameters as described above.
@@
 Funnel plots visualize the relationship between standard errors and effect sizes.
-They were created by adapting code from the R package metaviz (`r packageVersion("metaviz")`) [@kossmeier2020].
+They were created by adapting code from the R package metaviz (Version `r packageVersion("metaviz")`) [@kossmeier2020].
 The Egger regression test is a formal statistical test for this relationship between standard errors and effect sizes, probing if the weighted linear regression weight of the effect sizes on the standard errors is significantly different from zero.

### 2022-05-11 supplement.Rmd
Small tweaks to LaTeX

@@
 
-3. Compute the standard deviation of the mean looking time difference:
-
-$${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
+3. Compute the standard deviation of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
 
@@
 
-5. Compute the observed correlation between conditions based on rearranging an equation by @cohen1988:
-
-$$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
+5.
+Compute the observed correlation between conditions based on rearranging an equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
 
@@
 map2_dfr(
-  c("Meta-analysis", "Meta-regression", "Gender differences"),
+  c(
+    "Meta-analysis of mental rotation",
+    "Meta-regression of mental rotation",
+    "Meta-analysis of gender differences"
+  ),
   list(res_freq, res_reg_freq, res_gender_freq),
@@
       "$\\sigma_{\\text{Experiment}}^2$",
-      "Intercept",
+      "Intercept (Hedges' $g$)",
       "Female - mixed",
@@
       "Habituation - VoE",
-      "(Female - mixed) × age",
-      "(Male - female) × age",
+      "(Female - mixed) $\\times$ age",
+      "(Male - female) $\\times$ age",
       "$\\sigma_{\\text{Article}}^2$",
@@
   list(
-    `$b_Intercept\\sim\\mathcal{U}(-10,10)$` = c(
+    `$b\\sim\\mathcal{U}(-10,10)$` = c(
       set_prior("uniform(-10, 10)", class = "b", coef = "Intercept"),
@@
     transmute(
-      `Hedges $g$` = b_Intercept,
+      `Hedges' $g$` = b_Intercept,
       `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
@@
     transmute(
-      `Hedges $g$` = b_Intercept,
+      `Intercept` = b_Intercept,
       `Female - mixed` = b_gender2M1,
@@
       `Habituation - VoE` = b_task2M1,
-      `[Female - mixed] × age` = `b_gender2M1:age_c`,
-      `[Male - female] × age` = `b_gender3M2:age_c`
+      `[Female - mixed] $\\times$ age` = `b_gender2M1:age_c`,
+      `[Male - female] $\\times$ age` = `b_gender3M2:age_c`
     ) %>%
@@
   name_expr = c(
-    "Hedges ~ italic(g)", "italic(sigma)[article]", "italic(sigma)[experiment]"
+    "\"Hedges'\" ~ italic(g)",
+    "italic(sigma)[article]",
+    "italic(sigma)[experiment]"
   ),
@@
     conv_stats,
-    y = 0.45, x = -800, color = "black", parse = TRUE, angle = 90
+    y = 0.45, x = -0.042 * n_draws, color = "black", parse = TRUE, angle = 90
   ) +
@@
     conv_stats,
-    x = 13000, hjust = 1, color = "black", parse = TRUE,
+    x = 0.684 * n_draws, hjust = 1, color = "black", parse = TRUE,
   ) +
@@
     conv_stats,
-    x = 16000, hjust = 1, color = "black", parse = TRUE,
+    x = 0.842 * n_draws, hjust = 1, color = "black", parse = TRUE,
   ) +
@@
     conv_stats,
-    x = 19000, hjust = 1, color = "black", parse = TRUE,
+    x = n_draws, hjust = 1, color = "black", parse = TRUE,
   ) +
@@
 Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution.
-Rhat = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, Neff(bulk) = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), Neff(tail) = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
+$R\text{hat}$ = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
 For details about these and other convergence criteria, we refer the reader to @vehtari2021.

### 2022-05-11 manuscript.Rmd
Add jackknife analysis

@@
 library(magrittr)
+library(furrr)
 library(metafor)
@@
   bayesian_models = FALSE,
+  jackknife_analysis = FALSE,
   sensitivity_analysis = FALSE

### 2022-05-11 supplement.Rmd
Add jackknife analysis

@@
 
+```{r, jackknife, include=TRUE}
+# Helper functions for printing results from Bayesian model as a table
+print_res_table <- function(res,
+                            label_1 = NULL,
+                            label_2 = NULL,
+                            label_col_1 = "label_1",
+                            label_col_2 = "label_2") {
+  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+    transmute(
+      `Hedges' $g$` = b_Intercept,
+      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
+      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
+      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
+        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
+    ) %>%
+    summarize(across(.fns = mean_qi)) %>%
+    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
+  if (!is.null(label_2)) {
+    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
+      rename(!!label_col_2 := tmp)
+    tab <- cbind(label_2_tab, tab)
+  }
+  if (!is.null(label_1)) {
+    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
+      rename(!!label_col_1 := tmp)
+    tab <- cbind(label_1_tab, tab)
+  }
+  return(tab)
+}
+
+# Re-run the jackknife analysis only if requested
+jackknife_file <- here(tables_dir, "jackknife.csv")
+if (run$jackknife_analysis) {
+
+  # Re-fit the meta-analysis, leaving one experiment out at a time
+  # Using parallelization with `furrr`
+  n_cores <- availableCores()
+  n_workers <- n_cores %/% n_chains
+  plan(multisession, workers = n_workers)
+  future_map_dfr(seq_len(nrow(dat[1:2, ])), function(jackknife_index) {
+    dat_jackknife <- dat[-jackknife_index, ]
+    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
+    print_res_table(
+      res_jackknife,
+      label_1 = dat$article[jackknife_index],
+      label_2 = dat$group_long[jackknife_index],
+      label_col_1 = "Article", label_col_2 = "Experiment"
+    )
+  }) -> jackknife_tab
+
+  # Save the table
+  write_csv(jackknife_tab, file = jackknife_file)
+} else {
+
+  # Otherwise we load the pre-computed results
+  jackknife_tab <- read_csv(jackknife_file, col_types = "c")
+}
+
+# Display the table
+apa_table(
+  jackknife_tab,
+  align = "llcccc",
+  caption = "Jackknife (leave-one-out) analysis",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+```
+
 ```{r, sensitivity_analysis}
@@
 ```{r, tabs5, include=TRUE}
-# Helper functions for printing results as a table
-print_res_table <- function(res, label_1, label_2) {
-  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-    transmute(
-      `Hedges' $g$` = b_Intercept,
-      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
-      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
-      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
-        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
-    ) %>%
-    summarize(across(.fns = mean_qi)) %>%
-    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
-    bind_cols(Manipulation = label_1, ` ` = label_2, .)
-}
-
 # Combine results for the (main) meta-analysis of mental rotation performance
@@
   pmap_dfr(function(res, manipulation_name, manipulation_value) {
-    print_res_table(res, manipulation_name, manipulation_value)
+    print_res_table(
+      res,
+      label_1 = manipulation_name, label_2 = manipulation_value,
+      label_col_1 = "Manipulation", label_col_2 = " "
+    )
   })
@@
 # Helper functions for printing results as a table
-print_res_reg_table <- function(res_reg, label_1, label_2) {
+print_res_reg_table <- function(res_reg,
+                                label_1,
+                                label_2,
+                                label_col_1,
+                                label_col_2) {
   spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
@@
     summarize(across(.fns = mean_qi)) %>%
-    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
-    bind_cols(Manipulation = label_1, ` ` = label_2, .)
+    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
+  if (!is.null(label_2)) {
+    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
+      rename(!!label_col_2 := tmp)
+    tab <- cbind(label_2_tab, tab)
+  }
+  if (!is.null(label_1)) {
+    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
+      rename(!!label_col_1 := tmp)
+    tab <- cbind(label_1_tab, tab)
+  }
+  return(tab)
 }
@@
 tab_sens_reg <- res_sens %>%
-  select(res_reg, manipulation_name, manipulation_value) %>%
+  select(
+    res_reg, manipulation_name, manipulation_value
+  ) %>%
   pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
-    print_res_reg_table(res_reg, manipulation_name, manipulation_value)
+    print_res_reg_table(
+      res_reg,
+      label_1 = manipulation_name, label_2 = manipulation_value,
+      label_col_1 = "Manipulation", label_col_2 = " "
+    )
   })
@@
   pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
-    print_res_table(res_gender, manipulation_name, manipulation_value)
+    print_res_table(
+      res_gender,
+      label_1 = manipulation_name, label_2 = manipulation_value,
+      label_col_1 = "Manipulation", label_col_2 = " "
+    )
   })

### 2022-05-11 supplement.Rmd
Add jackknife analysis

@@
   plan(multisession, workers = n_workers)
-  future_map_dfr(seq_len(nrow(dat[1:2, ])), function(jackknife_index) {
+  future_map_dfr(seq_len(nrow(dat)), function(jackknife_index) {
     dat_jackknife <- dat[-jackknife_index, ]

### 2022-05-11 supplement.Rmd

@@
 # Re-run the jackknife analysis only if requested
-jackknife_file <- here(tables_dir, "jackknife.csv")
 if (run$jackknife_analysis) {
@@
     )
-  }) -> jackknife_tab
+  }) -> tab_jackknife
 
   # Save the table
-  write_csv(jackknife_tab, file = jackknife_file)
+  write_csv(tab_jackknife, file = here(tables_dir, "jackknife.csv"))
 } else {
@@
   # Otherwise we load the pre-computed results
-  jackknife_tab <- read_csv(jackknife_file, col_types = "c")
+  tab_jackknife <- read_csv(
+    here(tables_dir, "jackknife.csv"),
+    col_types = "c", na = character()
+  )
 }
@@
 apa_table(
-  jackknife_tab,
+  tab_jackknife,
   align = "llcccc",
@@
 
-```{r, sensitivity_analysis}
-# Re-run the sensitivity analyses only if requested
-if (run$sensitivity_analysis) {
-
-  # Re-run the meta-analysis for different values of r_assumed
-  seq(-0.9, 0.9, by = 0.3) %>%
-    map_dfr(function(ri_sens) {
-
-      # Re-compute standard errors of the effect sizes
-      mutate(
-        dat,
-        vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
-          (1 + gi^2 * (ni / (2 * (1 - ri_sens)))) - (gi^2 / ji^2),
-        sei = sqrt(vi)
-      ) -> dat_ri_sens
-
-      # Re-run meta-analysis
-      res <- update(res_brm, newdata = dat_ri_sens, refresh = 0)
-
-      # Re-run meta-regression
-      res_reg <- update(res_brm_reg, newdata = dat_ri_sens, refresh = 0)
-
-      # Return both as a tibble together with the label
-      return(
-        tibble(
-          manipulation_value = str_c("$r = ", print_num(ri_sens), "$"),
-          res = list(res),
-          res_reg = list(res_reg),
-        )
-      )
-    }) %>%
-    bind_cols(
-      manipulation_name = c("Assumed correlation", rep("", nrow(.) - 1)), .
-    ) -> res_ri_sens
-
-  # Prior sensitivity analysis
-  list(
-    `$b\\sim\\mathcal{U}(-10,10)$` = c(
-      set_prior("uniform(-10, 10)", class = "b", coef = "Intercept"),
-      set_prior("normal(0, 0.5)", class = "b"),
-      set_prior("cauchy(0, 0.3)", class = "sd")
-    ),
-    `$b\\sim\\mathcal{N}(0,0.2)$` = c(
-      set_prior("normal(0, 0.2)", class = "b", coef = "Intercept"),
-      set_prior("normal(0, 0.5)", class = "b"),
-      set_prior("cauchy(0, 0.3)", class = "sd")
-    ),
-    `$\\sigma\\sim\\mathcal{U}(0,10)$` = c(
-      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
-      set_prior("normal(0, 0.5)", class = "b"),
-      set_prior("uniform(0, 10)", class = "sd")
-    ),
-    `$\\sigma\\sim\\text{Student-}t(10,0,0.2)$` = c(
-      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
-      set_prior("normal(0, 0.5)", class = "b"),
-      set_prior("student_t(10, 0, 0.2)", class = "sd")
-    )
-  ) %>%
-    map2_dfr(names(.), function(prior_sens, prior_name) {
-
-      # Re-run meta-analysis of mental rotation performance
-      res <- update(res_brm, prior = prior_sens, refresh = 0)
-
-      # Re-run meta-regression of mental rotation performance
-      res_reg <- update(res_brm_reg, prior = prior_sens, refresh = 0)
-
-      # Re-run meta-analysis of gender differences
-      res_gender <- update(res_brm_gender, prior = prior_sens, refresh = 0)
-
-      # Return both as a tibble together with the label
-      return(
-        tibble(
-          manipulation_value = prior_name,
-          res = list(res),
-          res_reg = list(res_reg),
-          res_gender = list(res_gender)
-        )
-      )
-    }) %>%
-    bind_cols(
-      manipulation_name = c("Prior specification", rep("", nrow(.) - 1)), .
-    ) -> res_prior_sens
-
-  # Combine results from all sensitivity analyses
-  res_sens <- bind_rows(res_ri_sens, res_prior_sens)
-
-  # Backup for reuse
-  saveRDS(res_sens, here(models_dir, "res_sens.rds"))
-} else {
-  # Otherwise we load the pre-fitted models
-  res_sens <- readRDS(here(models_dir, "res_sens.rds"))
-}
-```
-
-\renewcommand{\arraystretch}{1.0}
-
-```{r, tabs5, include=TRUE}
-# Combine results for the (main) meta-analysis of mental rotation performance
-tab_sens <- res_sens %>%
-  select(res, manipulation_name, manipulation_value) %>%
-  pmap_dfr(function(res, manipulation_name, manipulation_value) {
-    print_res_table(
-      res,
-      label_1 = manipulation_name, label_2 = manipulation_value,
-      label_col_1 = "Manipulation", label_col_2 = " "
-    )
-  })
-
-# Display the table
-apa_table(
-  tab_sens,
-  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
-  font_size = "scriptsize", escape = FALSE
-)
-
-# Save the table
-write_csv(tab_sens, file = here(tables_dir, "tabs5_sens.csv"))
-```
-
-```{r, tabs6, include=TRUE}
+```{r, sensitivity_analysis, include=TRUE}
 # Helper functions for printing results as a table
@@
 
-# Combine results for the meta-regression of mental rotation performance
-tab_sens_reg <- res_sens %>%
+# Re-run the sensitivity analyses only if requested
+if (run$sensitivity_analysis) {
+
+  # Re-run the meta-analysis for different values of r_assumed
+  seq(-0.9, 0.9, by = 0.3) %>%
+    map_dfr(function(ri_sens) {
+
+      # Re-compute standard errors of the effect sizes
+      mutate(
+        dat,
+        vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
+          (1 + gi^2 * (ni / (2 * (1 - ri_sens)))) - (gi^2 / ji^2),
+        sei = sqrt(vi)
+      ) -> dat_ri_sens
+
+      # Re-run meta-analysis
+      res <- update(res_brm, newdata = dat_ri_sens, refresh = 0)
+
+      # Re-run meta-regression
+      res_reg <- update(res_brm_reg, newdata = dat_ri_sens, refresh = 0)
+
+      # Return both as a tibble together with the label
+      return(
+        tibble(
+          manipulation_value = str_c("$r = ", print_num(ri_sens), "$"),
+          res = list(res),
+          res_reg = list(res_reg),
+        )
+      )
+    }) %>%
+    bind_cols(
+      manipulation_name = c("Assumed correlation", rep("", nrow(.) - 1)), .
+    ) -> sens_ri
+
+  # Prior sensitivity analysis
+  list(
+    `$b\\sim\\mathcal{U}(-10,10)$` = c(
+      set_prior("uniform(-10, 10)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
+      set_prior("cauchy(0, 0.3)", class = "sd")
+    ),
+    `$b\\sim\\mathcal{N}(0,0.2)$` = c(
+      set_prior("normal(0, 0.2)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
+      set_prior("cauchy(0, 0.3)", class = "sd")
+    ),
+    `$\\sigma\\sim\\mathcal{U}(0,10)$` = c(
+      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
+      set_prior("uniform(0, 10)", class = "sd")
+    ),
+    `$\\sigma\\sim\\text{Student-}t(10,0,0.2)$` = c(
+      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
+      set_prior("normal(0, 0.5)", class = "b"),
+      set_prior("student_t(10, 0, 0.2)", class = "sd")
+    )
+  ) %>%
+    map2_dfr(names(.), function(prior_sens, prior_name) {
+
+      # Re-run meta-analysis of mental rotation performance
+      res <- update(res_brm, prior = prior_sens, refresh = 0)
+
+      # Re-run meta-regression of mental rotation performance
+      res_reg <- update(res_brm_reg, prior = prior_sens, refresh = 0)
+
+      # Re-run meta-analysis of gender differences
+      res_gender <- update(res_brm_gender, prior = prior_sens, refresh = 0)
+
+      # Return both as a tibble together with the label
+      return(
+        tibble(
+          manipulation_value = prior_name,
+          res = list(res),
+          res_reg = list(res_reg),
+          res_gender = list(res_gender)
+        )
+      )
+    }) %>%
+    bind_cols(
+      manipulation_name = c("Prior specification", rep("", nrow(.) - 1)), .
+    ) -> sens_prior
+
+  # Combine results from all sensitivity analyses
+  sens <- bind_rows(sens_ri, sens_prior)
+
+  # Create table for the (main) meta-analysis of mental rotation performance
+  sens %>%
+  select(res, manipulation_name, manipulation_value) %>%
+  pmap_dfr(function(res, manipulation_name, manipulation_value) {
+    print_res_table(
+      res,
+      label_1 = manipulation_name, label_2 = manipulation_value,
+      label_col_1 = "Manipulation", label_col_2 = " "
+    )
+    }) -> tab_sens
+  write_csv(tab_sens, file = here(tables_dir, "sens.csv"))
+
+  # Create table for the meta-regression of mental rotation performance
+  sens %>%
   select(
@@
     )
-  })
-
-# Display the table
-apa_table(
-  tab_sens_reg,
-  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
-  font_size = "scriptsize", landscape = TRUE, escape = FALSE
-)
-
-# Save the table
-write_csv(tab_sens_reg, file = here(tables_dir, "tabs6_sens_reg.csv"))
-```
-
-```{r, tabs7, include=TRUE}
-# Combine results for the meta-analysis of gender differences
-tab_sens_gender <- res_sens %>%
+    }) -> tab_sens_reg
+  write_csv(tab_sens_reg, file = here(tables_dir, "sens_reg.csv"))
+
+  # Create table for the meta-analysis of gender differences
+  sens %>%
   filter(!map_lgl(res_gender, is.null)) %>%
@@
     )
-  })
-
-# Display the table
+    }) -> tab_sens_gender
+  write_csv(tab_sens_gender, file = here(tables_dir, "sens_gender.csv"))
+} else {
+
+  # Otherwise we load the pre-computed results
+  tab_sens <- read_csv(
+    here(tables_dir, "sens.csv"),
+    col_types = "c", na = character(), trim_ws = FALSE
+  )
+  tab_sens_reg <- read_csv(
+    here(tables_dir, "sens_reg.csv"),
+    col_types = "c", na = character(), trim_ws = FALSE
+  )
+  tab_sens_gender <- read_csv(
+    here(tables_dir, "sens_gender.csv"),
+    col_types = "c", na = character(), trim_ws = FALSE
+  )
+}
+
+# Display the tables
+apa_table(
+  tab_sens,
+  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
+  font_size = "scriptsize", escape = FALSE
+)
+apa_table(
+  tab_sens_reg,
+  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
+  font_size = "scriptsize", landscape = TRUE, escape = FALSE
+)
 apa_table(
@@
 )
-
-# Save the table
-write_csv(tab_sens_gender, file = here(tables_dir, "tabs7_sens_gender.csv"))
 ```

### 2022-05-11 supplement.Rmd
Move `print_` functions to separate script

@@
   mutate(
-    age_mean = format_days_months(age_mean),
+    age_mean = print_days_months(age_mean),
     age_sd = str_c(as.character(round(age_sd)), "d"),
@@
 ```
-
-\renewcommand{\arraystretch}{1.5}
 
@@
 ```{r, jackknife, include=TRUE}
-# Helper functions for printing results from Bayesian model as a table
-print_res_table <- function(res,
-                            label_1 = NULL,
-                            label_2 = NULL,
-                            label_col_1 = "label_1",
-                            label_col_2 = "label_2") {
-  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-    transmute(
-      `Hedges' $g$` = b_Intercept,
-      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
-      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
-      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
-        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
-    ) %>%
-    summarize(across(.fns = mean_qi)) %>%
-    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
-  if (!is.null(label_2)) {
-    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
-      rename(!!label_col_2 := tmp)
-    tab <- cbind(label_2_tab, tab)
-  }
-  if (!is.null(label_1)) {
-    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
-      rename(!!label_col_1 := tmp)
-    tab <- cbind(label_1_tab, tab)
-  }
-  return(tab)
-}
-
 # Re-run the jackknife analysis only if requested
@@
   caption = "Jackknife (leave-one-out) analysis",
-  font_size = "scriptsize",
-  escape = FALSE
+  font_size = "scriptsize", landscape = TRUE, escape = FALSE
 )
@@
 ```{r, sensitivity_analysis, include=TRUE}
-# Helper functions for printing results as a table
-print_res_reg_table <- function(res_reg,
-                                label_1,
-                                label_2,
-                                label_col_1,
-                                label_col_2) {
-  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-    transmute(
-      `Intercept` = b_Intercept,
-      `Female - mixed` = b_gender2M1,
-      `Male - female` = b_gender3M2,
-      `Age (per year)` = b_age_c,
-      `Habituation - VoE` = b_task2M1,
-      `[Female - mixed] $\\times$ age` = `b_gender2M1:age_c`,
-      `[Male - female] $\\times$ age` = `b_gender3M2:age_c`
-    ) %>%
-    summarize(across(.fns = mean_qi)) %>%
-    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
-  if (!is.null(label_2)) {
-    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
-      rename(!!label_col_2 := tmp)
-    tab <- cbind(label_2_tab, tab)
-  }
-  if (!is.null(label_1)) {
-    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
-      rename(!!label_col_1 := tmp)
-    tab <- cbind(label_1_tab, tab)
-  }
-  return(tab)
-}
-
 # Re-run the sensitivity analyses only if requested
@@
     ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_print = print_ci(gi, ci_lb, ci_ub)
+    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
   ) %>%

### 2022-05-11 manuscript_files/helper_functions.R

@@ -1,0 +1,91 @@
+# Formatting days as months + days
+print_days_months <- function(days, long = FALSE) {
+  m_str <- ifelse(long, " months ", "m ")
+  d_str <- ifelse(long, " days", "d")
+  days_per_month <- 30.417
+  months <- days %/% days_per_month
+  days_left <- as.integer(days - months * days_per_month)
+  str <- paste0(as.character(months), m_str, as.character(days_left), d_str)
+  str[is.na(days)] <- NA
+  return(str)
+}
+
+# Formatting percentages with one decimal place
+print_perc <- function(x) scales::percent(x, accuracy = 0.1)
+
+# Formatting numbers with a certain number of decimal places
+print_num <- function(x, digits = 2) {
+  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
+  x[x == "NA"] <- NA
+  return(x)
+}
+
+# Format confidence interval
+print_ci <- function(lb, ub) {
+  paste0("[", print_num(lb), ", ", print_num(ub), "]")
+}
+
+# Format mean value and confidence interval
+print_mean_ci <- function(mean, lb, ub) {
+  paste(print_num(mean), print_ci(lb, ub))
+}
+
+# Format results of Bayesian meta-analsis as a table with optional labels
+print_res_table <- function(res,
+                            label_1 = NULL,
+                            label_2 = NULL,
+                            label_col_1 = "label_1",
+                            label_col_2 = "label_2") {
+  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+    transmute(
+      `Hedges' $g$` = b_Intercept,
+      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
+      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
+      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
+        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
+    ) %>%
+    summarize(across(.fns = mean_qi)) %>%
+    map_dfc(~ print_mean_ci(.$y, .$ymin, .$ymax)) -> tab
+  if (!is.null(label_2)) {
+    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
[…]

### 2022-05-11 manuscript.Rmd

@@
 library(cowplot)
+
+# Load custom helper functions
+source(here("manuscript_files", "helper_functions.R"))
 
@@
 
-# Helper functions to re-format age from days to months + days
-format_days_months <- function(days, long = FALSE) {
-  m_str <- ifelse(long, " months ", "m ")
-  d_str <- ifelse(long, " days", "d")
-  days_per_month <- 30.417
-  months <- days %/% days_per_month
-  days_left <- as.integer(days - months * days_per_month)
-  str <- paste0(as.character(months), m_str, as.character(days_left), d_str)
-  str[is.na(days)] <- NA
-  return(str)
-}
-
-# Helper function for printing percentages
-print_perc <- function(x) scales::percent(x, accuracy = 0.1)
-
 # Extract some descriptive statistics for usage in the main text
@@
   max_age_months = as.integer(max(dat$age_max, na.rm = TRUE) / 30.417),
-  mean_age_weighted = format_days_months(
+  mean_age_weighted = print_days_months(
     sum(dat$age_mean * dat$ni) / (sum(dat$ni)),
@@
 ```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
-# Helper functions for printing numbers with exactly 2 decimal points
-print_num <- function(x, digits = 2) {
-  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
-  x[x == "NA"] <- NA
-  return(x)
-}
-
-# Helper function for confidence intervals (optionally adding the mean)
-print_ci <- function(lb, ub, mean = NULL) {
-  mean_str <- ifelse(mean, paste0(print_num(mean), " "))
-  paste0(mean_str, "[", print_num(lb), ", ", print_num(ub), "]")
-}
-
 # Get posterior draws for the effect in each experiment
@@
     ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_print = print_ci(ci_lb, ci_ub, mean = gi)
+    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
   ) %>%

### 2022-05-11 supplement.Rmd
Prettify main (within) selection models

@@
 We ran a sensitivity analysis to test the robustness of our Bayesian meta-analytic model against this assumption (Supplementary Table 4).
+
+## Supplementary Methods 2 | Bias correction and sensitivity analysis for frequentist results
+
+We used a simplified two-level version (i.e., dropping the article level) of our frequentist three-level model to further correct our results for publication bias.
+We conducted a trim-and-fill analysis [@duval2000] to impute possible effect sizes of non-published experiments and then observed their influence on the meta-analytic effect size (Supplementary Tables 8 and 9).
+
+Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published.
+We ran one selection model assuming a weight function with fixed p-value cutoffs at p = .01, p = .05, and p = 0.3[@vevea1995], as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005].
+These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).
 
@@
 map2_dfr(
+  list(res_freq, res_reg_freq, res_gender_freq),
   c(
@@
   ),
-  list(res_freq, res_reg_freq, res_gender_freq),
-  function(name, res) {
-    # Intercept / regression weights
-    tibble(
-      Model = c(name, rep(NA, length(res$b) - 1)),
-      Parameter = rownames(res$b),
-      Estimate = print_num(as.numeric(res$b)),
-      `$SE$` = print_num(res$se),
-      `$z$` = print_num(res$zval),
-      `$p$` = print_num(res$pval, digits = 3),
-      ci_lower = print_num(res$ci.lb),
-      ci_upper = print_num(res$ci.ub)
-    ) %>%
-      # Re-format confidence interval
-      mutate(
-        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
-        .keep = "unused"
-      ) %>%
-      # Add variances
-      bind_rows(tibble(
-        Parameter = res$s.name,
-        Estimate = print_num(res$sigma2)
-      ))
-  }
+  ~ print_res_freq_table(
+    res_freq = .x, label_1 = .y, label_col_1 = "Model", print_sigma2s = TRUE
+  )
 ) %>%
@@
 
-```{r, trim_and_fill_within}
+```{r, trim_fill_selection}
+# Re-fit frequentist meta-analysis using a two-level model
+res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)
+
+# Run trim-and-fill analysis
+res_trim_fill <- trimfill(res_freq_2)
+print(res_trim_fill)
+
+# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
+res_selection_weights <- selmodel(
+  res_freq_2,
+  type = "stepfun", steps = c(0.01, .05, .3, 1)
+)
+print(res_selection_weights)
+
+# More selection models based on four different step functions
+tibble(
+  delta_one_tailed_moderate = c(
+    1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55,
+    0.50, 0.50, 0.50, 0.50, 0.50, 0.50
+  ),
+  delta_one_tailed_severe = c(
+    1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35,
+    0.30, 0.25, 0.10, 0.10, 0.10, 0.10
+  ),
+  delta_two_tailed_moderate = c(
+    1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60,
+    0.75, 0.80, 0.90, 0.95, 0.99, 1.00
+  ),
+  delta_two_tailed_severe = c(
+    1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25,
+    0.50, 0.60, 0.75, 0.90, 0.99, 1.00
+  )
+) %>%
+  print() %>%
+  map(function(delta) {
+    selmodel(
+      res_freq_2,
+      type = "stepfun",
+      steps = c(
+        0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50,
+        0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1
+      ),
+      delta = delta
+    )
+  }) -> res_selection_steps
+print(res_selection_steps)
+```
+
+```{r, tabs8, include=TRUE}
+# Combine all trim-and-fill and selection models into one table
+tibble(
+  res = c(
+    list(res_freq_2, res_trim_fill, res_selection_weights), res_selection_steps
+  ),
+  label_1 = c(
+    "Two-level model", "Trim-and-fill model",
+    "Selection models:", "", "", "", ""
+  ),
+  label_2 = c(
+    "", "", "Weight function [.01, .05, .30]",
+    "One-tailed, moderate bias", "One-tailed, severe bias",
+    "Two-tailed, moderate bias", "Two-tailed, severe bias"
+  )
+) %>%
+  pmap_dfr(
+    ~ print_res_freq_table(
+      res_freq = ..1, label_1 = ..2, label_2 = ..3,
+      label_col_1 = "Model", label_col_2 = " ", print_sigma2s = FALSE
+    )
+  ) %>%
+  select(-Parameter) %>%
+  rename(`Hedges' $g$` = Estimate) -> tab_trim_fill_selection
+
+# Save the table
+write_csv(
+  tab_trim_fill_selection,
+  file = here(tables_dir, "trim_fill_selection.csv")
+)
+
+# Display the table
+apa_table(
+  tab_trim_fill_selection,
+  align = "llccccc",
+  caption = "Trim-and-fill and selection model analyses",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+```
+
+```{r, figs4, include=TRUE, fig.width=6, fig.height=3.5, out.width="50%"}
+# Compute new funnel, taking into account the trim-and-fill results
+funnel_trim_fill <- with(
+  list(
+    z_crit_05 = stats::qnorm(0.975),
+    max_se = max(sqrt(res_trim_fill$vi)) + 0.05
+  ),
+  {
+    data.frame(
+      x = c(
+        res_trim_fill$b - z_crit_05 * sqrt(max_se^2),
+        res_trim_fill$b,
+        res_trim_fill$b + z_crit_05 * sqrt(max_se^2)
+      ),
+      y = c(max_se, 0, max_se)
+    )
+  }
+)
+
+# Create new funnel plot, enhanced by the filled in studies
+trim_fill_color <- "#e42536"
+plots_funnel[[1]] +
+  # Add trim and fill funnel
+  geom_path(
+    data = funnel_trim_fill,
+    aes(x = x, y = y),
+    color = trim_fill_color
+  ) +
+  geom_vline(xintercept = res_trim_fill$b, color = trim_fill_color) +
+  # Add filled in studies
+  geom_point(
+    data = with(res_trim_fill, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
+    color = trim_fill_color, shape = 0
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "funnel_trim_fill.pdf"), width = 6, height = 3.5)
+```
+
+```{r, trim_and_fill_gender}
+dat <- dat_gender
 
 # random-effects 2 level model
-r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)
 
 # run trim and fill
-res_tf <- trimfill(r_mod)
-print(res_tf)
-res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
+res_trim_fill <- trimfill(res_freq_2)
+print(res_trim_fill)
+# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
 
-summ_brm <- list(intercept = res_tf$beta)
+summ_brm <- list(intercept = res_trim_fill$beta)
 # Compute funnel
@@
 # # Create funnel plot
-plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
-ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
-  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
-  # Meta-analytic effect size
-  geom_vline(xintercept = summ_brm$intercept, color = "black") +
-  # Experiment-specific effect sizes
-  geom_point(shape = 0) +
-  # Funnel
-  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
-  # Styling
-  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
-  scale_y_reverse() +
-  coord_cartesian(
-    xlim = c(-2.5, 2.5),
-    ylim = c(funnel_max_se, 0),
-    expand = FALSE
-  ) +
-  labs(
-    x = expression("Hedges'" ~ italic("g")),
-    y = "Standard error",
-  ) +
-  theme_classic() +
-  theme(
-    axis.line = element_line(colour = "black"),
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    text = element_text(family = "Helvetica", color = "black")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
-```
-
-```{r,selection_models_within}
-# random-effects 2 level model
-r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
-
-# EASY WEIGHT_FUNCTION MODEL
-# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
-# to estimate the population effect size after adjusting for selection bias."
-# specifying p value cutpoints of 0.01, 0.05, and 0.10
-sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
-print(sel_mod)
-print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')
-
-# 4 DIFFERENT STEP FUNCTION MODELS
-# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
-# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
-tab <- data.frame(
-  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
-  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
-  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
-  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
-  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))
-
-sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
-sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
-sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
-sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)
-
-print(sel_moderateonetailed)
-print(sel_severeonetailed)
-print(sel_moderatetwotailed)
-print(sel_severetwotailed)
-
-print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
-print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
-print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
-print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')
-
-interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
-
-```
-
-```{r, tabs_trimfill_selectionmodels_within, include=TRUE}
-# Format all frequentist results together as a table
-map2_dfr(
-  c(
-    "Two-level random effects model",
-    "Trim-and-fill",
-    "Selection model: weight-function [0.01, 0.05, 0.3]",
-    "Selection model: moderate one-tailed",
-    "Selection model: severe one-tailed",
-    "Selection model: moderate two-tailed",
-  "Selection model: severe two-tailed"
-  ),
-    list(
-      r_mod,
-      res_tf,
-      sel_mod,
-      sel_moderateonetailed,
-      sel_severeonetailed,
-      sel_moderatetwotailed,
-      sel_severetwotailed
-      ),
-  function(name, res) {
-    print(name)
-    # Intercept / regression weights
-    tibble(
-      Model = c(name, rep(NA, length(res$b) - 1)),
-      Parameter = rownames(res$b),
-      Estimate = print_num(as.numeric(res$b)),
-      `$SE$` = print_num(res$se),
-      `$z$` = print_num(res$zval),
-      `$p$` = print_num(res$pval, digits = 3),
-      ci_lower = print_num(res$ci.lb),
-      ci_upper = print_num(res$ci.ub)
-    ) %>%
-      # Re-format confidence interval
-      mutate(
-        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
-        .keep = "unused"
-      ) %>%
-      bind_rows()
-  }
-) %>%
-  # Rename parameters for readibility
-  mutate(
-    Parameter = c(
-      "Hedges' $g$"
-    )
-  ) %>%
-  # Replace NAs with blank cells
-  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
-
-# Display the table
-apa_table(
-  tab_freq,
-  align = "llccccc",
-  caption = "Sensitivity/robustness analyses frequentist",
-  font_size = "scriptsize",
-  escape = FALSE
-)
-
-# Save the table
-write_csv(tab_freq, file = here(tables_dir, "robustness_freq.csv"))
-```
-
-```{r, trim_and_fill_gender}
-dat=dat_gender
-
-# random-effects 2 level model
-r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
-
-# run trim and fill
-res_tf <- trimfill(r_mod)
-print(res_tf)
-# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
-
-summ_brm <- list(intercept = res_tf$beta)
-# Compute funnel
-funnel_z_crit <- stats::qnorm(0.975)
-funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
-funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
-funnel <- data.frame(
-  x = c(
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
-  ),
-  y = c(funnel_max_se, 0, 0, funnel_max_se)
-)
-
-# # Create funnel plot
-plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
+plotdata <- as.data.frame(list(yi = res_trim_fill$yi, vi = sqrt(res_trim_fill$vi)))
 ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
@@
 # random-effects 2 level model
-r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)
+res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)
 
@@
 # specifying p value cutpoints of 0.01, 0.05, and 0.10
-sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
+sel_mod <- selmodel(res_freq_2, type = "stepfun", steps = c(0.01, .05, .3, 1), verbose = TRUE)
 print(sel_mod)
@@
   delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
-  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))
+  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00)
+)
 
-sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
-sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
-sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
-sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)
+sel_moderateonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.1, verbose = TRUE)
+sel_severeonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.1, verbose = TRUE)
+sel_moderatetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.2, verbose = TRUE)
+sel_severetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.2, verbose = TRUE)
 
@@
 # interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
-
 ```
@@
   list(
-      r_mod,
-      res_tf,
+    res_freq_2,
+    res_trim_fill,
     sel_mod,

### 2022-05-11 manuscript_files/helper_functions.R

@@ -61,10 +61,10 @@ print_res_table <- function(res,
 
 # Format results of Bayesian meta-regression as a table with optional labels
 print_res_reg_table <- function(res_reg,
-                                label_1,
-                                label_2,
-                                label_col_1,
-                                label_col_2) {
+                                label_1 = NULL,
+                                label_2 = NULL,
+                                label_col_1 = "label_1",
+                                label_col_2 = "label_2") {
   spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
     transmute(
       `Intercept` = b_Intercept,
@@ -86,6 +86,45 @@ print_res_reg_table <- function(res_reg,
     label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
       rename(!!label_col_1 := tmp)
     tab <- cbind(label_1_tab, tab)
+  }
+  return(tab)
+}
+
+# Format results of frequentist meta-analsis as a table with optional labels
+print_res_freq_table <- function(res_freq,
+                                 label_1 = NULL,
+                                 label_2 = NULL,
+                                 label_col_1 = "label_1",
+                                 label_col_2 = "label_2",
+                                 print_sigma2s = TRUE) {
+  tibble(
+    Parameter = rownames(res_freq$b),
+    Estimate = print_num(as.numeric(res_freq$b)),
+    `$SE$` = print_num(res_freq$se),
+    `$z$` = print_num(res_freq$zval),
+    `$p$` = print_num(res_freq$pval, digits = 3),
+    ci_lower = print_num(res_freq$ci.lb),
+    ci_upper = print_num(res_freq$ci.ub)
+  ) %>%
+    mutate(
+      `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
+      .keep = "unused"
+    ) -> tab
+  if (!is.null(label_2)) {
+    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
+      rename(!!label_col_2 := tmp)
+    tab <- cbind(label_2_tab, tab)
+  }
+  if (!is.null(label_1)) {
+    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
+      rename(!!label_col_1 := tmp)
+    tab <- cbind(label_1_tab, tab)
+  }
[…]

### 2022-05-12 supplement.Rmd
Add robustness checks for gender model

@@
 
-```{r, trim_fill_selection}
-# Re-fit frequentist meta-analysis using a two-level model
-res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)
+```{r, trim_fill_selection, include=TRUE}
+# Re-fit the two frequentist meta-analyses using a two-level model
+# This is because `rma.mv()` is not supported for trim-and-fill/selection models
+list(meta = dat, gender = dat_gender) %>%
+  map(function(x) rma.uni(gi, vi, data = x)) -> res_freq_2_lvl
 
-# Run trim-and-fill analysis
-res_trim_fill <- trimfill(res_freq_2)
-print(res_trim_fill)
+# Trim-and-fill analysis
+res_freq_2_lvl %>% map(trimfill) -> res_trim_fill
 
 # Easy weight function selection model (see metafor docs and Lauer et al., 2019)
-res_selection_weights <- selmodel(
-  res_freq_2,
-  type = "stepfun", steps = c(0.01, .05, .3, 1)
-)
-print(res_selection_weights)
+res_freq_2_lvl %>%
+  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 0.30, 1.00)) ->
+res_selection_weights
 
 # More selection models based on four different step functions
+res_freq_2_lvl %>%
+  map(function(res) {
+
+    # Define custom step functions
     tibble(
@@
     ) %>%
-  print() %>%
+      # Fit selection model for every step function
       map(function(delta) {
         selmodel(
-      res_freq_2,
+          res,
           type = "stepfun",
@@
         )
+      })
   }) -> res_selection_steps
-print(res_selection_steps)
-```
 
-```{r, tabs8, include=TRUE}
-# Combine all trim-and-fill and selection models into one table
+# Create seperate tables for the two different meta-analyses (rotation/gender)
+# Each table will contain the results of all trim-and-fill and selection models
+map(names(res_freq_2_lvl), function(name) {
+
+  # Combine two-level, trim-and-fill, and selection models
   tibble(
     res = c(
-    list(res_freq_2, res_trim_fill, res_selection_weights), res_selection_steps
+      list(
+        res_freq_2_lvl[[name]],
+        res_trim_fill[[name]],
+        res_selection_weights[[name]]
+      ),
+      res_selection_steps[[name]]
     ),
@@
   ) %>%
+    # Combine and format as a table
     pmap_dfr(
@@
     select(-Parameter) %>%
-  rename(`Hedges' $g$` = Estimate) -> tab_trim_fill_selection
+    rename(`Hedges' $g$` = Estimate)
+}) %>%
+  set_names(names(res_freq_2_lvl)) -> tabs_trim_fill_selection
 
-# Save the table
+# Save the tables
 write_csv(
-  tab_trim_fill_selection,
-  file = here(tables_dir, "trim_fill_selection.csv")
+  tabs_trim_fill_selection$meta,
+  file = here(tables_dir, "trim_fill_selection_meta.csv")
+)
+write_csv(
+  tabs_trim_fill_selection$gender,
+  file = here(tables_dir, "trim_fill_selection_gender.csv")
 )
 
-# Display the table
+# Display the tables
 apa_table(
-  tab_trim_fill_selection,
+  tabs_trim_fill_selection$meta,
   align = "llccccc",
-  caption = "Trim-and-fill and selection model analyses",
+  caption = "Trim-and-fill and selection models for the meta-analysis of mental rotation performance",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+apa_table(
+  tabs_trim_fill_selection$gender,
+  align = "llccccc",
+  caption = "Trim-and-fill and selection models for the meta-analysis of gender differences",
   font_size = "scriptsize",
@@
 
-```{r, figs4, include=TRUE, fig.width=6, fig.height=3.5, out.width="50%"}
-# Compute new funnel, taking into account the trim-and-fill results
+```{r, figs4, include=TRUE, fig.width=12, fig.height=3.5}
+# Create new funnel plots that take the trim-and-fill results into account
+map2(res_trim_fill, plots_funnel, function(res, plot) {
+
+  # Compute new funnel
   funnel_trim_fill <- with(
@@
       z_crit_05 = stats::qnorm(0.975),
-    max_se = max(sqrt(res_trim_fill$vi)) + 0.05
+      max_se = max(sqrt(res$vi)) + 0.05
     ),
@@
         x = c(
-        res_trim_fill$b - z_crit_05 * sqrt(max_se^2),
-        res_trim_fill$b,
-        res_trim_fill$b + z_crit_05 * sqrt(max_se^2)
+          res$b - z_crit_05 * sqrt(max_se^2),
+          res$b,
+          res$b + z_crit_05 * sqrt(max_se^2)
         ),
@@
 
-# Create new funnel plot, enhanced by the filled in studies
+  # Add new funnel on top of the original funnel plot
   trim_fill_color <- "#e42536"
-plots_funnel[[1]] +
+  plot +
     # Add trim and fill funnel
@@
     ) +
-  geom_vline(xintercept = res_trim_fill$b, color = trim_fill_color) +
+    geom_vline(xintercept = res$b, color = trim_fill_color) +
     # Add filled in studies
     geom_point(
-    data = with(res_trim_fill, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
+      data = with(res, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
       color = trim_fill_color, shape = 0
     )
+}) -> plots_funnel_trim_fill
+
+# Combine plots and legend
+plot_grid(
+  plotlist = plots_funnel_trim_fill, nrow = 1, labels = "auto",
+  label_size = 11, label_fontfamily = "Helvetica"
+) +
+  draw_plot(legend_funnel, x = -0.39, y = 0.355)
 
 # Save the plot
-ggsave(here(figures_dir, "funnel_trim_fill.pdf"), width = 6, height = 3.5)
+ggsave(here(figures_dir, "funnel_trim_fill.pdf"), width = 12, height = 3.5)
 ```
-
-```{r, trim_and_fill_gender}
-dat <- dat_gender
-
-# random-effects 2 level model
-res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)
-
-# run trim and fill
-res_trim_fill <- trimfill(res_freq_2)
-print(res_trim_fill)
-# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"
-
-summ_brm <- list(intercept = res_trim_fill$beta)
-# Compute funnel
-funnel_z_crit <- stats::qnorm(0.975)
-funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
-funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
-funnel <- data.frame(
-  x = c(
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
-    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
-    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
-  ),
-  y = c(funnel_max_se, 0, 0, funnel_max_se)
-)
-
-# # Create funnel plot
-plotdata <- as.data.frame(list(yi = res_trim_fill$yi, vi = sqrt(res_trim_fill$vi)))
-ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
-  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
-  # Meta-analytic effect size
-  geom_vline(xintercept = summ_brm$intercept, color = "black") +
-  # Experiment-specific effect sizes
-  geom_point(shape = 0) +
-  # Funnel
-  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
-  # Styling
-  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
-  scale_y_reverse() +
-  coord_cartesian(
-    xlim = c(-2.5, 2.5),
-    ylim = c(funnel_max_se, 0),
-    expand = FALSE
-  ) +
-  labs(
-    x = expression("Hedges'" ~ italic("g")),
-    y = "Standard error",
-  ) +
-  theme_classic() +
-  theme(
-    axis.line = element_line(colour = "black"),
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    text = element_text(family = "Helvetica", color = "black")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
-```
-
-```{r,selection_models_gender}
-# random-effects 2 level model
-res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)
-
-# EASY WEIGHT_FUNCTION MODEL
-# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model
-# to estimate the population effect size after adjusting for selection bias."
-# specifying p value cutpoints of 0.01, 0.05, and 0.10
-sel_mod <- selmodel(res_freq_2, type = "stepfun", steps = c(0.01, .05, .3, 1), verbose = TRUE)
-print(sel_mod)
-# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')
-
-# 4 DIFFERENT STEP FUNCTION MODELS
-# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that
-# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
-tab <- data.frame(
-  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
-  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
-  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
-  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
-  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00)
-)
-
-sel_moderateonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.1, verbose = TRUE)
-sel_severeonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.1, verbose = TRUE)
-sel_moderatetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.2, verbose = TRUE)
-sel_severetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.2, verbose = TRUE)
-
-print(sel_moderateonetailed)
-print(sel_severeonetailed)
-print(sel_moderatetwotailed)
-print(sel_severetwotailed)
-
-# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
-# print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
-# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
-# print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')
-
-# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
-```
-
-```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
-# Format all frequentist results together as a table
-map2_dfr(
-  c(
-    "Two-level random effects model",
-    "Trim-and-fill",
-    "Selection model: weight-function [0.01, 0.05, 0.3]",
-    "Selection model: moderate one-tailed",
-    "Selection model: severe one-tailed",
-    "Selection model: moderate two-tailed",
-    "Selection model: severe two-tailed"
-  ),
-  list(
-    res_freq_2,
-    res_trim_fill,
-    sel_mod,
-    sel_moderateonetailed,
-    sel_severeonetailed,
-    sel_moderatetwotailed,
-    sel_severetwotailed
-  ),
-  function(name, res) {
-    print(name)
-    # Intercept / regression weights
-    tibble(
-      Model = c(name, rep(NA, length(res$b) - 1)),
-      Parameter = rownames(res$b),
-      Estimate = print_num(as.numeric(res$b)),
-      `$SE$` = print_num(res$se),
-      `$z$` = print_num(res$zval),
-      `$p$` = print_num(res$pval, digits = 3),
-      ci_lower = print_num(res$ci.lb),
-      ci_upper = print_num(res$ci.ub)
-    ) %>%
-      # Re-format confidence interval
-      mutate(
-        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
-        .keep = "unused"
-      ) %>%
-      bind_rows()
-  }
-) %>%
-  # Rename parameters for readibility
-  mutate(
-    Parameter = c(
-      "Hedges' $g$"
-    )
-  ) %>%
-  # Replace NAs with blank cells
-  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
-
-# Display the table
-apa_table(
-  tab_freq,
-  align = "llccccc",
-  caption = "Sensitivity/robustness analyses frequentist",
-  font_size = "scriptsize",
-  escape = FALSE
-)
-
-# Save the table
-write_csv(tab_freq, file = here(tables_dir, "robustness_freq_gender.csv"))
-```

### 2022-05-12 supplement.Rmd
Re-order supplementary tables

@@
 
+```{r, primsa_checklist, include=TRUE}
+# Read the CSV file
+tab_prisma <- read_csv(
+  here(data_dir, "prisma_checklist.csv"),
+  col_types = "cic"
+)
+
+# Display the table
+apa_table(
+  tab_prisma,
+  align = "lcl",
+  caption = "PRISMA 2020 checklist",
+  font_size = "scriptsize"
+)
+```
+
 ```{r, sensitivity_analysis, include=TRUE}
@@
   font_size = "scriptsize", escape = FALSE
+)
+```
+
+```{r, trim_fill_selection, include=TRUE}
+# Re-fit the two frequentist meta-analyses using a two-level model
+# This is because `rma.mv()` is not supported for trim-and-fill/selection models
+list(meta = dat, gender = dat_gender) %>%
+  map(function(x) rma.uni(gi, vi, data = x)) -> res_freq_2_lvl
+
+# Trim-and-fill analysis
+res_freq_2_lvl %>% map(trimfill) -> res_trim_fill
+
+# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
+res_freq_2_lvl %>%
+  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 0.30, 1.00)) ->
+res_selection_weights
+
+# More selection models based on four different step functions
+res_freq_2_lvl %>%
+  map(function(res) {
+
+    # Define custom step functions
+    tibble(
+      delta_one_tailed_moderate = c(
+        1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55,
+        0.50, 0.50, 0.50, 0.50, 0.50, 0.50
+      ),
+      delta_one_tailed_severe = c(
+        1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35,
+        0.30, 0.25, 0.10, 0.10, 0.10, 0.10
+      ),
+      delta_two_tailed_moderate = c(
+        1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60,
+        0.75, 0.80, 0.90, 0.95, 0.99, 1.00
+      ),
+      delta_two_tailed_severe = c(
+        1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25,
+        0.50, 0.60, 0.75, 0.90, 0.99, 1.00
+      )
+    ) %>%
+      # Fit selection model for every step function
+      map(function(delta) {
+        selmodel(
+          res,
+          type = "stepfun",
+          steps = c(
+            0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50,
+            0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1
+          ),
+          delta = delta
+        )
+      })
+  }) -> res_selection_steps
+
+# Create seperate tables for the two different meta-analyses (rotation/gender)
+# Each table will contain the results of all trim-and-fill and selection models
+map(names(res_freq_2_lvl), function(name) {
+
+  # Combine two-level, trim-and-fill, and selection models
+  tibble(
+    res = c(
+      list(
+        res_freq_2_lvl[[name]],
+        res_trim_fill[[name]],
+        res_selection_weights[[name]]
+      ),
+      res_selection_steps[[name]]
+    ),
+    label_1 = c(
+      "Two-level model", "Trim-and-fill model",
+      "Selection models", "", "", "", ""
+    ),
+    label_2 = c(
+      "--", "--", "Weight function [.01, .05, .30]",
+      "One-tailed, moderate bias", "One-tailed, severe bias",
+      "Two-tailed, moderate bias", "Two-tailed, severe bias"
+    )
+  ) %>%
+    # Combine and format as a table
+    pmap_dfr(
+      ~ print_res_freq_table(
+        res_freq = ..1, label_1 = ..2, label_2 = ..3,
+        label_col_1 = "Model", label_col_2 = "Sub-model", print_sigma2s = FALSE
+      )
+    ) %>%
+    select(-Parameter) %>%
+    rename(`Hedges' $g$` = Estimate)
+}) %>%
+  set_names(names(res_freq_2_lvl)) -> tabs_trim_fill_selection
+
+# Save the tables
+write_csv(
+  tabs_trim_fill_selection$meta,
+  file = here(tables_dir, "trim_fill_selection_meta.csv")
+)
+write_csv(
+  tabs_trim_fill_selection$gender,
+  file = here(tables_dir, "trim_fill_selection_gender.csv")
+)
+
+# Display the tables
+apa_table(
+  tabs_trim_fill_selection$meta,
+  align = "llccccc",
+  caption = "Trim-and-fill and selection models for the meta-analysis of mental rotation performance",
+  font_size = "scriptsize",
+  escape = FALSE
+)
+apa_table(
+  tabs_trim_fill_selection$gender,
+  align = "llccccc",
+  caption = "Trim-and-fill and selection models for the meta-analysis of gender differences",
+  font_size = "scriptsize",
+  escape = FALSE
 )
@@
 
-```{r, trim_fill_selection, include=TRUE}
-# Re-fit the two frequentist meta-analyses using a two-level model
-# This is because `rma.mv()` is not supported for trim-and-fill/selection models
-list(meta = dat, gender = dat_gender) %>%
-  map(function(x) rma.uni(gi, vi, data = x)) -> res_freq_2_lvl
-
-# Trim-and-fill analysis
-res_freq_2_lvl %>% map(trimfill) -> res_trim_fill
-
-# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
-res_freq_2_lvl %>%
-  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 0.30, 1.00)) ->
-res_selection_weights
-
-# More selection models based on four different step functions
-res_freq_2_lvl %>%
-  map(function(res) {
-
-    # Define custom step functions
-    tibble(
-      delta_one_tailed_moderate = c(
-        1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55,
-        0.50, 0.50, 0.50, 0.50, 0.50, 0.50
-      ),
-      delta_one_tailed_severe = c(
-        1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35,
-        0.30, 0.25, 0.10, 0.10, 0.10, 0.10
-      ),
-      delta_two_tailed_moderate = c(
-        1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60,
-        0.75, 0.80, 0.90, 0.95, 0.99, 1.00
-      ),
-      delta_two_tailed_severe = c(
-        1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25,
-        0.50, 0.60, 0.75, 0.90, 0.99, 1.00
-      )
-    ) %>%
-      # Fit selection model for every step function
-      map(function(delta) {
-        selmodel(
-          res,
-          type = "stepfun",
-          steps = c(
-            0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50,
-            0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1
-          ),
-          delta = delta
-        )
-      })
-  }) -> res_selection_steps
-
-# Create seperate tables for the two different meta-analyses (rotation/gender)
-# Each table will contain the results of all trim-and-fill and selection models
-map(names(res_freq_2_lvl), function(name) {
-
-  # Combine two-level, trim-and-fill, and selection models
-  tibble(
-    res = c(
-      list(
-        res_freq_2_lvl[[name]],
-        res_trim_fill[[name]],
-        res_selection_weights[[name]]
-      ),
-      res_selection_steps[[name]]
-    ),
-    label_1 = c(
-      "Two-level model", "Trim-and-fill model",
-      "Selection models:", "", "", "", ""
-    ),
-    label_2 = c(
-      "", "", "Weight function [.01, .05, .30]",
-      "One-tailed, moderate bias", "One-tailed, severe bias",
-      "Two-tailed, moderate bias", "Two-tailed, severe bias"
-    )
-  ) %>%
-    # Combine and format as a table
-    pmap_dfr(
-      ~ print_res_freq_table(
-        res_freq = ..1, label_1 = ..2, label_2 = ..3,
-        label_col_1 = "Model", label_col_2 = " ", print_sigma2s = FALSE
-      )
-    ) %>%
-    select(-Parameter) %>%
-    rename(`Hedges' $g$` = Estimate)
-}) %>%
-  set_names(names(res_freq_2_lvl)) -> tabs_trim_fill_selection
-
-# Save the tables
-write_csv(
-  tabs_trim_fill_selection$meta,
-  file = here(tables_dir, "trim_fill_selection_meta.csv")
-)
-write_csv(
-  tabs_trim_fill_selection$gender,
-  file = here(tables_dir, "trim_fill_selection_gender.csv")
-)
-
-# Display the tables
-apa_table(
-  tabs_trim_fill_selection$meta,
-  align = "llccccc",
-  caption = "Trim-and-fill and selection models for the meta-analysis of mental rotation performance",
-  font_size = "scriptsize",
-  escape = FALSE
-)
-apa_table(
-  tabs_trim_fill_selection$gender,
-  align = "llccccc",
-  caption = "Trim-and-fill and selection models for the meta-analysis of gender differences",
-  font_size = "scriptsize",
-  escape = FALSE
-)
-```
-
-```{r, figs4, include=TRUE, fig.width=12, fig.height=3.5}
+```{r, figs4, include=TRUE, fig.width=12, fig.height=3.5, fig.cap="(ref:figs4-caption)"}
 # Create new funnel plots that take the trim-and-fill results into account
@@
 ```
+
+(ref:figs4-caption) **Trim-and-fill analyses.** As in Figure 3 in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance **(a)** and in the meta-analysis of gender differences within each article **(b)**.
+The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines).
+Gray shades indicate 95% pseudo-confidence intervals (dark gray) and 99% pseudo-confidence intervals (light gray) under the null hypothesis.
+Red squares show (fictional) experiments that were imputed via the trim-and-fill analyses, compensating for the small publication bias observed in the original funnel plots.
+Red lines show the meta-analytic effect sizes and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analyses.

### 2022-05-12 supplement.Rmd
Small tweaks to the supplementary tables, funnel

@@
 Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published.
-We ran one selection model assuming a weight function with fixed p-value cutoffs at p = .01, p = .05, and p = 0.3[@vevea1995], as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005].
+We ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30, as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005].
 These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).
@@
     Experiment = group_long,
-    `Sample size` = sample_size,
-    `Females` = round(female_percent * sample_size),
+    `Sample size` = as.integer(sample_size),
+    `Females` = as.integer(round(female_percent * sample_size)),
     Age = str_c(age_mean, "±", age_sd, sep = " "),
@@
 
-```{r, jackknife, include=TRUE}
+```{r, jackknife}
 # Re-run the jackknife analysis only if requested
@@
     )
-  }) -> tab_jackknife
+  }) %>%
+    # Show article labels only for the first experiment per article
+    mutate(
+      Article = if_else(Article == lag(Article, default = ""), "", Article),
+    ) -> tab_jackknife
 
@@
   write_csv(tab_jackknife, file = here(tables_dir, "jackknife.csv"))
-} else {
+}
+```
 
-  # Otherwise we load the pre-computed results
+```{r, tabs3, include=TRUE}
+# Read jackknife table from file
 tab_jackknife <- read_csv(
@@
 )
-}
 
@@
 
-```{r, primsa_checklist, include=TRUE}
-# Read the CSV file
+```{r, tabs4, include=TRUE}
+# Read PRISMA checklist from file
 tab_prisma <- read_csv(
   here(data_dir, "prisma_checklist.csv"),
-  col_types = "cic"
+  col_types = "ccc"
 )
@@
 
-```{r, sensitivity_analysis, include=TRUE}
+```{r, sensitivity_analysis}
 # Re-run the sensitivity analyses only if requested
@@
   write_csv(tab_sens_gender, file = here(tables_dir, "sens_gender.csv"))
-} else {
+}
+```
 
-  # Otherwise we load the pre-computed results
+```{r, tabs5, include=TRUE}
+# Load sensitivity analysis table from file
 tab_sens <- read_csv(
@@
 )
-  tab_sens_reg <- read_csv(
-    here(tables_dir, "sens_reg.csv"),
-    col_types = "c", na = character(), trim_ws = FALSE
-  )
-  tab_sens_gender <- read_csv(
-    here(tables_dir, "sens_gender.csv"),
-    col_types = "c", na = character(), trim_ws = FALSE
-  )
-}
 
-# Display the tables
+# Display the table
 apa_table(
@@
 )
+```
+
+```{r, tabs6, include=TRUE}
+# Load sensitivity analysis table from file
+tab_sens_reg <- read_csv(
+  here(tables_dir, "sens_reg.csv"),
+  col_types = "c", na = character(), trim_ws = FALSE
+)
+
+# Display the table
 apa_table(
@@
 )
+```
+
+```{r, tabs7, include=TRUE}
+# Load sensitivity analysis table from file
+tab_sens_gender <- read_csv(
+  here(tables_dir, "sens_gender.csv"),
+  col_types = "c", na = character(), trim_ws = FALSE
+)
+
+# Display the table
 apa_table(
@@
         res_freq = ..1, label_1 = ..2, label_2 = ..3,
-        label_col_1 = "Model", label_col_2 = "Sub-model", print_sigma2s = FALSE
+        label_col_1 = "Model", label_col_2 = "Sub-model",
+        print_sigma2s = FALSE
       )
@@
 )
+```
 
-# Display the tables
+```{r, tabs8, include=TRUE}
+# Display the table
 apa_table(
@@
 )
+```
+
+```{r, tabs9, include=TRUE}
+# Display the table
 apa_table(
@@
   # Add new funnel on top of the original funnel plot
-  trim_fill_color <- "#e42536"
+  trim_fill_color <- ifelse(sum(res$fill) >= 1, "#e42536", NA)
   plot +
@@
 Red lines show the meta-analytic effect sizes and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analyses.
+Note that for the meta-analysis of gender differences, the trim-and-fill analysis suggested that no additional experiments had to be imputed.

### 2022-05-12 manuscript_files/helper_functions.R

@@ -102,7 +102,7 @@ print_res_freq_table <- function(res_freq,
     Estimate = print_num(as.numeric(res_freq$b)),
     `$SE$` = print_num(res_freq$se),
     `$z$` = print_num(res_freq$zval),
-    `$p$` = print_num(res_freq$pval, digits = 3),
+    `$p$` = papaja::print_p(res_freq$pval),
     ci_lower = print_num(res_freq$ci.lb),
     ci_upper = print_num(res_freq$ci.ub)
   ) %>%

### 2022-05-12 manuscript.Rmd
Prettify main (within) selection models
Add OSF link

@@
 
-  The data and code for this study are openly available at ???.
   We have no conflict of interest to disclose.
@@
 To this end, we adapted code from the bootstrap R package (Version `r packageVersion("bootstrap")`) [@kostyshak2019].
-Specifically, we refitted the Bayesian three-level models repeatedly while leaving out a different one of the original experiments on every iteration.
+Specifically, we refitted the Bayesian three-level model repeatedly while leaving out a different one of the original experiments on every iteration.
 To take into account the variance inherent in Bayesian model estimation, we averaged over $x$ iterations of the jackknife.
 
+We also ran trim-and-fill analyses and selection models to confirm the robustness of the results from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables 8 and 9) [@duval2000; @vevea1995; @vevea2005].
+
 ## Data availability
 
-The data is available via (OSF link here).
+The data for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8.
+Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.
 
@@
 
-The code is available via (OSF link here).
+The code for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8.
+Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.
 

### 2022-05-12 manuscript.Rmd
Add Egger test for gender differences

@@
 ```{r, publication_bias, echo=TRUE}
-# Classical Egger regression test
-(egger <- regtest(x = dat$gi, sei = dat$sei, model = "lm", predictor = "sei"))
+# Classical Egger regression test for the meta-analysis of rotation performance
+(egger <- with(
+  dat, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
+))
 (egger_ci <- confint(egger$fit)["Xsei", ])
+
+# Classical Egger regression test for the meta-analysis of gender_differences
+(egger_gender <- with(
+  dat_gender, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
+))
+(egger_ci_gender <- confint(egger_gender$fit)["Xsei", ])
 ```
 
-By visual inspection of a funnel plot of standard errors and effect sizes we detected a slight asymmetry indicating a small publication bias (Fig.
+We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature that we had meta-analyzed.
+For the meta-analysis of mental rotation performance, we observed a slight assymetry in the funnel plot, indicating a small publication bias (Fig.
 3).
-Publication bias was also suggested by the results of an Egger regression test indicating that the slope of a weighted linear regression of the effect sizes on the standard errors is significantly different from zero in a two-sided $t$-test, $b = `r coef(egger$fit)["Xsei"]`$, $t(`r egger$dfs`) = `r egger$zval`$, $p = `r print_p(egger$pval)`$, 95% confidence interval (CI) [`r egger_ci["2.5 %"]`, `r egger_ci["97.5 %"]`].
-Nevertheless, a jackknife leave-one-out analysis confirmed that the current results are robust to the effects of individual studies (Supplementary Table 3).
+This was confirmed by an Egger regression test that showed a reliable association between experiments' effect sizes and their corresponding standard errors, $b = `r coef(egger$fit)["Xsei"]`$, $t(`r egger$dfs`) = `r egger$zval`$, $p = `r print_p(egger$pval)`$, 95% confidence interval (CI) [`r egger_ci["2.5 %"]`, `r egger_ci["97.5 %"]`] (two-sided test).
+Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table 3).
+For the meta-analysis of gender differences in mental rotation performance, the assymetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
 
-(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance **(a)** and for the meta-analysis of gender differences within each article **(b)**.
+(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance **(a)** and for the meta-analysis of gender differences in mental rotation performance **(b)**.
 The plots show the standard error and effect size for each of the individual experiments as a black square.
@@
 These shades thus illustrate which of the original studies observed a significant effect.
-A slight asymmetry induced by the underrepresentation of studies with high standard errors and small effect sizes suggests a small publication bias.
+For the meta-analysis of mental rotation performance, a slight asymmetry induced by the underrepresentation of studies with high standard errors and small effect sizes suggests a small publication bias.
 

### 2022-05-12 manuscript.Rmd
Add citation for data and code

@@
 
-The data for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8.
+The data for this study is available via the [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
 Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.
@@
 
-The code for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8.
+The data for this study is available via the [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
 Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.

### 2022-05-12 manuscript.Rmd
Small fixes to the text

@@
 keywords          : "mental rotation, spatial cognition, spatial ability, infants, children, gender, meta-analysis"
-wordcount         : "X"
 
@@
 (ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
-White squares depict the effect sizes (Hedges’ $g$) for infants’ mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
+White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
 Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI).
@@
 
-For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects.
+For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects.
 Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
@@
 
-(ref:fig2-caption) **Effects of gender, age, and task.** **a,** Squares show the effect size (Hedges’ g) for infants’ mental rotation performance in each of the 59 individual experiments.
+(ref:fig2-caption) **Effects of gender, age, and task.** **a,** Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments.
 Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
@@
 We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature that we had meta-analyzed.
-For the meta-analysis of mental rotation performance, we observed a slight assymetry in the funnel plot, indicating a small publication bias (Fig.
+For the meta-analysis of mental rotation performance, we observed a slight asymmetry in the funnel plot, indicating a small publication bias (Fig.
 3).
@@
 Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table 3).
-For the meta-analysis of gender differences in mental rotation performance, the assymetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+For the meta-analysis of gender differences in mental rotation performance, the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
 Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
-Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen’s weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]).
+Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen's weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]).
 Interrater agreement for the specific eligibility criteria were `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]).
@@
 We also conducted a meta-analysis of the gender differences in mental rotation performance observed within the original articles.
-For this analysis, the outcome measures were any summary statistic (Table 2) that could be used to determine the standardized mean difference between male infants’ mental rotation performance and female infants’ mental rotation performance.
+For this analysis, the outcome measures were any summary statistic (Table 2) that could be used to determine the standardized mean difference between male infants' mental rotation performance and female infants' mental rotation performance.
 Other extracted variables included the sample size, the mean age and its standard deviation, and the minimum and maximum age of each gender group.
@@
 
-For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges’ $g$) using the formulas provided in Table 1.
+For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Table 1.
 The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Table 1.
@@
 
-For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between non-redundant male and female groups of infants was converted into a standardized mean difference with small sample correction (Hedges’ $g$) using the formulas provided in Table 2.
-The standard error of Hedges’ $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$), and $J(df)$ is the correction factor for small samples as described in Row (1) of Table 2.
+For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between non-redundant male and female groups of infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Table 2.
+The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$), and $J(df)$ is the correction factor for small samples as described in Row (1) of Table 2.
 
@@
 A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 5).
-For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges’ g) between the novel and familiar rotation condition, weighted by its standard error (see Effect size measures above).
-For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges’ g) between male infants’ mental rotation performance and female infants’ mental rotation performance, weighted by its standard error.
+For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect size measures above).
+For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges' $g$) between male infants' mental rotation performance and female infants' mental rotation performance, weighted by its standard error.
 All Bayesian models were fitted using the brms package (Version `r packageVersion("brms")`) [@burkner2017; @burkner2018] in R (Version `r packageVersion("base")`) [@rcoreteam2021] and the Stan language (Version `r packageVersion("rstan")`) [@standevelopmentteam2022].

### 2022-05-12 manuscript.Rmd

@@
   - \renewcommand{\arraystretch}{0.6}
-  - \DeclareCaptionLabelSeparator{bar}{ | }
   - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
-  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
-  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
+  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=colon,textfont=bf,textformat=tabletext}
+  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=colon,name=Fig.,textfont=normalfont}
 ---
@@
 
-(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance **(a)** and for the meta-analysis of gender differences in mental rotation performance **(b)**.
+(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance (**a**) and for the meta-analysis of gender differences in mental rotation performance (**b**).
 The plots show the standard error and effect size for each of the individual experiments as a black square.

### 2022-05-12 supplement.Rmd

@@
 
-(ref:figs4-caption) **Trim-and-fill analyses.** As in Figure 3 in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance **(a)** and in the meta-analysis of gender differences within each article **(b)**.
+(ref:figs4-caption) **Trim-and-fill analyses.** As in Figure 3 in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
 The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines).

### 2022-05-12 supplement.Rmd

@@
 
-## Supplementary Methods 1 | Correlation between dependent samples
+## Supplementary Methods 1: Correlation between dependent samples
 
@@
 
-## Supplementary Methods 2 | Bias correction and sensitivity analysis for frequentist results
+## Supplementary Methods 2: Bias correction and sensitivity analysis for frequentist results
 

### 2022-05-13 manuscript.Rmd
Correct typos

@@
     d_z_diff = mean_diff / sd_diff,
-    # Add d_av from mean difference and standard devations
+    # Add d_av from mean difference and standard deviations
     # See http://dx.doi.org/10.20982/tqmp.14.4.p242
@@
 
-    # Recode task type as a categorical (factor) variale for meta-regression
+    # Recode task type as a categorical (factor) variable for meta-regression
     task = factor(task, levels = c("Habituation", "VoE")),
@@
 | (5\) Mean looking time and ${SD}$ per condition [@cumming2012] | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
-|                                                                | $d=\frac{m_\text{movel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
+|                                                                | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
@@
 
+\bigskip
+
 <div id="refs"></div>

### 2022-05-13 supplement.Rmd
Correct typos

@@
 ) %>%
-  # Rename parameters for readibility
+  # Rename parameters for readability
   mutate(
@@
 
-# Create seperate tables for the two different meta-analyses (rotation/gender)
+# Create separate tables for the two different meta-analyses (rotation/gender)
 # Each table will contain the results of all trim-and-fill and selection models

### 2022-05-13 manuscript.Rmd
Incorporate feedback

@@
   - id            : "1"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, 04103 Leipzig"
   - id            : "2"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin"
   - id            : "*"
@@
   \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
+
+  \addORCIDlink{Anne-Sophie Kieslinger}{https://orcid.org/0000-0001-9240-4077}
 
@@
   - \usepackage{setspace}
-  - \renewcommand{\arraystretch}{0.6}
+  - \renewcommand{\arraystretch}{0.59}
   - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
@@
 Effect sizes were assumed to be small.
+
+\newpage
 
@@
 
+## Eligibility criteria
+
+Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection process and items below).
+We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
+
 ```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", out.width="50%"}
@@
 Finally, we excluded an article that was based on a sample of infants  who were substantially older compared to all other articles (1 article).
-
-## Eligibility criteria
-
-Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection process and items below).
-We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
 
@@
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| (2\) $t$-statistic and group sizes     | $d=t\sqrt\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}$;\quad then (1)                       |
+| (2\) $t$-statistic and group sizes     | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
 | [@lakens2013]                          |                                                                                                  |

### 2022-05-13 supplement.Rmd
Incorporate feedback

@@
 This correlation between repeated measures unfortunately tends to go unreported in research articles.
-In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants’ looking times in the novel and familiar rotation object conditions.
+In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.
 
@@
   tab_freq,
-  align = "llccccc",
   caption = "Frequentist meta-analyses and meta-regression",
   font_size = "scriptsize",
-  escape = FALSE
+  escape = FALSE,
+  align = "llrrrrr",
 )
@@
   tab_jackknife,
-  align = "llcccc",
-  caption = "Jackknife (leave-one-out) analysis",
-  font_size = "scriptsize", landscape = TRUE, escape = FALSE
+  caption = "Jackknife (leave-one-out) analysis", font_size = "scriptsize",
+  landscape = TRUE, escape = FALSE, align = "llrrrr"
 )
@@
   tab_prisma,
-  align = "lcl",
   caption = "PRISMA 2020 checklist",
-  font_size = "scriptsize"
+  font_size = "scriptsize",
+  align = "lrl",
 )
@@
         tibble(
-          manipulation_value = str_c("$r = ", print_num(ri_sens), "$"),
+          manipulation_value = str_c("$r$ = ", print_num(ri_sens)),
           res = list(res),
@@
   caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
-  font_size = "scriptsize", escape = FALSE
+  font_size = "scriptsize", escape = FALSE, align = "llrrrr"
 )
@@
   caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
-  font_size = "scriptsize", landscape = TRUE, escape = FALSE
+  font_size = "scriptsize", landscape = TRUE, escape = FALSE,
+  align = "llrrrrrrr"
 )
@@
   caption = "Sensitivity analyses for the meta-analysis of gender differences",
-  font_size = "scriptsize", escape = FALSE
+  font_size = "scriptsize", escape = FALSE, align = "llrrrrrrr"
 )
@@
   tabs_trim_fill_selection$meta,
-  align = "llccccc",
-  caption = "Trim-and-fill and selection models for the meta-analysis of mental rotation performance",
-  font_size = "scriptsize",
-  escape = FALSE
+  caption = "Publication bias correction for the meta-analysis of mental rotation performance",
+  font_size = "scriptsize", escape = FALSE, align = "llrrrrr"
 )
@@
   tabs_trim_fill_selection$gender,
-  align = "llccccc",
-  caption = "Trim-and-fill and selection models for the meta-analysis of gender differences",
-  font_size = "scriptsize",
-  escape = FALSE
+  caption = "Publication bias correction for the meta-analysis of gender differences",
+  font_size = "scriptsize", escape = FALSE, align = "llrrrrr",
 )
@@
 (ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants.
-White squares indicate the effect sizes (Hedges’ $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals.
+White squares indicate the effect sizes (Hedges' $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals.
 Note that for experiments that observed a non-significant gender difference and did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
@@
     conv_stats,
-    y = 0.45, x = -0.042 * n_draws, color = "black", parse = TRUE, angle = 90
+    y = 0.45, x = -0.042 * n_draws, color = "black", parse = TRUE,
+    vjust = 1, angle = 90
   ) +
@@
     strip.background = element_blank(),
+    strip.text = element_text(family = "Helvetica", color = "black", size = 12),
     text = element_text(family = "Helvetica", color = "black")
@@
 
-(ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Profile likelihood plots [@raue2009; @viechtbauer2010] indicate that restricted maximum likelihood estimation (REML) was able to identify the most likely parameter estimates for the two variance components in the three-level meta-analytic model, that is, for the between-article variance and for the between-experiment (within-article) variance.
+(ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Black curves show the profile of the restricted log likelihood for the two variance components in the frequentist three-level model.
+The two peaks indicate that restricted maximum likelihood estimation (REML) was able to converge on the most likely parameter estimates [@raue2009; @viechtbauer2010].
 

### 2022-05-13 manuscript_files/helper_functions.R

@@ -90,7 +90,7 @@ print_res_reg_table <- function(res_reg,
   return(tab)
 }
 
-# Format results of frequentist meta-analsis as a table with optional labels
+# Format results of frequentist meta-analysis as a table with optional labels
 print_res_freq_table <- function(res_freq,
                                  label_1 = NULL,
                                  label_2 = NULL,
@@ -102,7 +102,9 @@ print_res_freq_table <- function(res_freq,
     Estimate = print_num(as.numeric(res_freq$b)),
     `$SE$` = print_num(res_freq$se),
     `$z$` = print_num(res_freq$zval),
-    `$p$` = papaja::print_p(res_freq$pval),
+    `$p$` = ifelse(
+      res_freq$pval < 0.001, "< 0.001", print_num(res_freq$pval, digits = 3)
+      ),
     ci_lower = print_num(res_freq$ci.lb),
     ci_upper = print_num(res_freq$ci.ub)
   ) %>%

### 2022-05-13 manuscript.Rmd
Revert colons in captions to bars

@@
   - \renewcommand{\arraystretch}{0.59}
+  - \DeclareCaptionLabelSeparator{bar}{ | }
   - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
-  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=colon,textfont=bf,textformat=tabletext}
-  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=colon,name=Fig.,textfont=normalfont}
+  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
+  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
 ---

### 2022-05-13 supplement.Rmd
Revert colons in captions to bars

@@
 
-## Supplementary Methods 1: Correlation between dependent samples
+## Supplementary Methods 1 | Correlation between dependent samples
 
@@
 
-## Supplementary Methods 2: Bias correction and sensitivity analysis for frequentist results
+## Supplementary Methods 2 | Bias correction and sensitivity analysis for frequentist results
 

### 2022-05-13 manuscript.Rmd
Incorporate changes from Drive

--- 2022-05-13 manuscript.Rmd
@@
     d_z_diff = mean_diff / sd_diff,
-    # Add d_av from mean difference and standard deviations
+    # Add d_av from mean difference and standard devations
     # See http://dx.doi.org/10.20982/tqmp.14.4.p242
@@
 
-    # Recode task type as a categorical (factor) variable for meta-regression
+    # Recode task type as a categorical (factor) variale for meta-regression
     task = factor(task, levels = c("Habituation", "VoE")),
@@
 
-Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average significantly longer in male compared to female infants.
+Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average longer in male compared to female infants.
 Effect sizes were assumed to be small.
@@
 
-We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature that we had meta-analyzed.
-For the meta-analysis of mental rotation performance, we observed a slight asymmetry in the funnel plot, indicating a small publication bias (Fig.
-3).
-This was confirmed by an Egger regression test that showed a reliable association between experiments' effect sizes and their corresponding standard errors, $b = `r coef(egger$fit)["Xsei"]`$, $t(`r egger$dfs`) = `r egger$zval`$, $p = `r print_p(egger$pval)`$, 95% confidence interval (CI) [`r egger_ci["2.5 %"]`, `r egger_ci["97.5 %"]`] (two-sided test).
+We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here.
+For the meta-analysis of mental rotation performance (Fig.
+3a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
+This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger$fit)["Xsei"]`$, $t(`r egger$dfs`) = `r egger$zval`$, $p = `r print_p(egger$pval)`$, 95% confidence interval (CI) [`r egger_ci["2.5 %"]`, `r egger_ci["97.5 %"]`] (two-sided test).
 Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table 3).
-For the meta-analysis of gender differences in mental rotation performance, the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+For the meta-analysis of gender differences in mental rotation performance (Fig.
+3a), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
 
-The present study robustly revealed that male infants look slightly but significantly longer at novel rotated objects than female infants.
-Thus, on average, males outperform females in mental rotation already in the first months of life.
+The present study robustly revealed that male infants look longer at novel rotated objects than female infants.
+Thus, on average, males show more reliable mental rotation behavior already in the first months of life.
 
@@
 **c,** Redundant articles comprising the same experiment(s) were excluded.
-aAdditionally, we excluded an article that was based on an uncommon experimental paradigm differing substantially from all other articles (1 article).
+Additionally, we excluded an article that was based on an uncommon experimental paradigm differing substantially from all other articles (1 article).
 Finally, we excluded an article that was based on a sample of infants  who were substantially older compared to all other articles (1 article).
@@
 
-To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false-positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993].
+To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993].
 To this end, we adapted code from the bootstrap R package (Version `r packageVersion("bootstrap")`) [@kostyshak2019].
-Specifically, we refitted the Bayesian three-level model repeatedly while leaving out a different one of the original experiments on every iteration.
+Specifically, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.
 To take into account the variance inherent in Bayesian model estimation, we averaged over $x$ iterations of the jackknife.
 
-We also ran trim-and-fill analyses and selection models to confirm the robustness of the results from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables 8 and 9) [@duval2000; @vevea1995; @vevea2005].
+We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables 8 and 9; Supplementary Figure 4) [@duval2000; @vevea1995; @vevea2005].
 
@@
 
-The data for this study is available via the [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
-Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.
+The data for this study is available  from an   [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) repository [@enge2022a].
+This link is intended for peer review only and will be replaced with a public link upon acceptance.
 
@@
 
-The data for this study is available via the [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
-Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.
+The data for this study is available from an  [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) repository [@enge2022a].
+This link is intended for peer review only and will be replaced with a public link upon acceptance.
 

### 2022-05-13 supplement.Rmd
Incorporate changes from Drive

--- 2022-05-13 supplement.Rmd
@@
 Meta-analytic methods require an estimate of the sampling variance of each included experiment [@harrer2021].
-For within-participant experimental designs (i.e., repeated measures on the same individuals in different conditions), this sampling variance needs to reflect that repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants, thus not providing independent information.
-This is reflected by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018].
-This correlation between repeated measures unfortunately tends to go unreported in research articles.
-In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants’ looking times in the novel and familiar rotation object conditions.
+For within-participant experimental designs, this sampling variance needs to account for the fact that repeated measures are taken from the same individuals in different conditions.
+Repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants and thus do not provide independent information.
+This is accounted for by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018].
+However, the correlation between repeated measures tends to go unreported in research articles.
+In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.
 
@@
 1.
-Extract an effect size $d_\text{diff}$ based on a paired $t$-test, a one-sample $t$-test of difference scores, or an ANOVA (see Rows (1) to (4) in Table 1).
+Extract an effect size $d_\text{diff}$ based on a paired $t$-test, a one-sample $t$-test of difference scores, or an analysis of variance (ANOVA) (see Rows (1) to (4) in Table 1).
 All three of these tests take the correlation between the repeated measures into account.
@@
 
-3. Compute the standard deviation of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
+3. Compute the standard deviation ($SD$) of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
 
-4. Extract the standard deviations ${SD}_\text{novel}$ and ${SD}_\text{familiar}$ of looking times within each of the two conditions.
+4. Extract the standard deviation of looking times for the novel condition ${SD}_\text{novel}$ and the familiar condition ${SD}_\text{familiar}$.
 
 5.
-Compute the observed correlation between conditions based on rearranging an equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
+Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
 
 Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]).
-However, we decided to assume a correlation of $r  = .50$ when computing ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments.
+However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments.
 This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
-We ran a sensitivity analysis to test the robustness of our Bayesian meta-analytic model against this assumption (Supplementary Table 4).
+To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Table 4).
 
-## Supplementary Methods 2: Bias correction and sensitivity analysis for frequentist results
+## Supplementary Methods 2: Publication bias correction for frequentist results
 
-We used a simplified two-level version (i.e., dropping the article level) of our frequentist three-level model to further correct our results for publication bias.
-We conducted a trim-and-fill analysis [@duval2000] to impute possible effect sizes of non-published experiments and then observed their influence on the meta-analytic effect size (Supplementary Tables 8 and 9).
+We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias.
+For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis.
+In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments.
+This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables 8 and 9).
 
-Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published.
-We ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30, as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005].
-These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).
+In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis.
+These models were based on the assumption that experiments yielding significant effects (i.e., small *p*-values) are more likely to get published.
+Specifically, we ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30.
+Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
+These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables 8 and 9).
 
@@
 ) %>%
-  # Rename parameters for readability
+  # Rename parameters for readibility
   mutate(
@@
 
-# Create separate tables for the two different meta-analyses (rotation/gender)
+# Create seperate tables for the two different meta-analyses (rotation/gender)
 # Each table will contain the results of all trim-and-fill and selection models
@@
 (ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants.
-White squares indicate the effect sizes (Hedges’ $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals.
-Note that for experiments that observed a non-significant gender difference and did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
-Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
-Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
-The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
+White squares indicate the effect sizes (Hedges' $g$) of gender differences in all individual experiments and black lines indicate their 95% confidence intervals.
+For experiments resulting in a non-significant gender difference and for which the authors did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
+Gray bars depict the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
+These intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
+The bold line at the bottom of the figure shows the meta-analytic effect size obtained from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
 
@@
 Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution.
-$R\text{hat}$ = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
-For details about these and other convergence criteria, we refer the reader to @vehtari2021.
+$R_\text{hat}$ = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
+Details about these convergence criteria can be found in @vehtari2021.
 
@@
 Gray shades indicate 95% pseudo-confidence intervals (dark gray) and 99% pseudo-confidence intervals (light gray) under the null hypothesis.
-Red squares show (fictional) experiments that were imputed via the trim-and-fill analyses, compensating for the small publication bias observed in the original funnel plots.
-Red lines show the meta-analytic effect sizes and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analyses.
-Note that for the meta-analysis of gender differences, the trim-and-fill analysis suggested that no additional experiments had to be imputed.
+Red squares show fictional experiments that were imputed using the trim-and-fill method  to compensate for the small publication bias observed in the original funnel plots.
+Red lines depict the meta-analytic effect size and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analysis of mental rotation performance.
+For the meta-analysis of gender differences, the results of the trim-and-fill analysis suggested that no additional experiments had to be imputed to compensate for publication bias.

### 2022-05-13 supplement.Rmd

--- 2022-05-13 supplement.Rmd
@@
 Meta-analytic methods require an estimate of the sampling variance of each included experiment [@harrer2021].
-For within-participant experimental designs (i.e., repeated measures on the same individuals in different conditions), this sampling variance needs to reflect that repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants, thus not providing independent information.
-This is reflected by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018].
-This correlation between repeated measures unfortunately tends to go unreported in research articles.
+For within-participant experimental designs, this sampling variance needs to account for the fact that repeated measures are taken from the same individuals in different conditions.
+Repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants and thus do not provide independent information.
+This is accounted for by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018].
+However, the correlation between repeated measures tends to go unreported in research articles.
 In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.
@@
 
-3. Compute the standard deviation of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
+3. Compute the standard deviation ($SD$) of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
 
-4. Extract the standard deviations ${SD}_\text{novel}$ and ${SD}_\text{familiar}$ of looking times within each of the two conditions.
+4. Extract the standard deviation of looking times for the novel condition ${SD}_\text{novel}$ and the familiar condition ${SD}_\text{familiar}$.
 
 5.
-Compute the observed correlation between conditions based on rearranging an equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
+Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
 
 Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]).
-However, we decided to assume a correlation of $r  = .50$ when computing ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments.
+However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments.
 This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
-We ran a sensitivity analysis to test the robustness of our Bayesian meta-analytic model against this assumption (Supplementary Table 4).
+To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Table 4).
 
@@
 
-We used a simplified two-level version (i.e., dropping the article level) of our frequentist three-level model to further correct our results for publication bias.
-We conducted a trim-and-fill analysis [@duval2000] to impute possible effect sizes of non-published experiments and then observed their influence on the meta-analytic effect size (Supplementary Tables 8 and 9).
+We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias.
+For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis.
+In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments.
+This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables 8 and 9).
 
-Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published.
-We ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30, as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005].
-These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).
+In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis.
+These models were based on the assumption that experiments yielding significant effects (i.e., small *p*-values) are more likely to get published.
+Specifically, we ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30.
+Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
+These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables 8 and 9).
 
@@
 (ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants.
-White squares indicate the effect sizes (Hedges' $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals.
-Note that for experiments that observed a non-significant gender difference and did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
-Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
-Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
-The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
+White squares indicate the effect sizes (Hedges' $g$) of gender differences in all individual experiments and black lines indicate their 95% confidence intervals.
+For experiments resulting in a non-significant gender difference and for which the authors did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
+Gray bars depict the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
+These intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
+The bold line at the bottom of the figure shows the meta-analytic effect size obtained from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
 

### 2022-05-13 manuscript.Rmd
Remove shared first authorship

@@
   - name          : "Alexander Enge"
-    affiliation   : "1,2,*"
+    affiliation   : "1,2"
     corresponding : "yes"
@@
   - name          : "Shreya Kapoor"
-    affiliation   : "1,*"
+    affiliation   : "1"
   - name          : "Anne-Sophie Kieslinger"
-    affiliation   : "1,*"
+    affiliation   : "1"
   - name          : "Michael A. Skeide"
@@
     institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin"
-  - id            : "*"
-    institution   : "These authors contributed equally"
 

### 2022-05-13 manuscript.Rmd
Fine-tune tables

@@
 
-  \addORCIDlink{Anne-Sophie Kieslinger}{https://orcid.org/0000-0001-9240-4077}
+  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
 
@@
   - \usepackage{setspace}
-  - \renewcommand{\arraystretch}{0.59}
   - \DeclareCaptionLabelSeparator{bar}{ | }
@@
 Effect sizes were assumed to be small.
-
-\newpage
-
-# Results
-
-## Mental rotation performance
 
@@
 
+\newpage
+
+# Results
+
+## Mental rotation performance
+
 (ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
@@
 
+\newpage
+\renewcommand{\arraystretch}{2}
+\singlespacing
 \scriptsize
@@
 
+\doublespacing
 \normalsize
@@
 
+\singlespacing
 \scriptsize
@@
 
-## Effect size measures
+## Effect measures
 
@@
 A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 5).
-For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect size measures above).
+For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect measures above).
 For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges' $g$) between male infants' mental rotation performance and female infants' mental rotation performance, weighted by its standard error.
@@
 \newpage
+\nolinenumbers
 
@@
 \newpage
+\linenumbers
 

### 2022-05-13 supplement.Rmd
Fine-tune tables

@@
 
+\singlespacing
+\renewcommand{\arraystretch}{0.97}
+
 ```{r, tabs1, include=TRUE}
@@
     `Sample size` = as.integer(sample_size),
-    `Females` = as.integer(round(female_percent * sample_size)),
+    Females = as.integer(round(female_percent * sample_size)),
     Age = str_c(age_mean, "±", age_sd, sep = " "),
@@
     `Stimulus dimensions` = stimuli_dimensions
+  ) %>%
+  mutate(
+    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
   ) -> tabs1
@@
 ```
+
+\renewcommand{\arraystretch}{1.10}
 
@@
 
+\renewcommand{\arraystretch}{0.97}
+
 ```{r, tabs3, include=TRUE}
@@
 
+\renewcommand{\arraystretch}{1.30}
+
 ```{r, tabs4, include=TRUE}
@@
   here(data_dir, "prisma_checklist.csv"),
-  col_types = "ccc"
+  col_types = "ccc", na = character()
 )
@@
   tab_prisma,
-  caption = "PRISMA 2020 checklist",
-  font_size = "scriptsize",
-  align = "lrl",
+  caption = "PRISMA 2020 checklist", font_size = "scriptsize",
+  landscape = TRUE, align = "p{1.5cm}p{2.5cm}p{1cm}p{12cm}p{5.5cm}",
 )

### 2022-05-14 manuscript.Rmd
Remove commented code

@@
 summary(res_prior)
-# plot(res_prior)
 
@@
 summary(res_brm)
-# plot(res_brm)
 
@@
 (hyp_brm <- hypothesis(res_brm, "Intercept > 0")$hypothesis)
-
-# # Summarise fixed effects (incl. Bayes factors)
-# describe_posterior(
-#   res_brm,
-#   centrality = "mean", ci = 0.95, ci_method = "ETI",
-#   test = c("p_direction", "rope", "bayesfactor"),
-#   rope_range = c(-0.1, 0.1)
-# )
 
@@
 summary(res_prior_reg)
-# plot(res_prior_reg)
 
@@
 summary(res_brm_reg)
-# plot(res_brm_reg)
 
@@
 ))
-
-# # Summarise fixed effects (incl. Bayes factors)
-# describe_posterior(
-#   res_brm_reg,
-#   centrality = "mean", ci = 0.95, ci_method = "ETI",
-#   test = c("p_direction", "rope", "bayesfactor"),
-#   rope_range = c(-0.1, 0.1)
-# )
 
@@
 summary(res_prior_gender)
-# plot(res_prior_gender)
 
@@
 summary(res_brm_gender)
-# plot(res_brm_gender)
 
@@
 (hyp_brm_gender <- hypothesis(res_brm_gender, "Intercept > 0")$hypothesis)
-
-# # Summarise fixed effects (incl. Bayes factors)
-# describe_posterior(
-#   res_brm_gender,
-#   centrality = "mean", ci = 0.95, ci_method = "ETI",
-#   test = c("p_direction", "rope", "bayesfactor"),
-#   rope_range = c(-0.1, 0.1)
-# )
 

### 2022-05-14 manuscript.Rmd
Proof reading by M.A.S.

@@
     affiliation   : "1,2"
-    corresponding : "yes"
-    address       : "Stephanstraße 1a, 04103 Leipzig"
-    email         : "enge@cbs.mpg.de"
   - name          : "Shreya Kapoor"
@@
   - id            : "1"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, 04103 Leipzig"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, Leipzig, Germany"
   - id            : "2"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, Berlin, Germany"
 
 authornote: |
-  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
-
-  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
-
-  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
-
-  We have no conflict of interest to disclose.
-  There were no ethical concerns since we did not collect any new data.
+  \noindent \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
+
+  \noindent \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
+
+  \noindent \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
+
+  \noindent We have no conflict of interest to disclose. There were no ethical concerns since we did not collect any new data.
+  Correspondence concerning this article should be addressed to Alexander Enge, Stephanstraße 1a, 04103 Leipzig, Germany. E-mail: enge@cbs.mpg.de
 
@@
 We robustly found that male infants recognized novel rotated objects more reliably than female infants.
-The effect size of this average difference was small and did not change with age.
 These findings indicate that gender differences in mental rotation are already present in the first months of life.
@@
 For the meta-analysis of gender differences in mental rotation performance (Fig.
-3a), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+3b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
 The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect size (vertical black line).
-Gray shades indicate a 95% pseudo-confidence interval (dark gray) and 99% pseudo-confidence interval (light gray) under the null hypothesis.
+Gray shades indicate a 95% pseudo-confidence interval (dark gray) and a 99% pseudo-confidence interval (light gray) under the null hypothesis.
 These shades thus illustrate which of the original studies observed a significant effect.
@@
 To this end, we scrutinized the robustness of `r descs$n_experiments` experimental effect sizes.
-We found that male infants looked on average slightly longer at novel rotated objects compared to female infants.
+We found that male infants looked on average longer at novel rotated objects compared to female infants.
 This effect was small and unrelated to age in the current range.
@@
 Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen's weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]).
-Interrater agreement for the specific eligibility criteria were `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]).
+Interrater agreement for the specific eligibility criteria was `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]).
 Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
@@
 Task was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast [@schad2020].
-We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender task type (i.e., [female - mixed] $\times$ age and [male - female] $\times$ age) into a Bayesian meta-regression model.
-This model used the same random effects structure and sampling parameters as described above.
+We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender and task type (i.e., [female - mixed] $\times$ age and [male - female] $\times$ age) into a Bayesian meta-regression model.
+This model was based on the same random effects structure and sampling parameters as described above.
 
@@
 To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993].
-To this end, we adapted code from the bootstrap R package (Version `r packageVersion("bootstrap")`) [@kostyshak2019].
-Specifically, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.
-To take into account the variance inherent in Bayesian model estimation, we averaged over $x$ iterations of the jackknife.
+To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.
+We then checked if the meta-analytic effect size and heterogeneity remained constant or if it was sensitive against the influence of any individual experiment (Supplementary Table 3).
 
@@
 
-The data for this study is available  from an   [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) repository [@enge2022a].
+The data for this study is available  from an   [Open Science Framework repository](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
 This link is intended for peer review only and will be replaced with a public link upon acceptance.
@@
 
-The data for this study is available from an  [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) repository [@enge2022a].
+The data for this study is available  from an   [Open Science Framework repository](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
 This link is intended for peer review only and will be replaced with a public link upon acceptance.

### 2022-05-14 manuscript.Rmd
Update contributions

@@
 
-M.A.S. conceived, designed, and obtained funding for the study.
-
-A.E., S.K., and A.K.
-designed and executed the search strategy, performed study selection and screening procedures, managed the database of search results and performed data analysis in consultation with M.A.S.
-
-A.E. and M.A.S. wrote the manuscript with feedback from S.K. and A.K.
+\noindent M.A.S. conceived, designed, and obtained funding for the study.
+
+\noindent A.E., S.K., and A.-S.K.
+designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results in consultation with M.A.S.
+
+\noindent A.E. and M.A.S. wrote the manuscript with additional input from S.K. and A.-S.K.
 

### 2022-05-15 manuscript.Rmd
Improve variable names, comments

@@
 library(tidyverse)
-library(magrittr)
 library(furrr)
@@
 library(brms)
-library(bayestestR)
 library(tidybayes)
@@
 source(here("manuscript_files", "helper_functions.R"))
+
+# Re-run steps that take a long time?
+run <- list(
+  bayesian_models = FALSE,
+  jackknife_analysis = FALSE,
+  sensitivity_analysis = FALSE
+)
 
@@
 
-# Re-run steps that take a long time?
-run <- list(
-  bayesian_models = FALSE,
-  jackknife_analysis = FALSE,
-  sensitivity_analysis = FALSE
-)
-
 # Options for MCMC sampling when fitting Bayesian multilevel models
@@
 
-# Download literature search spreadsheet from Google Drive
+# Download spreadsheets from the literature search from Google Drive
 excel_url <- "https://docs.google.com/spreadsheets/d/1xnC0NlQYTXavXaeqQidhi7UKb1pCGAl9Ry3h3Uz3mi0"
@@
 
-# Read sheets
-screening <- read_excel(excel_file, sheet = "screening")
-included <- read_excel(excel_file, sheet = "included", na = "NA")
-gender <- read_excel(excel_file, sheet = "gender_differences", na = "NA")
-
-# Add columns to the table of included experiments
-included %>%
+# Read the sheets
+raw_screening <- read_excel(excel_file, sheet = "screening")
+raw_meta <- read_excel(excel_file, sheet = "included", na = "NA")
+raw_gender <- read_excel(excel_file, sheet = "gender_differences", na = "NA")
+
+# Add columns to the table of experiments for the meta-analysis
+raw_meta %>%
   mutate(
@@
     ),
-    # Add d_z from paired t test of condition means (Rosenthal, 1991)
+    # Add d_z from paired-samples t-test of condition means (Rosenthal, 1991)
     d_z_t = t / sqrt(sample_size),
-    # Add d_z from ANOVA F value via conversion to a t value
+    # Add d_z from ANOVA F-statistic via conversion to a t-statistic
     d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
@@
     d_av = mean_diff / sd_av,
-    # Add d from one-sample t test of novelty preference scores
+    # Add d from one-sample t-test of novelty preference scores
     d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,
@@
       !is.na(d) ~ d,
-      # 2. If a paired sample t test was reported
+      # 2. If a paired-samples t-test was reported
       !is.na(d_z_t) ~ d_z_t,
-      # 3. If ANOVA was reported
+      # 3. If an ANOVA was reported
       !is.na(d_z_f) ~ d_z_f,
@@
 
-    # Recode mean sample age in years (centered) for meta-regression
+    # Recode mean sample age in years (mean-centered) for meta-regression
     age = age_mean / 365.25,
@@
 
-# Overview of the different effect sizes
+# Get an overview of the different effect sizes
 dat_all %>%
@@
 
-# Compute standard error of Cohen's d based on assumed correlation
+# Compute standard errors of the effect sizes based on assumed correlation
 # See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
-# This will need a sensitivity analysis regarding the values of `r_assumed`
+# You'll find a sensitivity analysis for `r_assumed` in the `supplement.Rmd`
 r_assumed <- 0.5
@@
   ) %>%
-  filter(!is.na(gi)) -> dat_all_r
-
-# Show number of experiments per gender grouping strategy
-table(dat_all_r$gender_split)
-
-# Extract split or mixed experiments only
-dat_split <- filter(dat_all_r, gender_split %in% c("split", "split_only"))
-dat_mixed <- filter(dat_all_r, gender_split %in% c("mixed", "mixed_only"))
-
-# Combine both strategies, preferring split experiments
+  filter(!is.na(gi)) -> dat_meta_all
+
+# Show number of experiments per gender grouping strategy (mixed/split)
+table(dat_meta_all$gender_split)
+
+# Extract either split or mixed experiments only
+dat_split <- filter(dat_meta_all, gender_split %in% c("split", "split_only"))
+dat_mixed <- filter(dat_meta_all, gender_split %in% c("mixed", "mixed_only"))
+
+# Combine both strategies but preferring split experiments
 dat_both_split <- filter(
-  dat_all_r, gender_split %in% c("split", "mixed_only", "split_only")
-)
-
-# Combine both strategies, preferring mixed experiments
+  dat_meta_all, gender_split %in% c("split", "mixed_only", "split_only")
+)
+
+# Combine both strategies but preferring mixed experiments
 dat_both_mixed <- filter(
-  dat_all_r, gender_split %in% c("mixed", "mixed_only", "split_only")
-)
-
-# We go ahead with the last solution as to use the maximum amount of information
-# while not biasing the gender results
-dat <- dat_both_mixed
-
-# Extract some descriptive statistics for usage in the main text
-descs <- list(
-  n_articles = length(unique(dat$article)),
-  n_experiments = nrow(dat),
-  n_infants = sum(dat$sample_size),
-  percent_female = mean(dat$female_percent, na.rm = TRUE),
-  min_age_months = as.integer(min(dat$age_min, na.rm = TRUE) / 30.417),
-  max_age_months = as.integer(max(dat$age_max, na.rm = TRUE) / 30.417),
+  dat_meta_all, gender_split %in% c("mixed", "mixed_only", "split_only")
+)
+
+# We go ahead with the last solution (i.e., prefer mixed experiments) as to use
+# the maximum amount of information while not biasing the gender results
+dat_meta <- dat_both_mixed
+
+# Extract some descriptive statistics so we can paste them in the main text
+descriptives <- list(
+  n_articles = length(unique(dat_meta$article)),
+  n_experiments = nrow(dat_meta),
+  n_infants = sum(dat_meta$sample_size),
+  percent_female = mean(dat_meta$female_percent, na.rm = TRUE),
+  min_age_months = as.integer(min(dat_meta$age_min, na.rm = TRUE) / 30.417),
+  max_age_months = as.integer(max(dat_meta$age_max, na.rm = TRUE) / 30.417),
   mean_age_weighted = print_days_months(
-    sum(dat$age_mean * dat$ni) / (sum(dat$ni)),
+    sum(dat_meta$age_mean * dat_meta$ni) / (sum(dat_meta$ni)),
     long = TRUE
   ),
-  n_experiments_habituation = nrow(filter(dat, task == "Habituation")),
-  n_experiments_voe = nrow(filter(dat, task == "VoE"))
+  n_experiments_habituation = nrow(filter(dat_meta, task == "Habituation")),
+  n_experiments_voe = nrow(filter(dat_meta, task == "VoE"))
 )
@@
 
-In the present study, we meta-analyzed `r descs$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descs$n_infants, big.mark = ",")` infants (`r print_perc(descs$percent_female)` female) aged `r descs$min_age_months` to `r descs$max_age_months` months (mean age of `r descs$mean_age_weighted`; Supplementary Table 1).
-All tasks were embedded either into habituation experiments (`r descs$n_experiments_habituation`) or violation of expectation experiments (`r descs$n_experiments_voe`) [@fantz1964; @baillargeon1985].
+In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table 1).
+All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985].
 These experiments comprised real world stimuli (e.g., toy objects [@antrilli2016]), three-dimensional digital stimuli (e.g., cube figures [@moore2008]), or two-dimensional digital stimuli (e.g., digits [@quinn2008]).
@@
 
-```{r, meta_analysis}
+```{r, meta}
 # Specify priors
-prior_c <- c(
+prior_meta <- c(
   set_prior("normal(0, 1)", class = "b"),
@@
 brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
-res_prior <- brm(
+res_prior_meta <- brm(
   gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
-  data = dat,
-  prior = prior_c,
+  data = dat_meta,
+  prior = prior_meta,
   sample_prior = "only",
@@
   seed = seed,
-  file = here(models_dir, "res_prior"),
+  file = here(models_dir, "res_prior_meta"),
   file_refit = brms_file_refit
 )
-summary(res_prior)
+summary(res_prior_meta)
 
 # Run Bayesian multilevel model
-res_brm <- update(
-  res_prior,
+res_meta <- update(
+  res_prior_meta,
   sample_prior = FALSE,
-  file = here(models_dir, "res_brm"),
+  file = here(models_dir, "res_meta"),
   file_refit = brms_file_refit
 )
-summary(res_brm)
+summary(res_meta)
 
 # Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_brm <- hypothesis(res_brm, "Intercept > 0")$hypothesis)
+(hyp_meta <- hypothesis(res_meta, "Intercept > 0")$hypothesis)
 
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_brm, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC
+spread_draws(res_meta, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+  # Compute variances and ICC from standard deviations
   mutate(
@@
     .keep = "unused"
-  ) -> draws_brm
-
-# Summarize as mean and 95% credible intervals
-(summ_brm <- as.list(mean_qi(draws_brm)))
+  ) -> draws_meta
+
+# Summarize as means and 95% credible intervals
+(summ_meta <- as.list(mean_qi(draws_meta)))
 ```
@@
 ```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
-# Get posterior draws for the effect in each experiment
-epred_draws_brm <- epred_draws(res_brm, dat, ndraws = NULL) %>%
+# Get posterior draws for the effect *in each experiment*
+epred_draws_meta <- epred_draws(res_meta, dat_meta, ndraws = NULL) %>%
   mutate(experiment_f = factor(experiment))
@@
 # Create forest plot
-dat %>%
+dat_meta %>%
   # Make sure the plot will be ordered alphabetically by experiment IDs
@@
     experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
-    # Show article labels only for the first experiment per article
+    # Show article labels only for the first experiment (row) per article
     article = if_else(article == lag(article, default = ""), "", article),
-    # Compute frequentist confidence intervals
+    # Compute frequentist confidence intervals for each experiment
     ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
@@
   geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
-  # Add Bayesian highest posterior density intervals for each experiment
+  # Add Bayesian credible intervals for each experiment
   stat_interval(
     aes(x = .epred),
-    data = epred_draws_brm,
+    data = epred_draws_meta,
     alpha = .8,
@@
     aes(x = intercept, y = -1),
-    draws_brm,
+    draws_meta,
     point_interval = "mean_qi",
@@
       "Three-level model",
-      print_num(summ_brm$intercept),
-      print_num(summ_brm$intercept.lower),
-      print_num(summ_brm$intercept.upper)
+      print_num(summ_meta$intercept),
+      print_num(summ_meta$intercept.lower),
+      print_num(summ_meta$intercept.upper)
     ),
@@
   ) +
-  # Add headers for each of the for columns
+  # Add column headers
   annotate(
@@
     xmax = Inf,
-    ymin = descs$n_experiments + 0.5,
+    ymin = descriptives$n_experiments + 0.5,
     ymax = Inf,
@@
     x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
-    y = descs$n_experiments + 1.5,
+    y = descriptives$n_experiments + 1.5,
     label = c(
@@
   coord_cartesian(
-    ylim = c(-1.5, descs$n_experiments + 2), expand = FALSE, clip = "off"
+    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
   ) +
@@
 dir.create(figures_dir, showWarnings = FALSE)
-ggsave(here(figures_dir, "forest.pdf"), width = 12, height = 14)
+ggsave(here(figures_dir, "fig1_meta.pdf"), width = 12, height = 14)
 ```
@@
 Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
-Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_brm$intercept`$, 95% credible interval (CrI) [`r summ_brm$intercept.lower`, `r summ_brm$intercept.upper`] (Fig.
+Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.
 1).
-The probability for this effect being greater than zero was `r print_perc(hyp_brm$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm$sigma2_experiment`$, 95% CrI [`r summ_brm$sigma2_experiment.lower`, `r summ_brm$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm$sigma2_article`$, 95% CrI [`r summ_brm$sigma2_article.lower`, `r summ_brm$sigma2_article.upper`] at the article level.
-Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_brm$icc)` was attributable to differences *between* articles.
+The probability for this effect being greater than zero was `r print_perc(hyp_meta$Post.Prob)`.
+The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level.
+Therefore, approximately `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.
 
@@
 
-```{r, meta_regression}
+```{r, reg}
 # Set numerical contrasts for factor variables
-contrasts(dat$gender) <- MASS::contr.sdif(3)
-contrasts(dat$task) <- MASS::contr.sdif(2)
+contrasts(dat_meta$gender) <- MASS::contr.sdif(3)
+contrasts(dat_meta$task) <- MASS::contr.sdif(2)
 
 # Specify priors
-prior_c <- c(
+prior_reg <- c(
   set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
@@
     (1 | article / experiment),
-  data = dat,
-  prior = prior_c,
+  data = dat_meta,
+  prior = prior_reg,
   sample_prior = "only",
@@
 # Run Bayesian multilevel model
-res_brm_reg <- update(
+res_reg <- update(
   res_prior_reg,
   sample_prior = FALSE,
-  file = here(models_dir, "res_brm_reg"),
+  file = here(models_dir, "res_reg"),
   file_refit = brms_file_refit
 )
-summary(res_brm_reg)
+summary(res_reg)
 
@@
 (hyps_brm_reg <- list(
-  intercept = hypothesis(res_brm_reg, "Intercept > 0")$hypothesis,
-  female_mixed = hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis,
-  male_female = hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis,
-  age = hypothesis(res_brm_reg, "age_c > 0")$hypothesis,
-  voe_habituation = hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis,
-  female_mixed_age = hypothesis(res_brm_reg, "gender2M1:age_c > 0")$hypothesis,
-  male_female_age = hypothesis(res_brm_reg, "gender3M2:age_c > 0")$hypothesis
+  intercept = hypothesis(res_reg, "Intercept > 0")$hypothesis,
+  female_mixed = hypothesis(res_reg, "gender2M1 < 0")$hypothesis,
+  male_female = hypothesis(res_reg, "gender3M2 > 0")$hypothesis,
+  age = hypothesis(res_reg, "age_c > 0")$hypothesis,
+  voe_habituation = hypothesis(res_reg, "task2M1 > 0")$hypothesis,
+  female_mixed_age = hypothesis(res_reg, "gender2M1:age_c > 0")$hypothesis,
+  male_female_age = hypothesis(res_reg, "gender3M2:age_c > 0")$hypothesis
 ))
@@
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_brm_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC
+spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+  # Compute variances and ICC from standard deviations
   mutate(
@@
     icc = sigma2_article / sigma2_total,
-  ) -> draws_brm_reg
-
-# Summarize as mean and 95% credible intervals
-(summ_brm_reg <- as.list(mean_qi(draws_brm_reg)))
+  ) -> draws_reg
+
+# Summarize as means and 95% credible intervals
+(summ_reg <- as.list(mean_qi(draws_reg)))
 ```
@@
 As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig. 2).
-Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_brm_reg$male_female`$, 95% CrI [`r summ_brm_reg$male_female.lower`, `r summ_brm_reg$male_female.upper`].
+Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$, 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
 The probability for this effect being larger than zero was `r print_perc(hyps_brm_reg$male_female$Post.Prob)`.
-We found no difference between mixed-gender and all-female samples, $b = `r -summ_brm_reg$female_mixed`$, 95% CrI [`r -summ_brm_reg$female_mixed.lower`, `r -summ_brm_reg$female_mixed.upper`] (`r print_perc(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
-Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_brm_reg$age`$, 95% [`r summ_brm_reg$age.lower`, `r summ_brm_reg$age.upper`].
-We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_brm_reg$female_mixed_age`$, 95% CrI [`r summ_brm_reg$female_mixed_age.lower`, `r summ_brm_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_brm_reg$male_female_age`$, 95% CrI [`r summ_brm_reg$male_female_age.lower`, `r summ_brm_reg$male_female_age.upper`]).
-Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_brm_reg$voe_habituation`$, 95% [`r summ_brm_reg$voe_habituation.lower`, `r summ_brm_reg$voe_habituation.upper`].
+We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_perc(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
+Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% [`r summ_reg$age.lower`, `r summ_reg$age.upper`].
+We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]).
+Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`].
 The probability for this effect being greater than zero was `r print_perc(hyps_brm_reg$voe_habituation$Post.Prob)`.
@@
 ```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
-# Get draws from the posterior distribution
-draws_reg <- epred_draws(
-  res_brm_reg,
-  dat,
+# Get draws from the posterior distribution *for each experiment*
+epred_draws_reg <- epred_draws(
+  res_reg,
+  dat_meta,
   ndraws = NULL,
@@
 # Use colors as proposed in https://arxiv.org/abs/2107.02270
-habi_colors <- c(
+# The four colors code for a combination of tasks (Habituation, VoE) and gender
+# (female, male, mixed)
+plot_reg_colors <- list(
+  habituation = c(
     "Female, Habituation" = "#5790fc",
@@
     "Mixed, Habituation" = "#e42536"
-)
-voe_colors <- c("Mixed, VoE" = "#964a8b")
-
-# Regression plot
-dat %>%
+  ),
+  voe = c("Mixed, VoE" = "#964a8b")
+)
+
+# Create regression plot
+dat_meta %>%
   ggplot(aes(x = age * 12, y = gi)) +
@@
   ) +
-  # Regression lines and HPDIs - Habituation tasks
+  # Regression lines and CrIs for Habituation tasks
   stat_lineribbon(
     aes(y = .epred, color = gender_task),
-    data = draws_reg,
+    data = epred_draws_reg,
     alpha = .4,
@@
   ) +
-  # Individual study effect sizes - Habituation tasks
+  # Individual study effect sizes for Habituation tasks
   geom_point(aes(color = gender_task, size = ni), shape = 0) +
   scale_color_manual(
-    values = habi_colors,
-    breaks = names(habi_colors),
+    values = plot_reg_colors$habituation,
+    breaks = names(plot_reg_colors$habituation),
     labels = c("Females", "Males", "Mixed gender"),
@@
   )) +
-  # Regression lines and HPDIs - VoE tasks
+  # Regression lines and CrIs for VoE tasks
   ggnewscale::new_scale_color() +
@@
     aes(y = .epred, color = gender_task),
-    data = draws_reg,
+    data = epred_draws_reg,
     fill = NA,
@@
   ) +
-  # Individual study effect sizes - VoE tasks
+  # Individual study effect sizes for VoE tasks
   geom_point(aes(color = gender_task, size = ni), shape = 0) +
   scale_color_manual(
-    values = voe_colors,
-    breaks = names(voe_colors),
+    values = plot_reg_colors$voe,
+    breaks = names(plot_reg_colors$voe),
     labels = c("Mixed gender"),
@@
 
-# Extract the legend so that we can put it inside the plotting area
+# Extract the legend so that we can put it inside the plot later on
 plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))
@@
 # Plot posterior distributions of the regression coefficients
-draws_reg_coef <- tidy_draws(res_brm_reg)
-draws_reg_coef %>%
+epred_draws_reg_coef <- tidy_draws(res_reg)
+epred_draws_reg_coef %>%
+  # Convert to long format
   select(all_of(names(coef_colnames))) %>%
@@
   mutate(coef = factor(key, levels = names(coef_colnames))) %>%
+  # Plot coefficients as "half eyes" (mean + CrIs + distribution)
   ggplot(aes(x = value, y = fct_rev(coef))) +
@@
   stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
+  # Styling
   coord_cartesian(xlim = c(-1.25, 1.25), clip = "off") +
@@
 
-# Combine plots
+# Combine the two regression plots
 plot_grid(
@@
 # Save plot
-ggsave(here(figures_dir, "regression_coef.pdf"), width = 12, height = 5)
+ggsave(here(figures_dir, "fig2_reg.pdf"), width = 12, height = 5)
 ```
@@
 
-```{r, gender_differences}
-# Extract relevant effect sizes
-gender %>%
-  # Remove redundant samples
+```{r, gender}
+# Compute relevant effect sizes for the meta-analysis of gender differences
+raw_gender %>%
+  # Remove effect sizes from experiments with redundant samples
   filter(!redundant) %>%
@@
 
-    # Re-code non-significant f values as an effect of 0
+    # Re-code non-significant F-statistics as an effect size of d = 0
     f = as.numeric(f),
@@
 
-    # Add d from two-samples t test (Lakens, 2013)
+    # Add d from two-samples t-test (Lakens, 2013)
     d_t = t * sqrt(1 / female_n + 1 / male_n),
 
-    # Add d from ANOVA F value via conversion to a t value
+    # Add d from ANOVA F-statistic via conversion to a t-statistic
     d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),
@@
 
-    # Add d from one-sample t test of novelty preference scores
+    # Add d from one-sample t-test of novelty preference scores
     mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
@@
       !is.na(d) ~ d,
-      # 2. If a t test was reported
+      # 2. If a t-test was reported
       !is.na(d_t) ~ d_t,
-      # 3. If ANOVA was reported
+      # 3. If an ANOVA was reported
       !is.na(d_f) ~ d_f,
@@
   ) %>%
-  # Remove experiments that didn't provide an effect size
+  # Remove experiments that didn't provide any effect size
   filter(!is.na(gi)) -> dat_gender
 
-# Overview of the different effect sizes
+# Get an overview of the different effect sizes
 dat_gender %>%
@@
 
-# Specify priors
-prior_c <- c(
-  set_prior("normal(0, 1)", class = "b"),
-  set_prior("cauchy(0, 0.3)", class = "sd")
-)
+# Use the same priors as for the main meta-analysis
+prior_gender <- prior_meta
 
@@
   data = dat_gender,
-  prior = prior_c,
+  prior = prior_gender,
   sample_prior = "only",
@@
 # Run Bayesian multilevel model
-res_brm_gender <- update(
+res_gender <- update(
   res_prior_gender,
   sample_prior = FALSE,
-  file = here(models_dir, "res_brm_gender"),
+  file = here(models_dir, "res_gender"),
   file_refit = brms_file_refit
 )
-summary(res_brm_gender)
+summary(res_gender)
 
 # Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_brm_gender <- hypothesis(res_brm_gender, "Intercept > 0")$hypothesis)
+(hyp_gender <- hypothesis(res_gender, "Intercept > 0")$hypothesis)
 
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_brm_gender, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC
+spread_draws(res_gender, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+  # Compute variances and ICC from standard deviations
   mutate(
@@
     .keep = "unused"
-  ) -> draws_brm_gender
-
-# Summarize as mean and 95% credible intervals
-(summ_brm_gender <- as.list(mean_qi(draws_brm_gender)))
+  ) -> draws_gender
+
+# Summarize as means and 95% credible intervals
+(summ_gender <- as.list(mean_qi(draws_gender)))
 ```
@@
 To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_brm_gender$intercept`$, 95% Crl [`r summ_brm_gender$intercept.lower`, `r summ_brm_gender$intercept.upper`] (Supplementary Fig.
-1) and a probability of this effect being greater than zero of `r print_perc(hyp_brm_gender$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm_gender$sigma2_experiment`$, 95% CrI [`r summ_brm_gender$sigma2_experiment.lower`, `r summ_brm_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm_gender$sigma2_article`$, 95% CrI [`r summ_brm_gender$sigma2_article.lower`, `r summ_brm_gender$sigma2_article.upper`] at the article level.
-This means that `r print_perc(summ_brm_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_brm_gender$icc)` to differences between experiments *within* articles.
+Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.
+1) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
+The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
+This means that `r print_perc(summ_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_gender$icc)` to differences between experiments *within* articles.
 
@@
 
-```{r, publication_bias, echo=TRUE}
+```{r, bias, echo=TRUE}
 # Classical Egger regression test for the meta-analysis of rotation performance
-(egger <- with(
-  dat, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
+(egger_meta <- with(
+  dat_meta, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
 ))
-(egger_ci <- confint(egger$fit)["Xsei", ])
+(egger_ci_meta <- confint(egger_meta$fit)["Xsei", ])
 
@@
 3a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
-This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger$fit)["Xsei"]`$, $t(`r egger$dfs`) = `r egger$zval`$, $p = `r print_p(egger$pval)`$, 95% confidence interval (CI) [`r egger_ci["2.5 %"]`, `r egger_ci["97.5 %"]`] (two-sided test).
+This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
 Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table 3).
@@
 ```{r, fig3, include=TRUE, fig.height=3.5, fig.width=12, fig.cap="(ref:fig3-caption)"}
-# Create funnel plots
-list(dat, dat_gender) %>%
-  map(function(plot_dat) {
-
-    # Define maximul SE of interest (a bit larger than the largest observed one)
-    max_se <- max(plot_dat$sei) + 0.05
+# Create funnel plots for the two meta-analyses
+map2(
+  list(dat_meta, dat_gender),
+  list(summ_meta, summ_meta),
+  function(dat, summ) {
+
+    # Define maximul SE of interest (a bit larger than the largest observed SE)
+    max_se <- max(dat$sei) + 0.05
 
@@
 
-    # Compute a 95% funnel around the observed meta-analytic effect size
-    funnel_observed <- mutate(funnel_greater_05, x = x + summ_brm$intercept)
-
-    # Plot the funnel(s)
-    ggplot(plot_dat, aes(x = gi, y = sei)) +
+    # Compute a 95% funnel around the *observed* meta-analytic effect size
+    funnel_observed <- mutate(funnel_greater_05, x = x + summ$intercept)
+
+    # Plot the funnels
+    ggplot(dat, aes(x = gi, y = sei)) +
       # Funnels under the null hypothesis
@@
       # Meta-analytic effect size
-      geom_vline(xintercept = summ_brm$intercept, color = "black") +
+      geom_vline(xintercept = summ$intercept, color = "black") +
       # Experiment-specific effect sizes
@@
       )
-  }) -> plots_funnel
+  }
+) -> plots_funnel
 
@@
 # Save the plot
-ggsave(here(figures_dir, "funnel.pdf"), width = 12, height = 3.5)
+ggsave(here(figures_dir, "fig3_funnel.pdf"), width = 12, height = 3.5)
 ```
@@
 
-We analyzed looking times during mental rotation in `r formatC(descs$n_infants, big.mark = ",")` infants ranging from `r descs$min_age_months` to `r descs$max_age_months` months of age.
-To this end, we scrutinized the robustness of `r descs$n_experiments` experimental effect sizes.
+We analyzed looking times during mental rotation in `r formatC(descriptives$n_infants, big.mark = ",")` infants ranging from `r descriptives$min_age_months` to `r descriptives$max_age_months` months of age.
+To this end, we scrutinized the robustness of `r descriptives$n_experiments` experimental effect sizes.
 We found that male infants looked on average longer at novel rotated objects compared to female infants.
@@
 
-We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_brm_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
+We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
 The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference more likely report separate effect sizes for males and females.
-In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_brm_gender$intercept`$) can be viewed as a lower bound of the true effect size.
+In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_gender$intercept`$) can be viewed as a lower bound of the true effect size.
 This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences were likely also observed but just not reported because of missing power to render these effects statistically significant.
@@
 ```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", out.width="50%"}
-# Include the flowchart (created with MS PowerPoint)
+# Include the flowchart (which was created manually with MS PowerPoint)
 knitr::include_graphics(here("manuscript_files/flowchart.pdf"))
@@
 # Compute interrater agreement for binary decision (include vs. exclude)
-(irr_bin_perc <- with(screening, mean(bin_1 == bin_2)))
-(irr_bin_kappa <- with(screening, psych::cohen.kappa(cbind(bin_1, bin_2))))
+(irr_bin_perc <- with(
+  raw_screening, mean(bin_1 == bin_2)
+))
+(irr_bin_kappa <- with(
+  raw_screening, psych::cohen.kappa(cbind(bin_1, bin_2))
+))
 irr_bin_kappa_w <- as.list(irr_bin_kappa$confid["weighted kappa", ])
@@
 # Compute interrater agreement for specific exclusion codes
-(irr_code_perc <- with(screening, mean(code_1 == code_2)))
-(irr_code_kappa <- with(screening, psych::cohen.kappa(cbind(code_1, code_2))))
+(irr_code_perc <- with(
+  raw_screening, mean(code_1 == code_2)
+))
+(irr_code_kappa <- with(
+  raw_screening, psych::cohen.kappa(cbind(code_1, code_2))
+))
 irr_code_kappa_w <- as.list(irr_code_kappa$confid["weighted kappa", ])
@@
   age_months <- age_years * 12
-  next_largest_age_months <- max(dat$age_mean) / 30.417
+  next_largest_age_months <- max(dat_meta$age_mean) / 30.417
   age <- age_years * 365.25
-  z <- (age - mean(dat$age_mean)) / sd(dat$age_mean)
+  z <- (age - mean(dat_meta$age_mean)) / sd(dat_meta$age_mean)
 })
@@
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of `r descs$n_articles` articles being included in the meta-analysis (Fig.
+This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.
 4).
@@
 Moreover, we disregarded effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of `r descs$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table 1) and 30 articles being included in the meta-analysis of gender differences in mental rotation performance.
+This procedure led to a total of `r descriptives$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table 1) and 30 articles being included in the meta-analysis of gender differences in mental rotation performance.
 

### 2022-05-15 supplement.Rmd
Improve variable names, comments

--- 2022-05-13 supplement.Rmd
@@
 # Compute empirical estimate of the correlation between dependent samples
-dat %>%
+dat_meta %>%
   mutate(
@@
 # Subset articles that have an empirical estimate for the correlation
-dat_ri_empirical <- filter(dat, !is.na(ri_empirical))
+dat_ri_empirical <- filter(dat_meta, !is.na(ri_empirical))
 
@@
 However, the correlation between repeated measures tends to go unreported in research articles.
-In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.
+In fact, none of the `r descriptives$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.
 
@@
 Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]).
-However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments.
+However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments.
 This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
@@
 
+\singlespacing
+\renewcommand{\arraystretch}{0.97}
+
 ```{r, tabs1, include=TRUE}
-# Save within-analysis table of experiments
-dat %>%
+# Save table of experiments for the meta-analysis of rotation
+dat_meta %>%
   mutate(
@@
 ```{r, frequentist}
-# Three-level model
-res_freq <- rma.mv(
+# Compute frequentist three-level model for the meta-analysis of rotation
+res_freq_meta <- rma.mv(
   gi, vi,
   random = ~ 1 | article / experiment,
-  data = dat,
+  data = dat_meta,
   slab = experiment
 )
-print(res_freq)
+print(res_freq_meta)
 
 # Check share of variance at each level of the model
-round(res_freq$sigma2[1] / sum(res_freq$sigma2), 3) # Between-art. (ICC)
-round(res_freq$sigma2[2] / sum(res_freq$sigma2), 3) # Within-art. (between-exp.)
+round(res_freq_meta$sigma2[1] / sum(res_freq_meta$sigma2), 3)
+round(res_freq_meta$sigma2[2] / sum(res_freq_meta$sigma2), 3)
 
 # Get profile likelihoods for sigmas to check that REML has converged
-prof_liks <- profile(res_freq, plot = FALSE)
+prof_liks <- profile(res_freq_meta, plot = FALSE)
 
-# Meta-regression with gender, age, and task
-res_reg_freq <- rma.mv(
+# Compute frequentist meta-regression with gender, age, and task
+res_freq_reg <- rma.mv(
   gi, vi,
@@
   random = ~ 1 | article / experiment,
-  data = dat,
+  data = dat_meta,
   slab = experiment
 )
-print(res_reg_freq)
+print(res_freq_reg)
 
-# Meta-analysis of gender differences
-res_gender_freq <- rma.mv(
+# Compute frequentist three-level model for the meta-analysis of gender
+res_freq_gender <- rma.mv(
   gi, vi,
@@
 )
-print(res_gender_freq)
+print(res_freq_gender)
 ```
+
+\renewcommand{\arraystretch}{1.10}
 
@@
 map2_dfr(
-  list(res_freq, res_reg_freq, res_gender_freq),
+  list(res_freq_meta, res_freq_reg, res_freq_gender),
   c(
@@
   ~ print_res_freq_table(
-    res_freq = .x, label_1 = .y, label_col_1 = "Model", print_sigma2s = TRUE
+    res_freq = .x, label_1 = .y, label_col_1 = "Model",
+    print_sigma2s = TRUE
   )
 ) %>%
-  # Rename parameters for readability
+  # Rename parameter labels
   mutate(
@@
   # Replace NAs with blank cells
-  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
+  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tabs2
 
@@
 apa_table(
-  tab_freq,
+  tabs2,
   caption = "Frequentist meta-analyses and meta-regression",
@@
 # Save the table
-write_csv(tab_freq, file = here(tables_dir, "tabs2_frequentist.csv"))
+write_csv(tabs2, file = here(tables_dir, "tabs2_frequentist.csv"))
 ```
@@
 ```{r, jackknife}
-# Re-run the jackknife analysis only if requested
+# Re-run the jackknife analysis if requested
 if (run$jackknife_analysis) {
 
-  # Re-fit the meta-analysis, leaving one experiment out at a time
+  # Re-fit the meta-analysis, leaving out one experiment at a time
   # Using parallelization with `furrr`
@@
   plan(multisession, workers = n_workers)
-  future_map_dfr(seq_len(nrow(dat)), function(jackknife_index) {
-    dat_jackknife <- dat[-jackknife_index, ]
-    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
+  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
+    dat_jackknife <- dat_meta[-jackknife_index, ]
+    res_jackknife <- update(res_meta, newdata = dat_jackknife, refresh = 0)
     print_res_table(
       res_jackknife,
-      label_1 = dat$article[jackknife_index],
-      label_2 = dat$group_long[jackknife_index],
+      label_1 = dat_meta$article[jackknife_index],
+      label_2 = dat_meta$group_long[jackknife_index],
       label_col_1 = "Article", label_col_2 = "Experiment"
@@
   }) %>%
-    # Show article labels only for the first experiment per article
+    # Show article labels only for the first experiment (row) per article
     mutate(
       Article = if_else(Article == lag(Article, default = ""), "", Article),
-    ) -> tab_jackknife
+    ) -> tabs3
 
   # Save the table
-  write_csv(tab_jackknife, file = here(tables_dir, "jackknife.csv"))
+  write_csv(tabs3, file = here(tables_dir, "tabs3_jackknife.csv"))
 }
@@
 
+\renewcommand{\arraystretch}{0.97}
+
 ```{r, tabs3, include=TRUE}
 # Read jackknife table from file
-tab_jackknife <- read_csv(
-  here(tables_dir, "jackknife.csv"),
+tabs3 <- read_csv(
+  here(tables_dir, "tabs3_jackknife.csv"),
   col_types = "c", na = character()
@@
 apa_table(
-  tab_jackknife,
+  tabs3,
   caption = "Jackknife (leave-one-out) analysis", font_size = "scriptsize",
@@
 
+\renewcommand{\arraystretch}{1.30}
+
 ```{r, tabs4, include=TRUE}
 # Read PRISMA checklist from file
-tab_prisma <- read_csv(
+tabs4 <- read_csv(
   here(data_dir, "prisma_checklist.csv"),
-  col_types = "ccc"
+  col_types = "ccc", na = character()
 )
@@
 apa_table(
-  tab_prisma,
-  caption = "PRISMA 2020 checklist",
-  font_size = "scriptsize",
-  align = "lrl",
+  tabs4,
+  caption = "PRISMA 2020 checklist", font_size = "scriptsize",
+  landscape = TRUE, align = "p{1.5cm}p{2.5cm}p{1cm}p{12cm}p{5.5cm}",
 )
@@
 
-```{r, sensitivity_analysis}
-# Re-run the sensitivity analyses only if requested
+```{r, sensitivity}
+# Re-run the sensitivity analyses if requested
 if (run$sensitivity_analysis) {
@@
       mutate(
-        dat,
+        dat_meta,
         vi = (dfi / (dfi - 2)) * ((2 * (1 - ri_sens)) / ni) *
@@
 
-      # Re-run meta-analysis
-      res <- update(res_brm, newdata = dat_ri_sens, refresh = 0)
+      # Re-run meta-analysis of mental rotation performance
+      res_meta <- update(res_meta, newdata = dat_ri_sens, refresh = 0)
 
-      # Re-run meta-regression
-      res_reg <- update(res_brm_reg, newdata = dat_ri_sens, refresh = 0)
+      # Re-run meta-regression of mental rotation performance
+      res_reg <- update(res_reg, newdata = dat_ri_sens, refresh = 0)
 
-      # Return both as a tibble together with the label
+      # Return both as a tibble and add a label
       return(
@@
           manipulation_value = str_c("$r$ = ", print_num(ri_sens)),
-          res = list(res),
+          res_meta = list(res_meta),
           res_reg = list(res_reg),
@@
   list(
+    # Less informative prior for the intercept
     `$b\\sim\\mathcal{U}(-10,10)$` = c(
@@
     ),
+    # More informative prior for the intercept
     `$b\\sim\\mathcal{N}(0,0.2)$` = c(
@@
     ),
+    # Less informative prior for the standard deviations
     `$\\sigma\\sim\\mathcal{U}(0,10)$` = c(
@@
     ),
+    # More informative prior for the standard deviations
     `$\\sigma\\sim\\text{Student-}t(10,0,0.2)$` = c(
@@
       # Re-run meta-analysis of mental rotation performance
-      res <- update(res_brm, prior = prior_sens, refresh = 0)
+      res_meta <- update(res_meta, prior = prior_sens, refresh = 0)
 
       # Re-run meta-regression of mental rotation performance
-      res_reg <- update(res_brm_reg, prior = prior_sens, refresh = 0)
+      res_reg <- update(res_reg, prior = prior_sens, refresh = 0)
 
       # Re-run meta-analysis of gender differences
-      res_gender <- update(res_brm_gender, prior = prior_sens, refresh = 0)
+      res_gender <- update(res_gender, prior = prior_sens, refresh = 0)
 
@@
           manipulation_value = prior_name,
-          res = list(res),
+          res_meta = list(res_meta),
           res_reg = list(res_reg),
@@
 
-  # Create table for the (main) meta-analysis of mental rotation performance
+  # Create table for the meta-analysis of mental rotation performance
   sens %>%
@@
       )
-    }) -> tab_sens
-  write_csv(tab_sens, file = here(tables_dir, "sens.csv"))
+    }) -> tabs5
+  write_csv(tabs5, file = here(tables_dir, "tabs5_sens_meta.csv"))
 
@@
       )
-    }) -> tab_sens_reg
-  write_csv(tab_sens_reg, file = here(tables_dir, "sens_reg.csv"))
+    }) -> tabs6
+  write_csv(tabs6, file = here(tables_dir, "tabs6_sens_reg.csv"))
 
@@
       )
-    }) -> tab_sens_gender
-  write_csv(tab_sens_gender, file = here(tables_dir, "sens_gender.csv"))
+    }) -> tabs7
+  write_csv(tabs7, file = here(tables_dir, "tabs7_sens_gender.csv"))
 }
@@
 
+\renewcommand{\arraystretch}{1.10}
+
 ```{r, tabs5, include=TRUE}
 # Load sensitivity analysis table from file
-tab_sens <- read_csv(
-  here(tables_dir, "sens.csv"),
+tabs5 <- read_csv(
+  here(tables_dir, "tabs5_sens_meta.csv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 apa_table(
-  tab_sens,
+  tabs5,
   caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
@@
 # Load sensitivity analysis table from file
-tab_sens_reg <- read_csv(
-  here(tables_dir, "sens_reg.csv"),
+tabs6 <- read_csv(
+  here(tables_dir, "tabs6_sens_reg.csv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 apa_table(
-  tab_sens_reg,
+  tabs6,
   caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
@@
 # Load sensitivity analysis table from file
-tab_sens_gender <- read_csv(
-  here(tables_dir, "sens_gender.csv"),
+tabs7 <- read_csv(
+  here(tables_dir, "tabs7_sens_gender.csv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 apa_table(
-  tab_sens_gender,
+  tabs7,
   caption = "Sensitivity analyses for the meta-analysis of gender differences",
@@
 
-```{r, trim_fill_selection, include=TRUE}
+```{r, correction}
 # Re-fit the two frequentist meta-analyses using a two-level model
 # This is because `rma.mv()` is not supported for trim-and-fill/selection models
-list(meta = dat, gender = dat_gender) %>%
+list(meta = dat_meta, gender = dat_gender) %>%
   map(function(x) rma.uni(gi, vi, data = x)) -> res_freq_2_lvl
@@
 }) %>%
-  set_names(names(res_freq_2_lvl)) -> tabs_trim_fill_selection
+  set_names(names(res_freq_2_lvl)) -> tabs_correction
 
@@
 write_csv(
-  tabs_trim_fill_selection$meta,
-  file = here(tables_dir, "trim_fill_selection_meta.csv")
+  tabs_correction$meta,
+  file = here(tables_dir, "tabs8_correction_meta.csv")
 )
 write_csv(
-  tabs_trim_fill_selection$gender,
-  file = here(tables_dir, "trim_fill_selection_gender.csv")
+  tabs_correction$gender,
+  file = here(tables_dir, "tabs9_correction_gender.csv")
 )
@@
 apa_table(
-  tabs_trim_fill_selection$meta,
+  tabs_correction$meta,
   caption = "Publication bias correction for the meta-analysis of mental rotation performance",
@@
 apa_table(
-  tabs_trim_fill_selection$gender,
+  tabs_correction$gender,
   caption = "Publication bias correction for the meta-analysis of gender differences",
@@
 ```{r, figs1, include=TRUE, fig.height=10, fig.width=12, fig.cap="(ref:figs1-caption)"}
-# Get posterior draws for the effect in each experiment
-epred_draws_brm_gender <- epred_draws(res_brm_gender, dat_gender, ndraws = NULL) %>%
+# Get posterior draws for the effect *in each experiment*
+epred_draws_gender <- epred_draws(res_gender, dat_gender, ndraws = NULL) %>%
   mutate(experiment_f = factor(experiment))
@@
     experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
-    # Show article labels only for the first experiment per article
+    # Show article labels only for the first experiment (row) per article
     article = if_else(article == lag(article, default = ""), "", article),
@@
   geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
-  # Add Bayesian highest posterior density intervals for each experiment
+  # Add Bayesian credible intervals for each experiment
   stat_interval(
     aes(x = .epred),
-    data = epred_draws_brm_gender,
+    data = epred_draws_gender,
     alpha = .8,
@@
     aes(x = intercept, y = -1),
-    draws_brm_gender,
+    draws_gender,
     point_interval = "mean_qi",
@@
       "Three-level model",
-      print_num(summ_brm_gender$intercept),
-      print_num(summ_brm_gender$intercept.lower),
-      print_num(summ_brm_gender$intercept.upper)
+      print_num(summ_gender$intercept),
+      print_num(summ_gender$intercept.lower),
+      print_num(summ_gender$intercept.upper)
     ),
@@
   ) +
-  # Add headers for each of the for columns
-  annotate( # Just to make the grid lines disappear
+  # Add column headers
+  annotate(
     "rect",
@@
 ```{r, figs2, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs2-caption)"}
-# Extract convergence statistics from results
-conv_stats <- with(summary(res_brm), tibble(
+# Extract convergence statistics (Rhat, Neff) from Bayesian results
+conv_stats <- with(summary(res_meta), tibble(
   parameter = c(
@@
 bayesplot::mcmc_trace(
-  res_brm,
+  res_meta,
   pars = conv_stats$parameter, facet_args = list(ncol = 1)
 ) +
+  # Parameter label
   geom_text(
@@
   ) +
+  # Rhat label
   geom_text(
@@
   ) +
+  # Neff labels
   geom_text(
@@
   ) +
+  # Styling
   labs(x = "Sample number", y = NULL, color = "MCMC\nchain") +
@@
 ```{r, figs3, include=TRUE, fig.height=4, fig.width=12, fig.cap="(ref:figs3-caption)"}
-# Combine profile likelihood results into one data frame
+# Combine frequentist profile likelihood results into one data frame
 prof_liks %>%
@@
   plot +
-    # Add trim and fill funnel
+    # Add trim-and-fill funnel
     geom_path(
@@
     geom_vline(xintercept = res$b, color = trim_fill_color) +
-    # Add filled in studies
+    # Add trim-and-fill studies
     geom_point(

### 2022-05-15 manuscript_files/helper_functions.R

@@ -30,7 +30,7 @@ print_mean_ci <- function(mean, lb, ub) {
   paste(print_num(mean), print_ci(lb, ub))
 }
 
-# Format results of Bayesian meta-analsis as a table with optional labels
+# Format results of Bayesian meta-analysis as a table with optional labels
 print_res_table <- function(res,
                             label_1 = NULL,
                             label_2 = NULL,
@@ -104,7 +104,7 @@ print_res_freq_table <- function(res_freq,
     `$z$` = print_num(res_freq$zval),
     `$p$` = ifelse(
       res_freq$pval < 0.001, "< 0.001", print_num(res_freq$pval, digits = 3)
-      ),
+    ),
     ci_lower = print_num(res_freq$ci.lb),
     ci_upper = print_num(res_freq$ci.ub)
   ) %>%

### 2022-05-15 manuscript.Rmd
Make sure random seed gets used for all models

@@
 run <- list(
-  bayesian_models = FALSE,
+  bayesian_models = TRUE,
   jackknife_analysis = FALSE,
@@
   sample_prior = FALSE,
+  seed = seed,
   file = here(models_dir, "res_meta"),
@@
   sample_prior = FALSE,
+  seed = seed,
   file = here(models_dir, "res_reg"),
@@
   sample_prior = FALSE,
+  seed = seed,
   file = here(models_dir, "res_gender"),

### 2022-05-15 supplement.Rmd
Make sure random seed gets used for all models

@@
     dat_jackknife <- dat_meta[-jackknife_index, ]
-    res_jackknife <- update(res_meta, newdata = dat_jackknife, refresh = 0)
+    res_jackknife <- update(
+      res_meta,
+      newdata = dat_jackknife,
+      seed = seed,
+      refresh = 0
+    )
     print_res_table(
@@
       # Re-run meta-analysis of mental rotation performance
-      res_meta <- update(res_meta, newdata = dat_ri_sens, refresh = 0)
+      res_meta <- update(
+        res_meta,
+        newdata = dat_ri_sens,
+        seed = seed,
+        refresh = 0
+      )
 
       # Re-run meta-regression of mental rotation performance
-      res_reg <- update(res_reg, newdata = dat_ri_sens, refresh = 0)
+      res_reg <- update(
+        res_reg,
+        newdata = dat_ri_sens,
+        seed = seed,
+        refresh = 0
+      )
 
@@
       # Re-run meta-analysis of mental rotation performance
-      res_meta <- update(res_meta, prior = prior_sens, refresh = 0)
+      res_meta <- update(
+        res_meta,
+        prior = prior_sens,
+        seed = seed,
+        refresh = 0
+      )
 
       # Re-run meta-regression of mental rotation performance
-      res_reg <- update(res_reg, prior = prior_sens, refresh = 0)
+      res_reg <- update(
+        res_reg,
+        prior = prior_sens,
+        seed = seed,
+        refresh = 0
+      )
 
       # Re-run meta-analysis of gender differences
-      res_gender <- update(res_gender, prior = prior_sens, refresh = 0)
+      res_gender <- update(
+        res_gender,
+        prior = prior_sens,
+        seed = seed,
+        refresh = 0
+      )
 

### 2022-05-16 supplement.Rmd
Add footnotes

@@
 
-```{r, r_assumed}
+```{r, correlation}
 # Compute empirical estimate of the correlation between dependent samples
@@
     Females = as.integer(round(female_percent * sample_size)),
-    Age = str_c(age_mean, "±", age_sd, sep = " "),
-    Task = task,
+    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
+    Task = as.character(task),
     `Stimulus type` = str_to_sentence(stimuli_presentation),
@@
 
+# Save the table
+dir.create(tables_dir, showWarnings = FALSE)
+write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")
+
+# Add footnotes
+colnames(tabs1)[5] <- str_c(colnames(tabs1)[5], "\\textsuperscript{a}")
+tabs1$Females[1] <- str_c(tabs1$Females[1], "\\textsuperscript{b}")
+tabs1$Task[3] <- str_c(tabs1$Task[3], "\\textsuperscript{c}")
+
 # Display the table
@@
   caption = "Experiments included in the main analysis",
-  landscape = TRUE, font_size = "scriptsize"
+  note = str_c(
+    "\\scriptsize",
+    "\\textsuperscript{a} = mean ± standard deviation, ",
+    "\\textsuperscript{b} = not available, ",
+    "\\textsuperscript{c} = violation of expectation."
+  ),
+  landscape = TRUE, font_size = "scriptsize", escape = FALSE
 )
-
-# Save the table
-dir.create(tables_dir, showWarnings = FALSE)
-write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")
 ```
@@
 
+# Save the table
+write_csv(tabs2, file = here(tables_dir, "tabs2_frequentist.csv"))
+
+# Add footnotes
+colnames(tabs2)[4] <- str_c(colnames(tabs2)[4], "\\textsuperscript{a}")
+colnames(tabs2)[7] <- str_c(colnames(tabs2)[7], "\\textsuperscript{b}")
+
 # Display the table
@@
   caption = "Frequentist meta-analyses and meta-regression",
+  note = str_c(
+    "\\scriptsize",
+    "\\textsuperscript{a} = standard error, ",
+    "\\textsuperscript{b} = 95\\% confidence interval."
+  ),
   font_size = "scriptsize",
   escape = FALSE,
-  align = "llrrrrr",
+  align = "llrrrrr"
 )
-
-# Save the table
-write_csv(tabs2, file = here(tables_dir, "tabs2_frequentist.csv"))
 ```
@@
 
+# Add footnotes
+colnames(tabs3)[6] <- str_c(colnames(tabs3)[6], "\\textsuperscript{a}")
+
 # Display the table
@@
   caption = "Jackknife (leave-one-out) analysis", font_size = "scriptsize",
+  note = "\\scriptsize\\textsuperscript{a} = intraclass correlation.",
   landscape = TRUE, escape = FALSE, align = "llrrrr"
@@
 
+# Add footnotes
+colnames(tabs5)[6] <- str_c(colnames(tabs5)[6], "\\textsuperscript{a}")
+tabs5$` `[8] <- str_c(tabs5$` `[8], "\\textsuperscript{b}")
+tabs5$` `[9] <- str_c(tabs5$` `[9], "\\textsuperscript{c}")
+tabs5$` `[10] <- str_c(tabs5$` `[10], "\\textsuperscript{d}")
+tabs5$` `[11] <- str_c(tabs5$` `[11], "\\textsuperscript{e}")
+
 # Display the table
@@
   caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
+  note = str_c(
+    "\\scriptsize",
+    "\\textsuperscript{a} = intraclass correlation, ",
+    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
+    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
+    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
+    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
+  ),
   font_size = "scriptsize", escape = FALSE, align = "llrrrr"
@@
 
+# Add footnotes
+tabs6$` `[8] <- str_c(tabs6$` `[8], "\\textsuperscript{a}")
+tabs6$` `[9] <- str_c(tabs6$` `[9], "\\textsuperscript{b}")
+tabs6$` `[10] <- str_c(tabs6$` `[10], "\\textsuperscript{c}")
+tabs6$` `[11] <- str_c(tabs6$` `[11], "\\textsuperscript{d}")
+
 # Display the table
@@
   caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
+  note = str_c(
+    "\\scriptsize",
+    "\\textsuperscript{a} = an uninformative (uniform) prior on the mean effect, ",
+    "\\textsuperscript{b} = an informative (normal) prior on the mean effect, ",
+    "\\textsuperscript{c} = an uninformative (uniform) prior on the standard deviations, ",
+    "\\textsuperscript{d} = an informative (Student-$t$) prior on the standard deviations."
+  ),
   font_size = "scriptsize", landscape = TRUE, escape = FALSE,
@@
 
+# Add footnotes
+colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "\\textsuperscript{a}")
+tabs7$` `[1] <- str_c(tabs7$` `[1], "\\textsuperscript{b}")
+tabs7$` `[2] <- str_c(tabs7$` `[2], "\\textsuperscript{c}")
+tabs7$` `[3] <- str_c(tabs7$` `[3], "\\textsuperscript{d}")
+tabs7$` `[4] <- str_c(tabs7$` `[4], "\\textsuperscript{e}")
+
 # Display the table
@@
   caption = "Sensitivity analyses for the meta-analysis of gender differences",
+  note = str_c(
+    "\\scriptsize",
+    "\\textsuperscript{a} = intraclass correlation, ",
+    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
+    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
+    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
+    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
+  ),
   font_size = "scriptsize", escape = FALSE, align = "llrrrrrrr"
@@
 # Save the tables
-write_csv(
-  tabs_correction$meta,
-  file = here(tables_dir, "tabs8_correction_meta.csv")
-)
-write_csv(
-  tabs_correction$gender,
-  file = here(tables_dir, "tabs9_correction_gender.csv")
-)
+tabs8 <- tabs_correction$meta
+tabs9 <- tabs_correction$gender
+write_csv(tabs8, file = here(tables_dir, "tabs8_correction_meta.csv"))
+write_csv(tabs9, file = here(tables_dir, "tabs9_correction_gender.csv"))
 ```
@@
 ```{r, tabs8, include=TRUE}
+# Add footnotes
+colnames(tabs8)[4] <- str_c(colnames(tabs8)[4], "\\textsuperscript{a}")
+colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "\\textsuperscript{b}")
+
 # Display the table
 apa_table(
-  tabs_correction$meta,
+  tabs8,
   caption = "Publication bias correction for the meta-analysis of mental rotation performance",
+  note = str_c(
+    "\\scriptsize",
+    "\\textsuperscript{a} = standard error, ",
+    "\\textsuperscript{b} = 95\\% confidence interval."
+  ),
   font_size = "scriptsize", escape = FALSE, align = "llrrrrr"
@@
 ```{r, tabs9, include=TRUE}
+# Add footnotes
+colnames(tabs9)[4] <- str_c(colnames(tabs9)[4], "\\textsuperscript{a}")
+colnames(tabs9)[7] <- str_c(colnames(tabs9)[7], "\\textsuperscript{b}")
+
 # Display the table
 apa_table(
-  tabs_correction$gender,
+  tabs9,
   caption = "Publication bias correction for the meta-analysis of gender differences",
+  note = str_c(
+    "\\scriptsize",
+    "\\textsuperscript{a} = standard error, ",
+    "\\textsuperscript{b} = 95\\% confidence interval."
+  ),
   font_size = "scriptsize", escape = FALSE, align = "llrrrrr",

### 2022-05-16 manuscript.Rmd
Shorten sub-headings
Create separate reference sections

@@
 
-bibliography      : "manuscript_files/references.bib"
+bibliography_main    : "manuscript_files/main.bib"
+bibliography_methods : "manuscript_files/methods.bib"
 csl                  : "manuscript_files/nature.csl"
+citeproc             : false
+link-citations       : yes
 
@@
 fontsize          : "10pt"
-output            : papaja::apa6_pdf
+
+output:
+  papaja::apa6_pdf:
+    pandoc_args: "--lua-filter=manuscript_files/multiple-bibliographies.lua"
+
 header-includes:
@@
 
-## Publication bias and certainty assessment
+## Publication bias assessment
 
@@
 
+\newpage
+\nolinenumbers
+
+# References
+
+\bigskip
+
+::: {#refs_main}
+:::
+
+\newpage
+\linenumbers
+
 # Methods
@@
 
-## Eligibility criteria
-
-Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection process and items below).
-We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
-
-```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", out.width="50%"}
+\bigskip
+
+```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", fig.pos="ht", out.width="50%"}
 # Include the flowchart (which was created manually with MS PowerPoint)
@@
 Finally, we excluded an article that was based on a sample of infants  who were substantially older compared to all other articles (1 article).
+
+## Eligibility criteria
+
+Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection process and items below).
+We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
 
@@
 
-\newpage
 \renewcommand{\arraystretch}{2}
@@
 
-## Reporting bias and certainty assessment
+## Publication bias assessment
 
@@
 
-# References
+# Methods references
 
@@
 
-<div id="refs"></div>
+::: {#refs_methods}
+:::
 

### 2022-05-16 manuscript.Rmd
Temporarily disable refitting the models

@@
 run <- list(
-  bayesian_models = TRUE,
+  bayesian_models = FALSE,
   jackknife_analysis = FALSE,

### 2022-05-16 manuscript.Rmd
Update statements

@@
   \noindent \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
-
-  \noindent We have no conflict of interest to disclose. There were no ethical concerns since we did not collect any new data.
-  Correspondence concerning this article should be addressed to Alexander Enge, Stephanstraße 1a, 04103 Leipzig, Germany. E-mail: enge@cbs.mpg.de
 
@@
 
-The data for this study is available  from an   [Open Science Framework repository](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
+The datasets generated and analyzed during the current study are available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
 This link is intended for peer review only and will be replaced with a public link upon acceptance.
@@
 
-The data for this study is available  from an   [Open Science Framework repository](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
+The analysis code for the current study is available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
 This link is intended for peer review only and will be replaced with a public link upon acceptance.
@@
 
-# Contributions
+# Author contributions
 
@@
 
+# Competing interests
+
+\noindent The authors declare no competing interests.
+
+# Corresponding author
+
+\noindent Correspondence concerning this article should be addressed to Alexander Enge, Stephanstraße 1a, 04103 Leipzig, Germany. E-mail: [enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)
+
 \newpage

### 2022-05-17 manuscript.Rmd
Update statements

@@
 The datasets generated and analyzed during the current study are available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
-This link is intended for peer review only and will be replaced with a public link upon acceptance.
+This link is intended for peer review only and will be replaced with a public DOI link upon publication.
 
@@
 The analysis code for the current study is available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
-This link is intended for peer review only and will be replaced with a public link upon acceptance.
+This link is intended for peer review only and will be replaced with a public DOI link upon publication.
 
@@
 ```
+
+- Cite all studies included in the MA
+- Change abstract and main headings
+- Move figures and tables from the methods to the supplement

### 2022-05-17 manuscript.Rmd
Cite included articles

@@
 
-In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table 1).
+In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table 1)[@antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @frick2013b; @frick2014b; @gerhard-samunda2021; @gerhard2018; @hespos1997; @kaaz2020; @kelch2021; @kellman1984; @lauer2015; @lauer2016; @mohring2013; @moore2008; @moore2011; @quinn2008; @quinn2014; @rochat1996; @schwarzer2013; @schwarzer2013a; @slone2018].
 All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985].

### 2022-05-17 manuscript.Rmd
Improve references

@@
 citeproc             : false
-link-citations       : yes
 

### 2022-05-17 manuscript.Rmd
Cross-reference Tables and Figures

@@
 
-In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table 1)[@antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @frick2013b; @frick2014b; @gerhard-samunda2021; @gerhard2018; @hespos1997; @kaaz2020; @kelch2021; @kellman1984; @lauer2015; @lauer2016; @mohring2013; @moore2008; @moore2011; @quinn2008; @quinn2014; @rochat1996; @schwarzer2013; @schwarzer2013a; @slone2018].
+In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table\ \@ref(tab:tabs1))[@antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @frick2013b; @frick2014b; @gerhard-samunda2021; @gerhard2018; @hespos1997; @kaaz2020; @kelch2021; @kellman1984; @lauer2015; @lauer2016; @mohring2013; @moore2008; @moore2011; @quinn2008; @quinn2014; @rochat1996; @schwarzer2013; @schwarzer2013a; @slone2018].
 All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985].
@@
 Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
-Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.
-1).
+Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)).
 The probability for this effect being greater than zero was `r print_perc(hyp_meta$Post.Prob)`.
@@
 
-As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig. 2).
+As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig.\ \@ref(fig:fig2)).
 Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$, 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
@@
 To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.
-1) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
+Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
 The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
@@
 We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here.
-For the meta-analysis of mental rotation performance (Fig.
-3a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
+For the meta-analysis of mental rotation performance (Fig.\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
 This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
-Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table 3).
-For the meta-analysis of gender differences in mental rotation performance (Fig.
-3b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table\ \@ref(tab:tabs3)).
+For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
 In the present meta-analysis we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021].
-The PRISMA flowchart is provided in Fig.
-4 and Supplementary Table 4 contains the PRISMA checklist.
+The PRISMA flowchart is provided in (Fig.\ \@ref(fig:fig4)) and Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.
 
@@
 We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Figure 4a).
+This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Fig.\ \@ref(fig:fig4)).
 We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills [@frick2014; @johnson2020; @kubicek2018; @lauer2019a; @linn1985; @moore2020; @uttal2013; @voyer1995; @yang2020].
@@
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.
-4).
+This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.\ \@ref(fig:fig4)).
 
@@
 Moreover, we disregarded effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of `r descriptives$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table 1) and 30 articles being included in the meta-analysis of gender differences in mental rotation performance.
+This procedure led to a total of `r descriptives$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table\ \@ref(tab:tabs1)) and 30 articles being included in the meta-analysis of gender differences in mental rotation performance.
 
@@
 We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Table 5).
+A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Table\ \@ref(tab:tabs5)).
 
@@
 We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for all standard deviations [@williams2018].
-A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 5).
+A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table\ \@ref(tab:tabs5)).
 For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect measures above).
@@
 Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r formatC(n_iter, big.mark = ",")` draws (including `r formatC(n_warmup, big.mark = ",")` warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig.
-2) [@vehtari2021].
+To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig.\ \@ref(fig:figs2)) [@vehtari2021].
 For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].
@@
 We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression.
-To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table 5).
+To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs5)).
 These models were fitted using restricted maximum likelihood estimation (REML).
-To verify that the REML converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; Supplementary Fig.
-3).
+To verify that the REML converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; Supplementary Fig.\ \@ref(fig:figs3)).
 
@@
 To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.
-We then checked if the meta-analytic effect size and heterogeneity remained constant or if it was sensitive against the influence of any individual experiment (Supplementary Table 3).
-
-We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables 8 and 9; Supplementary Figure 4) [@duval2000; @vevea1995; @vevea2005].
+We then checked if the meta-analytic effect size and heterogeneity remained constant or if it was sensitive against the influence of any individual experiment (Supplementary Table\ \@ref(tab:tabs3)).
+
+We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables\ \@ref(tab:tabs8) and \@ref(tab:tabs9); Supplementary Fig.\ \@ref(fig:figs4)) [@duval2000; @vevea1995; @vevea2005].
 

### 2022-05-17 supplement.Rmd
Cross-reference Tables and Figures

@@
 This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
-To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Table 4).
+To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Table\ \@ref(tab:tabs4)).
 
@@
 
-(ref:figs4-caption) **Trim-and-fill analyses.** As in Figure 3 in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
+(ref:figs4-caption) **Trim-and-fill analyses.** As in Fig.\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
 The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines).

### 2022-05-17 supplement.Rmd
Cross-reference Tables and Figures

@@
 In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments.
-This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables 8 and 9).
+This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs8) and \@ref(tab:tabs9); Supplementary Fig.\ \@ref(fig:figs4)).
 
@@
 Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
-These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables 8 and 9).
+These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables\ \@ref(tab:tabs8) and \@ref(tab:tabs9)).
 

### 2022-05-17 manuscript.Rmd
Add frequentist analyses to results
Move methods tables to the supplement

@@
 This means that `r print_perc(summ_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_gender$icc)` to differences between experiments *within* articles.
+The results obtained from our Bayesian analyses were reproduced by classical frequentist three-level meta-analysis and meta-regression models (Supplementary Table\ \@ref(tab:tabs2)).
 
@@
 Outcome measures and other relevant variables were extracted from each article by one of three raters and verified by a second rater.
-For the meta-analysis of mental rotation performance, outcome measures were any summary statistic (Table 1) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
-Other extracted variables included, if available, the sample size, the number of males and females, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habituation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table 1).
-
-\renewcommand{\arraystretch}{2}
-\singlespacing
-\scriptsize
-
-+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| Available statistics                                           | Conversion to standardized mean difference (Hedges' $g$)                                    |
-+================================================================+=============================================================================================+
-| (1\) Cohen's $d$ and sample size                               | ${df}=2(n-1)$;\quad                                                                         |
-| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
-|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
-+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| (2\) $t$-statistic and sample size [@rosenthal1991]            | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
-+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| (3\) $F$-statistic and sample size [@lakens2013]               | $t=\sqrt{f}$;\quad then (2\)                                                                |
-+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| (4\) Mean difference between conditions [@lakens2013]          | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
-+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| (5\) Mean looking time and ${SD}$ per condition [@cumming2012] | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
-|                                                                | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
-+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| (6\) Mean novelty preference score [@lakens2013]               | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
-+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-
-Table: Extracted between-article summary statistics and conversion to effect sizes
-
-\doublespacing
-\normalsize
+For the meta-analysis of mental rotation performance, outcome measures were any summary statistic (Supplementary Table\ \@ref(tab:tabs5)) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
+Other extracted variables included, if available, the sample size, the number of males and females, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habituation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table\ \@ref(tab:tabs1)).
 
 We also conducted a meta-analysis of the gender differences in mental rotation performance observed within the original articles.
-For this analysis, the outcome measures were any summary statistic (Table 2) that could be used to determine the standardized mean difference between male infants' mental rotation performance and female infants' mental rotation performance.
+For this analysis, the outcome measures were any summary statistic (Supplementary Table\ \@ref(tab:tabs6)) that could be used to determine the standardized mean difference between male infants' mental rotation performance and female infants' mental rotation performance.
 Other extracted variables included the sample size, the mean age and its standard deviation, and the minimum and maximum age of each gender group.
 
-\singlespacing
-\scriptsize
-
-+----------------------------------------+--------------------------------------------------------------------------------------------------+
-| Available statistics                   | Conversion to standardized mean difference (Hedges' $g$)                                         |
-+========================================+==================================================================================================+
-| (1\) Cohen's $d$ and group sizes       | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
-| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
-|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
-+----------------------------------------+--------------------------------------------------------------------------------------------------+
-| (2\) $t$-statistic and group sizes     | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
-| [@lakens2013]                          |                                                                                                  |
-+----------------------------------------+--------------------------------------------------------------------------------------------------+
-| (3\) $F$-statistic and group sizes     | $t=\sqrt{f}$;\quad then (2\)                                                                     |
-| [@lakens2013]                          |                                                                                                  |
-+----------------------------------------+--------------------------------------------------------------------------------------------------+
-| (4\) Mean differences between          | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
-| conditions or preference scores        | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
-| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
-+----------------------------------------+--------------------------------------------------------------------------------------------------+
-
-Table: Extracted within-article summary statistics and conversion to effect sizes
-
-\doublespacing
-\normalsize
-
 No investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
@@
 
-For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Table 1.
-The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Table 1.
+For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5).
+The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs5).
 The correlation $r$ was not reported in any of the original articles [@harrer2021].
 We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Table\ \@ref(tab:tabs5)).
-
-For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between non-redundant male and female groups of infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Table 2.
-The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$), and $J(df)$ is the correction factor for small samples as described in Row (1) of Table 2.
+A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Tables\ \@ref(tab:tabs7) and\ \@ref(tab:tabs8)).
+
+For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between non-redundant male and female groups of infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs6).
+The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$), and $J(df)$ is the correction factor for small samples as described in Row (1) of Supplementary Table\ \@ref(tab:tabs6).
 
@@
 We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for all standard deviations [@williams2018].
-A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table\ \@ref(tab:tabs5)).
+A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Tables\ \@ref(tab:tabs7), \@ref(tab:tabs8), and\ \@ref(tab:tabs9)).
 For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect measures above).
@@
 We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression.
-To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs5)).
+To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs2)).
 These models were fitted using restricted maximum likelihood estimation (REML).
@@
 
-We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables\ \@ref(tab:tabs8) and \@ref(tab:tabs9); Supplementary Fig.\ \@ref(fig:figs4)) [@duval2000; @vevea1995; @vevea2005].
+We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs4)) [@duval2000; @vevea1995; @vevea2005].
 
@@
 ```
-
-- Cite all studies included in the MA
-- Change abstract and main headings
-- Move figures and tables from the methods to the supplement

### 2022-05-17 supplement.Rmd
Move methods tables to the supplement

--- 2022-05-17 supplement.Rmd
@@
 This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
-To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Table\ \@ref(tab:tabs4)).
+To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Tables\ \@ref(tab:tabs7) and \@ref(tab:tabs8)).
 
@@
 In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments.
-This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables 8 and 9).
+This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs4)).
 
@@
 Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
-These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables 8 and 9).
+These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)).
 
@@
 
+\renewcommand{\arraystretch}{1.30}
+\scriptsize
+\LTcapwidth=\textwidth
+
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| \ \ Available statistics                                       | Conversion to standardized mean difference (Hedges' $g$)                                    |
++================================================================+=============================================================================================+
+| \ \ (1\) Cohen's $d$ and sample size                           | ${df}=2(n-1)$;\quad                                                                         |
+| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
+|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| \ \ (2\) $t$-statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| \ \ (3\) $F$-statistic and sample size [@lakens2013]           | $t=\sqrt{f}$;\quad then (2\)                                                                |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| \ \ (4\) Mean difference between conditions [@lakens2013]      | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| \ \ (5\) Mean looking time and ${SD}$ per condition            | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
+| [@cumming2012]                                                 | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+| \ \ (6\) Mean novelty preference score [@lakens2013]           | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
++----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
+
+Table: (\#tab:tabs5) Effect size conversion for the meta-analysis of mental rotation performance
+
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+| \ \ Available statistics               | Conversion to standardized mean difference (Hedges' $g$)                                         |
++========================================+==================================================================================================+
+| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
+| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
+|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+| \ \ (2\) $t$-statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
+| [@lakens2013]                          |                                                                                                  |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+| \ \ (3\) $F$-statistic and group sizes | $t=\sqrt{f}$;\quad then (2\)                                                                     |
+| [@lakens2013]                          |                                                                                                  |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+| \ \ (4\) Mean differences between\     | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
+| \ \ conditions or preference scores    | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
+| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
++----------------------------------------+--------------------------------------------------------------------------------------------------+
+
+Table: (\#tab:tabs6) Effect size conversion for the meta-analysis of gender differences
+
+\normalsize
+
 ```{r, sensitivity}
@@
       )
-    }) -> tabs5
-  write_csv(tabs5, file = here(tables_dir, "tabs5_sens_meta.csv"))
+    }) -> tabs7
+  write_csv(tabs7, file = here(tables_dir, "tabs7_sens_meta.csv"))
 
@@
       )
-    }) -> tabs6
-  write_csv(tabs6, file = here(tables_dir, "tabs6_sens_reg.csv"))
+    }) -> tabs8
+  write_csv(tabs8, file = here(tables_dir, "tabs8_sens_reg.csv"))
 
@@
       )
-    }) -> tabs7
-  write_csv(tabs7, file = here(tables_dir, "tabs7_sens_gender.csv"))
+    }) -> tabs9
+  write_csv(tabs9, file = here(tables_dir, "tabs9_sens_gender.csv"))
 }
@@
 
-```{r, tabs5, include=TRUE}
+```{r, tabs7, include=TRUE}
 # Load sensitivity analysis table from file
-tabs5 <- read_csv(
-  here(tables_dir, "tabs5_sens_meta.csv"),
+tabs7 <- read_csv(
+  here(tables_dir, "tabs7_sens_meta.csv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 # Add footnotes
-colnames(tabs5)[6] <- str_c(colnames(tabs5)[6], "\\textsuperscript{a}")
-tabs5$` `[8] <- str_c(tabs5$` `[8], "\\textsuperscript{b}")
-tabs5$` `[9] <- str_c(tabs5$` `[9], "\\textsuperscript{c}")
-tabs5$` `[10] <- str_c(tabs5$` `[10], "\\textsuperscript{d}")
-tabs5$` `[11] <- str_c(tabs5$` `[11], "\\textsuperscript{e}")
+colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "\\textsuperscript{a}")
+tabs7$` `[8] <- str_c(tabs7$` `[8], "\\textsuperscript{b}")
+tabs7$` `[9] <- str_c(tabs7$` `[9], "\\textsuperscript{c}")
+tabs7$` `[10] <- str_c(tabs7$` `[10], "\\textsuperscript{d}")
+tabs7$` `[11] <- str_c(tabs7$` `[11], "\\textsuperscript{e}")
 
@@
 apa_table(
-  tabs5,
+  tabs7,
   caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
@@
   ),
-  font_size = "scriptsize", escape = FALSE, align = "llrrrr"
-)
-```
-
-```{r, tabs6, include=TRUE}
+  placement = "hb", font_size = "scriptsize", escape = FALSE, align = "llrrrr"
+)
+```
+
+\renewcommand{\arraystretch}{0.97}
+
+```{r, tabs8, include=TRUE}
 # Load sensitivity analysis table from file
-tabs6 <- read_csv(
-  here(tables_dir, "tabs6_sens_reg.csv"),
+tabs8 <- read_csv(
+  here(tables_dir, "tabs8_sens_reg.csv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 # Add footnotes
-tabs6$` `[8] <- str_c(tabs6$` `[8], "\\textsuperscript{a}")
-tabs6$` `[9] <- str_c(tabs6$` `[9], "\\textsuperscript{b}")
-tabs6$` `[10] <- str_c(tabs6$` `[10], "\\textsuperscript{c}")
-tabs6$` `[11] <- str_c(tabs6$` `[11], "\\textsuperscript{d}")
+tabs8$` `[8] <- str_c(tabs8$` `[8], "\\textsuperscript{a}")
+tabs8$` `[9] <- str_c(tabs8$` `[9], "\\textsuperscript{b}")
+tabs8$` `[10] <- str_c(tabs8$` `[10], "\\textsuperscript{c}")
+tabs8$` `[11] <- str_c(tabs8$` `[11], "\\textsuperscript{d}")
 
@@
 apa_table(
-  tabs6,
+  tabs8,
   caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
@@
 
-```{r, tabs7, include=TRUE}
+```{r, tabs9, include=TRUE}
 # Load sensitivity analysis table from file
-tabs7 <- read_csv(
-  here(tables_dir, "tabs7_sens_gender.csv"),
+tabs9 <- read_csv(
+  here(tables_dir, "tabs9_sens_gender.csv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 # Add footnotes
-colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "\\textsuperscript{a}")
-tabs7$` `[1] <- str_c(tabs7$` `[1], "\\textsuperscript{b}")
-tabs7$` `[2] <- str_c(tabs7$` `[2], "\\textsuperscript{c}")
-tabs7$` `[3] <- str_c(tabs7$` `[3], "\\textsuperscript{d}")
-tabs7$` `[4] <- str_c(tabs7$` `[4], "\\textsuperscript{e}")
+colnames(tabs9)[6] <- str_c(colnames(tabs9)[6], "\\textsuperscript{a}")
+tabs9$` `[1] <- str_c(tabs9$` `[1], "\\textsuperscript{b}")
+tabs9$` `[2] <- str_c(tabs9$` `[2], "\\textsuperscript{c}")
+tabs9$` `[3] <- str_c(tabs9$` `[3], "\\textsuperscript{d}")
+tabs9$` `[4] <- str_c(tabs9$` `[4], "\\textsuperscript{e}")
 
@@
 apa_table(
-  tabs7,
+  tabs9,
   caption = "Sensitivity analyses for the meta-analysis of gender differences",
@@
 # Save the tables
-tabs8 <- tabs_correction$meta
-tabs9 <- tabs_correction$gender
-write_csv(tabs8, file = here(tables_dir, "tabs8_correction_meta.csv"))
-write_csv(tabs9, file = here(tables_dir, "tabs9_correction_gender.csv"))
-```
-
-```{r, tabs8, include=TRUE}
+tabs10 <- tabs_correction$meta
+tabs11 <- tabs_correction$gender
+write_csv(tabs10, file = here(tables_dir, "tabs10_correction_meta.csv"))
+write_csv(tabs11, file = here(tables_dir, "tabs11_correction_gender.csv"))
+```
+
+```{r, tabs10, include=TRUE}
 # Add footnotes
-colnames(tabs8)[4] <- str_c(colnames(tabs8)[4], "\\textsuperscript{a}")
-colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "\\textsuperscript{b}")
+colnames(tabs10)[4] <- str_c(colnames(tabs10)[4], "\\textsuperscript{a}")
+colnames(tabs10)[7] <- str_c(colnames(tabs10)[7], "\\textsuperscript{b}")
 
@@
 apa_table(
-  tabs8,
+  tabs10,
   caption = "Publication bias correction for the meta-analysis of mental rotation performance",
@@
 
-```{r, tabs9, include=TRUE}
+```{r, tabs11, include=TRUE}
 # Add footnotes
-colnames(tabs9)[4] <- str_c(colnames(tabs9)[4], "\\textsuperscript{a}")
-colnames(tabs9)[7] <- str_c(colnames(tabs9)[7], "\\textsuperscript{b}")
+colnames(tabs11)[4] <- str_c(colnames(tabs11)[4], "\\textsuperscript{a}")
+colnames(tabs11)[7] <- str_c(colnames(tabs11)[7], "\\textsuperscript{b}")
 
@@
 apa_table(
-  tabs9,
+  tabs11,
   caption = "Publication bias correction for the meta-analysis of gender differences",
@@
 ```
+
+\newpage
 

### 2022-05-17 manuscript.Rmd
Move methods figure to the supplement

@@
 In the present meta-analysis we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021].
-The PRISMA flowchart is provided in (Fig.\ \@ref(fig:fig4)) and Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.
-
-\bigskip
-
-```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", fig.pos="ht", out.width="50%"}
-# Include the flowchart (which was created manually with MS PowerPoint)
-knitr::include_graphics(here("manuscript_files/flowchart.pdf"))
-```
-
-(ref:fig4-caption) **Literature search and selection process.** **a,** We searched four online databases as well as reviews and reference sections to identify articles in which mental rotation experiments in infants were reported.
-**b,** Experiments were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
-**c,** Redundant articles comprising the same experiment(s) were excluded.
-Additionally, we excluded an article that was based on an uncommon experimental paradigm differing substantially from all other articles (1 article).
-Finally, we excluded an article that was based on a sample of infants  who were substantially older compared to all other articles (1 article).
+The PRISMA flowchart is provided in Supplementary Fig.\ \@ref(fig:figs2) and Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.
 
@@
 Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r formatC(n_iter, big.mark = ",")` draws (including `r formatC(n_warmup, big.mark = ",")` warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig.\ \@ref(fig:figs2)) [@vehtari2021].
+To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig.\ \@ref(fig:figs3)) [@vehtari2021].
 For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].
@@
 These models were fitted using restricted maximum likelihood estimation (REML).
-To verify that the REML converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; Supplementary Fig.\ \@ref(fig:figs3)).
+To verify that the REML converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; Supplementary Fig.\ \@ref(fig:figs4)).
 
@@
 
-We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs4)) [@duval2000; @vevea1995; @vevea2005].
+We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs5)) [@duval2000; @vevea1995; @vevea2005].
 

### 2022-05-17 supplement.Rmd
Move methods figure to the supplement

@@
 In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments.
-This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs4)).
+This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs5)).
 
@@
 
-```{r, figs2, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs2-caption)"}
+```{r, figs2, include=TRUE, fig.width=6, fig.cap="(ref:figs2-caption)", fig.pos="ht", out.width="50%"}
+# Include the flowchart (which was created manually with MS PowerPoint)
+knitr::include_graphics(here("manuscript_files/flowchart.pdf"))
+```
+
+(ref:figs2-caption) **Literature search and selection process.** **a,** We searched four online databases as well as reviews and reference sections to identify articles in which mental rotation experiments in infants were reported.
+**b,** Experiments were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
+**c,** Redundant articles comprising the same experiment(s) were excluded.
+Additionally, we excluded an article that was based on an uncommon experimental paradigm differing substantially from all other articles (1 article).
+Finally, we excluded an article that was based on a sample of infants  who were substantially older compared to all other articles (1 article).
+
+```{r, figs3, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs3-caption)"}
 # Extract convergence statistics (Rhat, Neff) from Bayesian results
@@
 # Save the plot
-ggsave(here(figures_dir, "figs2_convergence.pdf"), width = 12, height = 6)
-```
-
-(ref:figs2-caption) **Convergence checks for the Bayesian meta-analysis.** For each of the three parameters in the three-level meta-analytic model, gray traces show the exploration of the posterior distribution by four independent Markov Chain Monte Carlo (MCMC) chains.
+ggsave(here(figures_dir, "figs3_convergence.pdf"), width = 12, height = 6)
+```
+
+(ref:figs3-caption) **Convergence checks for the Bayesian meta-analysis.** For each of the three parameters in the three-level meta-analytic model, gray traces show the exploration of the posterior distribution by four independent Markov Chain Monte Carlo (MCMC) chains.
 Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution.
@@
 
-```{r, figs3, include=TRUE, fig.height=4, fig.width=12, fig.cap="(ref:figs3-caption)"}
+```{r, figs4, include=TRUE, fig.height=4, fig.width=12, fig.cap="(ref:figs4-caption)"}
 # Combine frequentist profile likelihood results into one data frame
@@
 # Save the plot
-ggsave(here(figures_dir, "figs3_convergence_freq.pdf"), width = 12, height = 4)
-```
-
-(ref:figs3-caption) **Convergence checks for the frequentist meta-analysis.** Black curves show the profile of the restricted log likelihood for the two variance components in the frequentist three-level model.
+ggsave(here(figures_dir, "figs4_convergence_freq.pdf"), width = 12, height = 4)
+```
+
+(ref:figs4-caption) **Convergence checks for the frequentist meta-analysis.** Black curves show the profile of the restricted log likelihood for the two variance components in the frequentist three-level model.
 The two peaks indicate that restricted maximum likelihood estimation (REML) was able to converge on the most likely parameter estimates [@raue2009; @viechtbauer2010].
 
-```{r, figs4, include=TRUE, fig.width=12, fig.height=3.5, fig.cap="(ref:figs4-caption)"}
+```{r, figs5, include=TRUE, fig.width=12, fig.height=3.5, fig.cap="(ref:figs5-caption)"}
 # Create new funnel plots that take the trim-and-fill results into account
@@
 # Save the plot
-ggsave(here(figures_dir, "funnel_trim_fill.pdf"), width = 12, height = 3.5)
-```
-
-(ref:figs4-caption) **Trim-and-fill analyses.** As in Fig.\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
+ggsave(
+  here(figures_dir, "figs5_funnel_trim_fill.pdf"),
+  width = 12, height = 3.5
+)
+```
+
+(ref:figs5-caption) **Trim-and-fill analyses.** As in Fig.\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
 The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines).

### 2022-05-17 manuscript.Rmd
Make headings comply with formatting guidelines

@@
   - name          : "Alexander Enge"
-    affiliation   : "1,2"
+    affiliation   : "1,2,*"
   - name          : "Shreya Kapoor"
@@
     institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, Berlin, Germany"
+  - id            : "*"
+    institution   : "Corresponding author (enge@cbs.mpg.de)"
 
@@
 
-# Introduction
+# Main
 
@@
 
-# Results
-
 ## Mental rotation performance
@@
 
-# Discussion
+## Discussion
 
@@
 
-## Effect size estimates
-
 We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
@@
 
-## Gender differences
-
 The gender differences observed here remain to be explained by interacting genetic and environmental factors that are largely unknown.
@@
 Possible biological developmental pathways, however, bridging the gap from hormonal to behavioral differences are currently far from understood.
-
-## Additional factors
 
@@
 Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].
-
-# Conclusion
 
@@
 
-\noindent M.A.S. conceived, designed, and obtained funding for the study.
-
-\noindent A.E., S.K., and A.-S.K.
-designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results in consultation with M.A.S.
-
-\noindent A.E. and M.A.S. wrote the manuscript with additional input from S.K. and A.-S.K.
+M.A.S.
+conceived, designed, and obtained funding for the study.
+A.E., S.K., and A.-S.K.
+(in consultation with M.A.S.) designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results.
+A.E.
+and M.A.S.
+wrote the manuscript with additional input from S.K.
+and A.-S.K.
 
@@
 
-\noindent The authors declare no competing interests.
-
-# Corresponding author
-
-\noindent Correspondence concerning this article should be addressed to Alexander Enge, Stephanstraße 1a, 04103 Leipzig, Germany. E-mail: [enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)
+The authors declare no competing interests.
+
+# Additional information
+
+Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
 

### 2022-05-17 manuscript.Rmd
Remove page break after abstract

@@
     institution   : "Corresponding author (enge@cbs.mpg.de)"
-
-authornote: |
-  \noindent \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
-
-  \noindent \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
-
-  \noindent \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
-
-abstract: |
-  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
-We robustly found that male infants recognized novel rotated objects more reliably than female infants.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
 
@@
 
+# Abstract
+
+Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
+On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
+When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
+Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
+We robustly found that male infants recognized novel rotated objects more reliably than female infants.
+These findings indicate that gender differences in mental rotation are already present in the first months of life.
+
 # Main
@@
 In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
-
-Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average longer in male compared to female infants.
-Effect sizes were assumed to be small.
 
@@
 
-\newpage
+Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average longer in male compared to female infants.
+Effect sizes were assumed to be small.
 
@@
 This means that `r print_perc(summ_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_gender$icc)` to differences between experiments *within* articles.
+
 The results obtained from our Bayesian analyses were reproduced by classical frequentist three-level meta-analysis and meta-regression models (Supplementary Table\ \@ref(tab:tabs2)).

### 2022-05-17 manuscript.Rmd
Merge split reference sections again

@@
 
-bibliography_main    : "manuscript_files/main.bib"
-bibliography_methods : "manuscript_files/methods.bib"
+bibliography      : "manuscript_files/references.bib"
 csl               : "manuscript_files/nature.csl"
-citeproc             : false
 
@@
 fontsize          : "10pt"
-
-output:
-  papaja::apa6_pdf:
-    pandoc_args: "--lua-filter=manuscript_files/multiple-bibliographies.lua"
+output            : "papaja::apa6_pdf"
 
@@
 
-\newpage
-\nolinenumbers
-
-# References
-
-\bigskip
-
-::: {#refs_main}
-:::
-
-\newpage
-\linenumbers
-
 # Methods
@@
 
-# Methods references
+# References
 
@@
 
-::: {#refs_methods}
-:::
+<div id="refs"></div>
 
 \newpage
-\linenumbers
 
@@
 
-M.A.S.
+\noindent M.A.S.
 conceived, designed, and obtained funding for the study.
@@
 
-The authors declare no competing interests.
-
-# Additional information
-
-Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
+\noindent The authors declare no competing interests.
+
+# Materials & Correspondence
+
+\noindent Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
 

### 2022-05-17 manuscript.Rmd
Improve formatting of frequentist statistics

@@
     d_z_t = t / sqrt(sample_size),
-    # Add d_z from ANOVA F-statistic via conversion to a t-statistic
+    # Add d_z from ANOVA F statistic via conversion to a t statistic
     d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
@@
 
-    # Re-code non-significant F-statistics as an effect size of d = 0
+    # Re-code non-significant F statistics as an effect size of d = 0
     f = as.numeric(f),
@@
 
-    # Add d from ANOVA F-statistic via conversion to a t-statistic
+    # Add d from ANOVA F statistic via conversion to a t statistic
     d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),
@@
 For the meta-analysis of mental rotation performance (Fig.\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
-This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
+This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $P = `r print_num(egger_meta$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
 Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table\ \@ref(tab:tabs3)).
-For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
 One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles.
-Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, 1)` months; $z = `r descs_pedrett2020$z`$ compared to all articles).
+Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, digits = 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, digits = 1)` months; $Z = `r descs_pedrett2020$z`$ compared to all articles).
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.\ \@ref(fig:fig4)).
+This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.\ \@ref(fig:figs2)).
 

### 2022-05-17 supplement.Rmd
Merge split reference sections again
Improve formatting of frequentist statistics

@@
 
-<!-- Restart numbering of figures, tables, equations, and pages -->
+<!-- Restart numbering of figures and tables -->
 \renewcommand{\thefigure}{\arabic{figure}}
 \renewcommand{\thetable}{\arabic{table}}
-\renewcommand{\theequation}{\arabic{table}}
 \setcounter{figure}{0}
 \setcounter{table}{0}
-\setcounter{equation}{0}
+
+<!-- Restart page and line numbers -->
 \setcounter{page}{1}
+\resetlinenumber
+\linenumbers
 
@@
 In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis.
-These models were based on the assumption that experiments yielding significant effects (i.e., small *p*-values) are more likely to get published.
-Specifically, we ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30.
+These models were based on the assumption that experiments yielding significant effects (i.e., small $P$ values) are more likely to get published.
+Specifically, we ran one selection model assuming a weight function with fixed $P$ value cutoffs [@vevea1995] at $P$ = .01, $P$ = .05, and $P$ = .30.
 Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
@@
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (2\) $t$-statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
+| \ \ (2\) $t$ statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (3\) $F$-statistic and sample size [@lakens2013]           | $t=\sqrt{f}$;\quad then (2\)                                                                |
+| \ \ (3\) $F$ statistic and sample size [@lakens2013]           | $t=\sqrt{f}$;\quad then (2\)                                                                |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
@@
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| \ \ (2\) $t$-statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
+| \ \ (2\) $t$ statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
 | [@lakens2013]                          |                                                                                                  |
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| \ \ (3\) $F$-statistic and group sizes | $t=\sqrt{f}$;\quad then (2\)                                                                     |
+| \ \ (3\) $F$ statistic and group sizes | $t=\sqrt{f}$;\quad then (2\)                                                                     |
 | [@lakens2013]                          |                                                                                                  |

### 2022-05-17 manuscript_files/helper_functions.R

@@ -13,21 +13,14 @@ print_days_months <- function(days, long = FALSE) {
 # Formatting percentages with one decimal place
 print_perc <- function(x) scales::percent(x, accuracy = 0.1)
 
-# Formatting numbers with a certain number of decimal places
-print_num <- function(x, digits = 2) {
-  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
-  x[x == "NA"] <- NA
-  return(x)
-}
-
 # Format confidence interval
 print_ci <- function(lb, ub) {
-  paste0("[", print_num(lb), ", ", print_num(ub), "]")
+  paste0("[", papaja::print_num(lb), ", ", papaja::print_num(ub), "]")
 }
 
 # Format mean value and confidence interval
 print_mean_ci <- function(mean, lb, ub) {
-  paste(print_num(mean), print_ci(lb, ub))
+  paste(papaja::print_num(mean), print_ci(lb, ub))
 }
 
 # Format results of Bayesian meta-analysis as a table with optional labels
@@ -101,8 +94,8 @@ print_res_freq_table <- function(res_freq,
     Parameter = rownames(res_freq$b),
     Estimate = print_num(as.numeric(res_freq$b)),
     `$SE$` = print_num(res_freq$se),
-    `$z$` = print_num(res_freq$zval),
-    `$p$` = ifelse(
+    `$Z$` = print_num(res_freq$zval),
+    `$P$` = ifelse(
       res_freq$pval < 0.001, "< 0.001", print_num(res_freq$pval, digits = 3)
     ),
     ci_lower = print_num(res_freq$ci.lb),

### 2022-05-18 manuscript.Rmd
Proof reading by A.E.

@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
   - \usepackage[all]{nowidow}
+  - \usepackage{lineno}
   - \usepackage{makecell}
@@
     age_c = age - mean(age, na.rm = TRUE),
-    age_sd = age_sd / 365.25,
 
@@
 
+\linenumbers
+
 # Abstract
 
-Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
+Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
 On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
@@
 Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
-We robustly found that male infants recognized novel rotated objects more reliably than female infants.
+We robustly found that male infants recognized rotated objects more reliably than female infants.
 These findings indicate that gender differences in mental rotation are already present in the first months of life.
@@
 Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
-Interestingly, a recent meta-analysis [@lauer2019a] in 3-17-year-old children and adolescents suggests even only a small-to-medium difference (mean weighted $g = 0.39$).
+Interestingly, a recent meta-analysis in 3-17-year-old children and adolescents [@lauer2019a] suggests even only a small-to-medium difference (mean weighted $g = 0.39$).
 Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
@@
 All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985].
-These experiments comprised real world stimuli (e.g., toy objects [@antrilli2016]), three-dimensional digital stimuli (e.g., cube figures [@moore2008]), or two-dimensional digital stimuli (e.g., digits [@quinn2008]).
+These experiments comprised real world stimuli (e.g., toy objects) [@antrilli2016], three-dimensional digital stimuli (e.g., cube figures) [@moore2008], or two-dimensional digital stimuli (e.g., digits) [@quinn2008].
 In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object.
@@
       "Effect size",
-      "Lower",
-      "Upper"
+      "2.5%",
+      "97.5%"
     ),
@@
 
-Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average longer in male compared to female infants.
-Effect sizes were assumed to be small.
-
-## Mental rotation performance
-
 (ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
@@
 Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI).
-These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the model.
+These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the data.
 The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
 
-For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects.
-Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
+Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average longer in male compared to female infants.
+Effect sizes were assumed to be small.
+
+## Mental rotation performance
+
+For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects.
+Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
 Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)).
-The probability for this effect being greater than zero was `r print_perc(hyp_meta$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level.
-Therefore, approximately `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.
+The probability for this effect being greater than zero was $\approx$ `r print_perc(hyp_meta$Post.Prob)`.
+The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level.
+Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.
 
@@
 
-To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
+To confirm the gender difference between males and females, we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between male and female infants reported *within* each experiment by the original authors.
 Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
-This means that `r print_perc(summ_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_gender$icc)` to differences between experiments *within* articles.
+The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
+Therefore, `r print_perc(1 - summ_gender$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_gender$icc)` was attributable to differences *between* articles.
 
@@
 This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $P = `r print_num(egger_meta$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
-Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table\ \@ref(tab:tabs3)).
-For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)).
+For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
         labels = c(
-          expression(italic(p) > .05),
-          expression(italic(p) < .05),
-          expression(italic(p) < .01)
+          expression(italic(P) > 0.05),
+          expression(italic(P) < 0.05),
+          expression(italic(P) < 0.01)
         )
@@
 Gray shades indicate a 95% pseudo-confidence interval (dark gray) and a 99% pseudo-confidence interval (light gray) under the null hypothesis.
-These shades thus illustrate which of the original studies observed a significant effect.
-For the meta-analysis of mental rotation performance, a slight asymmetry induced by the underrepresentation of studies with high standard errors and small effect sizes suggests a small publication bias.
+These shades thus illustrate which of the original experiments observed a significant effect.
+For the meta-analysis of mental rotation performance, a slight asymmetry induced by the underrepresentation of experiments with high standard errors and small effect sizes suggests a small publication bias.
 
@@
 To this end, we scrutinized the robustness of `r descriptives$n_experiments` experimental effect sizes.
-We found that male infants looked on average longer at novel rotated objects compared to female infants.
+We found that on average, male infants looked longer at novel rotated objects compared to female infants.
 This effect was small and unrelated to age in the current range.
@@
 We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
-The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference more likely report separate effect sizes for males and females.
+The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference would be more likely report separate effect sizes for males and females.
 In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_gender$intercept`$) can be viewed as a lower bound of the true effect size.
@@
 Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance [@toivainen2018; @constantinescu2018; @erdmann2019].
-Possible biological developmental pathways, however, bridging the gap from hormonal to behavioral differences are currently far from understood.
+However, possible biological developmental pathways, bridging the gap from hormonal to behavioral differences, are currently far from understood.
 
@@
 This relation also applies to previous experience with manually rotating toys [@schwarzer2013a].
-While these preliminary results require replication they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g.
+While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g.
 [@ausubel1968; @bradley1983; @halberda2008]).
@@
 
-In the present meta-analysis we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021].
-The PRISMA flowchart is provided in Supplementary Fig.\ \@ref(fig:figs2) and Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.
+In the present meta-analysis, we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021].
+The PRISMA flowchart is provided in Supplementary Fig.\ \@ref(fig:figs2) while Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.
 
@@
 
-We entered the search terms (“mental rotation” OR “mental transformation” OR “spatial rotation” OR “spatial transformation” OR “spatial ability” OR “spatial skills”) AND (“infant” OR “infants” OR “infanthood” OR “toddler” OR “toddlers” OR “toddlerhood” OR “child” OR “children” OR “childhood” OR “month” OR “months”) into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, and ProQuest Dissertations & Theses Global).
+We entered the search terms ("mental rotation" OR "mental transformation" OR "spatial rotation" OR "spatial transformation" OR "spatial ability" OR "spatial skills") AND ("infant" OR "infants" OR "infanthood" OR "toddler" OR "toddlers" OR "toddlerhood" OR "child" OR "children" OR "childhood" OR "month" OR "months") into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, and ProQuest Dissertations & Theses Global).
 All database queries were completed on December 6, 2021.
 We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Fig.\ \@ref(fig:fig4)).
+This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Fig.\ \@ref(fig:figs2)).
 We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills [@frick2014; @johnson2020; @kubicek2018; @lauer2019a; @linn1985; @moore2020; @uttal2013; @voyer1995; @yang2020].
@@
 For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5).
-The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2*(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs5).
+The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs5).
 The correlation $r$ was not reported in any of the original articles [@harrer2021].
-We therefore always assumed a correlation of $r = .50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx .50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from $r = -.90$ via $r = .00$ to $r = .90$ had no meaningful impact on the meta-analytic effect size (Supplementary Tables\ \@ref(tab:tabs7) and\ \@ref(tab:tabs8)).
-
-For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between non-redundant male and female groups of infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs6).
-The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$), and $J(df)$ is the correction factor for small samples as described in Row (1) of Supplementary Table\ \@ref(tab:tabs6).
+We therefore always assumed a correlation of $r = 0.50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx 0.50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
+A sensitivity analysis indicated that changing the assumed correlation to values from $r = -0.90$ via $r = 0.00$ to $r = 0.90$ had no meaningful impact on the meta-analytic effect sizes (Supplementary Tables\ \@ref(tab:tabs7) and\ \@ref(tab:tabs8)).
+
+For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between male and female infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs6).
+In some cases where the authors of the original articles did not observe a statistically significant gender differences, they did not report a precise outcome measure.
+In these cases, we assumed an effect size of $g$ = 0, thus rendering our meta-analytic effect size of the gender difference more conservative.
+The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=2/(n_\text{female}^{-1}+n_\text{male}^{-1})$), and $J(df)$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs6).
 
@@
 This model had three levels, with infant participants nested in experiments and experiments nested in articles [@vandennoortgate2013].
-We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for all standard deviations [@williams2018].
-A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Tables\ \@ref(tab:tabs7), \@ref(tab:tabs8), and\ \@ref(tab:tabs9)).
+We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for the two standard deviations (i.e., the random effects of experiments and articles) [@williams2018].
+A prior sensitivity analysis indicated that making these priors either more informative or less informative did not have a strong influence on the meta-analytic results (Supplementary Tables\ \@ref(tab:tabs7), \@ref(tab:tabs8), and\ \@ref(tab:tabs9)).
 For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect measures above).
@@
 Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r formatC(n_iter, big.mark = ",")` draws (including `r formatC(n_warmup, big.mark = ",")` warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig.\ \@ref(fig:figs3)) [@vehtari2021].
+To verify the convergence of the Markov chains, we examined rank plots as well as the $\widehat{R}$ and $N_\text{eff}$ statistics (Supplementary Fig.\ \@ref(fig:figs3)) [@vehtari2021].
 For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].
@@
 
-We examined the influence of three moderator variables on the mental rotation outcomes across studies, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
+We examined the influence of three moderator variables on the mental rotation outcomes across experiments, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
 Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts [@schad2020] so that we could compare all-female versus mixed samples and all-male samples versus all-female samples.
-Age was coded as a continuous predictor in years and centered by subtracting the average across all studies.
-Task was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast [@schad2020].
-We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender and task type (i.e., [female - mixed] $\times$ age and [male - female] $\times$ age) into a Bayesian meta-regression model.
-This model was based on the same random effects structure and sampling parameters as described above.
+Age was coded as a continuous predictor in years and centered by subtracting the average across all experiments.
+Task type was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast [@schad2020].
+We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender and task type (i.e., [female - mixed] $\times$ age, [male - female] $\times$ age) into a Bayesian meta-regression model.
+This model was based on the same random effects structure, sampling parameters, and prior specification as described above, but adding a weakly-informative $\mathcal{N}(0,0.5)$ (normal) prior for all regression coefficients.
 
@@
 These models were fitted using restricted maximum likelihood estimation (REML).
-To verify that the REML converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the between-experiment variance and the between-article variance; Supplementary Fig.\ \@ref(fig:figs4)).
+To verify that this procedure converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Fig.\ \@ref(fig:figs4)).
 
@@
 The Egger regression test is a formal statistical test for this relationship between standard errors and effect sizes, probing if the weighted linear regression weight of the effect sizes on the standard errors is significantly different from zero.
-This test was performed using code from the metafor package and applying a two-sided false-positive error rate of $\alpha = .05$.
+This test was performed using code from the metafor package and applying a two-sided false-positive error rate of $\alpha = 0.05$.
 
@@
 
-The datasets generated and analyzed during the current study are available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
+The datasets generated and analyzed during the current study are available in an Open Science Framework repository [@enge2022a], [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8).
 This link is intended for peer review only and will be replaced with a public DOI link upon publication.
@@
 
-The analysis code for the current study is available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a].
+The analysis code for the current study is available in an Open Science Framework repository [@enge2022a], [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8).
 This link is intended for peer review only and will be replaced with a public DOI link upon publication.

### 2022-05-18 supplement.Rmd
Proof reading by A.E.

@@
 1.
-Extract an effect size $d_\text{diff}$ based on a paired $t$-test, a one-sample $t$-test of difference scores, or an analysis of variance (ANOVA) (see Rows (1) to (4) in Table 1).
+Extract an effect size $d_\text{diff}$ based on a paired $t$-test, a one-sample $t$-test of difference scores, or an analysis of variance (ANOVA) (see rows (1) to (4) in Supplementary Table\ \@ref(tab:tabs5)).
 All three of these tests take the correlation between the repeated measures into account.
@@
 Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]).
-However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments.
+However, we decided to assume a correlation of $r  = 0.50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments.
 This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
-To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Tables\ \@ref(tab:tabs7) and \@ref(tab:tabs8)).
-
-## Supplementary Methods 2 | Bias correction and sensitivity analysis for frequentist results
+To  evaluate the robustness of our Bayesian meta-analytic models against the assumption of a correlation of $r  = 0.50$, we ran a sensitivity analysis (Supplementary Tables\ \@ref(tab:tabs7) and \@ref(tab:tabs8)).
+
+## Supplementary Methods 2 | Publication bias correction
 
@@
 These models were based on the assumption that experiments yielding significant effects (i.e., small $P$ values) are more likely to get published.
-Specifically, we ran one selection model assuming a weight function with fixed $P$ value cutoffs [@vevea1995] at $P$ = .01, $P$ = .05, and $P$ = .30.
+Specifically, we ran one selection model assuming a weight function with fixed $P$ value cutoffs [@vevea1995] at $P$ = 0.01, $P$ = 0.05, and $P$ = 0.30.
 Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
@@
       "Hedges' $g$",
-      "$\\sigma_{\\text{Article}}^2$",
-      "$\\sigma_{\\text{Experiment}}^2$",
+      "$\\sigma_{\\text{article}}^2$",
+      "$\\sigma_{\\text{experiment}}^2$",
       "Intercept (Hedges' $g$)",
@@
       "(Male - female) $\\times$ age",
-      "$\\sigma_{\\text{Article}}^2$",
-      "$\\sigma_{\\text{Experiment}}^2$",
+      "$\\sigma_{\\text{article}}^2$",
+      "$\\sigma_{\\text{experiment}}^2$",
       "Hedges' $g$",
-      "$\\sigma_{\\text{Article}}^2$",
-      "$\\sigma_{\\text{Experiment}}^2$"
+      "$\\sigma_{\\text{article}}^2$",
+      "$\\sigma_{\\text{experiment}}^2$"
     )
@@
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (3\) $F$ statistic and sample size [@lakens2013]           | $t=\sqrt{f}$;\quad then (2\)                                                                |
+| \ \ (3\) $F$ statistic and sample size [@lakens2013]           | $t=\sqrt{F}$;\quad then (2\)                                                                |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
@@
 
-Table: (\#tab:tabs5) Effect size conversion for the meta-analysis of mental rotation performance
+Table: (\#tab:tabs5) Effect sizes for the meta-analysis of mental rotation performance
 
@@
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| \ \ (3\) $F$ statistic and group sizes | $t=\sqrt{f}$;\quad then (2\)                                                                     |
+| \ \ (3\) $F$ statistic and group sizes | $t=\sqrt{F}$;\quad then (2\)                                                                     |
 | [@lakens2013]                          |                                                                                                  |
@@
 
-Table: (\#tab:tabs6) Effect size conversion for the meta-analysis of gender differences
+Table: (\#tab:tabs6) Effect sizes for the meta-analysis of gender differences
 
@@
     label_2 = c(
-      "--", "--", "Weight function [.01, .05, .30]",
+      "--", "--", "Weight function [0.01, 0.05, 0.30]",
       "One-tailed, moderate bias", "One-tailed, severe bias",
@@
 Gray bars depict the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
-These intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes.
-The bold line at the bottom of the figure shows the meta-analytic effect size obtained from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
+The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
 
@@
 **c,** Redundant articles comprising the same experiment(s) were excluded.
-Additionally, we excluded an article that was based on an uncommon experimental paradigm differing substantially from all other articles (1 article).
-Finally, we excluded an article that was based on a sample of infants  who were substantially older compared to all other articles (1 article).
+\textsuperscript{a} = We decided to excluded two additional articles: one article because it was based on an uncommon experimental paradigm, differing substantially from all other articles, and another article because it was based on a sample of infants who were substantially older compared to all other articles.
 
@@
   tail_ess = round(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
-  r_hat_expr = str_c("italic(R)[hat] == ", r_hat),
+  r_hat_expr = str_c("italic(widehat(R)) == ", r_hat),
   bulk_ess_expr = str_c("italic(N)[eff(bulk)] == ", bulk_ess),
@@
     conv_stats,
-    y = 0.45, x = -0.042 * n_draws, color = "black", parse = TRUE,
-    vjust = 1, angle = 90
+    y = 0.45, x = -0.042 * n_draws, vjust = 1, color = "black", parse = TRUE,
+    angle = 90
   ) +
@@
     conv_stats,
-    x = 0.684 * n_draws, hjust = 1, color = "black", parse = TRUE,
+    x = 0.684 * n_draws, hjust = 1, vjust = 0.2, color = "black", parse = TRUE
   ) +
@@
 Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution.
-$R_\text{hat}$ = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
+$\widehat{R}$ = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
 Details about these convergence criteria can be found in @vehtari2021.
@@
 
-(ref:figs5-caption) **Trim-and-fill analyses.** As in Fig.\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
+(ref:figs5-caption) **Trim-and-fill analysis.** As in Fig.\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
 The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines).
 Gray shades indicate 95% pseudo-confidence intervals (dark gray) and 99% pseudo-confidence intervals (light gray) under the null hypothesis.
-Red squares show fictional experiments that were imputed using the trim-and-fill method  to compensate for the small publication bias observed in the original funnel plots.
+Red squares show fictional experiments that were imputed using the trim-and-fill method  to compensate for the small publication bias observed in the original funnel plot.
 Red lines depict the meta-analytic effect size and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analysis of mental rotation performance.

### 2022-05-18 manuscript.Rmd
Add raw data as TSV

@@
 
-# Download spreadsheets from the literature search from Google Drive
-excel_url <- "https://docs.google.com/spreadsheets/d/1xnC0NlQYTXavXaeqQidhi7UKb1pCGAl9Ry3h3Uz3mi0"
-excel_file <- here(data_dir, "literature_search.xlsx")
-# googledrive::drive_auth(use_oob = TRUE)
-# googledrive::drive_download(excel_url, excel_file, overwrite = TRUE)
-
-# Read the sheets
-raw_screening <- read_excel(excel_file, sheet = "screening")
-raw_meta <- read_excel(excel_file, sheet = "included", na = "NA")
-raw_gender <- read_excel(excel_file, sheet = "gender_differences", na = "NA")
+# Read the relevant spreadsheets
+raw_screen <- read_tsv(here(data_dir, "02_screen.tsv"), na = "NA")
+raw_meta <- read_tsv(here(data_dir, "03_meta.tsv"), na = "NA")
+raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")
 
@@
     # Add unique experiment identifier
-    experiment = str_c(year, article, group_long, sep = ", "),
+    experiment = str_c(year, article, group, sep = ", "),
 
@@
   geom_text(aes(x = -9.9, label = article), hjust = 0) +
-  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
+  geom_text(aes(x = -7.1, label = group), hjust = 0) +
   # Add experiment-specific effect sizes and CIs as text on the right
@@
     article,
-    group_long,
+    group,
     gi,
@@
 # Compute interrater agreement for binary decision (include vs. exclude)
-(irr_bin_perc <- with(
-  raw_screening, mean(bin_1 == bin_2)
-))
-(irr_bin_kappa <- with(
-  raw_screening, psych::cohen.kappa(cbind(bin_1, bin_2))
-))
+(irr_bin_perc <- with(raw_screen, mean(bin_1 == bin_2)))
+(irr_bin_kappa <- with(raw_screen, psych::cohen.kappa(cbind(bin_1, bin_2))))
 irr_bin_kappa_w <- as.list(irr_bin_kappa$confid["weighted kappa", ])
@@
 # Compute interrater agreement for specific exclusion codes
-(irr_code_perc <- with(
-  raw_screening, mean(code_1 == code_2)
-))
-(irr_code_kappa <- with(
-  raw_screening, psych::cohen.kappa(cbind(code_1, code_2))
-))
+(irr_code_perc <- with(raw_screen, mean(code_1 == code_2)))
+(irr_code_kappa <- with(raw_screen, psych::cohen.kappa(cbind(code_1, code_2))))
 irr_code_kappa_w <- as.list(irr_code_kappa$confid["weighted kappa", ])

### 2022-05-18 supplement.Rmd
Add raw data as TSV

@@
     Article = if_else(article == lag(article, default = ""), "", article),
-    Experiment = group_long,
+    Experiment = group,
     `Sample size` = as.integer(sample_size),
@@
     `Stimulus type` = str_to_sentence(stimuli_presentation),
-    `Stimulus dimensions` = stimuli_dimensions
+    `Stimulus dimensions` = str_c(as.integer(stimuli_dimensions), "D")
   ) %>%
@@
       label_1 = dat_meta$article[jackknife_index],
-      label_2 = dat_meta$group_long[jackknife_index],
+      label_2 = dat_meta$group[jackknife_index],
       label_col_1 = "Article", label_col_2 = "Experiment"
@@
 # Read PRISMA checklist from file
-tabs4 <- read_csv(
-  here(data_dir, "prisma_checklist.csv"),
-  col_types = "ccc", na = character()
-)
+tabs4 <- read_tsv(here(data_dir, "05_prisma.tsv"), na = character())
 

### 2022-05-18 supplement.Rmd
Save all tables as TSV

@@
 dir.create(tables_dir, showWarnings = FALSE)
-write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")
+write_tsv(tabs1, file = here(tables_dir, "tabs1_experiments.tsv"), na = "n/a")
 
@@
 # Save the table
-write_csv(tabs2, file = here(tables_dir, "tabs2_frequentist.csv"))
+write_tsv(tabs2, file = here(tables_dir, "tabs2_frequentist.tsv"))
 
@@
   # Save the table
-  write_csv(tabs3, file = here(tables_dir, "tabs3_jackknife.csv"))
+  write_tsv(tabs3, file = here(tables_dir, "tabs3_jackknife.tsv"))
 }
@@
 # Read jackknife table from file
-tabs3 <- read_csv(
-  here(tables_dir, "tabs3_jackknife.csv"),
+tabs3 <- read_tsv(
+  here(tables_dir, "tabs3_jackknife.tsv"),
   col_types = "c", na = character()
@@
     }) -> tabs7
-  write_csv(tabs7, file = here(tables_dir, "tabs7_sens_meta.csv"))
+  write_tsv(tabs7, file = here(tables_dir, "tabs7_sens_meta.tsv"))
 
@@
     }) -> tabs8
-  write_csv(tabs8, file = here(tables_dir, "tabs8_sens_reg.csv"))
+  write_tsv(tabs8, file = here(tables_dir, "tabs8_sens_reg.tsv"))
 
@@
     }) -> tabs9
-  write_csv(tabs9, file = here(tables_dir, "tabs9_sens_gender.csv"))
+  write_tsv(tabs9, file = here(tables_dir, "tabs9_sens_gender.tsv"))
 }
@@
 # Load sensitivity analysis table from file
-tabs7 <- read_csv(
-  here(tables_dir, "tabs7_sens_meta.csv"),
+tabs7 <- read_tsv(
+  here(tables_dir, "tabs7_sens_meta.tsv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 # Load sensitivity analysis table from file
-tabs8 <- read_csv(
-  here(tables_dir, "tabs8_sens_reg.csv"),
+tabs8 <- read_tsv(
+  here(tables_dir, "tabs8_sens_reg.tsv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 # Load sensitivity analysis table from file
-tabs9 <- read_csv(
-  here(tables_dir, "tabs9_sens_gender.csv"),
+tabs9 <- read_tsv(
+  here(tables_dir, "tabs9_sens_gender.tsv"),
   col_types = "c", na = character(), trim_ws = FALSE
@@
 tabs11 <- tabs_correction$gender
-write_csv(tabs10, file = here(tables_dir, "tabs10_correction_meta.csv"))
-write_csv(tabs11, file = here(tables_dir, "tabs11_correction_gender.csv"))
+write_tsv(tabs10, file = here(tables_dir, "tabs10_correction_meta.tsv"))
+write_tsv(tabs11, file = here(tables_dir, "tabs11_correction_gender.tsv"))
 ```

### 2022-05-18 supplement.Rmd
Fix sensitivity analysis

@@
   sens %>%
-    select(res, manipulation_name, manipulation_value) %>%
-    pmap_dfr(function(res, manipulation_name, manipulation_value) {
+    select(res_meta, manipulation_name, manipulation_value) %>%
+    pmap_dfr(function(res_meta, manipulation_name, manipulation_value) {
       print_res_table(
-        res,
+        res_meta,
         label_1 = manipulation_name, label_2 = manipulation_value,

### 2022-05-18 supplement.Rmd
Improve number format in trace plot

--- 2022-05-18 supplement.Rmd
@@
   r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
-  bulk_ess = round(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
-  tail_ess = round(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
-  r_hat_expr = str_c("italic(widehat(R)) == ", r_hat),
-  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == ", bulk_ess),
-  tail_ess_expr = str_c("italic(N)[eff(tail)] == ", tail_ess),
+  bulk_ess = print_big(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
+  tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
+  r_hat_expr = str_c("italic(widehat(R)) == \"", r_hat, "\""),
+  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == \"", bulk_ess, "\""),
+  tail_ess_expr = str_c("italic(N)[eff(tail)] == \"", tail_ess, "\""),
   y_pos = c(0.7, 0.75, 0.8)

### 2022-05-18 manuscript_files/helper_functions.R

@@ -1,4 +1,4 @@
-# Formatting days as months + days
+# Format days as months + days
 print_days_months <- function(days, long = FALSE) {
   m_str <- ifelse(long, " months ", "m ")
   d_str <- ifelse(long, " days", "d")
@@ -10,7 +10,7 @@ print_days_months <- function(days, long = FALSE) {
   return(str)
 }
 
-# Formatting percentages with one decimal place
+# Format percentages with one decimal place
 print_perc <- function(x) scales::percent(x, accuracy = 0.1)
 
 # Format confidence interval
@@ -21,6 +21,11 @@ print_ci <- function(lb, ub) {
 # Format mean value and confidence interval
 print_mean_ci <- function(mean, lb, ub) {
   paste(papaja::print_num(mean), print_ci(lb, ub))
+}
+
+# Format big numbers (> 1,000) with commas
+print_big <- function(x, digits = 0) {
+  formatC(x, digits = digits, format = "f", big.mark = ",")
 }
 
 # Format results of Bayesian meta-analysis as a table with optional labels

### 2022-05-18 manuscript.Rmd
Use journal abbreviations

@@
 
-To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993].
+To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@efron1993].
 To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.

### 2022-05-18 manuscript.Rmd
Re-format probabilities > 99.9%

@@
 Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)).
-The probability for this effect being greater than zero was $\approx$ `r print_perc(hyp_meta$Post.Prob)`.
+The probability for this effect being greater than zero was $\approx$ `r print_prob(hyp_meta$Post.Prob)`.
 The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level.
@@
 Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$, 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
-The probability for this effect being larger than zero was `r print_perc(hyps_brm_reg$male_female$Post.Prob)`.
-We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_perc(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
+The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`.
+We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
 Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% [`r summ_reg$age.lower`, `r summ_reg$age.upper`].
@@
 Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`].
-The probability for this effect being greater than zero was `r print_perc(hyps_brm_reg$voe_habituation$Post.Prob)`.
+The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.
 
@@
 To confirm the gender difference between males and females, we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between male and female infants reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
+Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_prob(hyp_gender$Post.Prob)`.
 The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
@@
 
-One recent study on 5--6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work [@constantinescu2018].
+One recent study on 5- to 6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work [@constantinescu2018].
 As far as we know, potentially mediating and moderating factors that could already be operational in infancy, however, are not yet empirically established.

### 2022-05-18 manuscript_files/helper_functions.R

@@ -23,6 +23,11 @@ print_mean_ci <- function(mean, lb, ub) {
   paste(papaja::print_num(mean), print_ci(lb, ub))
 }
 
+# Format probabilities as percent
+print_prob <- function(x) {
+  ifelse(x < 0.999, print_perc(x), "> 99.9%")
+}
+
 # Format big numbers (> 1,000) with commas
 print_big <- function(x, digits = 0) {
   formatC(x, digits = digits, format = "f", big.mark = ",")

### 2022-05-18 manuscript.Rmd
Format paragraphs as one line of code
Re-format probabilities > 99.9%
Add references for effect size conversion

@@
 Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)).
-The probability for this effect being greater than zero was $\approx$ `r print_prob(hyp_meta$Post.Prob)`.
+The probability for this effect being greater than zero was `r print_prob(hyp_meta$Post.Prob)`.
 The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level.
@@
 
-For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5).
+For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5) [@goulet-pelletier2018; @hedges1985; @lakens2013; @rosenthal1991; @cumming2012].
 The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs5).

### 2022-05-18 manuscript.Rmd
Prepare for fitting on the HPC

@@
 run <- list(
-  bayesian_models = FALSE,
-  jackknife_analysis = FALSE,
-  sensitivity_analysis = FALSE
+  bayesian_models = TRUE,
+  jackknife_analysis = TRUE,
+  sensitivity_analysis = TRUE
 )

### 2022-05-19 manuscript.Rmd
Small fixes
Proof reading by A.E., A.-S.K.

@@
 When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months.
+Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
 We robustly found that male infants recognized rotated objects more reliably than female infants.
@@
 Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
-Interestingly, a recent meta-analysis in 3-17-year-old children and adolescents [@lauer2019a] suggests even only a small-to-medium difference (mean weighted $g = 0.39$).
+Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents [@lauer2019a] suggests even only a small-to-medium difference (mean weighted $g = 0.39$).
 Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
 
-In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table\ \@ref(tab:tabs1))[@antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @frick2013b; @frick2014b; @gerhard-samunda2021; @gerhard2018; @hespos1997; @kaaz2020; @kelch2021; @kellman1984; @lauer2015; @lauer2016; @mohring2013; @moore2008; @moore2011; @quinn2008; @quinn2014; @rochat1996; @schwarzer2013; @schwarzer2013a; @slone2018].
+In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table\ \@ref(tab:tabs1))[@kellman1984; @rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @lauer2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
 All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985].
 These experiments comprised real world stimuli (e.g., toy objects) [@antrilli2016], three-dimensional digital stimuli (e.g., cube figures) [@moore2008], or two-dimensional digital stimuli (e.g., digits) [@quinn2008].
-In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object.
+In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or the familiar object at a new angle.
 Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation.
@@
 White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
-Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI).
-These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the data.
+Gray bars indicate the 50% and 95% credible intervals (CrI) from the Bayesian model, which take into account that experiments with smaller sample sizes or more extreme effect sizes provide less reliable information.
 The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
 
-Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average longer in male compared to female infants.
+Following previous work in older populations, we hypothesized that looking time differences in mental rotation experiments are on average longer in male compared to female infants.
 Effect sizes were assumed to be small.
@@
 Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
-Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 95% and 50% credible interval (CrI).
-**b,** Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 95% Crl (thin black lines) and 50% Crl (thick black lines).
+Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI).
+**b,** Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines).
 Gray curves indicate the posterior distribution for each effect.
@@
 To confirm the gender difference between males and females, we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between male and female infants reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_prob(hyp_gender$Post.Prob)`.
+Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% CrI [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_prob(hyp_gender$Post.Prob)`.
 The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
@@
 This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $P = `r print_num(egger_meta$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
-Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)).
+Nevertheless, a jackknife (leave-one-out) analysis confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)).
 For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
@@
 We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
-The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference would be more likely report separate effect sizes for males and females.
+The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference would be more likely to report separate effect sizes for males and females.
 In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_gender$intercept`$) can be viewed as a lower bound of the true effect size.
@@
 
-One recent study on 5- to 6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work [@constantinescu2018].
+One recent study on 5--6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work [@constantinescu2018].
 As far as we know, potentially mediating and moderating factors that could already be operational in infancy, however, are not yet empirically established.
@@
 This relation also applies to previous experience with manually rotating toys [@schwarzer2013a].
-While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g.
-[@ausubel1968; @bradley1983; @halberda2008]).
+While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g., [@ausubel1968; @bradley1983; @halberda2008]).
 Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].
@@
 In the present meta-analysis, we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021].
-The PRISMA flowchart is provided in Supplementary Fig.\ \@ref(fig:figs2) while Supplementary Table\ \@ref(tab:tabs4) contains the PRISMA checklist.
+The PRISMA checklist is provided in Supplementary Table\ \@ref(tab:tabs4) while Supplementary Fig.\ \@ref(fig:figs2) displays the PRISMA flowchart.
 
@@
 
-Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article was written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that could be converted into a standardized mean difference (see Data collection process and items below).
+Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article is written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that can be converted into a standardized mean difference (see Data collection process and items below).
 We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
@@
 We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Fig.\ \@ref(fig:figs2)).
+This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Supplementary Fig.\ \@ref(fig:figs2)).
 We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills [@frick2014; @johnson2020; @kubicek2018; @lauer2019a; @linn1985; @moore2020; @uttal2013; @voyer1995; @yang2020].
@@
 Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
-One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles.
+One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigms used in the other articles.
 Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, digits = 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, digits = 1)` months; $Z = `r descs_pedrett2020$z`$ compared to all articles).
@@
 Moreover, we disregarded effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of `r descriptives$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table\ \@ref(tab:tabs1)) and 30 articles being included in the meta-analysis of gender differences in mental rotation performance.
+This procedure led to a total of `r descriptives$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table\ \@ref(tab:tabs1)) and 30 experiments being included in the meta-analysis of gender differences in mental rotation performance.
 
@@
 For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between male and female infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs6).
-In some cases where the authors of the original articles did not observe a statistically significant gender differences, they did not report a precise outcome measure.
-In these cases, we assumed an effect size of $g$ = 0, thus rendering our meta-analytic effect size of the gender difference more conservative.
+In some cases where the authors of the original articles did not observe a statistically significant gender difference, they did not report a precise outcome measure.
+In these cases, we assumed an effect size of $g$ = 0.00, thus rendering our meta-analytic effect size of the gender difference more conservative.
 The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=2/(n_\text{female}^{-1}+n_\text{male}^{-1})$), and $J(df)$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs6).
@@
 All Bayesian models were fitted using the brms package (Version `r packageVersion("brms")`) [@burkner2017; @burkner2018] in R (Version `r packageVersion("base")`) [@rcoreteam2021] and the Stan language (Version `r packageVersion("rstan")`) [@standevelopmentteam2022].
-Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r formatC(n_iter, big.mark = ",")` draws (including `r formatC(n_warmup, big.mark = ",")` warm-up draws) from the posterior distribution.
+Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r print_big(n_iter)` draws (including `r print_big(n_warmup)` warm-up draws) from the posterior distribution.
 To verify the convergence of the Markov chains, we examined rank plots as well as the $\widehat{R}$ and $N_\text{eff}$ statistics (Supplementary Fig.\ \@ref(fig:figs3)) [@vehtari2021].
@@
 We examined the influence of three moderator variables on the mental rotation outcomes across experiments, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
-Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts [@schad2020] so that we could compare all-female versus mixed samples and all-male samples versus all-female samples.
+Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts [@schad2020] so that we could compare all-female samples versus mixed samples and all-male samples versus all-female samples.
 Age was coded as a continuous predictor in years and centered by subtracting the average across all experiments.
@@
 These models were fitted using restricted maximum likelihood estimation (REML).
-To verify that this procedure converged on the correct estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Fig.\ \@ref(fig:figs4)).
+To verify that this procedure converged on the most probable estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Fig.\ \@ref(fig:figs4)).
 
@@
 The Egger regression test is a formal statistical test for this relationship between standard errors and effect sizes, probing if the weighted linear regression weight of the effect sizes on the standard errors is significantly different from zero.
-This test was performed using code from the metafor package and applying a two-sided false-positive error rate of $\alpha = 0.05$.
-
-To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@efron1993].
+This test was performed using the metafor package and applying a two-sided false-positive error rate of $\alpha = 0.05$.
+
+To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife (leave-one-out) analysis for the meta-analysis of mental rotation performance [@efron1993].
 To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.
@@
 
-\noindent M.A.S.
+M.A.S.
 conceived, designed, and obtained funding for the study.
@@
 
-\noindent The authors declare no competing interests.
+The authors declare no competing interests.
 
@@
 
-\noindent Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
+Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
 

### 2022-05-19 supplement.Rmd
Proof reading by A.E., A.-S.K.

--- 2022-05-18 supplement.Rmd
@@
 # Summarise the estimated correlations
-(summ_ri_empirical <- print_num(summary(ri_empirical)))
+(summ_ri_empirical <- list(
+  mean = mean(ri_empirical, na.rm = TRUE),
+  median = median(ri_empirical, na.rm = TRUE),
+  min = min(ri_empirical, na.rm = TRUE),
+  max = max(ri_empirical, na.rm = TRUE)
+) %>%
+  map(print_num))
 ```
@@
 5.
-Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$
-
-Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]).
+Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}^2}{-2\cdot{SD}_\text{novel}\cdot{SD}_\text{familiar}}$$
+
+Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical$mean`$ (median $r = `r summ_ri_empirical$median`$, range [`r summ_ri_empirical$min`, `r summ_ri_empirical$max`]).
 However, we decided to assume a correlation of $r  = 0.50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments.
@@
 For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis.
-In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments.
+In our first step, we computed a trim-and-fill model by imputing possible effect sizes of non-published experiments [@duval2000].
 This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs5)).
@@
       label_2 = dat_meta$group[jackknife_index],
-      label_col_1 = "Article", label_col_2 = "Experiment"
+      label_col_1 = "Article", label_col_2 = "Left-out experiment"
     )
@@
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (5\) Mean looking time and ${SD}$ per condition            | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
-| [@cumming2012]                                                 | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
+| \ \ (5\) Mean looking times$ per condition [@cumming2012]      | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
+|                                                                | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
@@
 +========================================+==================================================================================================+
-| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
+| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-2$; \quad                                                    |
 | [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
@@
     label_2 = c(
-      "--", "--", "Weight function [0.01, 0.05, 0.30]",
+      "--", "--", "Weight function, $P$ cutoffs [0.01, 0.05, 0.30]",
       "One-tailed, moderate bias", "One-tailed, severe bias",
@@
 For experiments resulting in a non-significant gender difference and for which the authors did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
-Gray bars depict the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
+Gray bars depict the 50% and 95% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
 The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
@@
   r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
-  bulk_ess = round(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
-  tail_ess = round(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
-  r_hat_expr = str_c("italic(widehat(R)) == ", r_hat),
-  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == ", bulk_ess),
-  tail_ess_expr = str_c("italic(N)[eff(tail)] == ", tail_ess),
+  bulk_ess = print_big(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
+  tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
+  r_hat_expr = str_c("italic(widehat(R)) ~ == ~ \"", r_hat, "\""),
+  bulk_ess_expr = str_c("italic(N)[eff(bulk)] ~ == ~ \"", bulk_ess, "\""),
+  tail_ess_expr = str_c("italic(N)[eff(tail)] ~ == ~ \"", tail_ess, "\""),
   y_pos = c(0.7, 0.75, 0.8)
@@
 Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution.
-$\widehat{R}$ = potential scale reduction factor, with values close to 1.0 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
+$\widehat{R}$ = potential scale reduction factor, with values close to 1.00 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
 Details about these convergence criteria can be found in @vehtari2021.

### 2022-05-19 supplement.Rmd
Proof read by A.-S.K.

@@
 **c,** Redundant articles comprising the same experiment(s) were excluded.
-\textsuperscript{a} = We decided to excluded two additional articles: one article because it was based on an uncommon experimental paradigm, differing substantially from all other articles, and another article because it was based on a sample of infants who were substantially older compared to all other articles.
+\textsuperscript{a} = We decided to exclude two additional articles: one article because it was based on an uncommon experimental paradigm, differing substantially from all other articles, and another article because it was based on a sample of infants who were substantially older compared to all other articles.
 

### 2022-05-19 supplement.Rmd
Fix trace plot labels

--- 2022-05-19 supplement.Rmd
@@
   tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
-  r_hat_expr = str_c("italic(widehat(R)) ~ == ~ \"", r_hat, "\""),
-  bulk_ess_expr = str_c("italic(N)[eff(bulk)] ~ == ~ \"", bulk_ess, "\""),
-  tail_ess_expr = str_c("italic(N)[eff(tail)] ~ == ~ \"", tail_ess, "\""),
+  r_hat_expr = str_c("italic(widehat(R)) == \"", r_hat, "\""),
+  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == \"", bulk_ess, "\""),
+  tail_ess_expr = str_c("italic(N)[eff(tail)] == \"", tail_ess, "\""),
   y_pos = c(0.7, 0.75, 0.8)

### 2022-05-19 manuscript.Rmd
Small fixes

@@
 These experiments comprised real world stimuli (e.g., toy objects) [@antrilli2016], three-dimensional digital stimuli (e.g., cube figures) [@moore2008], or two-dimensional digital stimuli (e.g., digits) [@quinn2008].
-In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or the familiar object at a new angle.
+In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or with the familiar object at a new angle.
 Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation.
@@
 In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
+
+\vspace{1cm}
 
@@
 
-```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
+```{r, fig1, include=TRUE, fig.height=14, fig.pos="bh", fig.width=12, fig.cap="(ref:fig1-caption)"}
 # Get posterior draws for the effect *in each experiment*

### 2022-05-19 supplement.Rmd
Small fixes

@@
     label_2 = c(
-      "--", "--", "Weight function, $P$ cutoffs [0.01, 0.05, 0.30]",
+      "--", "--", "Weight function, $P$ value cutoffs [0.01, 0.05, 0.30]",
       "One-tailed, moderate bias", "One-tailed, severe bias",

### 2022-05-20 manuscript.Rmd
Include sign of F for gender
Improve text

@@
     # Add d from ANOVA F statistic via conversion to a t statistic
-    d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),
+    d_f = sqrt(f_assumed) * sign_f * sqrt(1 / female_n + 1 / male_n),
 
@@
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.\ \@ref(fig:figs2)).
+This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Supplementary Fig.\ \@ref(fig:figs2)).
 
@@
 For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5) [@goulet-pelletier2018; @hedges1985; @lakens2013; @rosenthal1991; @cumming2012].
-The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs5).
+The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs5).
 The correlation $r$ was not reported in any of the original articles [@harrer2021].
@@
 In these cases, we assumed an effect size of $g$ = 0.00, thus rendering our meta-analytic effect size of the gender difference more conservative.
-The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=2/(n_\text{female}^{-1}+n_\text{male}^{-1})$), and $J(df)$ is the correction factor for small samples as described in row (1) of Supplementary Table\ \@ref(tab:tabs6).
+The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=2/(n_\text{female}^{-1}+n_\text{male}^{-1})$), and $J(df)$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs6).
 
@@
 We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender and task type (i.e., [female - mixed] $\times$ age, [male - female] $\times$ age) into a Bayesian meta-regression model.
-This model was based on the same random effects structure, sampling parameters, and prior specification as described above, but adding a weakly-informative $\mathcal{N}(0,0.5)$ (normal) prior for all regression coefficients.
+This model was based on the same random effects structure, sampling parameters, and prior specification as described above, but adding a weakly-informative $\mathcal{N}(0,0.5)$ (normal) prior for all slope parameters.
 

### 2022-05-20 supplement.Rmd
Include sign of F for gender

@@
 res_freq_2_lvl %>%
-  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 0.30, 1.00)) ->
+  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 1.00)) ->
 res_selection_weights

### 2022-05-23 manuscript.Rmd
Add discussion of familiarity preferences

@@
 run <- list(
-  bayesian_models = TRUE,
-  jackknife_analysis = TRUE,
-  sensitivity_analysis = TRUE
+  bayesian_models = FALSE,
+  jackknife_analysis = FALSE,
+  sensitivity_analysis = FALSE
 )
@@
 
+As a final statistical consideration, we have coded the effect size of the looking time difference between novel and familiar rotation events in a linear fashion.
+This means that a positive looking time difference (i.e., a novelty preference) is taken as stronger evidence for mental rotation than a looking time difference of zero (i.e., no systematic preference), which in turn is taken as stronger evidence for mental rotation than a negative looking time difference (i.e., a familiarity preference).
+Although novelty preference is the more paradigmatic case, some authors have argued that familiarity preference should also be taken as evidence for mental rotation ability [@erdmann2018; @moore2020; @johnson2020].
+We have instead decided to model the looking time differences in a linear fashion to facilitate the interpretability of our models (for related discussion, see [@houston-price2004; @black2017; @cristia2018]).
+This procedure has rendered our meta-analytic effect sizes of mental rotation performance and of gender differences smaller than they would have been if both novelty preference and familiarity preference are interpreted as successful mental rotation.
+
 The gender differences observed here remain to be explained by interacting genetic and environmental factors that are largely unknown.

### 2022-05-23 manuscript.Rmd
Proof reading by M.A.S., A.E.

--- 2022-05-20 manuscript.Rmd
@@
 Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
-We robustly found that male infants recognized rotated objects more reliably than female infants.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
+We robustly found that male infants recognized rotated objects slightly more reliably than female infants.
+These findings indicate that subtle gender differences in mental rotation are already present in the first months of life.
 
@@
 Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
-Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents [@lauer2019a] suggests even only a small-to-medium difference (mean weighted $g = 0.39$).
+Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents suggests only a small-to-medium difference (mean weighted $g = 0.39$) [@lauer2019a].
 Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
@@
 As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig.\ \@ref(fig:fig2)).
-Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$, 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
+Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
 The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`.
@@
 We found that on average, male infants looked longer at novel rotated objects compared to female infants.
-This effect was small and unrelated to age in the current range.
+This effect was small to medium and unrelated to age in the current range.
 
@@
 This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences were likely also observed but just not reported because of missing power to render these effects statistically significant.
+
+To facilitate the interpretability of our models, the effect size of the looking time difference between novel and familiar rotation events was coded in a linear fashion.
+Accordingly, a positive looking time difference (i.e., a novelty preference) was taken as stronger evidence for mental rotation than a looking time difference of zero (i.e., no systematic preference).
+A zero difference in turn was taken as stronger evidence for mental rotation than a negative looking time difference (i.e., a familiarity preference).
+This approach can be corroborated by the established view that novelty preference is generally considered as the paradigmatic mental rotation behavior (for related discussion, see [@houston-price2004; @black2017; @cristia2018]).
+Nevertheless, some authors have argued that familiarity preference should also be taken as evidence for mental rotation ability [@erdmann2018; @moore2020; @johnson2020].
+Interpreting novelty preference *and* familiarity preference as successful mental rotation would have increased the effect sizes reported here.
 
@@
 
-The present study robustly revealed that male infants look longer at novel rotated objects than female infants.
-Thus, on average, males show more reliable mental rotation behavior already in the first months of life.
+The present study robustly revealed that male infants look slightly longer at novel rotated objects than female infants.
+Thus, on average, males show slightly more reliable mental rotation behavior already in the first months of life.
 

### 2022-05-23 supplement.Rmd
Tiny fixes

@@
 
-```{r, figs1, include=TRUE, fig.height=10, fig.width=12, fig.cap="(ref:figs1-caption)"}
+```{r, figs1, include=TRUE, fig.height=8, fig.width=12, fig.cap="(ref:figs1-caption)"}
 # Get posterior draws for the effect *in each experiment*

### 2022-06-14 manuscript.Rmd
Small changes for new submission

@@
   - id            : "1"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, Leipzig, Germany"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, 04103 Leipzig, Germany"
   - id            : "2"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, Berlin, Germany"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin, Germany"
   - id            : "*"
@@
 
-keywords          : "mental rotation, spatial cognition, spatial ability, infants, children, gender, meta-analysis"
-
 bibliography      : "manuscript_files/references.bib"
-csl               : "manuscript_files/nature.csl"
+csl               : "manuscript_files/pnas.csl"
 
@@
 Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
-We robustly found that male infants recognized rotated objects slightly more reliably than female infants.
-These findings indicate that subtle gender differences in mental rotation are already present in the first months of life.
-
-# Main
+We robustly found that male infants recognized rotated objects more reliably than female infants.
+These findings indicate that gender differences in mental rotation are already present in the first months of life.
+
+# Significance statement
+
+Are there gender differences in cognitive ability?
+So far, putative differences in most cognitive domains turned out to be myths.
+However, mental rotation, the ability to move an object in mind to predict how it would look in a new orientation, is considered as a serious candidate.
+Here we investigated how early during development mental rotation behavior differs in male and female infants.
+We found that, on average, males recognized rotated objects more reliably than females as early as in the first months of life.
+These results are an important step towards narrowing down possible social and genetic origins of gender differences in mental rotation ability.
+
+\newpage
+
+# Introduction
 
@@
 In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table\ \@ref(tab:tabs1))[@kellman1984; @rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @lauer2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
-All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation`) or violation of expectation experiments (`r descriptives$n_experiments_voe`) [@fantz1964; @baillargeon1985].
-These experiments comprised real world stimuli (e.g., toy objects) [@antrilli2016], three-dimensional digital stimuli (e.g., cube figures) [@moore2008], or two-dimensional digital stimuli (e.g., digits) [@quinn2008].
+All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation` experiments) or violation of expectation experiments (`r descriptives$n_experiments_voe` experiments) [@fantz1964; @baillargeon1985].
+These experiments comprised real world stimuli (e.g., toy objects), three-dimensional digital stimuli (e.g., cube figures), or two-dimensional digital stimuli (e.g., digits).
 In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or with the familiar object at a new angle.
@@
 
-\vspace{1cm}
+Following previous work in older populations, we hypothesized that looking time differences in mental rotation experiments are on average longer in male compared to female infants.
+Effect sizes were assumed to be small.
 
@@
 
-```{r, fig1, include=TRUE, fig.height=14, fig.pos="bh", fig.width=12, fig.cap="(ref:fig1-caption)"}
+```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
 # Get posterior draws for the effect *in each experiment*
@@
 
-Following previous work in older populations, we hypothesized that looking time differences in mental rotation experiments are on average longer in male compared to female infants.
-Effect sizes were assumed to be small.
+# Results
 
@@
 
-## Discussion
+# Discussion
 
@@
 
-The present study robustly revealed that male infants look slightly longer at novel rotated objects than female infants.
-Thus, on average, males show slightly more reliable mental rotation behavior already in the first months of life.
-
-# Methods
+The present study robustly revealed that male infants look longer at novel rotated objects than female infants.
+Thus, on average, males show more reliable mental rotation behavior already in the first months of life.
+
+# Materials and methods
 
@@
 
-## Data availability
-
-The datasets generated and analyzed during the current study are available in an Open Science Framework repository [@enge2022a], [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8).
-This link is intended for peer review only and will be replaced with a public DOI link upon publication.
-
-## Code availability
-
-The analysis code for the current study is available in an Open Science Framework repository [@enge2022a], [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8).
-This link is intended for peer review only and will be replaced with a public DOI link upon publication.
+## Data and code availability
+
+The data and code for this study are available in an Open Science Framework repository ([https://doi.org/10.17605/OSF.IO/K3WDG](https://doi.org/10.17605/OSF.IO/K3WDG)).
 
@@
 
-# Author contributions
-
-M.A.S.
-conceived, designed, and obtained funding for the study.
-A.E., S.K., and A.-S.K.
-(in consultation with M.A.S.) designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results.
-A.E.
-and M.A.S.
-wrote the manuscript with additional input from S.K.
-and A.-S.K.
-
-# Competing interests
-
-The authors declare no competing interests.
-
-# Materials & Correspondence
-
-Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
-
-\newpage
-
 ```{r child = "supplement.Rmd"}

### 2022-07-06 manuscript.Rmd
Update for re-submission

@@
   - name          : "Alexander Enge"
-    affiliation   : "1,2,*"
+    affiliation   : "1,2"
+    corresponding : "yes"
+    address       : "Stephanstraße 1a"
+    email         : "enge@cbs.mpg.de"
   - name          : "Shreya Kapoor"
@@
   - id            : "1"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, 04103 Leipzig, Germany"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
   - id            : "2"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin, Germany"
-  - id            : "*"
-    institution   : "Corresponding author (enge@cbs.mpg.de)"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
+
+authornote: |
+  We have no conflicts of interest to disclose.
+  The data and code for this study are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
+
+abstract: |
+  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
+On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
+When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
+Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
+We robustly found that male infants recognized rotated objects more reliably than female infants.
+These findings indicate that gender differences in mental rotation are already present in the first months of life.
+keywords: "mental rotation; spatial cognition; infants; gender; meta-analysis"
 
 bibliography      : "manuscript_files/references.bib"
-csl               : "manuscript_files/pnas.csl"
+csl               : "manuscript_files/apa.csl"
 
@@
   - \usepackage{setspace}
-  - \DeclareCaptionLabelSeparator{bar}{ | }
   - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
-  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
-  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
+  - \captionsetup[table]{belowskip=20pt,labelfont=bf,labelsep=period,textfont=bf,textformat=tabletext}
+  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=period,textfont=normalfont}
 ---
@@
 
-\linenumbers
-
-# Abstract
-
-Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
-We robustly found that male infants recognized rotated objects more reliably than female infants.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
-
-# Significance statement
-
-Are there gender differences in cognitive ability?
-So far, putative differences in most cognitive domains turned out to be myths.
-However, mental rotation, the ability to move an object in mind to predict how it would look in a new orientation, is considered as a serious candidate.
-Here we investigated how early during development mental rotation behavior differs in male and female infants.
-We found that, on average, males recognized rotated objects more reliably than females as early as in the first months of life.
-These results are an important step towards narrowing down possible social and genetic origins of gender differences in mental rotation ability.
-
-\newpage
-
-# Introduction
+# Gender differences in infant mental rotation
 
@@
 Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
-Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents suggests only a small-to-medium difference (mean weighted $g = 0.39$) [@lauer2019a].
+Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents suggests only a small-to-medium difference [mean weighted $g = 0.39$\; @lauer2019a].
 Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
 
-In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`; Supplementary Table\ \@ref(tab:tabs1))[@kellman1984; @rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @lauer2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
+In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`\; Supplementary Table\ \@ref(tab:tabs1)) [@kellman1984; @rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @lauer2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
 All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation` experiments) or violation of expectation experiments (`r descriptives$n_experiments_voe` experiments) [@fantz1964; @baillargeon1985].
-These experiments comprised real world stimuli (e.g., toy objects), three-dimensional digital stimuli (e.g., cube figures), or two-dimensional digital stimuli (e.g., digits).
+These experiments comprised real world stimuli [e.g., toy objects\; @antrilli2016], three-dimensional digital stimuli [e.g., cube figures\; @moore2008], or two-dimensional digital stimuli [e.g., digits\; @quinn2008].
 In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or with the familiar object at a new angle.
@@
 Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
-Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Fig.\ \@ref(fig:fig1)).
+Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Figure\ \@ref(fig:fig1)).
 The probability for this effect being greater than zero was `r print_prob(hyp_meta$Post.Prob)`.
@@
 
-As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig.\ \@ref(fig:fig2)).
+As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Figure\ \@ref(fig:fig2)).
 Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
@@
   plot_reg, plot_coef,
-  nrow = 1, rel_widths = c(3, 2), labels = "auto",
+  nrow = 1, rel_widths = c(3, 2), labels = "AUTO",
   label_size = 11, label_fontfamily = "Helvetica",
@@
 
-(ref:fig2-caption) **Effects of gender, age, and task.** **a,** Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments.
+(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments.
 Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
 Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI).
-**b,** Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines).
+(B) Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines).
 Gray curves indicate the posterior distribution for each effect.
@@
 
+\newpage
+
 To confirm the gender difference between males and females, we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between male and female infants reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% CrI [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_prob(hyp_gender$Post.Prob)`.
+Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% CrI [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Figure\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_prob(hyp_gender$Post.Prob)`.
 The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
@@
 We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here.
-For the meta-analysis of mental rotation performance (Fig.\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
-This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $P = `r print_num(egger_meta$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
+For the meta-analysis of mental rotation performance (Figure\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
+This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
 Nevertheless, a jackknife (leave-one-out) analysis confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)).
-For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+For the meta-analysis of gender differences in mental rotation performance (Figure\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
 plot_grid(
-  plotlist = plots_funnel, nrow = 1, labels = "auto",
+  plotlist = plots_funnel, nrow = 1, labels = "AUTO",
   label_size = 11, label_fontfamily = "Helvetica"
@@
 
-(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance (**a**) and for the meta-analysis of gender differences in mental rotation performance (**b**).
+(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance (A) and for the meta-analysis of gender differences in mental rotation performance (B).
 The plots show the standard error and effect size for each of the individual experiments as a black square.
@@
 A zero difference in turn was taken as stronger evidence for mental rotation than a negative looking time difference (i.e., a familiarity preference).
-This approach can be corroborated by the established view that novelty preference is generally considered as the paradigmatic mental rotation behavior (for related discussion, see [@houston-price2004; @black2017; @cristia2018]).
+This approach can be corroborated by the established view that novelty preference is generally considered as the paradigmatic mental rotation behavior [for related discussion, see @black2017; @cristia2018; @houston-price2004].
 Nevertheless, some authors have argued that familiarity preference should also be taken as evidence for mental rotation ability [@erdmann2018; @moore2020; @johnson2020].
@@
 This relation also applies to previous experience with manually rotating toys [@schwarzer2013a].
-While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains (e.g., [@ausubel1968; @bradley1983; @halberda2008]).
+While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains [e.g., @ausubel1968; @bradley1983; @halberda2008].
 Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].
@@
 
-# Materials and methods
+# Method
 
@@
 
-In the present meta-analysis, we followed the established PRISMA 2020 guidelines (Preferred Reporting Items for Systematic reviews and Meta-Analyses) [@page2021].
-The PRISMA checklist is provided in Supplementary Table\ \@ref(tab:tabs4) while Supplementary Fig.\ \@ref(fig:figs2) displays the PRISMA flowchart.
+In the present meta-analysis, we followed the established PRISMA 2020 guidelines [Preferred Reporting Items for Systematic reviews and Meta-Analyses\; @page2021].
+The PRISMA checklist is provided in Supplementary Table\ \@ref(tab:tabs4) while Supplementary Figure\ \@ref(fig:figs2) displays the PRISMA flowchart.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
 
@@
 We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Supplementary Fig.\ \@ref(fig:figs2)).
+This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Supplementary Figure\ \@ref(fig:figs2)).
 We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills [@frick2014; @johnson2020; @kubicek2018; @lauer2019a; @linn1985; @moore2020; @uttal2013; @voyer1995; @yang2020].
@@
 
+The final sample size of articles was determined by including all articles that fulfilled the inclusion criteria described above.
 Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
@@
 One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigms used in the other articles.
-Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, digits = 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, digits = 1)` months; $Z = `r descs_pedrett2020$z`$ compared to all articles).
+Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, digits = 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, digits = 1)` months; $z = `r descs_pedrett2020$z`$ compared to all articles).
 We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Supplementary Fig.\ \@ref(fig:figs2)).
+This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Supplementary Figure\ \@ref(fig:figs2)).
 
@@
 The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs5).
-The correlation $r$ was not reported in any of the original articles [@harrer2021].
+The correlation $r$ was not reported in any of the original articles [see also @harrer2021].
 We therefore always assumed a correlation of $r = 0.50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx 0.50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
@@
 This model had three levels, with infant participants nested in experiments and experiments nested in articles [@vandennoortgate2013].
-We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for the two standard deviations (i.e., the random effects of experiments and articles) [@williams2018].
+We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for the two standard deviations [i.e., the random effects of experiments and articles\; @williams2018].
 A prior sensitivity analysis indicated that making these priors either more informative or less informative did not have a strong influence on the meta-analytic results (Supplementary Tables\ \@ref(tab:tabs7), \@ref(tab:tabs8), and\ \@ref(tab:tabs9)).
@@
 For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges' $g$) between male infants' mental rotation performance and female infants' mental rotation performance, weighted by its standard error.
-All Bayesian models were fitted using the brms package (Version `r packageVersion("brms")`) [@burkner2017; @burkner2018] in R (Version `r packageVersion("base")`) [@rcoreteam2021] and the Stan language (Version `r packageVersion("rstan")`) [@standevelopmentteam2022].
+All Bayesian models were fitted using the brms package [Version `r packageVersion("brms")`\; @burkner2017; @burkner2018] in R [Version `r packageVersion("base")`\; @rcoreteam2021] and the Stan language [Version `r packageVersion("rstan")`\; @standevelopmentteam2022].
 Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r print_big(n_iter)` draws (including `r print_big(n_warmup)` warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the $\widehat{R}$ and $N_\text{eff}$ statistics (Supplementary Fig.\ \@ref(fig:figs3)) [@vehtari2021].
+To verify the convergence of the Markov chains, we examined rank plots as well as the $\widehat{R}$ and $N_\text{eff}$ statistics [@vehtari2021\; Supplementary Figure\ \@ref(fig:figs3)].
 For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].
@@
 We examined the influence of three moderator variables on the mental rotation outcomes across experiments, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
-Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts [@schad2020] so that we could compare all-female samples versus mixed samples and all-male samples versus all-female samples.
+Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts so that we could compare all-female samples versus mixed samples and all-male samples versus all-female samples [@schad2020].
 Age was coded as a continuous predictor in years and centered by subtracting the average across all experiments.
@@
 We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression.
-To this end, we used the metafor package (Version `r packageVersion("metafor")`) [@viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs2)).
+To this end, we used the metafor package [Version `r packageVersion("metafor")`\; @viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs2)).
 These models were fitted using restricted maximum likelihood estimation (REML).
-To verify that this procedure converged on the most probable estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Fig.\ \@ref(fig:figs4)).
+To verify that this procedure converged on the most probable estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Figure\ \@ref(fig:figs4)).
 
@@
 Funnel plots visualize the relationship between standard errors and effect sizes.
-They were created by adapting code from the R package metaviz (Version `r packageVersion("metaviz")`) [@kossmeier2020].
+They were created by adapting code from the R package metaviz [Version `r packageVersion("metaviz")`\; @kossmeier2020].
 The Egger regression test is a formal statistical test for this relationship between standard errors and effect sizes, probing if the weighted linear regression weight of the effect sizes on the standard errors is significantly different from zero.
@@
 
-We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs5)) [@duval2000; @vevea1995; @vevea2005].
-
-## Data and code availability
-
-The data and code for this study are available in an Open Science Framework repository ([https://doi.org/10.17605/OSF.IO/K3WDG](https://doi.org/10.17605/OSF.IO/K3WDG)).
+We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias [@duval2000; @vevea1995; @vevea2005\; Supplementary Methods 2\; Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)\; Supplementary Figure\ \@ref(fig:figs5)].
+
+## Transparency and openness
+
+The data and code for this study are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
+This study was not preregistered.
 

### 2022-07-06 supplement.Rmd
Update for re-submission

@@
 \captionsetup[table]{name=Supplementary Table}
-\captionsetup[figure]{name=Supplementary Fig.}
+\captionsetup[figure]{name=Supplementary Figure}
 
@@
 Repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants and thus do not provide independent information.
-This is accounted for by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018].
+This is accounted for by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ [see Methods and @goulet-pelletier2018].
 However, the correlation between repeated measures tends to go unreported in research articles.
@@
 
-## Supplementary Methods 2 | Publication bias correction
+## Supplementary Methods 2: Publication bias correction
 
@@
 In our first step, we computed a trim-and-fill model by imputing possible effect sizes of non-published experiments [@duval2000].
-This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs5)).
+This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Figure\ \@ref(fig:figs5)).
 
 In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis.
-These models were based on the assumption that experiments yielding significant effects (i.e., small $P$ values) are more likely to get published.
-Specifically, we ran one selection model assuming a weight function with fixed $P$ value cutoffs [@vevea1995] at $P$ = 0.01, $P$ = 0.05, and $P$ = 0.30.
+These models were based on the assumption that experiments yielding significant effects (i.e., small $p$ values) are more likely to get published.
+Specifically, we ran one selection model assuming a weight function with fixed $p$ value cutoffs [@vevea1995] at $p$ = 0.01, $p$ = 0.05, and $p$ = 0.30.
 Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
@@
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ Available statistics                                       | Conversion to standardized mean difference (Hedges' $g$)                                    |
+| Available statistics                                           | Conversion to standardized mean difference (Hedges' $g$)                                    |
 +================================================================+=============================================================================================+
-| \ \ (1\) Cohen's $d$ and sample size                           | ${df}=2(n-1)$;\quad                                                                         |
+| (1\) Cohen's $d$ and sample size                               | ${df}=2(n-1)$;\quad                                                                         |
 | [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
@@
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (2\) $t$ statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
+| (2\) $t$ statistic and sample size [@rosenthal1991]            | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (3\) $F$ statistic and sample size [@lakens2013]           | $t=\sqrt{F}$;\quad then (2\)                                                                |
+| (3\) $F$ statistic and sample size [@lakens2013]               | $t=\sqrt{F}$;\quad then (2\)                                                                |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (4\) Mean difference between conditions [@lakens2013]      | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
+| (4\) Mean difference between conditions [@lakens2013]          | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (5\) Mean looking times$ per condition [@cumming2012]      | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
+| (5\) Mean looking times$ per condition [@cumming2012]          | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
 |                                                                | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
-| \ \ (6\) Mean novelty preference score [@lakens2013]           | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
+| (6\) Mean novelty preference score [@lakens2013]               | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
 +----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
@@
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| \ \ Available statistics               | Conversion to standardized mean difference (Hedges' $g$)                                         |
+| Available statistics                   | Conversion to standardized mean difference (Hedges' $g$)                                         |
 +========================================+==================================================================================================+
-| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-2$; \quad                                                    |
+| (1\) Cohen's $d$ and group sizes       | ${df}=n_\text{female}+n_\text{male}-2$; \quad                                                    |
 | [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
@@
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| \ \ (2\) $t$ statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
+| (2\) $t$ statistic and group sizes     | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
 | [@lakens2013]                          |                                                                                                  |
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| \ \ (3\) $F$ statistic and group sizes | $t=\sqrt{F}$;\quad then (2\)                                                                     |
+| (3\) $F$ statistic and group sizes     | $t=\sqrt{F}$;\quad then (2\)                                                                     |
 | [@lakens2013]                          |                                                                                                  |
 +----------------------------------------+--------------------------------------------------------------------------------------------------+
-| \ \ (4\) Mean differences between\     | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
-| \ \ conditions or preference scores    | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
+| (4\) Mean differences between\         | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
+| conditions or preference scores        | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
 | [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
@@
     label_2 = c(
-      "--", "--", "Weight function, $P$ value cutoffs [0.01, 0.05, 0.30]",
+      "--", "--", "Weight function, $p$ value cutoffs [0.01, 0.05, 0.30]",
       "One-tailed, moderate bias", "One-tailed, severe bias",
@@
 
-(ref:figs2-caption) **Literature search and selection process.** **a,** We searched four online databases as well as reviews and reference sections to identify articles in which mental rotation experiments in infants were reported.
-**b,** Experiments were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
-**c,** Redundant articles comprising the same experiment(s) were excluded.
+(ref:figs2-caption) **Literature search and selection process.** (A) We searched four online databases as well as reviews and reference sections to identify articles in which mental rotation experiments in infants were reported.
+(B) Experiments were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
+(C) Redundant articles comprising the same experiment(s) were excluded.
 \textsuperscript{a} = We decided to exclude two additional articles: one article because it was based on an uncommon experimental paradigm, differing substantially from all other articles, and another article because it was based on a sample of infants who were substantially older compared to all other articles.
@@
 plot_grid(
-  plotlist = plots_funnel_trim_fill, nrow = 1, labels = "auto",
+  plotlist = plots_funnel_trim_fill, nrow = 1, labels = "AUTO",
   label_size = 11, label_fontfamily = "Helvetica"
@@
 
-(ref:figs5-caption) **Trim-and-fill analysis.** As in Fig.\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (**a**) and in the meta-analysis of gender differences within each article (**b**).
+(ref:figs5-caption) **Trim-and-fill analysis.** As in Figure\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (A) and in the meta-analysis of gender differences within each article (B).
 The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines).

### 2022-07-06 manuscript_files/helper_functions.R

@@ -104,8 +104,8 @@ print_res_freq_table <- function(res_freq,
     Parameter = rownames(res_freq$b),
     Estimate = print_num(as.numeric(res_freq$b)),
     `$SE$` = print_num(res_freq$se),
-    `$Z$` = print_num(res_freq$zval),
-    `$P$` = ifelse(
+    `$z$` = print_num(res_freq$zval),
+    `$p$` = ifelse(
       res_freq$pval < 0.001, "< 0.001", print_num(res_freq$pval, digits = 3)
     ),
     ci_lower = print_num(res_freq$ci.lb),

### 2022-07-12 manuscript.Rmd
Update for re-submission

@@
 
-abstract: |
-  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
-We robustly found that male infants recognized rotated objects more reliably than female infants.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
-keywords: "mental rotation; spatial cognition; infants; gender; meta-analysis"
-
 bibliography      : "manuscript_files/references.bib"
@@
 
-# Gender differences in infant mental rotation
+\newpage
+
+\
+
+\newpage
+
+\resetlinenumber
+
+# Highlights
+
+* We analyzed effect sizes of 59 mental rotation experiments including 1,798 infants
+
+* Looking time reveals that 3--16-months-old infants are able to perform mental rotation
+
+* Mental rotation is more reliable in male infants compared to female infants
+
+\newpage
+
+# Abstract
+
+Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
+On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
+When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
+Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
+We robustly found that male infants recognized rotated objects more reliably than female infants.
+These findings indicate that gender differences in mental rotation are already present in the first months of life.
+
+\newpage
+
+# Introduction
 
@@
 
-## Transparency and openness
+## Data and code availability
 
 The data and code for this study are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
-This study was not preregistered.
 

### 2022-07-15 manuscript.Rmd
Update for re-submission

--- 2022-07-06 manuscript.Rmd
@@
   We have no conflicts of interest to disclose.
-  The data and code for this study are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
+  The data and code necessary to reproduce the analyses presented here are publicly accessible at the following URL: [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
+  The analyses presented here were not preregistered.
 
@@
 We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
-Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% [`r summ_reg$age.lower`, `r summ_reg$age.upper`].
+Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% CrI [`r summ_reg$age.lower`, `r summ_reg$age.upper`].
 We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]).
-Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`].
+Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% CrI [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`].
 The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.
@@
 coef_colnames <- c(
-  b_Intercept = expression("Intercept (Hedges" ~ italic(g) * ")"),
+  b_Intercept = expression("Intercept (Hedges'" ~ italic(g) * ")"),
   b_gender2M1 = expression("Females - mixed"),
@@
 (ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments.
-Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample).
+Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample; yellow = habituation task, all-male sample; red = habituation task, mixed-gender sample; purple = violation of expectation [VoE] task, mixed-gender sample).
 Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI).
@@
 We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here.
-For the meta-analysis of mental rotation performance (Figure\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
+For the meta-analysis of mental rotation performance (Figure\ \@ref(fig:fig3)A), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
 This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
 Nevertheless, a jackknife (leave-one-out) analysis confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)).
-For the meta-analysis of gender differences in mental rotation performance (Figure\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
+For the meta-analysis of gender differences in mental rotation performance (Figure\ \@ref(fig:fig3)B), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
 
@@
         labels = c(
-          expression(italic(P) > 0.05),
-          expression(italic(P) < 0.05),
-          expression(italic(P) < 0.01)
+          expression(italic(p) > 0.05),
+          expression(italic(p) < 0.05),
+          expression(italic(p) < 0.01)
         )
@@
 
-## Transparency and openness
-
-The data and code for this study are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
-This study was not preregistered.
+## Data and code availability
+
+The data and code necessary to reproduce the analyses presented here are publicly accessible at the following URL: [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
 

### 2022-07-15 supplement.Rmd
Update for re-submission

@@
 # Add footnotes
-tabs8$` `[8] <- str_c(tabs8$` `[8], "\\textsuperscript{a}")
-tabs8$` `[9] <- str_c(tabs8$` `[9], "\\textsuperscript{b}")
-tabs8$` `[10] <- str_c(tabs8$` `[10], "\\textsuperscript{c}")
-tabs8$` `[11] <- str_c(tabs8$` `[11], "\\textsuperscript{d}")
+colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "\\textsuperscript{a}")
+tabs8$` `[8] <- str_c(tabs8$` `[8], "\\textsuperscript{b}")
+tabs8$` `[9] <- str_c(tabs8$` `[9], "\\textsuperscript{c}")
+tabs8$` `[10] <- str_c(tabs8$` `[10], "\\textsuperscript{d}")
+tabs8$` `[11] <- str_c(tabs8$` `[11], "\\textsuperscript{e}")
 
@@
     "\\scriptsize",
-    "\\textsuperscript{a} = an uninformative (uniform) prior on the mean effect, ",
-    "\\textsuperscript{b} = an informative (normal) prior on the mean effect, ",
-    "\\textsuperscript{c} = an uninformative (uniform) prior on the standard deviations, ",
-    "\\textsuperscript{d} = an informative (Student-$t$) prior on the standard deviations."
+    "\\textsuperscript{a} = violation of expectation, ",
+    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
+    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
+    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
+    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
   ),

### 2022-07-22 manuscript.Rmd
Update for re-submission
Developmental Science

@@
     corresponding : "yes"
-    address       : "Stephanstraße 1a"
+    address       : "Stephanstraße 1a, 04103 Leipzig, Germany"
     email         : "enge@cbs.mpg.de"
@@
 authornote: |
-  We have no conflicts of interest to disclose.
-  The data and code necessary to reproduce the analyses presented here are publicly accessible at the following URL: [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
-  The analyses presented here were not preregistered.
-
-abstract: |
-  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
-We robustly found that male infants recognized rotated objects more reliably than female infants.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
-keywords: "mental rotation; spatial cognition; infants; gender; meta-analysis"
+  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
+
+  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
+
+  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
+
+  The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
+
+  M.A.S.
+was supported by the German Research Foundation (DFG Grants 433715509 and 433758790), the European Research Council (ERC Starting Grant 850752), and a Jacobs Foundation Research Scholarship.
+A.E.
+was supported by a PhD scholarship from the German Academic Scholarship Foundation (Studienstiftung des deutschen Volkes).
+
+  The authors declare that they have no conflicts of interest to disclose.
 
@@
 
+\setcounter{page}{1}
+\resetlinenumber
+
 # Gender differences in infant mental rotation
+
+\bigskip
+
+# Research highlights
+
+* We analyzed effect sizes of 59 mental rotation experiments including 1,798 infants
+
+* Looking time reveals that 3–16-months-old infants are able to perform mental rotation
+
+* Mental rotation is more reliable in male infants compared to female infants
+
+# Abstract
+
+Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
+On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
+When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
+Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
+We robustly found that male infants recognized rotated objects more reliably than female infants.
+These findings indicate that gender differences in mental rotation are already present in the first months of life.
+
+*Keywords*: mental rotation; spatial cognition; spatial ability; infants; gender; meta-analysis
+
+\newpage
+
+# Introduction
 
@@
 
-The data and code necessary to reproduce the analyses presented here are publicly accessible at the following URL: [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
+The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
 

### 2022-11-04 supplement.Rmd
Fix selection model description

@@
 These models were based on the assumption that experiments yielding significant effects (i.e., small $p$ values) are more likely to get published.
-Specifically, we ran one selection model assuming a weight function with fixed $p$ value cutoffs [@vevea1995] at $p$ = 0.01, $p$ = 0.05, and $p$ = 0.30.
+Specifically, we ran one selection model assuming a weight function with fixed $p$ value cutoffs [@vevea1995] at $p$ = 0.01 and $p$ = 0.05.
 Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
@@
     label_2 = c(
-      "--", "--", "Weight function, $p$ value cutoffs [0.01, 0.05, 0.30]",
+      "--", "--", "Weight function, $p$ value cutoffs [0.01, 0.05]",
       "One-tailed, moderate bias", "One-tailed, severe bias",

### 2022-11-07 manuscript.Rmd
Exclude lauer2016 (redundant), kellmann1984 (task)

@@
 
-In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`\; Supplementary Table\ \@ref(tab:tabs1)) [@kellman1984; @rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @lauer2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
+In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`\; Supplementary Table\ \@ref(tab:tabs1)) [@rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
 All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation` experiments) or violation of expectation experiments (`r descriptives$n_experiments_voe` experiments) [@fantz1964; @baillargeon1985].

### 2022-11-07 manuscript.Rmd
Use split experiments when available
Using mixed experiments by default would bias the beta for gender

@@
 
+# Combine both strategies but preferring mixed experiments
+dat_both_mixed <- filter(
+  dat_meta_all, gender_split %in% c("mixed", "mixed_only", "split_only")
+)
+
 # Combine both strategies but preferring split experiments
@@
 
-# Combine both strategies but preferring mixed experiments
-dat_both_mixed <- filter(
-  dat_meta_all, gender_split %in% c("mixed", "mixed_only", "split_only")
-)
-
-# We go ahead with the last solution (i.e., prefer mixed experiments) as to use
+# We go ahead with the last solution (i.e., prefer split experiments) as to use
 # the maximum amount of information while not biasing the gender results
-dat_meta <- dat_both_mixed
+dat_meta <- dat_both_split
 
@@
 ```{r child = "supplement.Rmd"}
+
 ```

### 2022-11-08 supplement.Rmd
Update for resubmission

@@
 These models were based on the assumption that experiments yielding significant effects (i.e., small $p$ values) are more likely to get published.
-Specifically, we ran one selection model assuming a weight function with fixed $p$ value cutoffs [@vevea1995] at $p$ = 0.01 and $p$ = 0.05.
+Specifically, we ran one selection model assuming a weight function with fixed $p$ value cutoffs [@vevea1995] at $p$ = 0.05 and $p$ = 0.01.
 Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
@@
   caption = "PRISMA 2020 checklist", font_size = "scriptsize",
-  landscape = TRUE, align = "p{1.5cm}p{2.5cm}p{1cm}p{12cm}p{5.5cm}",
+  landscape = TRUE,
+  align = "lllll" # For Word
+  # align = "p{1.5cm}p{2.5cm}p{1cm}p{12cm}p{5.5cm}" # For LaTeX
 )
@@
     label_2 = c(
-      "--", "--", "Weight function, $p$ value cutoffs [0.01, 0.05]",
+      "--", "--", "Weight function, $p$ value cutoffs [0.05, 0.01]",
       "One-tailed, moderate bias", "One-tailed, severe bias",

### 2023-02-06 main.qmd
Re-name scripts

--- 2022-11-07 manuscript.Rmd
@@
 
-* We analyzed effect sizes of 59 mental rotation experiments including 1,798 infants
+* We analyzed effect sizes of `r descriptives$n_experiments` mental rotation experiments including `r formatC(descriptives$n_infants, big.mark = ",")` infants
 
@@
 When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
+Here we analyzed effect sizes derived from `r descriptives$n_experiments` experiments conducted in `r formatC(descriptives$n_infants, big.mark = ",")` infants aged 3--16 months.
 We robustly found that male infants recognized rotated objects more reliably than female infants.
@@
 The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`.
-We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
+We found no difference between all-female and mixed-gender samples, $b = `r summ_reg$female_mixed`$, 95% CrI [`r summ_reg$female_mixed.lower`, `r summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
 Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% CrI [`r summ_reg$age.lower`, `r summ_reg$age.upper`].
@@
 
-(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments.
+(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the `r descriptives$n_experiments` individual experiments.
 Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample; yellow = habituation task, all-male sample; red = habituation task, mixed-gender sample; purple = violation of expectation [VoE] task, mixed-gender sample).
@@
 We found that on average, male infants looked longer at novel rotated objects compared to female infants.
-This effect was small to medium and unrelated to age in the current range.
-
-We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
+This effect was small and unrelated to age in the current range.
+
+We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported separate effect sizes for males and females.
 The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference would be more likely to report separate effect sizes for males and females.

### 2023-02-06 supplement.qmd
Re-name scripts

--- 2022-11-08 supplement.Rmd
@@
 For the meta-analysis of gender differences, the results of the trim-and-fill analysis suggested that no additional experiments had to be imputed to compensate for publication bias.
+
+```{r, meta_pos}
+# Re-code familiarity preference to be treated the same as novelty preference
+dat_meta_pos <- mutate(dat_meta, gi = abs(gi))
+
+# Specify new priors
+prior_meta_pos <- c(
+  set_prior("normal(0, 1)", class = "b", lb = 0),
+  set_prior("cauchy(0, 0.3)", class = "sd")
+)
+
+# Re-fit meta-analysis using the new data and priors
+res_meta_pos <- update(
+  res_meta,
+  newdata = dat_meta_pos,
+  prior = prior_meta_pos,
+  file = here(models_dir, "res_meta_pos"),
+  file_refit = brms_file_refit
+)
+summary(res_meta_pos)
+
+# Extract posterior draws for the meta-analytic effects
+spread_draws(res_meta_pos, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+  # Compute variances and ICC from standard deviations
+  mutate(
+    intercept = b_Intercept,
+    sigma_article = sd_article__Intercept,
+    sigma_experiment = `sd_article:experiment__Intercept`,
+    sigma2_article = sigma_article^2,
+    sigma2_experiment = sigma_experiment^2,
+    sigma2_total = sigma2_article + sigma2_experiment,
+    icc = sigma2_article / sigma2_total,
+    .keep = "unused"
+  ) -> draws_meta_pos
+
+# Summarize as means and 95% credible intervals
+(summ_meta_pos <- as.list(mean_qi(draws_meta_pos)))
+```
+
+```{r, figs5new, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:figs5new-caption)"}
+# Get posterior draws for the effect *in each experiment*
+epred_draws_meta_pos <-
+  epred_draws(res_meta_pos, dat_meta_pos, ndraws = NULL) %>%
+  mutate(experiment_f = factor(experiment))
+
+# Create forest plot
+dat_meta_pos %>%
+  # Make sure the plot will be ordered alphabetically by experiment IDs
+  arrange(experiment) %>%
+  mutate(
+    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
+    # Show article labels only for the first experiment (row) per article
+    article = if_else(article == lag(article, default = ""), "", article),
+    # Compute frequentist confidence intervals for each experiment
+    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
+  ) %>%
+  # Prepare plotting canvas
+  ggplot(aes(x = gi, y = experiment_f)) +
+  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
+  # Add article and group labels as text on the left
+  geom_text(aes(x = -9.9, label = article), hjust = 0) +
+  geom_text(aes(x = -7.1, label = group), hjust = 0) +
+  # Add experiment-specific effect sizes and CIs as text on the right
+  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
+  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
+  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
+  # Add Bayesian credible intervals for each experiment
+  stat_interval(
+    aes(x = .epred),
+    data = epred_draws_meta_pos,
+    alpha = .8,
+    point_interval = "mean_qi",
+    .width = c(0.5, 0.95),
+  ) +
+  scale_color_grey(
+    start = 0.85, end = 0.65,
+    labels = as_mapper(~ scales::percent(as.numeric(.x)))
+  ) +
+  # Add experiment-specific effect sizes and CIs as dots with error bars
+  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
+  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
+  # Add posterior distribution for the meta-analytic effect
+  stat_halfeye(
+    aes(x = intercept, y = -1),
+    draws_meta_pos,
+    point_interval = "mean_qi",
+    .width = c(0.95)
+  ) +
+  annotate(
+    "text",
+    x = c(-9.9, 3.7, 4.4, 5.1),
+    y = -0.5,
+    label = c(
+      "Three-level model",
+      print_num(summ_meta_pos$intercept),
+      print_num(summ_meta_pos$intercept.lower),
+      print_num(summ_meta_pos$intercept.upper)
+    ),
+    hjust = c(0, 1, 1, 1),
+    fontface = "bold"
+  ) +
+  # Add column headers
+  annotate(
+    "rect",
+    xmin = -Inf,
+    xmax = Inf,
+    ymin = descriptives$n_experiments + 0.5,
+    ymax = Inf,
+    fill = "white"
+  ) +
+  annotate(
+    "text",
+    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
+    y = descriptives$n_experiments + 1.5,
+    label = c(
+      "Article",
+      "Experiment",
+      "Effect size plot",
+      "Effect size",
+      "2.5%",
+      "97.5%"
+    ),
+    hjust = c(0, 0, 0.5, 1, 1, 1),
+    fontface = "bold"
+  ) +
+  # Styling
+  coord_cartesian(
+    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
+  ) +
+  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
+  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    size = "Sample size",
+    color = "CrI level"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.position = "bottom",
+    axis.text.x = element_text(family = "Helvetica", color = "black"),
+    axis.text.y = element_blank(),
+    axis.ticks.x = element_line(colour = "black"),
+    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
+    axis.title.y = element_blank(),
+    panel.grid = element_blank(),
+    text = element_text(family = "Helvetica")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "figs5new_meta_pos.pdf"), width = 12, height = 14)
+```
+
+(ref:figs5new-caption) **Meta-analysis of mental rotation performance, accounting for familiarity preferences.** Analysis and formatting are the same as in Figure 2, but with effect sizes that indicated a familiarity preference (i.e., longer looking times at the familiar stimulus as compared to the novel stimulus) being re-coded as providing positive evidence for (preliminary) mental rotation ability.
+
+```{r, meta_gender_pos}
+# Re-code familiarity preference to be treated the same as novelty preference
+dat_gender_pos <- mutate(dat_gender, gi = abs(gi))
+
+# Use the same priors as for the main meta-analysis
+prior_gender_pos <- prior_meta_pos
+
+# Re-fit meta-analysis
+res_gender_pos <- update(
+  res_gender,
+  newdata = dat_gender_pos,
+  prior = prior_gender_pos,
+  file = here(models_dir, "res_gender_pos"),
+  file_refit = brms_file_refit
+)
+summary(res_gender_pos)
+
+# Extract posterior draws for the meta-analytic effects
+spread_draws(res_gender_pos, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+  # Compute variances and ICC from standard deviations
+  mutate(
+    intercept = b_Intercept,
+    sigma_article = sd_article__Intercept,
+    sigma_experiment = `sd_article:experiment__Intercept`,
+    sigma2_article = sigma_article^2,
+    sigma2_experiment = sigma_experiment^2,
+    sigma2_total = sigma2_article + sigma2_experiment,
+    icc = sigma2_article / sigma2_total,
+    .keep = "unused"
+  ) -> draws_gender_pos
+
+# Summarize as means and 95% credible intervals
+(summ_gender_pos <- as.list(mean_qi(draws_gender_pos)))
+```
+
+```{r, figs6new, include=TRUE, fig.height=8, fig.width=12, fig.cap="(ref:figs6new-caption)"}
+# Get posterior draws for the effect *in each experiment*
+epred_draws_gender_pos <-
+  epred_draws(res_gender_pos, dat_gender_pos, ndraws = NULL) %>%
+  mutate(experiment_f = factor(experiment))
+
+# Create forest plot
+dat_gender_pos %>%
+  # Make sure the plot will be ordered alphabetically by experiment IDs
+  arrange(experiment) %>%
+  mutate(
+    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
+    # Show article labels only for the first experiment (row) per article
+    article = if_else(article == lag(article, default = ""), "", article),
+    # Compute frequentist confidence intervals
+    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
+    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
+  ) %>%
+  # Prepare plotting canvas
+  ggplot(aes(x = gi, y = experiment_f)) +
+  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
+  # Add article and group labels as text on the left
+  geom_text(aes(x = -9.9, label = article), hjust = 0) +
+  geom_text(aes(x = -7.1, label = group), hjust = 0) +
+  # Add experiment-specific effect sizes and CIs as text on the right
+  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
+  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
+  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
+  # Add Bayesian credible intervals for each experiment
+  stat_interval(
+    aes(x = .epred),
+    data = epred_draws_gender_pos,
+    alpha = .8,
+    point_interval = "mean_qi",
+    .width = c(0.5, 0.95),
+  ) +
+  scale_color_grey(
+    start = 0.85, end = 0.65,
+    labels = as_mapper(~ scales::percent(as.numeric(.x)))
+  ) +
+  # Add experiment-specific effect sizes and CIs as dots with error bars
+  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
+  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
+  # Add posterior distribution for the meta-analytic effect
+  stat_halfeye(
+    aes(x = intercept, y = -1),
+    draws_gender_pos,
+    point_interval = "mean_qi",
+    .width = c(0.95)
+  ) +
+  annotate(
+    "text",
+    x = c(-9.9, 3.7, 4.4, 5.1),
+    y = -0.5,
+    label = c(
+      "Three-level model",
+      print_num(summ_gender_pos$intercept),
+      print_num(summ_gender_pos$intercept.lower),
+      print_num(summ_gender_pos$intercept.upper)
+    ),
+    hjust = c(0, 1, 1, 1),
+    fontface = "bold"
+  ) +
+  # Add column headers
+  annotate(
+    "rect",
+    xmin = -Inf,
+    xmax = Inf,
+    ymin = nrow(dat_gender_pos) + 0.5,
+    ymax = Inf,
+    fill = "white"
+  ) +
+  annotate(
+    "text",
+    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
+    y = nrow(dat_gender_pos) + 1.5,
+    label = c(
+      "Article",
+      "Experiment",
+      "Effect size plot",
+      "Effect size",
+      "2.5%",
+      "97.5%"
+    ),
+    hjust = c(0, 0, 0.5, 1, 1, 1),
+    fontface = "bold"
+  ) +
+  # Styling
+  coord_cartesian(
+    ylim = c(-1.5, nrow(dat_gender_pos) + 2), expand = FALSE, clip = "off"
+  ) +
+  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
+  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
+  labs(
+    x = expression("Hedges'" ~ italic("g")),
+    size = "Sample size",
+    color = "CrI level"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.position = "bottom",
+    axis.text.x = element_text(family = "Helvetica", color = "black"),
+    axis.text.y = element_blank(),
+    axis.ticks.x = element_line(colour = "black"),
+    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
+    axis.title.y = element_blank(),
+    panel.grid = element_blank(),
+    text = element_text(family = "Helvetica")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "figs6new_gender_pos.pdf"), width = 12, height = 8)
+```
+
+(ref:figs6new-caption) **Meta-analysis of gender differences, accounting for familiarity preferences.** Analysis and formatting are the same as in Supplementary Figure 4, but with one effect size [@moore2011] re-coded as a male advantage (rather than as a female advantage) in mental rotation performance.
+Male infants in this study showed a familiarity preference (i.e., longer looking times at the familiar stimulus as compared to the novel stimulus), which may be interpreted as preliminary mental rotation ability, while female infants showed no discrimination between stimuli.

### 2023-02-08 index.qmd
Initialize Quarto book

--- 2022-11-07 manuscript.Rmd
@@
----
-title             : "Gender differences in infant mental rotation"
-shorttitle        : "Infant mental rotation"
+# Welcome {.unnumbered}
 
-author:
-  - name          : "Alexander Enge"
-    affiliation   : "1,2"
-    corresponding : "yes"
-    address       : "Stephanstraße 1a, 04103 Leipzig, Germany"
-    email         : "enge@cbs.mpg.de"
-  - name          : "Shreya Kapoor"
-    affiliation   : "1"
-  - name          : "Anne-Sophie Kieslinger"
-    affiliation   : "1"
-  - name          : "Michael A. Skeide"
-    affiliation   : "1"
-affiliation:
-  - id            : "1"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
-  - id            : "2"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
+This webpage contains the code and results for the following paper:
 
-authornote: |
-  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
+> Enge, A., Kapoor, S., Kieslinger, A.-S., & Skeide, M. A. (*under review*). A meta-analysis of mental rotation in the first years of life
 
-  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
+## Acknowledgments
 
-  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
-
-  The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
-
-  M.A.S.
-was supported by the German Research Foundation (DFG Grants 433715509 and 433758790), the European Research Council (ERC Starting Grant 850752), and a Jacobs Foundation Research Scholarship.
-A.E.
-was supported by a PhD scholarship from the German Academic Scholarship Foundation (Studienstiftung des deutschen Volkes).
+M.A.S. was supported by the German Research Foundation (DFG Grants 433715509 and 433758790), the European Research Council (ERC Starting Grant 850752), and a Jacobs Foundation Research Scholarship.
+A.E. was supported by a PhD scholarship from the German Academic Scholarship Foundation (Studienstiftung des deutschen Volkes).
 
 The authors declare that they have no conflicts of interest to disclose.
-
-bibliography      : "manuscript_files/references.bib"
-csl               : "manuscript_files/apa.csl"
-
-appendix          : "supplement.Rmd"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa7"
-classoption       : "man,donotrepeattitle"
-fontsize          : "10pt"
-output            : "papaja::apa6_pdf"
-
-header-includes:
-  - \geometry{a4paper}
-  - \raggedbottom
-  - \usepackage[all]{nowidow}
-  - \usepackage{lineno}
-  - \usepackage{makecell}
-  - \usepackage{setspace}
-  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
-  - \captionsetup[table]{belowskip=20pt,labelfont=bf,labelsep=period,textfont=bf,textformat=tabletext}
-  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=period,textfont=normalfont}
----
-
-```{r, setup, include=FALSE}
-# Load packages
-library(papaja)
-library(here)
-library(readxl)
-library(scales)
-library(tidyverse)
-library(furrr)
-library(metafor)
-library(brms)
-library(tidybayes)
-library(cowplot)
-
-# Load custom helper functions
-source(here("manuscript_files", "helper_functions.R"))
-
-# Re-run steps that take a long time?
-run <- list(
-  bayesian_models = FALSE,
-  jackknife_analysis = FALSE,
-  sensitivity_analysis = FALSE
-)
-
-# Global chunk options
-knitr::opts_chunk$set(
-  include = FALSE,
-  message = FALSE,
-  fig.align = "center",
-  fig.height = 10,
-  fig.pos = "tp",
-  fig.width = 7.5,
-  out.width = "100%",
-  warning = FALSE
-)
-
-# Options for MCMC sampling when fitting Bayesian multilevel models
-n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
-n_warmup <- 2000 # Warmup samples per chain
-n_chains <- 4 # Number of (parallel) chains
-seed <- 1234 # Random seed to make the results reproducible
-
-# Directory paths
-data_dir <- here("data")
-models_dir <- here("results/models")
-figures_dir <- here("results/figures")
-tables_dir <- here("results/tables")
-
-# Read the relevant spreadsheets
-raw_screen <- read_tsv(here(data_dir, "02_screen.tsv"), na = "NA")
-raw_meta <- read_tsv(here(data_dir, "03_meta.tsv"), na = "NA")
-raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")
-
-# Add columns to the table of experiments for the meta-analysis
-raw_meta %>%
-  mutate(
-
-    # Add unique experiment identifier
-    experiment = str_c(year, article, group, sep = ", "),
-
-    # Add difference between condition means
-    mean_diff = case_when(
-      !is.na(mean_diff) ~ mean_diff,
-      TRUE ~ mean_novel - mean_familiar
-    ),
-    # Add d_z from paired-samples t-test of condition means (Rosenthal, 1991)
-    d_z_t = t / sqrt(sample_size),
-    # Add d_z from ANOVA F statistic via conversion to a t statistic
-    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
-    # Add d_z from mean and standard deviation of the difference
-    d_z_diff = mean_diff / sd_diff,
-    # Add d_av from mean difference and standard deviations
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
-    d_av = mean_diff / sd_av,
-    # Add d from one-sample t-test of novelty preference scores
-    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,
-
-    # Choose one type of outcome variable for each experiment
-    di = case_when(
-      # 1. If d was reported directed
-      !is.na(d) ~ d,
-      # 2. If a paired-samples t-test was reported
-      !is.na(d_z_t) ~ d_z_t,
-      # 3. If an ANOVA was reported
-      !is.na(d_z_f) ~ d_z_f,
-      # 4. If the difference between means and its SD were reported
-      !is.na(d_z_diff) ~ d_z_diff,
-      # 5. If the individual condition means and their SDs were reported
-      !is.na(d_av) ~ d_av,
-      # 6. If a novelty preference score and its SD were reported
-      !is.na(d_nov_pref) ~ d_nov_pref
-    ),
-    # Keep track which type of outcome measure was chosen for each article
-    di_type = case_when(
-      !is.na(d) ~ "d",
-      !is.na(d_z_t) ~ "d_z_t",
-      !is.na(d_z_f) ~ "d_z_f",
-      !is.na(d_z_diff) ~ "d_z_diff",
-      !is.na(d_av) ~ "d_av",
-      !is.na(d_nov_pref) ~ "d_nov_pref",
-      TRUE ~ "none"
-    ) %>%
-      factor(levels = c(
-        "d", "d_z_t", "d_z_f", "d_z_diff", "d_av", "d_nov_pref", "none"
-      )),
-
-    # Apply small sample correction using Hedges' exact method
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    dfi = 2 * (sample_size - 1),
-    ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
-    gi = di * ji,
-
-    # Recode gender as a categorical (factor) variable for meta-regression
-    gender = case_when(
-      female_percent == 1.0 ~ "Female",
-      female_percent == 0.0 ~ "Male",
-      TRUE ~ "Mixed"
-    ) %>% factor(levels = c("Mixed", "Female", "Male")),
-
-    # Recode mean sample age in years (mean-centered) for meta-regression
-    age = age_mean / 365.25,
-    age_c = age - mean(age, na.rm = TRUE),
-
-    # Recode task type as a categorical (factor) variable for meta-regression
-    task = factor(task, levels = c("Habituation", "VoE")),
-
-    # Combine gender and task into one column for plotting
-    gender_task = factor(
-      str_c(gender, task, sep = ", "),
-      levels = c(
-        "Female, Habituation",
-        "Male, Habituation",
-        "Mixed, Habituation",
-        "Mixed, VoE"
-      )
-    )
-  ) %>%
-  # Order rows by experiment ID
-  arrange(experiment) -> dat_all
-
-# Get an overview of the different effect sizes
-dat_all %>%
-  select(
-    article,
-    group,
-    gender_split,
-    gi,
-    di,
-    di_type,
-    d,
-    d_z_t,
-    d_z_f,
-    d_z_diff,
-    d_av,
-    d_nov_pref
-  ) %>%
-  print(n = Inf)
-
-# Compute standard errors of the effect sizes based on assumed correlation
-# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
-# You'll find a sensitivity analysis for `r_assumed` in the `supplement.Rmd`
-r_assumed <- 0.5
-dat_all %>%
-  mutate(
-    ni = sample_size,
-    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
-      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
-    sei = sqrt(vi)
-  ) %>%
-  filter(!is.na(gi)) -> dat_meta_all
-
-# Show number of experiments per gender grouping strategy (mixed/split)
-table(dat_meta_all$gender_split)
-
-# Extract either split or mixed experiments only
-dat_split <- filter(dat_meta_all, gender_split %in% c("split", "split_only"))
-dat_mixed <- filter(dat_meta_all, gender_split %in% c("mixed", "mixed_only"))
-
-# Combine both strategies but preferring mixed experiments
-dat_both_mixed <- filter(
-  dat_meta_all, gender_split %in% c("mixed", "mixed_only", "split_only")
-)
-
-# Combine both strategies but preferring split experiments
-dat_both_split <- filter(
-  dat_meta_all, gender_split %in% c("split", "mixed_only", "split_only")
-)
-
-# We go ahead with the last solution (i.e., prefer split experiments) as to use
-# the maximum amount of information while not biasing the gender results
-dat_meta <- dat_both_split
-
-# Extract some descriptive statistics so we can paste them in the main text
-descriptives <- list(
-  n_articles = length(unique(dat_meta$article)),
-  n_experiments = nrow(dat_meta),
-  n_infants = sum(dat_meta$sample_size),
-  percent_female = mean(dat_meta$female_percent, na.rm = TRUE),
-  min_age_months = as.integer(min(dat_meta$age_min, na.rm = TRUE) / 30.417),
-  max_age_months = as.integer(max(dat_meta$age_max, na.rm = TRUE) / 30.417),
-  mean_age_weighted = print_days_months(
-    sum(dat_meta$age_mean * dat_meta$ni) / (sum(dat_meta$ni)),
-    long = TRUE
-  ),
-  n_experiments_habituation = nrow(filter(dat_meta, task == "Habituation")),
-  n_experiments_voe = nrow(filter(dat_meta, task == "VoE"))
-)
-```
-
-\setcounter{page}{1}
-\resetlinenumber
-
-# Gender differences in infant mental rotation
-
-\bigskip
-
-# Research highlights
-
-* We analyzed effect sizes of 59 mental rotation experiments including 1,798 infants
-
-* Looking time reveals that 3–16-months-old infants are able to perform mental rotation
-
-* Mental rotation is more reliable in male infants compared to female infants
-
-# Abstract
-
-Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
-We robustly found that male infants recognized rotated objects more reliably than female infants.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
-
-*Keywords*: mental rotation; spatial cognition; spatial ability; infants; gender; meta-analysis
-
-\newpage
-
-# Introduction
-
-The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life [@moore2020; @johnson2020].
-Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-
-Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
-Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents suggests only a small-to-medium difference [mean weighted $g = 0.39$\; @lauer2019a].
-Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
-
-In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`\; Supplementary Table\ \@ref(tab:tabs1)) [@rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
-All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation` experiments) or violation of expectation experiments (`r descriptives$n_experiments_voe` experiments) [@fantz1964; @baillargeon1985].
-These experiments comprised real world stimuli [e.g., toy objects\; @antrilli2016], three-dimensional digital stimuli [e.g., cube figures\; @moore2008], or two-dimensional digital stimuli [e.g., digits\; @quinn2008].
-In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or with the familiar object at a new angle.
-Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation.
-In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle.
-Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle.
-Subsequently, the object disappeared behind an occluder.
-Finally, the occluder was removed and either the object or its mirror object were shown.
-Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle.
-In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
-
-Following previous work in older populations, we hypothesized that looking time differences in mental rotation experiments are on average longer in male compared to female infants.
-Effect sizes were assumed to be small.
-
-```{r, meta}
-# Specify priors
-prior_meta <- c(
-  set_prior("normal(0, 1)", class = "b"),
-  set_prior("cauchy(0, 0.3)", class = "sd")
-)
-
-# Run prior predictive simulation
-dir.create(models_dir, showWarnings = FALSE, recursive = TRUE)
-brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
-res_prior_meta <- brm(
-  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
-  data = dat_meta,
-  prior = prior_meta,
-  sample_prior = "only",
-  save_pars = save_pars(all = TRUE),
-  chains = n_chains,
-  iter = n_iter,
-  warmup = n_warmup,
-  cores = n_chains,
-  control = list(adapt_delta = 0.99),
-  seed = seed,
-  file = here(models_dir, "res_prior_meta"),
-  file_refit = brms_file_refit
-)
-summary(res_prior_meta)
-
-# Run Bayesian multilevel model
-res_meta <- update(
-  res_prior_meta,
-  sample_prior = FALSE,
-  seed = seed,
-  file = here(models_dir, "res_meta"),
-  file_refit = brms_file_refit
-)
-summary(res_meta)
-
-# Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_meta <- hypothesis(res_meta, "Intercept > 0")$hypothesis)
-
-# Extract posterior draws for the meta-analytic effects
-spread_draws(res_meta, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC from standard deviations
-  mutate(
-    intercept = b_Intercept,
-    sigma_article = sd_article__Intercept,
-    sigma_experiment = `sd_article:experiment__Intercept`,
-    sigma2_article = sigma_article^2,
-    sigma2_experiment = sigma_experiment^2,
-    sigma2_total = sigma2_article + sigma2_experiment,
-    icc = sigma2_article / sigma2_total,
-    .keep = "unused"
-  ) -> draws_meta
-
-# Summarize as means and 95% credible intervals
-(summ_meta <- as.list(mean_qi(draws_meta)))
-```
-
-```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
-# Get posterior draws for the effect *in each experiment*
-epred_draws_meta <- epred_draws(res_meta, dat_meta, ndraws = NULL) %>%
-  mutate(experiment_f = factor(experiment))
-
-# Create forest plot
-dat_meta %>%
-  # Make sure the plot will be ordered alphabetically by experiment IDs
-  arrange(experiment) %>%
-  mutate(
-    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
-    # Show article labels only for the first experiment (row) per article
-    article = if_else(article == lag(article, default = ""), "", article),
-    # Compute frequentist confidence intervals for each experiment
-    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
-    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
-  ) %>%
-  # Prepare plotting canvas
-  ggplot(aes(x = gi, y = experiment_f)) +
-  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
-  # Add article and group labels as text on the left
-  geom_text(aes(x = -9.9, label = article), hjust = 0) +
-  geom_text(aes(x = -7.1, label = group), hjust = 0) +
-  # Add experiment-specific effect sizes and CIs as text on the right
-  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
-  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
-  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
-  # Add Bayesian credible intervals for each experiment
-  stat_interval(
-    aes(x = .epred),
-    data = epred_draws_meta,
-    alpha = .8,
-    point_interval = "mean_qi",
-    .width = c(0.5, 0.95),
-  ) +
-  scale_color_grey(
-    start = 0.85, end = 0.65,
-    labels = as_mapper(~ scales::percent(as.numeric(.x)))
-  ) +
-  # Add experiment-specific effect sizes and CIs as dots with error bars
-  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
-  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
-  # Add posterior distribution for the meta-analytic effect
-  stat_halfeye(
-    aes(x = intercept, y = -1),
-    draws_meta,
-    point_interval = "mean_qi",
-    .width = c(0.95)
-  ) +
-  annotate(
-    "text",
-    x = c(-9.9, 3.7, 4.4, 5.1),
-    y = -0.5,
-    label = c(
-      "Three-level model",
-      print_num(summ_meta$intercept),
-      print_num(summ_meta$intercept.lower),
-      print_num(summ_meta$intercept.upper)
-    ),
-    hjust = c(0, 1, 1, 1),
-    fontface = "bold"
-  ) +
-  # Add column headers
-  annotate(
-    "rect",
-    xmin = -Inf,
-    xmax = Inf,
-    ymin = descriptives$n_experiments + 0.5,
-    ymax = Inf,
-    fill = "white"
-  ) +
-  annotate(
-    "text",
-    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
-    y = descriptives$n_experiments + 1.5,
-    label = c(
-      "Article",
-      "Experiment",
-      "Effect size plot",
-      "Effect size",
-      "2.5%",
-      "97.5%"
-    ),
-    hjust = c(0, 0, 0.5, 1, 1, 1),
-    fontface = "bold"
-  ) +
-  # Styling
-  coord_cartesian(
-    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
-  ) +
-  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
-  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
-  labs(
-    x = expression("Hedges'" ~ italic("g")),
-    size = "Sample size",
-    color = "CrI level"
-  ) +
-  theme_minimal() +
-  theme(
-    legend.position = "bottom",
-    axis.text.x = element_text(family = "Helvetica", color = "black"),
-    axis.text.y = element_blank(),
-    axis.ticks.x = element_line(colour = "black"),
-    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
-    axis.title.y = element_blank(),
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica")
-  )
-
-# Save the plot
-dir.create(figures_dir, showWarnings = FALSE)
-ggsave(here(figures_dir, "fig1_meta.pdf"), width = 12, height = 14)
-```
-
-(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
-White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
-Gray bars indicate the 50% and 95% credible intervals (CrI) from the Bayesian model, which take into account that experiments with smaller sample sizes or more extreme effect sizes provide less reliable information.
-The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
-
-# Results
-
-## Mental rotation performance
-
-For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects.
-Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
-Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Figure\ \@ref(fig:fig1)).
-The probability for this effect being greater than zero was `r print_prob(hyp_meta$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level.
-Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.
-
-## Effects of gender, age, and task type
-
-```{r, reg}
-# Set numerical contrasts for factor variables
-contrasts(dat_meta$gender) <- MASS::contr.sdif(3)
-contrasts(dat_meta$task) <- MASS::contr.sdif(2)
-
-# Specify priors
-prior_reg <- c(
-  set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
-  set_prior("normal(0, 0.5)", class = "b"),
-  set_prior("cauchy(0, 0.3)", class = "sd")
-)
-
-# Run prior predictive simulation
-res_prior_reg <- brm(
-  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
-    (1 | article / experiment),
-  data = dat_meta,
-  prior = prior_reg,
-  sample_prior = "only",
-  save_pars = save_pars(all = TRUE),
-  chains = n_chains,
-  iter = n_iter,
-  warmup = n_warmup,
-  cores = n_chains,
-  control = list(adapt_delta = 0.99),
-  seed = seed,
-  file = here(models_dir, "res_prior_reg"),
-  file_refit = brms_file_refit
-)
-summary(res_prior_reg)
-
-# Run Bayesian multilevel model
-res_reg <- update(
-  res_prior_reg,
-  sample_prior = FALSE,
-  seed = seed,
-  file = here(models_dir, "res_reg"),
-  file_refit = brms_file_refit
-)
-summary(res_reg)
-
-# Get posterior probability mass > 0 for all regression weights
-(hyps_brm_reg <- list(
-  intercept = hypothesis(res_reg, "Intercept > 0")$hypothesis,
-  female_mixed = hypothesis(res_reg, "gender2M1 < 0")$hypothesis,
-  male_female = hypothesis(res_reg, "gender3M2 > 0")$hypothesis,
-  age = hypothesis(res_reg, "age_c > 0")$hypothesis,
-  voe_habituation = hypothesis(res_reg, "task2M1 > 0")$hypothesis,
-  female_mixed_age = hypothesis(res_reg, "gender2M1:age_c > 0")$hypothesis,
-  male_female_age = hypothesis(res_reg, "gender3M2:age_c > 0")$hypothesis
-))
-
-# Extract posterior draws for the meta-analytic effects
-spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC from standard deviations
-  mutate(
-    intercept = b_Intercept,
-    female_mixed = b_gender2M1,
-    male_female = b_gender3M2,
-    age = b_age_c,
-    voe_habituation = b_task2M1,
-    female_mixed_age = `b_gender2M1:age_c`,
-    male_female_age = `b_gender3M2:age_c`,
-    sigma_article = sd_article__Intercept,
-    sigma_experiment = `sd_article:experiment__Intercept`,
-    sigma2_article = sd_article__Intercept^2,
-    sigma2_experiment = `sd_article:experiment__Intercept`^2,
-    sigma2_total = sigma2_article + sigma2_experiment,
-    icc = sigma2_article / sigma2_total,
-  ) -> draws_reg
-
-# Summarize as means and 95% credible intervals
-(summ_reg <- as.list(mean_qi(draws_reg)))
-```
-
-As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Figure\ \@ref(fig:fig2)).
-Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
-The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`.
-We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
-Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% CrI [`r summ_reg$age.lower`, `r summ_reg$age.upper`].
-We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]).
-Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% CrI [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`].
-The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.
-
-```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
-# Get draws from the posterior distribution *for each experiment*
-epred_draws_reg <- epred_draws(
-  res_reg,
-  dat_meta,
-  ndraws = NULL,
-  re_formula = NA
-)
-
-# Use colors as proposed in https://arxiv.org/abs/2107.02270
-# The four colors code for a combination of tasks (Habituation, VoE) and gender
-# (female, male, mixed)
-plot_reg_colors <- list(
-  habituation = c(
-    "Female, Habituation" = "#5790fc",
-    "Male, Habituation" = "#f89c20",
-    "Mixed, Habituation" = "#e42536"
-  ),
-  voe = c("Mixed, VoE" = "#964a8b")
-)
-
-# Create regression plot
-dat_meta %>%
-  ggplot(aes(x = age * 12, y = gi)) +
-  geom_hline(yintercept = seq(-1, 2, 0.5), color = "grey90") +
-  annotate(
-    "rect",
-    xmin = 5.5, xmax = Inf, ymin = 1.25, ymax = Inf,
-    color = NA, fill = "white"
-  ) +
-  # Regression lines and CrIs for Habituation tasks
-  stat_lineribbon(
-    aes(y = .epred, color = gender_task),
-    data = epred_draws_reg,
-    alpha = .4,
-    point_interval = "mean_qi",
-    .width = c(0.5, 0.95)
-  ) +
-  # Individual study effect sizes for Habituation tasks
-  geom_point(aes(color = gender_task, size = ni), shape = 0) +
-  scale_color_manual(
-    values = plot_reg_colors$habituation,
-    breaks = names(plot_reg_colors$habituation),
-    labels = c("Females", "Males", "Mixed gender"),
-    na.value = NA
-  ) +
-  guides(color = guide_legend(
-    title = "Habituation tasks",
-    override.aes = list(fill = NA),
-    order = 1
-  )) +
-  # Regression lines and CrIs for VoE tasks
-  ggnewscale::new_scale_color() +
-  stat_lineribbon(
-    aes(y = .epred, color = gender_task),
-    data = epred_draws_reg,
-    fill = NA,
-    alpha = .4,
-    point_interval = "mean_qi",
-    .width = c(0.5, 0.95)
-  ) +
-  # Individual study effect sizes for VoE tasks
-  geom_point(aes(color = gender_task, size = ni), shape = 0) +
-  scale_color_manual(
-    values = plot_reg_colors$voe,
-    breaks = names(plot_reg_colors$voe),
-    labels = c("Mixed gender"),
-    na.value = NA
-  ) +
-  guides(color = guide_legend(title = "VoE tasks", order = 2)) +
-  # Styling
-  coord_cartesian(expand = FALSE) +
-  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
-  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
-  scale_fill_grey(
-    start = 0.85, end = 0.65,
-    labels = as_mapper(~ scales::percent(as.numeric(.x)))
-  ) +
-  labs(
-    x = "Age (months)",
-    y = expression("Hedges'" ~ italic("g")),
-    fill = "CrI level",
-    size = "Sample size"
-  ) +
-  theme_classic() +
-  theme(
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    legend.direction = "vertical",
-    legend.key = element_blank(),
-    legend.position = "none",
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica", color = "black")
-  ) -> plot_reg
-
-# Extract the legend so that we can put it inside the plot later on
-plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))
-
-# Define new labels for the regression coefficients
-coef_colnames <- c(
-  b_Intercept = expression("Intercept (Hedges'" ~ italic(g) * ")"),
-  b_gender2M1 = expression("Females - mixed"),
-  b_gender3M2 = expression("Males - females"),
-  b_age_c = expression("Age (per year)"),
-  b_task2M1 = expression("Habituation - VoE"),
-  `b_gender2M1:age_c` = expression("(Females - Mixed)" %*% "age"),
-  `b_gender3M2:age_c` = expression("(Males - Females)" %*% "age")
-)
-
-# Plot posterior distributions of the regression coefficients
-epred_draws_reg_coef <- tidy_draws(res_reg)
-epred_draws_reg_coef %>%
-  # Convert to long format
-  select(all_of(names(coef_colnames))) %>%
-  gather() %>%
-  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
-  # Plot coefficients as "half eyes" (mean + CrIs + distribution)
-  ggplot(aes(x = value, y = fct_rev(coef))) +
-  geom_vline(xintercept = seq(-1, 1, 0.5), color = "grey90") +
-  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
-  # Styling
-  coord_cartesian(xlim = c(-1.25, 1.25), clip = "off") +
-  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
-  scale_y_discrete(labels = coef_colnames) +
-  labs(x = expression("Regression weight (" * Delta * italic("g") * ")")) +
-  annotate(
-    "text",
-    label = "Fixed effects", x = -3.175, y = 7.86, hjust = 0,
-    family = "Helvetica", fontface = "bold", color = "black"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.line.x = element_line(colour = "black"),
-    axis.text.x = element_text(family = "Helvetica", color = "black"),
-    axis.text.y = element_text(
-      family = "Helvetica", color = "black", size = 3.88 * .pt,
-      hjust = 0, vjust = -0.1, margin = margin(l = 20)
-    ),
-    axis.ticks.x = element_line(color = "black"),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank(),
-    panel.grid = element_blank(),
-    text = element_text(family = "Helvetica", color = "black")
-  ) -> plot_coef
-
-# Combine the two regression plots
-plot_grid(
-  plot_reg, plot_coef,
-  nrow = 1, rel_widths = c(3, 2), labels = "AUTO",
-  label_size = 11, label_fontfamily = "Helvetica",
-  label_x = 0.008, label_y = 0.99
-) +
-  draw_plot(plot_reg_legend, x = 0.385, y = 0.865, hjust = 0.5, vjust = 0.5)
-
-# Save plot
-ggsave(here(figures_dir, "fig2_reg.pdf"), width = 12, height = 5)
-```
-
-(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments.
-Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample; yellow = habituation task, all-male sample; red = habituation task, mixed-gender sample; purple = violation of expectation [VoE] task, mixed-gender sample).
-Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI).
-(B) Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines).
-Gray curves indicate the posterior distribution for each effect.
-
-```{r, gender}
-# Compute relevant effect sizes for the meta-analysis of gender differences
-raw_gender %>%
-  # Remove effect sizes from experiments with redundant samples
-  filter(!redundant) %>%
-  # Add columns
-  mutate(
-
-    # Add unique experiment identifier
-    experiment = str_c(year, article, group, sep = ", "),
-
-    # Re-code non-significant F statistics as an effect size of d = 0
-    f = as.numeric(f),
-    f_assumed = ifelse(is.nan(f), 0, f),
-
-    # Add d from two-samples t-test (Lakens, 2013)
-    d_t = t * sqrt(1 / female_n + 1 / male_n),
-
-    # Add d from ANOVA F statistic via conversion to a t statistic
-    d_f = sqrt(f_assumed) * sign_f * sqrt(1 / female_n + 1 / male_n),
-
-    # Add d from mean difference and pooled standard deviation
-    mean_diff = mean_diff_males_mean - mean_diff_females_mean,
-    sd_diff_pooled_numerator = (male_n - 1) * (mean_diff_males_sd^2) +
-      (female_n - 1) * (mean_diff_females_sd^2),
-    df = male_n + female_n - 2,
-    sd_diff_pooled = sqrt(sd_diff_pooled_numerator / df),
-    d_diff = mean_diff / sd_diff_pooled,
-
-    # Add d from one-sample t-test of novelty preference scores
-    mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
-    sd_nov_pref_pooled_numerator = (male_n - 1) * (novelty_pref_males_sd^2) +
-      (female_n) * (novelty_pref_females_sd^2),
-    sd_nov_pref_pooled = sqrt(sd_nov_pref_pooled_numerator / df),
-    d_nov_pref = mean_nov_pref / sd_nov_pref_pooled,
-
-    # Choose one type of outcome variable for each experiment
-    di = case_when(
-      # 1. If d was reported directed
-      !is.na(d) ~ d,
-      # 2. If a t-test was reported
-      !is.na(d_t) ~ d_t,
-      # 3. If an ANOVA was reported
-      !is.na(d_f) ~ d_f,
-      # 4. If the difference between means and their SDs were reported
-      !is.na(d_diff) ~ d_diff,
-      # 5. If novelty preference scores and their SDs were reported
-      !is.na(d_nov_pref) ~ d_nov_pref
-    ),
-    # Keep track which type of outcome measure was chosen for each article
-    di_type = case_when(
-      !is.na(d) ~ "d",
-      !is.na(d_t) ~ "d_t",
-      !is.na(d_f) ~ "d_f",
-      !is.na(d_diff) ~ "d_diff",
-      !is.na(d_nov_pref) ~ "d_nov_pref"
-    ) %>%
-      factor(levels = c("d", "d_t", "d_f", "d_diff", "d_nov_pref")),
-
-    # Apply small sample correction using Hedges' exact method
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    j = exp(lgamma(df / 2) - log(sqrt(df / 2)) - lgamma((df - 1) / 2)),
-    gi = di * j,
-
-    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
-    ni = female_n + male_n,
-    nhi = 2 / (1 / female_n + 1 / male_n),
-    vi = (df / (df - 2)) * (2 / nhi) * (1 + gi^2 * (nhi / 2)) - (gi^2 / (j^2)),
-    sei = sqrt(vi)
-  ) %>%
-  # Remove experiments that didn't provide any effect size
-  filter(!is.na(gi)) -> dat_gender
-
-# Get an overview of the different effect sizes
-dat_gender %>%
-  select(
-    article,
-    group,
-    gi,
-    di,
-    di_type,
-    d,
-    d_t,
-    d_f,
-    d_diff,
-    sei
-  ) %>%
-  print(n = Inf)
-
-# Use the same priors as for the main meta-analysis
-prior_gender <- prior_meta
-
-# Run prior predictive simulation
-res_prior_gender <- brm(
-  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
-  data = dat_gender,
-  prior = prior_gender,
-  sample_prior = "only",
-  save_pars = save_pars(all = TRUE),
-  chains = n_chains,
-  iter = n_iter,
-  warmup = n_warmup,
-  cores = n_chains,
-  control = list(adapt_delta = 0.99),
-  seed = seed,
-  file = here(models_dir, "res_prior_gender"),
-  file_refit = brms_file_refit
-)
-summary(res_prior_gender)
-
-# Run Bayesian multilevel model
-res_gender <- update(
-  res_prior_gender,
-  sample_prior = FALSE,
-  seed = seed,
-  file = here(models_dir, "res_gender"),
-  file_refit = brms_file_refit
-)
-summary(res_gender)
-
-# Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_gender <- hypothesis(res_gender, "Intercept > 0")$hypothesis)
-
-# Extract posterior draws for the meta-analytic effects
-spread_draws(res_gender, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
-  # Compute variances and ICC from standard deviations
-  mutate(
-    intercept = b_Intercept,
-    sigma_article = sd_article__Intercept,
-    sigma_experiment = `sd_article:experiment__Intercept`,
-    sigma2_article = sigma_article^2,
-    sigma2_experiment = sigma_experiment^2,
-    sigma2_total = sigma2_article + sigma2_experiment,
-    icc = sigma2_article / sigma2_total,
-    .keep = "unused"
-  ) -> draws_gender
-
-# Summarize as means and 95% credible intervals
-(summ_gender <- as.list(mean_qi(draws_gender)))
-```
-
-\newpage
-
-To confirm the gender difference between males and females, we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between male and female infants reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% CrI [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Figure\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_prob(hyp_gender$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
-Therefore, `r print_perc(1 - summ_gender$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_gender$icc)` was attributable to differences *between* articles.
-
-The results obtained from our Bayesian analyses were reproduced by classical frequentist three-level meta-analysis and meta-regression models (Supplementary Table\ \@ref(tab:tabs2)).
-
-## Publication bias assessment
-
-```{r, bias, echo=TRUE}
-# Classical Egger regression test for the meta-analysis of rotation performance
-(egger_meta <- with(
-  dat_meta, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
-))
-(egger_ci_meta <- confint(egger_meta$fit)["Xsei", ])
-
-# Classical Egger regression test for the meta-analysis of gender_differences
-(egger_gender <- with(
-  dat_gender, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
-))
-(egger_ci_gender <- confint(egger_gender$fit)["Xsei", ])
-```
-
-We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here.
-For the meta-analysis of mental rotation performance (Figure\ \@ref(fig:fig3)A), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
-This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
-Nevertheless, a jackknife (leave-one-out) analysis confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)).
-For the meta-analysis of gender differences in mental rotation performance (Figure\ \@ref(fig:fig3)B), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
-
-```{r, fig3, include=TRUE, fig.height=3.5, fig.width=12, fig.cap="(ref:fig3-caption)"}
-# Create funnel plots for the two meta-analyses
-map2(
-  list(dat_meta, dat_gender),
-  list(summ_meta, summ_meta),
-  function(dat, summ) {
-
-    # Define maximul SE of interest (a bit larger than the largest observed SE)
-    max_se <- max(dat$sei) + 0.05
-
-    # Compute a 95% funnel under the null hypothesis
-    z_crit_05 <- stats::qnorm(0.975)
-    funnel_greater_05 <- data.frame(
-      x = c(0 - z_crit_05 * sqrt(max_se^2), 0, 0 + z_crit_05 * sqrt(max_se^2)),
-      y = c(max_se, 0, max_se),
-      level = "greater_05"
-    )
-
-    # Compute a 99% funnel under the null hypothesis
-    z_crit_01 <- stats::qnorm(0.995)
-    funnel_smaller_05 <- data.frame(
-      x = c(0 - z_crit_01 * sqrt(max_se^2), 0, 0 + z_crit_01 * sqrt(max_se^2)),
-      y = c(max_se, 0, max_se),
-      level = "smaller_05"
-    )
-
-    # Create a third pseudo-funnel under the null hypothesis just for the legend
-    funnel_smaller_01 <- mutate(funnel_greater_05, level = "smaller_01")
-
-    # Compute a 95% funnel around the *observed* meta-analytic effect size
-    funnel_observed <- mutate(funnel_greater_05, x = x + summ$intercept)
-
-    # Plot the funnels
-    ggplot(dat, aes(x = gi, y = sei)) +
-      # Funnels under the null hypothesis
-      geom_polygon(data = funnel_smaller_01, aes(x = x, y = y, fill = level)) +
-      geom_polygon(data = funnel_smaller_05, aes(x = x, y = y, fill = level)) +
-      geom_polygon(data = funnel_greater_05, aes(x = x, y = y, fill = level)) +
-      scale_fill_manual(
-        values = c("gray80", "grey90", "white"),
-        breaks = c("greater_05", "smaller_05", "smaller_01"),
-        labels = c(
-          expression(italic(p) > 0.05),
-          expression(italic(p) < 0.05),
-          expression(italic(p) < 0.01)
-        )
-      ) +
-      # Grid lines
-      geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
-      # Observed_funnel
-      geom_path(data = funnel_observed, aes(x = x, y = y)) +
-      # Meta-analytic effect size
-      geom_vline(xintercept = summ$intercept, color = "black") +
-      # Experiment-specific effect sizes
-      geom_point(shape = 0) +
-      # Styling
-      scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
-      scale_y_reverse() +
-      coord_cartesian(
-        xlim = c(-2.5, 2.5),
-        ylim = c(max_se, 0),
-        expand = FALSE
-      ) +
-      labs(
-        x = expression("Hedges'" ~ italic("g")), y = "Standard error",
-        fill = "Significance level"
-      ) +
-      theme_classic() +
-      theme(
-        axis.line = element_line(colour = "black"),
-        axis.text = element_text(family = "Helvetica", color = "black"),
-        axis.ticks = element_line(color = "black"),
-        legend.position = "none",
-        text = element_text(family = "Helvetica", color = "black")
-      )
-  }
-) -> plots_funnel
-
-# Extract legend
-legend_funnel <- get_legend(
-  plots_funnel[[1]] + theme(legend.position = "right")
-)
-
-# Combine plots and legend
-plot_grid(
-  plotlist = plots_funnel, nrow = 1, labels = "AUTO",
-  label_size = 11, label_fontfamily = "Helvetica"
-) +
-  draw_plot(legend_funnel, x = -0.39, y = 0.355)
-
-# Save the plot
-ggsave(here(figures_dir, "fig3_funnel.pdf"), width = 12, height = 3.5)
-```
-
-(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance (A) and for the meta-analysis of gender differences in mental rotation performance (B).
-The plots show the standard error and effect size for each of the individual experiments as a black square.
-The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect size (vertical black line).
-Gray shades indicate a 95% pseudo-confidence interval (dark gray) and a 99% pseudo-confidence interval (light gray) under the null hypothesis.
-These shades thus illustrate which of the original experiments observed a significant effect.
-For the meta-analysis of mental rotation performance, a slight asymmetry induced by the underrepresentation of experiments with high standard errors and small effect sizes suggests a small publication bias.
-
-# Discussion
-
-We analyzed looking times during mental rotation in `r formatC(descriptives$n_infants, big.mark = ",")` infants ranging from `r descriptives$min_age_months` to `r descriptives$max_age_months` months of age.
-To this end, we scrutinized the robustness of `r descriptives$n_experiments` experimental effect sizes.
-We found that on average, male infants looked longer at novel rotated objects compared to female infants.
-This effect was small to medium and unrelated to age in the current range.
-
-We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
-The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference would be more likely to report separate effect sizes for males and females.
-In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_gender$intercept`$) can be viewed as a lower bound of the true effect size.
-This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences were likely also observed but just not reported because of missing power to render these effects statistically significant.
-
-To facilitate the interpretability of our models, the effect size of the looking time difference between novel and familiar rotation events was coded in a linear fashion.
-Accordingly, a positive looking time difference (i.e., a novelty preference) was taken as stronger evidence for mental rotation than a looking time difference of zero (i.e., no systematic preference).
-A zero difference in turn was taken as stronger evidence for mental rotation than a negative looking time difference (i.e., a familiarity preference).
-This approach can be corroborated by the established view that novelty preference is generally considered as the paradigmatic mental rotation behavior [for related discussion, see @black2017; @cristia2018; @houston-price2004].
-Nevertheless, some authors have argued that familiarity preference should also be taken as evidence for mental rotation ability [@erdmann2018; @moore2020; @johnson2020].
-Interpreting novelty preference *and* familiarity preference as successful mental rotation would have increased the effect sizes reported here.
-
-The gender differences observed here remain to be explained by interacting genetic and environmental factors that are largely unknown.
-To the best of our knowledge, there are currently no genetic association or gene-environment interaction studies with a focus on mental rotation.
-Nevertheless, it is documented that genetic contributions to behavioral variance in mental rotation are substantially smaller than unique non-shared environmental contributions both in male and female adults [@shakeshaft2016].
-Whether this observation also applies to infants remains to be explored.
-
-One recent study on 5--6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work [@constantinescu2018].
-As far as we know, potentially mediating and moderating factors that could already be operational in infancy, however, are not yet empirically established.
-In a similar vein, while mental rotation training has small-to-medium post-test effects in children, it is unclear whether it can remove gender differences and be adapted to infants [@uttal2013].
-
-Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance [@toivainen2018; @constantinescu2018; @erdmann2019].
-However, possible biological developmental pathways, bridging the gap from hormonal to behavioral differences, are currently far from understood.
-
-A number of additional factors have been associated with individual differences in infant mental rotation performance.
-For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task [@mohring2013; @schwarzer2013a; @slone2018].
-This relation also applies to previous experience with manually rotating toys [@schwarzer2013a].
-While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains [e.g., @ausubel1968; @bradley1983; @halberda2008].
-Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].
-
-The present study robustly revealed that male infants look longer at novel rotated objects than female infants.
-Thus, on average, males show more reliable mental rotation behavior already in the first months of life.
-
-# Method
-
-## Protocol
-
-In the present meta-analysis, we followed the established PRISMA 2020 guidelines [Preferred Reporting Items for Systematic reviews and Meta-Analyses\; @page2021].
-The PRISMA checklist is provided in Supplementary Table\ \@ref(tab:tabs4) while Supplementary Figure\ \@ref(fig:figs2) displays the PRISMA flowchart.
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-## Eligibility criteria
-
-Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article is written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that can be converted into a standardized mean difference (see Data collection process and items below).
-We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
-
-## Information sources and search strategy
-
-We entered the search terms ("mental rotation" OR "mental transformation" OR "spatial rotation" OR "spatial transformation" OR "spatial ability" OR "spatial skills") AND ("infant" OR "infants" OR "infanthood" OR "toddler" OR "toddlers" OR "toddlerhood" OR "child" OR "children" OR "childhood" OR "month" OR "months") into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, and ProQuest Dissertations & Theses Global).
-All database queries were completed on December 6, 2021.
-We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Supplementary Figure\ \@ref(fig:figs2)).
-We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills [@frick2014; @johnson2020; @kubicek2018; @lauer2019a; @linn1985; @moore2020; @uttal2013; @voyer1995; @yang2020].
-Of these, 34 articles had not been covered by the database search.
-We also identified 94 articles by screening the reference sections of all publications that had been included after the first pass of the selection process.
-Of these, 49 articles had not been covered by the database search.
-Accordingly, we screened 2,037 unique articles in total.
-
-## Selection process
-
-```{r, selection_process}
-# Compute interrater agreement for binary decision (include vs. exclude)
-(irr_bin_perc <- with(raw_screen, mean(bin_1 == bin_2)))
-(irr_bin_kappa <- with(raw_screen, psych::cohen.kappa(cbind(bin_1, bin_2))))
-irr_bin_kappa_w <- as.list(irr_bin_kappa$confid["weighted kappa", ])
-
-# Compute interrater agreement for specific exclusion codes
-(irr_code_perc <- with(raw_screen, mean(code_1 == code_2)))
-(irr_code_kappa <- with(raw_screen, psych::cohen.kappa(cbind(code_1, code_2))))
-irr_code_kappa_w <- as.list(irr_code_kappa$confid["weighted kappa", ])
-
-# Justify exclusion of @pedrett2020 based on outlier mean age
-descs_pedrett2020 <- list(age_years = 2.56)
-descs_pedrett2020 <- within(descs_pedrett2020, {
-  age_months <- age_years * 12
-  next_largest_age_months <- max(dat_meta$age_mean) / 30.417
-  age <- age_years * 365.25
-  z <- (age - mean(dat_meta$age_mean)) / sd(dat_meta$age_mean)
-})
-```
-
-The final sample size of articles was determined by including all articles that fulfilled the inclusion criteria described above.
-Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
-Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen's weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]).
-Interrater agreement for the specific eligibility criteria was `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]).
-Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
-One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigms used in the other articles.
-Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, digits = 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, digits = 1)` months; $z = `r descs_pedrett2020$z`$ compared to all articles).
-We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Supplementary Figure\ \@ref(fig:figs2)).
-
-Many of these articles consisted of multiple experiments, e.g., using different variations of the mental rotation task or different subsamples of infants.
-We included all of these experiments in the meta-analysis and accounted for the dependencies between them by means of multilevel modeling with by-article random effects (see Bayesian meta-analysis below).
-However, we excluded experiments if there was insufficient information to compute a standardized effect size (see Data collection process and items below).
-Whenever an article reported separate effect sizes for males and females---or other subgroups like crawling and non-crawling infants---but also an effect size combining these groups, we only included the combined effect size.
-Moreover, we disregarded effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of `r descriptives$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table\ \@ref(tab:tabs1)) and 30 experiments being included in the meta-analysis of gender differences in mental rotation performance.
-
-## Data collection process and items
-
-Outcome measures and other relevant variables were extracted from each article by one of three raters and verified by a second rater.
-For the meta-analysis of mental rotation performance, outcome measures were any summary statistic (Supplementary Table\ \@ref(tab:tabs5)) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
-Other extracted variables included, if available, the sample size, the number of males and females, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habituation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table\ \@ref(tab:tabs1)).
-
-We also conducted a meta-analysis of the gender differences in mental rotation performance observed within the original articles.
-For this analysis, the outcome measures were any summary statistic (Supplementary Table\ \@ref(tab:tabs6)) that could be used to determine the standardized mean difference between male infants' mental rotation performance and female infants' mental rotation performance.
-Other extracted variables included the sample size, the mean age and its standard deviation, and the minimum and maximum age of each gender group.
-
-No investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
-
-## Effect measures
-
-For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5) [@goulet-pelletier2018; @hedges1985; @lakens2013; @rosenthal1991; @cumming2012].
-The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs5).
-The correlation $r$ was not reported in any of the original articles [see also @harrer2021].
-We therefore always assumed a correlation of $r = 0.50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx 0.50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from $r = -0.90$ via $r = 0.00$ to $r = 0.90$ had no meaningful impact on the meta-analytic effect sizes (Supplementary Tables\ \@ref(tab:tabs7) and\ \@ref(tab:tabs8)).
-
-For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between male and female infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs6).
-In some cases where the authors of the original articles did not observe a statistically significant gender difference, they did not report a precise outcome measure.
-In these cases, we assumed an effect size of $g$ = 0.00, thus rendering our meta-analytic effect size of the gender difference more conservative.
-The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=2/(n_\text{female}^{-1}+n_\text{male}^{-1})$), and $J(df)$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs6).
-
-## Bayesian meta-analysis
-
-We synthesized the effect sizes and their sampling variances using a Bayesian multilevel model.
-This model had three levels, with infant participants nested in experiments and experiments nested in articles [@vandennoortgate2013].
-We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for the two standard deviations [i.e., the random effects of experiments and articles\; @williams2018].
-A prior sensitivity analysis indicated that making these priors either more informative or less informative did not have a strong influence on the meta-analytic results (Supplementary Tables\ \@ref(tab:tabs7), \@ref(tab:tabs8), and\ \@ref(tab:tabs9)).
-For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect measures above).
-For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges' $g$) between male infants' mental rotation performance and female infants' mental rotation performance, weighted by its standard error.
-All Bayesian models were fitted using the brms package [Version `r packageVersion("brms")`\; @burkner2017; @burkner2018] in R [Version `r packageVersion("base")`\; @rcoreteam2021] and the Stan language [Version `r packageVersion("rstan")`\; @standevelopmentteam2022].
-Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r print_big(n_iter)` draws (including `r print_big(n_warmup)` warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the $\widehat{R}$ and $N_\text{eff}$ statistics [@vehtari2021\; Supplementary Figure\ \@ref(fig:figs3)].
-For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].
-
-## Bayesian meta-regression
-
-We examined the influence of three moderator variables on the mental rotation outcomes across experiments, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
-Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts so that we could compare all-female samples versus mixed samples and all-male samples versus all-female samples [@schad2020].
-Age was coded as a continuous predictor in years and centered by subtracting the average across all experiments.
-Task type was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast [@schad2020].
-We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender and task type (i.e., [female - mixed] $\times$ age, [male - female] $\times$ age) into a Bayesian meta-regression model.
-This model was based on the same random effects structure, sampling parameters, and prior specification as described above, but adding a weakly-informative $\mathcal{N}(0,0.5)$ (normal) prior for all slope parameters.
-
-## Frequentist meta-analysis
-
-We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression.
-To this end, we used the metafor package [Version `r packageVersion("metafor")`\; @viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs2)).
-These models were fitted using restricted maximum likelihood estimation (REML).
-To verify that this procedure converged on the most probable estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Figure\ \@ref(fig:figs4)).
-
-## Publication bias assessment
-
-Publication bias was evaluated based on funnel plots and Egger regression tests [@egger1997; @sterne2005].
-Funnel plots visualize the relationship between standard errors and effect sizes.
-They were created by adapting code from the R package metaviz [Version `r packageVersion("metaviz")`\; @kossmeier2020].
-The Egger regression test is a formal statistical test for this relationship between standard errors and effect sizes, probing if the weighted linear regression weight of the effect sizes on the standard errors is significantly different from zero.
-This test was performed using the metafor package and applying a two-sided false-positive error rate of $\alpha = 0.05$.
-
-To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife (leave-one-out) analysis for the meta-analysis of mental rotation performance [@efron1993].
-To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.
-We then checked if the meta-analytic effect size and heterogeneity remained constant or if it was sensitive against the influence of any individual experiment (Supplementary Table\ \@ref(tab:tabs3)).
-
-We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias [@duval2000; @vevea1995; @vevea2005\; Supplementary Methods 2\; Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)\; Supplementary Figure\ \@ref(fig:figs5)].
-
-## Data and code availability
-
-The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
-
-\newpage
-\nolinenumbers
-
-# References
-
-\bigskip
-
-<div id="refs"></div>
-
-\newpage
-
-```{r child = "supplement.Rmd"}
-
-```

### 2023-02-08 main.qmd
Initialize Quarto book

--- 2022-11-07 manuscript.Rmd
@@
----
-title             : "Gender differences in infant mental rotation"
-shorttitle        : "Infant mental rotation"
-
-author:
-  - name          : "Alexander Enge"
-    affiliation   : "1,2"
-    corresponding : "yes"
-    address       : "Stephanstraße 1a, 04103 Leipzig, Germany"
-    email         : "enge@cbs.mpg.de"
-  - name          : "Shreya Kapoor"
-    affiliation   : "1"
-  - name          : "Anne-Sophie Kieslinger"
-    affiliation   : "1"
-  - name          : "Michael A. Skeide"
-    affiliation   : "1"
-affiliation:
-  - id            : "1"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
-  - id            : "2"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
-
-authornote: |
-  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
-
-  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}
-
-  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}
-
-  The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
-
-  M.A.S.
-was supported by the German Research Foundation (DFG Grants 433715509 and 433758790), the European Research Council (ERC Starting Grant 850752), and a Jacobs Foundation Research Scholarship.
-A.E.
-was supported by a PhD scholarship from the German Academic Scholarship Foundation (Studienstiftung des deutschen Volkes).
-
-  The authors declare that they have no conflicts of interest to disclose.
-
-bibliography      : "manuscript_files/references.bib"
-csl               : "manuscript_files/apa.csl"
-
-appendix          : "supplement.Rmd"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa7"
-classoption       : "man,donotrepeattitle"
-fontsize          : "10pt"
-output            : "papaja::apa6_pdf"
-
-header-includes:
-  - \geometry{a4paper}
-  - \raggedbottom
-  - \usepackage[all]{nowidow}
-  - \usepackage{lineno}
-  - \usepackage{makecell}
-  - \usepackage{setspace}
-  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
-  - \captionsetup[table]{belowskip=20pt,labelfont=bf,labelsep=period,textfont=bf,textformat=tabletext}
-  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=period,textfont=normalfont}
----
-
-```{r, setup, include=FALSE}
+# Main text
+
+## Setup
+
+```{r, message=FALSE}
 # Load packages
@@
 library(here)
-library(readxl)
 library(scales)
@@
 
-# Global chunk options
-knitr::opts_chunk$set(
-  include = FALSE,
-  message = FALSE,
-  fig.align = "center",
-  fig.height = 10,
-  fig.pos = "tp",
-  fig.width = 7.5,
-  out.width = "100%",
-  warning = FALSE
-)
-
 # Options for MCMC sampling when fitting Bayesian multilevel models
@@
 data_dir <- here("data")
-models_dir <- here("results/models")
-figures_dir <- here("results/figures")
-tables_dir <- here("results/tables")
-
-# Read the relevant spreadsheets
+results_dir <- here("results")
+models_dir <- here(results_dir, "models")
+figures_dir <- here(results_dir, "figures")
+tables_dir <- here(results_dir, "tables")
+```
+
+## Introduction / Methods
+
+### Protocol
+
+#### PRISMA flowchart (Figure 1)
+
+![PRISMA flowchart](results/figures/fig1_flowchart.png)
+
+### Selection process
+
+#### Percent agreement for binary decision (include vs. exclude)
+
+```{r}
+# Read the raw data from the screening process
 raw_screen <- read_tsv(here(data_dir, "02_screen.tsv"), na = "NA")
+
+# Percent agreement for binary decision (include vs. exclude)
+with(raw_screen, mean(bin_1 == bin_2))
+```
+
+#### Cohen's $\kappa_w$ (weighted kappa)
+
+```{r}
+# Cohen's kappa
+with(raw_screen, psych::cohen.kappa(cbind(bin_1, bin_2)))
+```
+
+#### Percent agreement for specific exclusion criteria
+
+```{r}
+# Compute interrater agreement for specific exclusion codes
+with(raw_screen, mean(code_1 == code_2))
+```
+
+#### Cohen's $\kappa_w$ (weighted kappa)
+
+```{r}
+with(raw_screen, psych::cohen.kappa(cbind(code_1, code_2)))
+```
+
+### Effect measures
+
+#### Conversion of effect sizes for mental rotation performance
+
+```{r}
+# Read raw data for the meta-analysis of mental rotation performance
 raw_meta <- read_tsv(here(data_dir, "03_meta.tsv"), na = "NA")
-raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")
-
-# Add columns to the table of experiments for the meta-analysis
-raw_meta %>%
+
+# Add columns to the table of experiments
+dat_all <- raw_meta %>%
   mutate(
@@
   # Order rows by experiment ID
-  arrange(experiment) -> dat_all
-
-# Get an overview of the different effect sizes
-dat_all %>%
-  select(
-    article,
-    group,
-    gender_split,
-    gi,
-    di,
-    di_type,
-    d,
-    d_z_t,
-    d_z_f,
-    d_z_diff,
-    d_av,
-    d_nov_pref
-  ) %>%
-  print(n = Inf)
+  arrange(experiment)
 
@@
 r_assumed <- 0.5
-dat_all %>%
+dat_meta_all <- dat_all %>%
   mutate(
@@
   ) %>%
-  filter(!is.na(gi)) -> dat_meta_all
-
-# Show number of experiments per gender grouping strategy (mixed/split)
-table(dat_meta_all$gender_split)
+  filter(!is.na(gi))
 
@@
 dat_meta <- dat_both_split
-
+```
+
+#### Conversion of effect sizes for gender differences
+
+```{r}
+# Read raw data for the meta-analysis of gender differences
+raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")
+
+# Compute relevant effect sizes for the meta-analysis of gender differences
+dat_gender <- raw_gender %>%
+  # Remove effect sizes from experiments with redundant samples
+  filter(!redundant) %>%
+  # Add columns
+  mutate(
+
+    # Add unique experiment identifier
+    experiment = str_c(year, article, group, sep = ", "),
+
+    # Re-code non-significant F statistics as an effect size of d = 0
+    f = as.numeric(f),
+    f_assumed = ifelse(is.nan(f), 0, f),
+
+    # Add d from two-samples t-test (Lakens, 2013)
+    d_t = t * sqrt(1 / female_n + 1 / male_n),
+
+    # Add d from ANOVA F statistic via conversion to a t statistic
+    d_f = sqrt(f_assumed) * sign_f * sqrt(1 / female_n + 1 / male_n),
+
+    # Add d from mean difference and pooled standard deviation
+    mean_diff = mean_diff_males_mean - mean_diff_females_mean,
+    sd_diff_pooled_numerator = (male_n - 1) * (mean_diff_males_sd^2) +
+      (female_n - 1) * (mean_diff_females_sd^2),
+    df = male_n + female_n - 2,
+    sd_diff_pooled = sqrt(sd_diff_pooled_numerator / df),
+    d_diff = mean_diff / sd_diff_pooled,
+
+    # Add d from one-sample t-test of novelty preference scores
+    mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
+    sd_nov_pref_pooled_numerator = (male_n - 1) * (novelty_pref_males_sd^2) +
+      (female_n) * (novelty_pref_females_sd^2),
+    sd_nov_pref_pooled = sqrt(sd_nov_pref_pooled_numerator / df),
+    d_nov_pref = mean_nov_pref / sd_nov_pref_pooled,
+
+    # Choose one type of outcome variable for each experiment
+    di = case_when(
+      # 1. If d was reported directed
+      !is.na(d) ~ d,
+      # 2. If a t-test was reported
+      !is.na(d_t) ~ d_t,
+      # 3. If an ANOVA was reported
+      !is.na(d_f) ~ d_f,
+      # 4. If the difference between means and their SDs were reported
+      !is.na(d_diff) ~ d_diff,
+      # 5. If novelty preference scores and their SDs were reported
+      !is.na(d_nov_pref) ~ d_nov_pref
+    ),
+    # Keep track which type of outcome measure was chosen for each article
+    di_type = case_when(
+      !is.na(d) ~ "d",
+      !is.na(d_t) ~ "d_t",
+      !is.na(d_f) ~ "d_f",
+      !is.na(d_diff) ~ "d_diff",
+      !is.na(d_nov_pref) ~ "d_nov_pref"
+    ) %>%
+      factor(levels = c("d", "d_t", "d_f", "d_diff", "d_nov_pref")),
+
+    # Apply small sample correction using Hedges' exact method
+    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
+    j = exp(lgamma(df / 2) - log(sqrt(df / 2)) - lgamma((df - 1) / 2)),
+    gi = di * j,
+
+    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
+    ni = female_n + male_n,
+    nhi = 2 / (1 / female_n + 1 / male_n),
+    vi = (df / (df - 2)) * (2 / nhi) * (1 + gi^2 * (nhi / 2)) - (gi^2 / (j^2)),
+    sei = sqrt(vi)
+  ) %>%
+  # Remove experiments that didn't provide any effect size
+  filter(!is.na(gi))
+```
+
+#### Justification for excluding the Pedrett et al. (2020) paper
+
+```{r}
+# Justify exclusion of @pedrett2020 based on outlier mean age
+descs_pedrett2020 <- list(age_years = 2.56)
+within(descs_pedrett2020, {
+  age_months <- age_years * 12
+  next_largest_age_months <- max(dat_meta$age_mean) / 30.417
+  age <- age_years * 365.25
+  z <- (age - mean(dat_meta$age_mean)) / sd(dat_meta$age_mean)
+})
+```
+
+#### Descriptive information
+
+```{r}
 # Extract some descriptive statistics so we can paste them in the main text
-descriptives <- list(
+(descriptives <- list(
   n_articles = length(unique(dat_meta$article)),
@@
   n_experiments_voe = nrow(filter(dat_meta, task == "VoE"))
-)
-```
-
-\setcounter{page}{1}
-\resetlinenumber
-
-# Gender differences in infant mental rotation
-
-\bigskip
-
-# Research highlights
-
-* We analyzed effect sizes of 59 mental rotation experiments including 1,798 infants
-
-* Looking time reveals that 3–16-months-old infants are able to perform mental rotation
-
-* Mental rotation is more reliable in male infants compared to female infants
-
-# Abstract
-
-Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a].
-Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months.
-We robustly found that male infants recognized rotated objects more reliably than female infants.
-These findings indicate that gender differences in mental rotation are already present in the first months of life.
-
-*Keywords*: mental rotation; spatial cognition; spatial ability; infants; gender; meta-analysis
-
-\newpage
-
-# Introduction
-
-The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life [@moore2020; @johnson2020].
-Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement [@shepard1971; @hegarty1999; @johnson2005].
-
-Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013].
-Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$).
-Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents suggests only a small-to-medium difference [mean weighted $g = 0.39$\; @lauer2019a].
-Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.
-
-In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`\; Supplementary Table\ \@ref(tab:tabs1)) [@rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021].
-All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation` experiments) or violation of expectation experiments (`r descriptives$n_experiments_voe` experiments) [@fantz1964; @baillargeon1985].
-These experiments comprised real world stimuli [e.g., toy objects\; @antrilli2016], three-dimensional digital stimuli [e.g., cube figures\; @moore2008], or two-dimensional digital stimuli [e.g., digits\; @quinn2008].
-In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or with the familiar object at a new angle.
-Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation.
-In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle.
-Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle.
-Subsequently, the object disappeared behind an occluder.
-Finally, the occluder was removed and either the object or its mirror object were shown.
-Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle.
-In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.
-
-Following previous work in older populations, we hypothesized that looking time differences in mental rotation experiments are on average longer in male compared to female infants.
-Effect sizes were assumed to be small.
-
-```{r, meta}
+))
+```
+
+#### Experiments included in the main analysis (Table 1)
+
+```{r}
+# Save table of experiments for the meta-analysis of rotation
+tab1 <- dat_meta %>%
+  mutate(
+    age_mean = print_days_months(age_mean),
+    age_sd = str_c(as.character(round(age_sd)), "d"),
+  ) %>%
+  transmute(
+    Article = if_else(article == lag(article, default = ""), "", article),
+    Experiment = group,
+    `Sample size` = as.integer(sample_size),
+    Females = as.integer(round(female_percent * sample_size)),
+    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
+    Task = as.character(task),
+    `Stimulus type` = str_to_sentence(stimuli_presentation),
+    `Stimulus dimensions` = str_c(as.integer(stimuli_dimensions), "D")
+  ) %>%
+  mutate(
+    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
+  )
+
+# Save the table
+dir.create(tables_dir, showWarnings = FALSE)
+write_tsv(tab1, file = here(tables_dir, "tab1_experiments.tsv"), na = "n/a")
+
+# Add footnotes
+colnames(tab1)[5] <- str_c(colnames(tab1)[5], "^a^")
+tab1$Females[1] <- str_c(tab1$Females[1], "^b^")
+tab1$Task[3] <- str_c(tab1$Task[3], "^c^")
+
+# Display the table
+apa_table(
+  tab1,
+  note = str_c(
+    "^a^ = mean ± standard deviation, ",
+    "^b^ = not available, ",
+    "^c^ = violation of expectation."
+  ),
+  landscape = TRUE, font_size = "scriptsize", escape = FALSE
+)
+```
+
+## Results
+
+### Mental rotation performance
+
+#### Prior predictive check
+
+```{r}
 # Specify priors
@@
 summary(res_prior_meta)
-
+```
+
+#### Bayesian three-level meta-analysis
+
+```{r}
 # Run Bayesian multilevel model
@@
 summary(res_meta)
-
+```
+
+#### "Test" posterior probability mass above/below zero
+
+```{r}
 # Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_meta <- hypothesis(res_meta, "Intercept > 0")$hypothesis)
-
+hypothesis(res_meta, "Intercept > 0")$hypothesis
+```
+
+#### Summary of model paramters incl. 95% credible interval (CrI)
+
+```{r}
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_meta, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+draws_meta <- spread_draws(
+  res_meta, `b_.*`, `sd_.*`,
+  regex = TRUE, ndraws = NULL
+) %>%
   # Compute variances and ICC from standard deviations
@@
     .keep = "unused"
-  ) -> draws_meta
+  )
 
 # Summarize as means and 95% credible intervals
-(summ_meta <- as.list(mean_qi(draws_meta)))
-```
-
-```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
+(summ_meta <- mean_qi(draws_meta))
+```
+
+#### Forest plot (Figure 2)
+
+```{r, fig.height=14, fig.width=12}
 # Get posterior draws for the effect *in each experiment*
@@
 # Create forest plot
+dir.create(figures_dir, showWarnings = FALSE)
 dat_meta %>%
@@
   coord_cartesian(
-    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
+    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE,
+    clip = "off"
   ) +
@@
 dir.create(figures_dir, showWarnings = FALSE)
-ggsave(here(figures_dir, "fig1_meta.pdf"), width = 12, height = 14)
-```
-
-(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants.
-White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals.
-Gray bars indicate the 50% and 95% credible intervals (CrI) from the Bayesian model, which take into account that experiments with smaller sample sizes or more extreme effect sizes provide less reliable information.
-The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
-
-# Results
-
-## Mental rotation performance
-
-For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects.
-Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation.
-Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Figure\ \@ref(fig:fig1)).
-The probability for this effect being greater than zero was `r print_prob(hyp_meta$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level.
-Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.
-
-## Effects of gender, age, and task type
-
-```{r, reg}
+ggsave(here(figures_dir, "fig2_meta.pdf"), width = 12, height = 14)
+```
+
+### Effects of gender, age, and task type
+
+#### Prior predictive check
+
+```{r}
 # Set numerical contrasts for factor variables
@@
 summary(res_prior_reg)
-
+```
+
+#### Bayesian three-level meta-regression
+
+```{r}
 # Run Bayesian multilevel model
@@
 summary(res_reg)
-
+```
+
+#### "Test" posterior probability mass above/below zero
+
+```{r}
 # Get posterior probability mass > 0 for all regression weights
-(hyps_brm_reg <- list(
-  intercept = hypothesis(res_reg, "Intercept > 0")$hypothesis,
-  female_mixed = hypothesis(res_reg, "gender2M1 < 0")$hypothesis,
-  male_female = hypothesis(res_reg, "gender3M2 > 0")$hypothesis,
-  age = hypothesis(res_reg, "age_c > 0")$hypothesis,
-  voe_habituation = hypothesis(res_reg, "task2M1 > 0")$hypothesis,
-  female_mixed_age = hypothesis(res_reg, "gender2M1:age_c > 0")$hypothesis,
-  male_female_age = hypothesis(res_reg, "gender3M2:age_c > 0")$hypothesis
-))
-
+bind_rows(
+  hypothesis(res_reg, "Intercept > 0")$hypothesis,
+  hypothesis(res_reg, "gender2M1 < 0")$hypothesis,
+  hypothesis(res_reg, "gender3M2 > 0")$hypothesis,
+  hypothesis(res_reg, "age_c > 0")$hypothesis,
+  hypothesis(res_reg, "task2M1 > 0")$hypothesis,
+  hypothesis(res_reg, "gender2M1:age_c > 0")$hypothesis,
+  hypothesis(res_reg, "gender3M2:age_c > 0")$hypothesis
+)
+```
+
+#### Summary of model paramters incl. 95% CrI
+
+```{r}
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+draws_reg <- spread_draws(
+  res_reg, `b_.*`, `sd_.*`,
+  regex = TRUE, ndraws = NULL
+) %>%
   # Compute variances and ICC from standard deviations
@@
     icc = sigma2_article / sigma2_total,
-  ) -> draws_reg
+  )
 
 # Summarize as means and 95% credible intervals
-(summ_reg <- as.list(mean_qi(draws_reg)))
-```
-
-As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Figure\ \@ref(fig:fig2)).
-Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`].
-The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`.
-We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
-Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% CrI [`r summ_reg$age.lower`, `r summ_reg$age.upper`].
-We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]).
-Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% CrI [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`].
-The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.
-
-```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
+(summ_reg <- mean_qi(draws_reg))
+```
+
+#### Meta-regression plot (Figure 3)
+
+```{r, fig.height=5, fig.width=12}
 # Get draws from the posterior distribution *for each experiment*
@@
 # Create regression plot
-dat_meta %>%
+plot_reg <- dat_meta %>%
   ggplot(aes(x = age * 12, y = gi)) +
@@
     text = element_text(family = "Helvetica", color = "black")
-  ) -> plot_reg
+  )
 
@@
 epred_draws_reg_coef <- tidy_draws(res_reg)
-epred_draws_reg_coef %>%
+plot_coef <- epred_draws_reg_coef %>%
   # Convert to long format
@@
     text = element_text(family = "Helvetica", color = "black")
-  ) -> plot_coef
+  )
 
@@
 # Save plot
-ggsave(here(figures_dir, "fig2_reg.pdf"), width = 12, height = 5)
-```
-
-(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments.
-Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample; yellow = habituation task, all-male sample; red = habituation task, mixed-gender sample; purple = violation of expectation [VoE] task, mixed-gender sample).
-Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI).
-(B) Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines).
-Gray curves indicate the posterior distribution for each effect.
-
-```{r, gender}
-# Compute relevant effect sizes for the meta-analysis of gender differences
-raw_gender %>%
-  # Remove effect sizes from experiments with redundant samples
-  filter(!redundant) %>%
-  # Add columns
-  mutate(
-
-    # Add unique experiment identifier
-    experiment = str_c(year, article, group, sep = ", "),
-
-    # Re-code non-significant F statistics as an effect size of d = 0
-    f = as.numeric(f),
-    f_assumed = ifelse(is.nan(f), 0, f),
-
-    # Add d from two-samples t-test (Lakens, 2013)
-    d_t = t * sqrt(1 / female_n + 1 / male_n),
-
-    # Add d from ANOVA F statistic via conversion to a t statistic
-    d_f = sqrt(f_assumed) * sign_f * sqrt(1 / female_n + 1 / male_n),
-
-    # Add d from mean difference and pooled standard deviation
-    mean_diff = mean_diff_males_mean - mean_diff_females_mean,
-    sd_diff_pooled_numerator = (male_n - 1) * (mean_diff_males_sd^2) +
-      (female_n - 1) * (mean_diff_females_sd^2),
-    df = male_n + female_n - 2,
-    sd_diff_pooled = sqrt(sd_diff_pooled_numerator / df),
-    d_diff = mean_diff / sd_diff_pooled,
-
-    # Add d from one-sample t-test of novelty preference scores
-    mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
-    sd_nov_pref_pooled_numerator = (male_n - 1) * (novelty_pref_males_sd^2) +
-      (female_n) * (novelty_pref_females_sd^2),
-    sd_nov_pref_pooled = sqrt(sd_nov_pref_pooled_numerator / df),
-    d_nov_pref = mean_nov_pref / sd_nov_pref_pooled,
-
-    # Choose one type of outcome variable for each experiment
-    di = case_when(
-      # 1. If d was reported directed
-      !is.na(d) ~ d,
-      # 2. If a t-test was reported
-      !is.na(d_t) ~ d_t,
-      # 3. If an ANOVA was reported
-      !is.na(d_f) ~ d_f,
-      # 4. If the difference between means and their SDs were reported
-      !is.na(d_diff) ~ d_diff,
-      # 5. If novelty preference scores and their SDs were reported
-      !is.na(d_nov_pref) ~ d_nov_pref
-    ),
-    # Keep track which type of outcome measure was chosen for each article
-    di_type = case_when(
-      !is.na(d) ~ "d",
-      !is.na(d_t) ~ "d_t",
-      !is.na(d_f) ~ "d_f",
-      !is.na(d_diff) ~ "d_diff",
-      !is.na(d_nov_pref) ~ "d_nov_pref"
-    ) %>%
-      factor(levels = c("d", "d_t", "d_f", "d_diff", "d_nov_pref")),
-
-    # Apply small sample correction using Hedges' exact method
-    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
-    j = exp(lgamma(df / 2) - log(sqrt(df / 2)) - lgamma((df - 1) / 2)),
-    gi = di * j,
-
-    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
-    ni = female_n + male_n,
-    nhi = 2 / (1 / female_n + 1 / male_n),
-    vi = (df / (df - 2)) * (2 / nhi) * (1 + gi^2 * (nhi / 2)) - (gi^2 / (j^2)),
-    sei = sqrt(vi)
-  ) %>%
-  # Remove experiments that didn't provide any effect size
-  filter(!is.na(gi)) -> dat_gender
-
-# Get an overview of the different effect sizes
-dat_gender %>%
-  select(
-    article,
-    group,
-    gi,
-    di,
-    di_type,
-    d,
-    d_t,
-    d_f,
-    d_diff,
-    sei
-  ) %>%
-  print(n = Inf)
-
+ggsave(here(figures_dir, "fig3_reg.pdf"), width = 12, height = 5)
+```
+
+### Meta-analysis of gender differences
+
+#### Prior predictive check
+
+```{r}
 # Use the same priors as for the main meta-analysis
@@
 summary(res_prior_gender)
-
+```
+
+#### Bayesian three-level meta-analysis
+
+```{r}
 # Run Bayesian multilevel model
@@
 summary(res_gender)
-
+```
+
+#### "Test" posterior probability mass above/below zero
+
+```{r}
 # Get posterior probability mass > 0 for the meta-analytic effect
-(hyp_gender <- hypothesis(res_gender, "Intercept > 0")$hypothesis)
-
+hypothesis(res_gender, "Intercept > 0")$hypothesis
+```
+
+#### Summary of model paramters incl. 95% CrI
+
+```{r}
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_gender, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+draws_gender <- spread_draws(
+  res_gender, `b_.*`, `sd_.*`,
+  regex = TRUE, ndraws = NULL
+) %>%
   # Compute variances and ICC from standard deviations
@@
     .keep = "unused"
-  ) -> draws_gender
+  )
 
 # Summarize as means and 95% credible intervals
-(summ_gender <- as.list(mean_qi(draws_gender)))
-```
-
-\newpage
-
-To confirm the gender difference between males and females, we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between male and female infants reported *within* each experiment by the original authors.
-Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% CrI [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Figure\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_prob(hyp_gender$Post.Prob)`.
-The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level.
-Therefore, `r print_perc(1 - summ_gender$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_gender$icc)` was attributable to differences *between* articles.
-
-The results obtained from our Bayesian analyses were reproduced by classical frequentist three-level meta-analysis and meta-regression models (Supplementary Table\ \@ref(tab:tabs2)).
-
-## Publication bias assessment
-
-```{r, bias, echo=TRUE}
+(summ_gender <- mean_qi(draws_gender))
+```
+
+### Publication bias assessment
+
+#### Egger regression test for mental rotation performance
+
+```{r, echo=TRUE}
 # Classical Egger regression test for the meta-analysis of rotation performance
-(egger_meta <- with(
-  dat_meta, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
-))
+(egger_meta <- regtest(x = dat_meta$gi, sei = dat_meta$sei, model = "lm"))
 (egger_ci_meta <- confint(egger_meta$fit)["Xsei", ])
-
+```
+
+#### Egger regression test for gender differences
+
+```{r}
 # Classical Egger regression test for the meta-analysis of gender_differences
-(egger_gender <- with(
-  dat_gender, regtest(x = gi, sei = sei, model = "lm", predictor = "sei")
-))
+(egger_gender <- regtest(x = dat_gender$gi, sei = dat_gender$sei, model = "lm"))
 (egger_ci_gender <- confint(egger_gender$fit)["Xsei", ])
@@
 
-We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here.
-For the meta-analysis of mental rotation performance (Figure\ \@ref(fig:fig3)A), we observed a slight asymmetry in the funnel plot, indicating a small publication bias.
-This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test).
-Nevertheless, a jackknife (leave-one-out) analysis confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)).
-For the meta-analysis of gender differences in mental rotation performance (Figure\ \@ref(fig:fig3)B), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).
-
-```{r, fig3, include=TRUE, fig.height=3.5, fig.width=12, fig.cap="(ref:fig3-caption)"}
+#### Funnel plot (Figure 4)
+
+```{r, fig.height=3.5, fig.width=12}
 # Create funnel plots for the two meta-analyses
-map2(
+plots_funnel <- map2(
   list(dat_meta, dat_gender),
-  list(summ_meta, summ_meta),
+  list(summ_meta, summ_gender),
   function(dat, summ) {
-
     # Define maximul SE of interest (a bit larger than the largest observed SE)
@@
   }
-) -> plots_funnel
+)
 
@@
 # Save the plot
-ggsave(here(figures_dir, "fig3_funnel.pdf"), width = 12, height = 3.5)
-```
-
-(ref:fig3-caption) **Evaluation of publication bias.**  Funnel plots for the meta-analysis of mental rotation performance (A) and for the meta-analysis of gender differences in mental rotation performance (B).
-The plots show the standard error and effect size for each of the individual experiments as a black square.
-The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect size (vertical black line).
-Gray shades indicate a 95% pseudo-confidence interval (dark gray) and a 99% pseudo-confidence interval (light gray) under the null hypothesis.
-These shades thus illustrate which of the original experiments observed a significant effect.
-For the meta-analysis of mental rotation performance, a slight asymmetry induced by the underrepresentation of experiments with high standard errors and small effect sizes suggests a small publication bias.
-
-# Discussion
-
-We analyzed looking times during mental rotation in `r formatC(descriptives$n_infants, big.mark = ",")` infants ranging from `r descriptives$min_age_months` to `r descriptives$max_age_months` months of age.
-To this end, we scrutinized the robustness of `r descriptives$n_experiments` experimental effect sizes.
-We found that on average, male infants looked longer at novel rotated objects compared to female infants.
-This effect was small to medium and unrelated to age in the current range.
-
-We interpret the meta-regression-based estimate of the gender difference ($b = `r summ_reg$male_female`$, where $b = \Delta{g}$) as an upper bound of the true effect size since this estimate is based on experiments that reported only separate effect sizes for males and females.
-The gender effect of these experiments can be considered as positively biased when assuming that authors who observe a statistically significant gender difference would be more likely to report separate effect sizes for males and females.
-In contrast, the meta-analytic estimate derived from the observed gender differences within each experiment ($g = `r summ_gender$intercept`$) can be viewed as a lower bound of the true effect size.
-This view is plausible because the unknown effect sizes of experiments without significant gender differences were set to zero although non-zero differences were likely also observed but just not reported because of missing power to render these effects statistically significant.
-
-To facilitate the interpretability of our models, the effect size of the looking time difference between novel and familiar rotation events was coded in a linear fashion.
-Accordingly, a positive looking time difference (i.e., a novelty preference) was taken as stronger evidence for mental rotation than a looking time difference of zero (i.e., no systematic preference).
-A zero difference in turn was taken as stronger evidence for mental rotation than a negative looking time difference (i.e., a familiarity preference).
-This approach can be corroborated by the established view that novelty preference is generally considered as the paradigmatic mental rotation behavior [for related discussion, see @black2017; @cristia2018; @houston-price2004].
-Nevertheless, some authors have argued that familiarity preference should also be taken as evidence for mental rotation ability [@erdmann2018; @moore2020; @johnson2020].
-Interpreting novelty preference *and* familiarity preference as successful mental rotation would have increased the effect sizes reported here.
-
-The gender differences observed here remain to be explained by interacting genetic and environmental factors that are largely unknown.
-To the best of our knowledge, there are currently no genetic association or gene-environment interaction studies with a focus on mental rotation.
-Nevertheless, it is documented that genetic contributions to behavioral variance in mental rotation are substantially smaller than unique non-shared environmental contributions both in male and female adults [@shakeshaft2016].
-Whether this observation also applies to infants remains to be explored.
-
-One recent study on 5--6-month-old female infants provided preliminary evidence for possible social-environmental effects related to parental attitudes towards gender which might partly explain the results of our present work [@constantinescu2018].
-As far as we know, potentially mediating and moderating factors that could already be operational in infancy, however, are not yet empirically established.
-In a similar vein, while mental rotation training has small-to-medium post-test effects in children, it is unclear whether it can remove gender differences and be adapted to infants [@uttal2013].
-
-Sex hormone concentration in male infants, especially postnatal testosterone in the first six months of life, could also contribute to gender differences in mental rotation performance [@toivainen2018; @constantinescu2018; @erdmann2019].
-However, possible biological developmental pathways, bridging the gap from hormonal to behavioral differences, are currently far from understood.
-
-A number of additional factors have been associated with individual differences in infant mental rotation performance.
-For example, mental rotation is related to previous relevant experience with the particular objects used in the specific task [@mohring2013; @schwarzer2013a; @slone2018].
-This relation also applies to previous experience with manually rotating toys [@schwarzer2013a].
-While these preliminary results require replication, they are in line with the longstanding notion that prior knowledge is the strongest predictor of learning outcomes in a range of cognitive domains [e.g., @ausubel1968; @bradley1983; @halberda2008].
-Furthermore, there is yet to be confirmed preliminary evidence for possible links between mental rotation performance and several sensory motor skills including fine and gross motor skills, oculomotor control, and crawling skills [@schwarzer2013; @schwarzer2013a].
-
-The present study robustly revealed that male infants look longer at novel rotated objects than female infants.
-Thus, on average, males show more reliable mental rotation behavior already in the first months of life.
-
-# Method
-
-## Protocol
-
-In the present meta-analysis, we followed the established PRISMA 2020 guidelines [Preferred Reporting Items for Systematic reviews and Meta-Analyses\; @page2021].
-The PRISMA checklist is provided in Supplementary Table\ \@ref(tab:tabs4) while Supplementary Figure\ \@ref(fig:figs2) displays the PRISMA flowchart.
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-## Eligibility criteria
-
-Articles needed to fulfill six criteria for being included in this meta-analysis: (1) The article is written in English or German; (2) The article includes results from a group study with human samples (thus excluding review articles, meta-analyses, case studies, and animal studies); (3) These samples include at least one group of infants (mean age between 0 months and 36 months); (4) Infants were not born preterm and had no clinical diagnosis; (5) Infants performed a mental rotation task; (6) The article contains quantitative scores that can be converted into a standardized mean difference (see Data collection process and items below).
-We explicitly included works that were not peer reviewed (e.g., dissertations and preprints) to reduce the impact of publication bias.
-
-## Information sources and search strategy
-
-We entered the search terms ("mental rotation" OR "mental transformation" OR "spatial rotation" OR "spatial transformation" OR "spatial ability" OR "spatial skills") AND ("infant" OR "infants" OR "infanthood" OR "toddler" OR "toddlers" OR "toddlerhood" OR "child" OR "children" OR "childhood" OR "month" OR "months") into four online databases (APA PsycINFO, PubMed/MEDLINE, Scopus, and ProQuest Dissertations & Theses Global).
-All database queries were completed on December 6, 2021.
-We configured the databases to check for article titles, abstracts, and keywords while applying no other filters or limits.
-This yielded 2,616 articles in total, 1,954 of which remained after removing duplicate records (Supplementary Figure\ \@ref(fig:figs2)).
-We further identified 76 articles by screening the reference sections of previous reviews and meta-analyses on mental rotation and related skills [@frick2014; @johnson2020; @kubicek2018; @lauer2019a; @linn1985; @moore2020; @uttal2013; @voyer1995; @yang2020].
-Of these, 34 articles had not been covered by the database search.
-We also identified 94 articles by screening the reference sections of all publications that had been included after the first pass of the selection process.
-Of these, 49 articles had not been covered by the database search.
-Accordingly, we screened 2,037 unique articles in total.
-
-## Selection process
-
-```{r, selection_process}
-# Compute interrater agreement for binary decision (include vs. exclude)
-(irr_bin_perc <- with(raw_screen, mean(bin_1 == bin_2)))
-(irr_bin_kappa <- with(raw_screen, psych::cohen.kappa(cbind(bin_1, bin_2))))
-irr_bin_kappa_w <- as.list(irr_bin_kappa$confid["weighted kappa", ])
-
-# Compute interrater agreement for specific exclusion codes
-(irr_code_perc <- with(raw_screen, mean(code_1 == code_2)))
-(irr_code_kappa <- with(raw_screen, psych::cohen.kappa(cbind(code_1, code_2))))
-irr_code_kappa_w <- as.list(irr_code_kappa$confid["weighted kappa", ])
-
-# Justify exclusion of @pedrett2020 based on outlier mean age
-descs_pedrett2020 <- list(age_years = 2.56)
-descs_pedrett2020 <- within(descs_pedrett2020, {
-  age_months <- age_years * 12
-  next_largest_age_months <- max(dat_meta$age_mean) / 30.417
-  age <- age_years * 365.25
-  z <- (age - mean(dat_meta$age_mean)) / sd(dat_meta$age_mean)
-})
-```
-
-The final sample size of articles was determined by including all articles that fulfilled the inclusion criteria described above.
-Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria.
-Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen's weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]).
-Interrater agreement for the specific eligibility criteria was `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]).
-Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached.
-One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigms used in the other articles.
-Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, digits = 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, digits = 1)` months; $z = `r descs_pedrett2020$z`$ compared to all articles).
-We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life.
-This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Supplementary Figure\ \@ref(fig:figs2)).
-
-Many of these articles consisted of multiple experiments, e.g., using different variations of the mental rotation task or different subsamples of infants.
-We included all of these experiments in the meta-analysis and accounted for the dependencies between them by means of multilevel modeling with by-article random effects (see Bayesian meta-analysis below).
-However, we excluded experiments if there was insufficient information to compute a standardized effect size (see Data collection process and items below).
-Whenever an article reported separate effect sizes for males and females---or other subgroups like crawling and non-crawling infants---but also an effect size combining these groups, we only included the combined effect size.
-Moreover, we disregarded effect sizes that were clearly based on the same data but reported in different articles.
-This procedure led to a total of `r descriptives$n_experiments` experiments being included in the meta-analysis of mental rotation performance (Supplementary Table\ \@ref(tab:tabs1)) and 30 experiments being included in the meta-analysis of gender differences in mental rotation performance.
-
-## Data collection process and items
-
-Outcome measures and other relevant variables were extracted from each article by one of three raters and verified by a second rater.
-For the meta-analysis of mental rotation performance, outcome measures were any summary statistic (Supplementary Table\ \@ref(tab:tabs5)) that could be used to determine the standardized mean difference between novel/unexpected rotation events and familiar/expected rotation events (see Introduction).
-Other extracted variables included, if available, the sample size, the number of males and females, the mean age and its standard deviation, the minimum and maximum age, the type of mental rotation task (habituation or violation of expectation), the modality of stimulus presentation (real objects or objects on a computer screen), and the dimensionality of the stimuli (2D or 3D; Supplementary Table\ \@ref(tab:tabs1)).
-
-We also conducted a meta-analysis of the gender differences in mental rotation performance observed within the original articles.
-For this analysis, the outcome measures were any summary statistic (Supplementary Table\ \@ref(tab:tabs6)) that could be used to determine the standardized mean difference between male infants' mental rotation performance and female infants' mental rotation performance.
-Other extracted variables included the sample size, the mean age and its standard deviation, and the minimum and maximum age of each gender group.
-
-No investigators were contacted for obtaining or confirming additional data and no automated tools were used in the data collection process.
-
-## Effect measures
-
-For the meta-analysis of mental rotation performance, one outcome measure per experiment was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs5) [@goulet-pelletier2018; @hedges1985; @lakens2013; @rosenthal1991; @cumming2012].
-The standard error of Hedges' $g$ for each experiment was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{rotation}=\sqrt{\frac{{df}}{{df}-2}\frac{2(1-r)}{n}\left(1+g_\text{rotation}^2\frac{n}{2(1-r)}\right)-\frac{g_\text{rotation}^2}{J({df})^2}}$$ where $n$ is the sample size of the experiment, ${df}$ are the degrees of freedom (with ${df} = 2(n-1)$), $r$ is the correlation between the two dependent measures in the experiment, and $J({df})$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs5).
-The correlation $r$ was not reported in any of the original articles [see also @harrer2021].
-We therefore always assumed a correlation of $r = 0.50$ to make our analysis comparable to standard (between-group) meta-analyses [@cohen1988; @lakens2013; @morris2002] and because we were able to infer an average correlation of $r \approx 0.50$ from a subsample of articles which provided sufficient information (Supplementary Methods 1).
-A sensitivity analysis indicated that changing the assumed correlation to values from $r = -0.90$ via $r = 0.00$ to $r = 0.90$ had no meaningful impact on the meta-analytic effect sizes (Supplementary Tables\ \@ref(tab:tabs7) and\ \@ref(tab:tabs8)).
-
-For the meta-analysis of gender differences in mental rotation performance, one outcome measure per contrast between male and female infants was converted into a standardized mean difference with small sample correction (Hedges' $g$) using the formulas provided in Supplementary Table\ \@ref(tab:tabs6).
-In some cases where the authors of the original articles did not observe a statistically significant gender difference, they did not report a precise outcome measure.
-In these cases, we assumed an effect size of $g$ = 0.00, thus rendering our meta-analytic effect size of the gender difference more conservative.
-The standard error of Hedges' $g$ for each gender contrast was computed using the formula provided by @goulet-pelletier2018: $${SE}_\text{gender}=\sqrt{\frac{{df}}{{df}-2}\frac{2}{\tilde{n}}\left(1+g_\text{gender}^2\frac{\tilde{n}}{2}\right)-\frac{g_\text{gender}^2}{J({df})^2}}$$ where $df$ are the degrees of freedom (with $df=n_\text{female}+n_\text{male}-2$), $\tilde{n}$ is the harmonic mean of the group sizes (i.e., $\tilde{n}=2/(n_\text{female}^{-1}+n_\text{male}^{-1})$), and $J(df)$ is the correction factor for small samples as described in Supplementary Table\ \@ref(tab:tabs6).
-
-## Bayesian meta-analysis
-
-We synthesized the effect sizes and their sampling variances using a Bayesian multilevel model.
-This model had three levels, with infant participants nested in experiments and experiments nested in articles [@vandennoortgate2013].
-We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for the two standard deviations [i.e., the random effects of experiments and articles\; @williams2018].
-A prior sensitivity analysis indicated that making these priors either more informative or less informative did not have a strong influence on the meta-analytic results (Supplementary Tables\ \@ref(tab:tabs7), \@ref(tab:tabs8), and\ \@ref(tab:tabs9)).
-For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect measures above).
-For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges' $g$) between male infants' mental rotation performance and female infants' mental rotation performance, weighted by its standard error.
-All Bayesian models were fitted using the brms package [Version `r packageVersion("brms")`\; @burkner2017; @burkner2018] in R [Version `r packageVersion("base")`\; @rcoreteam2021] and the Stan language [Version `r packageVersion("rstan")`\; @standevelopmentteam2022].
-Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r print_big(n_iter)` draws (including `r print_big(n_warmup)` warm-up draws) from the posterior distribution.
-To verify the convergence of the Markov chains, we examined rank plots as well as the $\widehat{R}$ and $N_\text{eff}$ statistics [@vehtari2021\; Supplementary Figure\ \@ref(fig:figs3)].
-For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].
-
-## Bayesian meta-regression
-
-We examined the influence of three moderator variables on the mental rotation outcomes across experiments, namely (a) the gender of the sample of infants, (b) the age of the sample of infants, and (c) the type of mental rotation task.
-Gender was coded as a categorical predictor (mixed-gender sample, all-female sample, all-male sample) and contrast-coded using two successive difference contrasts so that we could compare all-female samples versus mixed samples and all-male samples versus all-female samples [@schad2020].
-Age was coded as a continuous predictor in years and centered by subtracting the average across all experiments.
-Task type was coded as a categorical predictor (habituation task, violation of expectation task) and contrast-coded using a scaled sum contrast [@schad2020].
-We then included these predictors for gender, age, and task type as well as two predictors for the interaction between gender and task type (i.e., [female - mixed] $\times$ age, [male - female] $\times$ age) into a Bayesian meta-regression model.
-This model was based on the same random effects structure, sampling parameters, and prior specification as described above, but adding a weakly-informative $\mathcal{N}(0,0.5)$ (normal) prior for all slope parameters.
-
-## Frequentist meta-analysis
-
-We verified the results obtained from our Bayesian analyses using classical frequentist meta-analysis and meta-regression.
-To this end, we used the metafor package [Version `r packageVersion("metafor")`\; @viechtbauer2010] in R to specify the same three-level models as described above but without the Bayesian priors (Supplementary Table\ \@ref(tab:tabs2)).
-These models were fitted using restricted maximum likelihood estimation (REML).
-To verify that this procedure converged on the most probable estimates, we examined profile likelihood plots [@raue2009; @viechtbauer2010] for the two variance components in the model (i.e., the random effects of experiments and articles; Supplementary Figure\ \@ref(fig:figs4)).
-
-## Publication bias assessment
-
-Publication bias was evaluated based on funnel plots and Egger regression tests [@egger1997; @sterne2005].
-Funnel plots visualize the relationship between standard errors and effect sizes.
-They were created by adapting code from the R package metaviz [Version `r packageVersion("metaviz")`\; @kossmeier2020].
-The Egger regression test is a formal statistical test for this relationship between standard errors and effect sizes, probing if the weighted linear regression weight of the effect sizes on the standard errors is significantly different from zero.
-This test was performed using the metafor package and applying a two-sided false-positive error rate of $\alpha = 0.05$.
-
-To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife (leave-one-out) analysis for the meta-analysis of mental rotation performance [@efron1993].
-To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration.
-We then checked if the meta-analytic effect size and heterogeneity remained constant or if it was sensitive against the influence of any individual experiment (Supplementary Table\ \@ref(tab:tabs3)).
-
-We also performed trim-and-fill analyses and tested selection models to confirm the robustness of the results obtained from the frequentist meta-analyses against publication bias [@duval2000; @vevea1995; @vevea2005\; Supplementary Methods 2\; Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)\; Supplementary Figure\ \@ref(fig:figs5)].
-
-## Data and code availability
-
-The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
-
-\newpage
-\nolinenumbers
-
-# References
-
-\bigskip
-
-<div id="refs"></div>
-
-\newpage
-
-```{r child = "supplement.Rmd"}
-
-```
+ggsave(here(figures_dir, "fig4_funnel.pdf"), width = 12, height = 3.5)
+
+# Save current workspace
+save(
+  run,
+  data_dir,
+  models_dir,
+  figures_dir,
+  tables_dir,
+  n_iter,
+  n_warmup,
+  brms_file_refit,
+  descriptives,
+  dat_meta,
+  dat_gender,
+  res_meta,
+  res_reg,
+  res_gender,
+  summ_gender,
+  draws_gender,
+  plots_funnel,
+  legend_funnel,
+  file = here("results", "workspace.RData")
+)
+```

### 2023-02-08 supplement.qmd
Initialize Quarto book

@@
-<!-- Re-define labels for tables and figures -->
-\captionsetup[table]{name=Supplementary Table}
-\captionsetup[figure]{name=Supplementary Figure}
-
-<!-- Restart numbering of figures and tables -->
-\renewcommand{\thefigure}{\arabic{figure}}
-\renewcommand{\thetable}{\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-<!-- Restart page and line numbers -->
-\setcounter{page}{1}
-\resetlinenumber
-\linenumbers
-
 # Supplementary information
 
-<!-- Supplementary methods -->
-
-## Supplementary Methods 1: Correlation between dependent samples
-
-```{r, correlation}
+## Setup
+
+```{r, message=FALSE}
+# Load packages
+library(papaja)
+library(here)
+library(scales)
+library(tidyverse)
+library(furrr)
+library(metafor)
+library(brms)
+library(tidybayes)
+library(cowplot)
+
+# Load custom helper functions
+source(here("manuscript_files", "helper_functions.R"))
+
+# Read work space from the main text script
+load(here("results", "workspace.RData"))
+```
+
+## Supplementary methods
+
+### Correlation between dependent samples
+
+#### Empirical estimate for the correlation (Supplementary Methods 1)
+
+```{r}
 # Compute empirical estimate of the correlation between dependent samples
-dat_meta %>%
+ri_empirical <- dat_meta %>%
   mutate(
@@
   ) %>%
-  pull(ri) -> ri_empirical
+  pull(ri)
 
@@
 # Summarise the estimated correlations
-(summ_ri_empirical <- list(
+list(
   mean = mean(ri_empirical, na.rm = TRUE),
@@
 ) %>%
-  map(print_num))
-```
-
-Meta-analytic methods require an estimate of the sampling variance of each included experiment [@harrer2021].
-For within-participant experimental designs, this sampling variance needs to account for the fact that repeated measures are taken from the same individuals in different conditions.
-Repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants and thus do not provide independent information.
-This is accounted for by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ [see Methods and @goulet-pelletier2018].
-However, the correlation between repeated measures tends to go unreported in research articles.
-In fact, none of the `r descriptives$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.
-
-However, there were `r nrow(dat_ri_empirical)` experiments taken from seven different articles that included enough statistical information to reconstruct this correlation.
-This was done using the following procedure:
-
-1.
-Extract an effect size $d_\text{diff}$ based on a paired $t$-test, a one-sample $t$-test of difference scores, or an analysis of variance (ANOVA) (see rows (1) to (4) in Supplementary Table\ \@ref(tab:tabs5)).
-All three of these tests take the correlation between the repeated measures into account.
-
-2. Extract the mean looking time difference $m_\text{diff}$ (in seconds) between the novel and familiar conditions.
-
-3. Compute the standard deviation ($SD$) of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$
-
-4. Extract the standard deviation of looking times for the novel condition ${SD}_\text{novel}$ and the familiar condition ${SD}_\text{familiar}$.
-
-5.
-Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}^2}{-2\cdot{SD}_\text{novel}\cdot{SD}_\text{familiar}}$$
-
-Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical$mean`$ (median $r = `r summ_ri_empirical$median`$, range [`r summ_ri_empirical$min`, `r summ_ri_empirical$max`]).
-However, we decided to assume a correlation of $r  = 0.50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments.
-This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002].
-To  evaluate the robustness of our Bayesian meta-analytic models against the assumption of a correlation of $r  = 0.50$, we ran a sensitivity analysis (Supplementary Tables\ \@ref(tab:tabs7) and \@ref(tab:tabs8)).
-
-## Supplementary Methods 2: Publication bias correction
-
-We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias.
-For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis.
-In our first step, we computed a trim-and-fill model by imputing possible effect sizes of non-published experiments [@duval2000].
-This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Figure\ \@ref(fig:figs5)).
-
-In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis.
-These models were based on the assumption that experiments yielding significant effects (i.e., small $p$ values) are more likely to get published.
-Specifically, we ran one selection model assuming a weight function with fixed $p$ value cutoffs [@vevea1995] at $p$ = 0.05 and $p$ = 0.01.
-Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005].
-These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)).
-
-<!-- Supplementary tables -->
-
-\singlespacing
-\renewcommand{\arraystretch}{0.97}
-
-```{r, tabs1, include=TRUE}
-# Save table of experiments for the meta-analysis of rotation
-dat_meta %>%
-  mutate(
-    age_mean = print_days_months(age_mean),
-    age_sd = str_c(as.character(round(age_sd)), "d"),
-  ) %>%
-  transmute(
-    Article = if_else(article == lag(article, default = ""), "", article),
-    Experiment = group,
-    `Sample size` = as.integer(sample_size),
-    Females = as.integer(round(female_percent * sample_size)),
-    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
-    Task = as.character(task),
-    `Stimulus type` = str_to_sentence(stimuli_presentation),
-    `Stimulus dimensions` = str_c(as.integer(stimuli_dimensions), "D")
-  ) %>%
-  mutate(
-    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
-  ) -> tabs1
-
-# Save the table
-dir.create(tables_dir, showWarnings = FALSE)
-write_tsv(tabs1, file = here(tables_dir, "tabs1_experiments.tsv"), na = "n/a")
-
-# Add footnotes
-colnames(tabs1)[5] <- str_c(colnames(tabs1)[5], "\\textsuperscript{a}")
-tabs1$Females[1] <- str_c(tabs1$Females[1], "\\textsuperscript{b}")
-tabs1$Task[3] <- str_c(tabs1$Task[3], "\\textsuperscript{c}")
-
-# Display the table
-apa_table(
-  tabs1,
-  caption = "Experiments included in the main analysis",
-  note = str_c(
-    "\\scriptsize",
-    "\\textsuperscript{a} = mean ± standard deviation, ",
-    "\\textsuperscript{b} = not available, ",
-    "\\textsuperscript{c} = violation of expectation."
-  ),
-  landscape = TRUE, font_size = "scriptsize", escape = FALSE
-)
-```
-
-```{r, frequentist}
+  map(print_num)
+```
+
+## Supplementary tables
+
+### Frequentist meta-analyses and meta-regression
+
+#### Frequentist meta-analysis of mental rotation performance
+
+```{r}
 # Compute frequentist three-level model for the meta-analysis of rotation
@@
 print(res_freq_meta)
-
+```
+
+#### Variance at each level of the model
+
+```{r}
 # Check share of variance at each level of the model
@@
 round(res_freq_meta$sigma2[2] / sum(res_freq_meta$sigma2), 3)
-
-# Get profile likelihoods for sigmas to check that REML has converged
-prof_liks <- profile(res_freq_meta, plot = FALSE)
-
+```
+
+#### Frequentist meta-regression of mental rotation performance
+
+```{r}
 # Compute frequentist meta-regression with gender, age, and task
@@
 print(res_freq_reg)
-
+```
+
+#### Frequentist meta-analysis of gender differences
+
+```{r}
 # Compute frequentist three-level model for the meta-analysis of gender
@@
 
-\renewcommand{\arraystretch}{1.10}
-
-```{r, tabs2, include=TRUE}
+#### Summary table (Supplementary Table 1)
+
+```{r}
 # Format all frequentist results together as a table
-map2_dfr(
+tabs2 <- map2_dfr(
   list(res_freq_meta, res_freq_reg, res_freq_gender),
@@
   # Replace NAs with blank cells
-  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tabs2
+  mutate(across(.fns = ~ ifelse(is.na(.), "", .)))
 
@@
 # Add footnotes
-colnames(tabs2)[4] <- str_c(colnames(tabs2)[4], "\\textsuperscript{a}")
-colnames(tabs2)[7] <- str_c(colnames(tabs2)[7], "\\textsuperscript{b}")
+colnames(tabs2)[4] <- str_c(colnames(tabs2)[4], "^a^")
+colnames(tabs2)[7] <- str_c(colnames(tabs2)[7], "^b^")
 
@@
   tabs2,
-  caption = "Frequentist meta-analyses and meta-regression",
   note = str_c(
-    "\\scriptsize",
-    "\\textsuperscript{a} = standard error, ",
-    "\\textsuperscript{b} = 95\\% confidence interval."
+    "^a^ = standard error, ",
+    "^b^ = 95\\% confidence interval."
   ),
@@
 
-```{r, jackknife}
+### Jackknife (leave-one-out) analysis
+
+#### Re-fit Bayesian meta-analysis, leaving one experiment out
+
+```{r}
 # Re-run the jackknife analysis if requested
 if (run$jackknife_analysis) {
-
   # Re-fit the meta-analysis, leaving out one experiment at a time
@@
   plan(multisession, workers = n_workers)
-  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
+  tabs3 <- future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
     dat_jackknife <- dat_meta[-jackknife_index, ]
@@
       Article = if_else(Article == lag(Article, default = ""), "", Article),
-    ) -> tabs3
+    )
 
@@
 
-\renewcommand{\arraystretch}{0.97}
-
-```{r, tabs3, include=TRUE}
+#### Summary table (Supplementary Table 3)
+
+```{r}
 # Read jackknife table from file
@@
 # Add footnotes
-colnames(tabs3)[6] <- str_c(colnames(tabs3)[6], "\\textsuperscript{a}")
+colnames(tabs3)[6] <- str_c(colnames(tabs3)[6], "^a^")
 
@@
   tabs3,
-  caption = "Jackknife (leave-one-out) analysis", font_size = "scriptsize",
-  note = "\\scriptsize\\textsuperscript{a} = intraclass correlation.",
+  font_size = "scriptsize",
+  note = "^a^ = intraclass correlation.",
   landscape = TRUE, escape = FALSE, align = "llrrrr"
@@
 
-\renewcommand{\arraystretch}{1.30}
-
-```{r, tabs4, include=TRUE}
+### PRISMA checklist
+
+#### Print PRISMA checklist (Supplementary Table 4)
+
+```{r}
 # Read PRISMA checklist from file
@@
   tabs4,
-  caption = "PRISMA 2020 checklist", font_size = "scriptsize",
+  font_size = "scriptsize",
   landscape = TRUE,
@@
 ```
+
+### Effect size conversion
+
+#### Formulas for mental rotation performance (Supplementary Table 5)
 
@@
 
-Table: (\#tab:tabs5) Effect sizes for the meta-analysis of mental rotation performance
+#### Formulas for gender differences (Supplementary Table 6)
 
@@
 
-Table: (\#tab:tabs6) Effect sizes for the meta-analysis of gender differences
-
-\normalsize
-
-```{r, sensitivity}
+### Sensitivity analyses
+
+#### Re-fit Bayesian meta-analysis with different correlations and priors
+
+```{r}
 # Re-run the sensitivity analyses if requested
 if (run$sensitivity_analysis) {
-
   # Re-run the meta-analysis for different values of r_assumed
-  seq(-0.9, 0.9, by = 0.3) %>%
+  sens_ri <- seq(-0.9, 0.9, by = 0.3) %>%
     map_dfr(function(ri_sens) {
-
       # Re-compute standard errors of the effect sizes
-      mutate(
+      dat_ri_sens <- mutate(
         dat_meta,
@@
         sei = sqrt(vi)
-      ) -> dat_ri_sens
+      )
 
@@
       manipulation_name = c("Assumed correlation", rep("", nrow(.) - 1)), .
-    ) -> sens_ri
+    )
 
   # Prior sensitivity analysis
-  list(
+  sens_prior <- list(
     # Less informative prior for the intercept
@@
     map2_dfr(names(.), function(prior_sens, prior_name) {
-
       # Re-run meta-analysis of mental rotation performance
@@
       manipulation_name = c("Prior specification", rep("", nrow(.) - 1)), .
-    ) -> sens_prior
+    )
 
@@
   # Create table for the meta-analysis of mental rotation performance
-  sens %>%
+  tabs7 <- sens %>%
     select(res_meta, manipulation_name, manipulation_value) %>%
@@
       )
-    }) -> tabs7
+    })
   write_tsv(tabs7, file = here(tables_dir, "tabs7_sens_meta.tsv"))
@@
   # Create table for the meta-regression of mental rotation performance
-  sens %>%
+  tabs8 <- sens %>%
     select(
@@
       )
-    }) -> tabs8
+    })
   write_tsv(tabs8, file = here(tables_dir, "tabs8_sens_reg.tsv"))
@@
   # Create table for the meta-analysis of gender differences
-  sens %>%
+  tabs9 <- sens %>%
     filter(!map_lgl(res_gender, is.null)) %>%
@@
       )
-    }) -> tabs9
+    })
   write_tsv(tabs9, file = here(tables_dir, "tabs9_sens_gender.tsv"))
@@
 
-\renewcommand{\arraystretch}{1.10}
-
-```{r, tabs7, include=TRUE}
+#### Sensitivity table for mental rotation performance (Supplementary Table 7)
+
+```{r}
 # Load sensitivity analysis table from file
@@
 # Add footnotes
-colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "\\textsuperscript{a}")
-tabs7$` `[8] <- str_c(tabs7$` `[8], "\\textsuperscript{b}")
-tabs7$` `[9] <- str_c(tabs7$` `[9], "\\textsuperscript{c}")
-tabs7$` `[10] <- str_c(tabs7$` `[10], "\\textsuperscript{d}")
-tabs7$` `[11] <- str_c(tabs7$` `[11], "\\textsuperscript{e}")
+colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "^a}")
+tabs7$` `[8] <- str_c(tabs7$` `[8], "^b^")
+tabs7$` `[9] <- str_c(tabs7$` `[9], "^c^")
+tabs7$` `[10] <- str_c(tabs7$` `[10], "^d^")
+tabs7$` `[11] <- str_c(tabs7$` `[11], "^e^")
 
@@
   tabs7,
-  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
   note = str_c(
-    "\\scriptsize",
-    "\\textsuperscript{a} = intraclass correlation, ",
-    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
-    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
-    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
-    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
+    "^a^ = intraclass correlation, ",
+    "^b^ = an uninformative (uniform) prior on the mean effect, ",
+    "^c^ = an informative (normal) prior on the mean effect, ",
+    "^d^ = an uninformative (uniform) prior on the standard deviations, ",
+    "^e^ = an informative (Student-$t$) prior on the standard deviations."
   ),
@@
 
-\renewcommand{\arraystretch}{0.97}
-
-```{r, tabs8, include=TRUE}
+#### Sensitivity table for meta-regression (Supplementary Table 8)
+
+```{r}
 # Load sensitivity analysis table from file
@@
 # Add footnotes
-colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "\\textsuperscript{a}")
-tabs8$` `[8] <- str_c(tabs8$` `[8], "\\textsuperscript{b}")
-tabs8$` `[9] <- str_c(tabs8$` `[9], "\\textsuperscript{c}")
-tabs8$` `[10] <- str_c(tabs8$` `[10], "\\textsuperscript{d}")
-tabs8$` `[11] <- str_c(tabs8$` `[11], "\\textsuperscript{e}")
+colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "^a^")
+tabs8$` `[8] <- str_c(tabs8$` `[8], "^b^")
+tabs8$` `[9] <- str_c(tabs8$` `[9], "^c^")
+tabs8$` `[10] <- str_c(tabs8$` `[10], "^d^")
+tabs8$` `[11] <- str_c(tabs8$` `[11], "^e^")
 
@@
   tabs8,
-  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
   note = str_c(
-    "\\scriptsize",
-    "\\textsuperscript{a} = violation of expectation, ",
-    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
-    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
-    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
-    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
+    "^a^ = violation of expectation, ",
+    "^b^ = an uninformative (uniform) prior on the mean effect, ",
+    "^c^ = an informative (normal) prior on the mean effect, ",
+    "^d^ = an uninformative (uniform) prior on the standard deviations, ",
+    "^e^ = an informative (Student-$t$) prior on the standard deviations."
   ),
@@
 
-```{r, tabs9, include=TRUE}
+#### Sensitivity table for gender differences (Supplementary Table 9)
+
+```{r}
 # Load sensitivity analysis table from file
@@
 # Add footnotes
-colnames(tabs9)[6] <- str_c(colnames(tabs9)[6], "\\textsuperscript{a}")
-tabs9$` `[1] <- str_c(tabs9$` `[1], "\\textsuperscript{b}")
-tabs9$` `[2] <- str_c(tabs9$` `[2], "\\textsuperscript{c}")
-tabs9$` `[3] <- str_c(tabs9$` `[3], "\\textsuperscript{d}")
-tabs9$` `[4] <- str_c(tabs9$` `[4], "\\textsuperscript{e}")
+colnames(tabs9)[6] <- str_c(colnames(tabs9)[6], "^a}")
+tabs9$` `[1] <- str_c(tabs9$` `[1], "^b^")
+tabs9$` `[2] <- str_c(tabs9$` `[2], "^c^")
+tabs9$` `[3] <- str_c(tabs9$` `[3], "^d^")
+tabs9$` `[4] <- str_c(tabs9$` `[4], "^e^")
 
@@
   tabs9,
-  caption = "Sensitivity analyses for the meta-analysis of gender differences",
   note = str_c(
-    "\\scriptsize",
-    "\\textsuperscript{a} = intraclass correlation, ",
-    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
-    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
-    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
-    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
+    "^a^ = intraclass correlation, ",
+    "^b^ = an uninformative (uniform) prior on the mean effect, ",
+    "^c^ = an informative (normal) prior on the mean effect, ",
+    "^d^ = an uninformative (uniform) prior on the standard deviations, ",
+    "^e^ = an informative (Student-$t$) prior on the standard deviations."
   ),
@@
 
-```{r, correction}
+### Publication bias correction
+
+#### Fit trim-and-fill and selection models
+
+```{r}
 # Re-fit the two frequentist meta-analyses using a two-level model
 # This is because `rma.mv()` is not supported for trim-and-fill/selection models
-list(meta = dat_meta, gender = dat_gender) %>%
-  map(function(x) rma.uni(gi, vi, data = x)) -> res_freq_2_lvl
+res_freq_2_lvl <- list(meta = dat_meta, gender = dat_gender) %>%
+  map(function(x) rma.uni(gi, vi, data = x))
 
 # Trim-and-fill analysis
-res_freq_2_lvl %>% map(trimfill) -> res_trim_fill
+res_trim_fill <- res_freq_2_lvl %>% map(trimfill)
 
 # Easy weight function selection model (see metafor docs and Lauer et al., 2019)
-res_freq_2_lvl %>%
-  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 1.00)) ->
-res_selection_weights
+res_selection_weights <- res_freq_2_lvl %>%
+  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 1.00))
 
 # More selection models based on four different step functions
-res_freq_2_lvl %>%
+res_selection_steps <- res_freq_2_lvl %>%
   map(function(res) {
-
     # Define custom step functions
@@
       })
-  }) -> res_selection_steps
+  })
 
@@
 # Each table will contain the results of all trim-and-fill and selection models
-map(names(res_freq_2_lvl), function(name) {
-
+tabs_correction <- map(names(res_freq_2_lvl), function(name) {
   # Combine two-level, trim-and-fill, and selection models
@@
 }) %>%
-  set_names(names(res_freq_2_lvl)) -> tabs_correction
+  set_names(names(res_freq_2_lvl))
 
@@
 
-```{r, tabs10, include=TRUE}
+#### Correction table for mental rotation performance (Supplementary Table 10)
+
+```{r}
 # Add footnotes
-colnames(tabs10)[4] <- str_c(colnames(tabs10)[4], "\\textsuperscript{a}")
-colnames(tabs10)[7] <- str_c(colnames(tabs10)[7], "\\textsuperscript{b}")
+colnames(tabs10)[4] <- str_c(colnames(tabs10)[4], "^a^")
+colnames(tabs10)[7] <- str_c(colnames(tabs10)[7], "^b^")
 
@@
   tabs10,
-  caption = "Publication bias correction for the meta-analysis of mental rotation performance",
   note = str_c(
-    "\\scriptsize",
-    "\\textsuperscript{a} = standard error, ",
-    "\\textsuperscript{b} = 95\\% confidence interval."
+    "^a^ = standard error, ",
+    "^b^ = 95\\% confidence interval."
   ),
@@
 
-```{r, tabs11, include=TRUE}
+#### Correction table for gender differences (Supplementary Table 11)
+
+```{r}
 # Add footnotes
-colnames(tabs11)[4] <- str_c(colnames(tabs11)[4], "\\textsuperscript{a}")
-colnames(tabs11)[7] <- str_c(colnames(tabs11)[7], "\\textsuperscript{b}")
+colnames(tabs11)[4] <- str_c(colnames(tabs11)[4], "^a^")
+colnames(tabs11)[7] <- str_c(colnames(tabs11)[7], "^b^")
 
@@
   tabs11,
-  caption = "Publication bias correction for the meta-analysis of gender differences",
   note = str_c(
-    "\\scriptsize",
-    "\\textsuperscript{a} = standard error, ",
-    "\\textsuperscript{b} = 95\\% confidence interval."
+    "^a^ = standard error, ",
+    "^b^ = 95\\% confidence interval."
   ),
@@
 
-\newpage
-
-<!-- Supplementary figures -->
-
-```{r, figs1, include=TRUE, fig.height=8, fig.width=12, fig.cap="(ref:figs1-caption)"}
+## Supplementary figures
+
+### Convergence checks
+
+#### Trace plots (Supplementary Figure 1)
+
+```{r, fig.height=6, fig.width=12}
+# Extract convergence statistics (Rhat, Neff) from Bayesian results
+conv_stats <- with(summary(res_meta), tibble(
+  parameter = c(
+    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
+  ),
+  name_expr = c(
+    "\"Hedges'\" ~ italic(g)",
+    "italic(sigma)[article]",
+    "italic(sigma)[experiment]"
+  ),
+  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
+  bulk_ess = print_big(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
+  tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
+  r_hat_expr = str_c("italic(widehat(R)) == \"", r_hat, "\""),
+  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == \"", bulk_ess, "\""),
+  tail_ess_expr = str_c("italic(N)[eff(tail)] == \"", tail_ess, "\""),
+  y_pos = c(0.7, 0.75, 0.8)
+))
+
+# Create trace plot
+n_draws <- n_iter - n_warmup
+bayesplot::mcmc_trace(
+  res_meta,
+  pars = conv_stats$parameter, facet_args = list(ncol = 1)
+) +
+  # Parameter label
+  geom_text(
+    aes(y = 0.45, label = name_expr, color = NA),
+    conv_stats,
+    y = 0.45, x = -0.042 * n_draws, vjust = 1, color = "black", parse = TRUE,
+    angle = 90
+  ) +
+  # Rhat label
+  geom_text(
+    aes(y = y_pos, label = r_hat_expr, color = NA),
+    conv_stats,
+    x = 0.684 * n_draws, hjust = 1, vjust = 0.2, color = "black", parse = TRUE
+  ) +
+  # Neff labels
+  geom_text(
+    aes(y = y_pos, label = bulk_ess_expr, color = NA),
+    conv_stats,
+    x = 0.842 * n_draws, hjust = 1, color = "black", parse = TRUE,
+  ) +
+  geom_text(
+    aes(y = y_pos, label = tail_ess_expr, color = NA),
+    conv_stats,
+    x = n_draws, hjust = 1, color = "black", parse = TRUE,
+  ) +
+  # Styling
+  labs(x = "Sample number", y = NULL, color = "MCMC\nchain") +
+  coord_cartesian(expand = FALSE, clip = "off") +
+  scale_x_continuous(limits = c(0, n_draws), breaks = seq(0, n_draws, 2000)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  scale_color_grey(start = 0.0, end = 0.9) +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    plot.margin = margin(t = 10, l = 25),
+    strip.background = element_blank(),
+    strip.text = element_blank(),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "figs1_convergence.pdf"), width = 12, height = 6)
+```
+
+#### Profile likelihood plots (Supplementary Figure 2)
+
+```{r, fig.height=4, fig.width=12}
+# Get profile likelihoods for sigmas to check that REML has converged
+prof_liks <- profile(res_freq_meta, plot = FALSE)
+
+# Combine frequentist profile likelihood results into one data frame
+prof_liks_df <- prof_liks %>%
+  head(-1) %>% # Remove the `comp` element
+  map(~ tibble(sigma2 = .$sigma2, ll = .$ll)) %>%
+  bind_rows(.id = "parameter") %>%
+  # Create new labels for plotting
+  mutate(parameter = factor(
+    parameter,
+    levels = c(1, 2),
+    labels = c("italic(sigma)[article]^2", "italic(sigma)[experiment]^2")
+  ))
+
+# Find the best-fitting parameter estimates
+prof_liks_max <- prof_liks_df %>%
+  group_by(parameter) %>%
+  filter(ll == max(ll))
+
+# Create plot
+prof_liks_df %>%
+  ggplot(aes(x = sigma2, y = ll)) +
+  facet_wrap(~parameter, scales = "free", labeller = label_parsed) +
+  # Best fitting parameters
+  geom_hline(
+    aes(yintercept = ll),
+    data = prof_liks_max, linetype = "dashed"
+  ) +
+  geom_vline(
+    aes(xintercept = sigma2),
+    data = prof_liks_max, linetype = "dashed"
+  ) +
+  # All tested parameters
+  geom_point() +
+  geom_line() +
+  # Styling
+  labs(x = "Parameter value", y = "Restricted log-likelihood") +
+  theme_classic() +
+  theme(
+    axis.line = element_line(colour = "black"),
+    axis.text = element_text(family = "Helvetica", color = "black"),
+    axis.ticks = element_line(color = "black"),
+    strip.background = element_blank(),
+    strip.text = element_text(family = "Helvetica", color = "black", size = 12),
+    text = element_text(family = "Helvetica", color = "black")
+  )
+
+# Save the plot
+ggsave(here(figures_dir, "figs2_convergence_freq.pdf"), width = 12, height = 4)
+```
+
+### Trim-and-fill plot
+
+#### Funnel plot for trim-and-fill model (Supplementary Figure 3)
+
+```{r, fig.width=12, fig.height=3.5}
+# Create new funnel plots that take the trim-and-fill results into account
+plots_funnel_trim_fill <- map2(
+  res_trim_fill, plots_funnel,
+  function(res, plot) {
+    # Compute new funnel
+    funnel_trim_fill <- with(
+      list(
+        z_crit_05 = stats::qnorm(0.975),
+        max_se = max(sqrt(res$vi)) + 0.05
+      ),
+      {
+        data.frame(
+          x = c(
+            res$b - z_crit_05 * sqrt(max_se^2),
+            res$b,
+            res$b + z_crit_05 * sqrt(max_se^2)
+          ),
+          y = c(max_se, 0, max_se)
+        )
+      }
+    )
+
+    # Add new funnel on top of the original funnel plot
+    trim_fill_color <- ifelse(sum(res$fill) >= 1, "#e42536", NA)
+    plot +
+      # Add trim-and-fill funnel
+      geom_path(
+        data = funnel_trim_fill,
+        aes(x = x, y = y),
+        color = trim_fill_color
+      ) +
+      geom_vline(xintercept = res$b, color = trim_fill_color) +
+      # Add trim-and-fill studies
+      geom_point(
+        data = with(res, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
+        color = trim_fill_color, shape = 0
+      )
+  }
+)
+
+# Combine plots and legend
+plot_grid(
+  plotlist = plots_funnel_trim_fill, nrow = 1, labels = "AUTO",
+  label_size = 11, label_fontfamily = "Helvetica"
+) +
+  draw_plot(legend_funnel, x = -0.39, y = 0.355)
+
+# Save the plot
+ggsave(
+  here(figures_dir, "figs3_funnel_trim_fill.pdf"),
+  width = 12, height = 3.5
+)
+```
+
+### Meta-analysis of gender differences
+
+#### Forest plot (Supplementary Figure 4)
+
+```{r, fig.height=8, fig.width=12}
 # Get posterior draws for the effect *in each experiment*
@@
 # Save the plot
-ggsave(here(figures_dir, "figs1_gender.pdf"), width = 12, height = 8)
-```
-
-(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants.
-White squares indicate the effect sizes (Hedges' $g$) of gender differences in all individual experiments and black lines indicate their 95% confidence intervals.
-For experiments resulting in a non-significant gender difference and for which the authors did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$.
-Gray bars depict the 50% and 95% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model.
-The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
-
-```{r, figs2, include=TRUE, fig.width=6, fig.cap="(ref:figs2-caption)", fig.pos="ht", out.width="50%"}
-# Include the flowchart (which was created manually with MS PowerPoint)
-knitr::include_graphics(here("manuscript_files/flowchart.pdf"))
-```
-
-(ref:figs2-caption) **Literature search and selection process.** (A) We searched four online databases as well as reviews and reference sections to identify articles in which mental rotation experiments in infants were reported.
-(B) Experiments were included in the meta-analysis if they fulfilled six pre-specified inclusion criteria.
-(C) Redundant articles comprising the same experiment(s) were excluded.
-\textsuperscript{a} = We decided to exclude two additional articles: one article because it was based on an uncommon experimental paradigm, differing substantially from all other articles, and another article because it was based on a sample of infants who were substantially older compared to all other articles.
-
-```{r, figs3, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs3-caption)"}
-# Extract convergence statistics (Rhat, Neff) from Bayesian results
-conv_stats <- with(summary(res_meta), tibble(
-  parameter = c(
-    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
-  ),
-  name_expr = c(
-    "\"Hedges'\" ~ italic(g)",
-    "italic(sigma)[article]",
-    "italic(sigma)[experiment]"
-  ),
-  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
-  bulk_ess = print_big(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
-  tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
-  r_hat_expr = str_c("italic(widehat(R)) == \"", r_hat, "\""),
-  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == \"", bulk_ess, "\""),
-  tail_ess_expr = str_c("italic(N)[eff(tail)] == \"", tail_ess, "\""),
-  y_pos = c(0.7, 0.75, 0.8)
-))
-
-# Create trace plot
-n_draws <- n_iter - n_warmup
-bayesplot::mcmc_trace(
-  res_meta,
-  pars = conv_stats$parameter, facet_args = list(ncol = 1)
-) +
-  # Parameter label
-  geom_text(
-    aes(y = 0.45, label = name_expr, color = NA),
-    conv_stats,
-    y = 0.45, x = -0.042 * n_draws, vjust = 1, color = "black", parse = TRUE,
-    angle = 90
-  ) +
-  # Rhat label
-  geom_text(
-    aes(y = y_pos, label = r_hat_expr, color = NA),
-    conv_stats,
-    x = 0.684 * n_draws, hjust = 1, vjust = 0.2, color = "black", parse = TRUE
-  ) +
-  # Neff labels
-  geom_text(
-    aes(y = y_pos, label = bulk_ess_expr, color = NA),
-    conv_stats,
-    x = 0.842 * n_draws, hjust = 1, color = "black", parse = TRUE,
-  ) +
-  geom_text(
-    aes(y = y_pos, label = tail_ess_expr, color = NA),
-    conv_stats,
-    x = n_draws, hjust = 1, color = "black", parse = TRUE,
-  ) +
-  # Styling
-  labs(x = "Sample number", y = NULL, color = "MCMC\nchain") +
-  coord_cartesian(expand = FALSE, clip = "off") +
-  scale_x_continuous(limits = c(0, n_draws), breaks = seq(0, n_draws, 2000)) +
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
-  scale_color_grey(start = 0.0, end = 0.9) +
-  theme_classic() +
-  theme(
-    axis.line = element_line(colour = "black"),
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    plot.margin = margin(t = 10, l = 25),
-    strip.background = element_blank(),
-    strip.text = element_blank(),
-    text = element_text(family = "Helvetica", color = "black")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "figs3_convergence.pdf"), width = 12, height = 6)
-```
-
-(ref:figs3-caption) **Convergence checks for the Bayesian meta-analysis.** For each of the three parameters in the three-level meta-analytic model, gray traces show the exploration of the posterior distribution by four independent Markov Chain Monte Carlo (MCMC) chains.
-Overlap of the gray traces as well as random upward and downward fluctuations (rather than systematic drifts) indicate efficient exploration of the posterior distribution.
-$\widehat{R}$ = potential scale reduction factor, with values close to 1.00 indicating convergence of the chains, $N_\text{eff(bulk)}$ = bulk effective sample size, with larger values indicating better sampling efficiency in the bulk of the distribution (e.g., for estimating the posterior mean), $N_\text{eff(tail)}$ = tail effective sample size, with larger values indicating better sampling efficiency in the tails of the distribution (e.g., for estimating the 95% credible interval [CrI]).
-Details about these convergence criteria can be found in @vehtari2021.
-
-```{r, figs4, include=TRUE, fig.height=4, fig.width=12, fig.cap="(ref:figs4-caption)"}
-# Combine frequentist profile likelihood results into one data frame
-prof_liks %>%
-  head(-1) %>% # Remove the `comp` element
-  map(~ tibble(sigma2 = .$sigma2, ll = .$ll)) %>%
-  bind_rows(.id = "parameter") %>%
-  # Create new labels for plotting
-  mutate(parameter = factor(
-    parameter,
-    levels = c(1, 2),
-    labels = c("italic(sigma)[article]^2", "italic(sigma)[experiment]^2")
-  )) -> prof_liks_df
-
-# Find the best-fitting parameter estimates
-prof_liks_df %>%
-  group_by(parameter) %>%
-  filter(ll == max(ll)) -> prof_liks_max
-
-# Create plot
-prof_liks_df %>%
-  ggplot(aes(x = sigma2, y = ll)) +
-  facet_wrap(~parameter, scales = "free", labeller = label_parsed) +
-  # Best fitting parameters
-  geom_hline(
-    aes(yintercept = ll),
-    data = prof_liks_max, linetype = "dashed"
-  ) +
-  geom_vline(
-    aes(xintercept = sigma2),
-    data = prof_liks_max, linetype = "dashed"
-  ) +
-  # All tested parameters
-  geom_point() +
-  geom_line() +
-  # Styling
-  labs(x = "Parameter value", y = "Restricted log-likelihood") +
-  theme_classic() +
-  theme(
-    axis.line = element_line(colour = "black"),
-    axis.text = element_text(family = "Helvetica", color = "black"),
-    axis.ticks = element_line(color = "black"),
-    strip.background = element_blank(),
-    strip.text = element_text(family = "Helvetica", color = "black", size = 12),
-    text = element_text(family = "Helvetica", color = "black")
-  )
-
-# Save the plot
-ggsave(here(figures_dir, "figs4_convergence_freq.pdf"), width = 12, height = 4)
-```
-
-(ref:figs4-caption) **Convergence checks for the frequentist meta-analysis.** Black curves show the profile of the restricted log likelihood for the two variance components in the frequentist three-level model.
-The two peaks indicate that restricted maximum likelihood estimation (REML) was able to converge on the most likely parameter estimates [@raue2009; @viechtbauer2010].
-
-```{r, figs5, include=TRUE, fig.width=12, fig.height=3.5, fig.cap="(ref:figs5-caption)"}
-# Create new funnel plots that take the trim-and-fill results into account
-map2(res_trim_fill, plots_funnel, function(res, plot) {
-
-  # Compute new funnel
-  funnel_trim_fill <- with(
-    list(
-      z_crit_05 = stats::qnorm(0.975),
-      max_se = max(sqrt(res$vi)) + 0.05
-    ),
-    {
-      data.frame(
-        x = c(
-          res$b - z_crit_05 * sqrt(max_se^2),
-          res$b,
-          res$b + z_crit_05 * sqrt(max_se^2)
-        ),
-        y = c(max_se, 0, max_se)
-      )
-    }
-  )
-
-  # Add new funnel on top of the original funnel plot
-  trim_fill_color <- ifelse(sum(res$fill) >= 1, "#e42536", NA)
-  plot +
-    # Add trim-and-fill funnel
-    geom_path(
-      data = funnel_trim_fill,
-      aes(x = x, y = y),
-      color = trim_fill_color
-    ) +
-    geom_vline(xintercept = res$b, color = trim_fill_color) +
-    # Add trim-and-fill studies
-    geom_point(
-      data = with(res, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
-      color = trim_fill_color, shape = 0
-    )
-}) -> plots_funnel_trim_fill
-
-# Combine plots and legend
-plot_grid(
-  plotlist = plots_funnel_trim_fill, nrow = 1, labels = "AUTO",
-  label_size = 11, label_fontfamily = "Helvetica"
-) +
-  draw_plot(legend_funnel, x = -0.39, y = 0.355)
-
-# Save the plot
-ggsave(
-  here(figures_dir, "figs5_funnel_trim_fill.pdf"),
-  width = 12, height = 3.5
-)
-```
-
-(ref:figs5-caption) **Trim-and-fill analysis.** As in Figure\ \@ref(fig:fig3) in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance (A) and in the meta-analysis of gender differences within each article (B).
-The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines).
-Gray shades indicate 95% pseudo-confidence intervals (dark gray) and 99% pseudo-confidence intervals (light gray) under the null hypothesis.
-Red squares show fictional experiments that were imputed using the trim-and-fill method  to compensate for the small publication bias observed in the original funnel plot.
-Red lines depict the meta-analytic effect size and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analysis of mental rotation performance.
-For the meta-analysis of gender differences, the results of the trim-and-fill analysis suggested that no additional experiments had to be imputed to compensate for publication bias.
-
-```{r, meta_pos}
+ggsave(here(figures_dir, "figs4_gender.pdf"), width = 12, height = 8)
+```
+
+### Accounting for familiarity preferences
+
+#### Re-fit meta-analysis of mental rotation performance
+
+```{r}
 # Re-code familiarity preference to be treated the same as novelty preference
@@
 summary(res_meta_pos)
-
+```
+
+#### Summary of model parameters
+
+```{r}
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_meta_pos, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+draws_meta_pos <- spread_draws(
+  res_meta_pos, `b_.*`, `sd_.*`,
+  regex = TRUE, ndraws = NULL
+) %>%
   # Compute variances and ICC from standard deviations
@@
     .keep = "unused"
-  ) -> draws_meta_pos
+  )
 
 # Summarize as means and 95% credible intervals
-(summ_meta_pos <- as.list(mean_qi(draws_meta_pos)))
-```
-
-```{r, figs5new, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:figs5new-caption)"}
+(summ_meta_pos <- mean_qi(draws_meta_pos))
+```
+
+#### Forest plot (Supplementary Figure 5)
+
+```{r, fig.height=14, fig.width=12}
 # Get posterior draws for the effect *in each experiment*
@@
 # Save the plot
-ggsave(here(figures_dir, "figs5new_meta_pos.pdf"), width = 12, height = 14)
-```
-
-(ref:figs5new-caption) **Meta-analysis of mental rotation performance, accounting for familiarity preferences.** Analysis and formatting are the same as in Figure 2, but with effect sizes that indicated a familiarity preference (i.e., longer looking times at the familiar stimulus as compared to the novel stimulus) being re-coded as providing positive evidence for (preliminary) mental rotation ability.
-
-```{r, meta_gender_pos}
+ggsave(here(figures_dir, "figs5_meta_pos.pdf"), width = 12, height = 14)
+```
+
+#### Re-fit meta-analysis of gender differences
+
+```{r}
 # Re-code familiarity preference to be treated the same as novelty preference
@@
 summary(res_gender_pos)
-
+```
+
+#### Summary of model paramters
+
+```{r}
 # Extract posterior draws for the meta-analytic effects
-spread_draws(res_gender_pos, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
+draws_gender_pos <- spread_draws(
+  res_gender_pos, `b_.*`, `sd_.*`,
+  regex = TRUE, ndraws = NULL
+) %>%
   # Compute variances and ICC from standard deviations
@@
     .keep = "unused"
-  ) -> draws_gender_pos
+  )
 
 # Summarize as means and 95% credible intervals
-(summ_gender_pos <- as.list(mean_qi(draws_gender_pos)))
-```
-
-```{r, figs6new, include=TRUE, fig.height=8, fig.width=12, fig.cap="(ref:figs6new-caption)"}
+(summ_gender_pos <- mean_qi(draws_gender_pos))
+```
+
+#### Forest plot (Supplementary Figure 6)
+
+```{r, fig.height=8, fig.width=12}
 # Get posterior draws for the effect *in each experiment*
@@
 # Save the plot
-ggsave(here(figures_dir, "figs6new_gender_pos.pdf"), width = 12, height = 8)
-```
-
-(ref:figs6new-caption) **Meta-analysis of gender differences, accounting for familiarity preferences.** Analysis and formatting are the same as in Supplementary Figure 4, but with one effect size [@moore2011] re-coded as a male advantage (rather than as a female advantage) in mental rotation performance.
-Male infants in this study showed a familiarity preference (i.e., longer looking times at the familiar stimulus as compared to the novel stimulus), which may be interpreted as preliminary mental rotation ability, while female infants showed no discrimination between stimuli.
+ggsave(here(figures_dir, "figs6_gender_pos.pdf"), width = 12, height = 8)
+```

### 2023-02-13 main.qmd
Create misc folder
Remove .Rprofile

@@
 # Load custom helper functions
-source(here("manuscript_files", "helper_functions.R"))
+source(here("misc", "helper_functions.R"))
 
@@
 # Options for MCMC sampling when fitting Bayesian multilevel models
+options(brms.backend = "cmdstanr") # Can choose "rstan" instead
+options(mc.cores = parallel::detectCores()) # Use all available cores
 n_iter <- 20000 # Posterior samples per chain, including `n_warmup`

### 2023-02-13 index.qmd
Update index and README

@@
 
-This webpage contains the code and results for the following paper:
+[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/SkeideLab/meta_rotation.git/HEAD?urlpath=rstudio)
+[![R version 4.1.2](https://img.shields.io/badge/R%20version-4.1.2-blue)](https://www.r-project.org)
+[![GitHub workflow](https://img.shields.io/github/actions/workflow/status/SkeideLab/meta_rotation/docker-publish.yml)](https://github.com/SkeideLab/meta_rotation/actions/workflows/docker-publish.yml)
+[![License](https://img.shields.io/github/license/SkeideLab/meta_rotation)](https://github.com/SkeideLab/meta_semantics/blob/main/LICENSE)
 
-> Enge, A., Kapoor, S., Kieslinger, A.-S., & Skeide, M. A. (*under review*). A meta-analysis of mental rotation in the first years of life
+This webpage contains the code, data, and results for the following paper:
 
-## Acknowledgments
+> Enge, A., Kapoor, S., Kieslinger, A.-S., & Skeide, M. A. (forthcoming). A meta-analysis of mental rotation in the first years of life. *Developmental Science*.
 
-M.A.S. was supported by the German Research Foundation (DFG Grants 433715509 and 433758790), the European Research Council (ERC Starting Grant 850752), and a Jacobs Foundation Research Scholarship.
-A.E. was supported by a PhD scholarship from the German Academic Scholarship Foundation (Studienstiftung des deutschen Volkes).
+BibTeX citation:
 
-The authors declare that they have no conflicts of interest to disclose.
+```bibtex
+@article{enge2023,
+  title = {A Meta-Analysis of Mental Rotation in the First Years of Life},
+  author = {Enge, Alexander and Kapoor, Shreya and Kieslinger, Anne-Sophie and Skeide, Michael A.},
+  year = {forthcoming},
+  journal = {Developmental Science}
+}
+```
+
+![SkeideLab at MPI CBS](https://i.imgur.com/iPjdsfc.png)

### 2023-02-24 main.qmd
Add mean age to Table 1 even when SD not available

@@
     Females = as.integer(round(female_percent * sample_size)),
-    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
+    `Age ($M$ ± $SD$)` = ifelse(
+      is.na(age_sd), paste(age_mean, "± n/a"), paste(age_mean, "±", age_sd)
+    ),
     Task = as.character(task),
